### 2021-09-08 code/INSEE_vaccination_COVID.Rmd
Add code
code for API extraction, data transformation and manhattan plot (animated or not)

---
title: "INSEE_vaccination_COVID"
author: "Emmanuel LECOEUR"
date: "07/09/2021"
output: html_document
---

```{r, echo=FALSE, message=FALSE, warning=F}
library(tidyverse)
library(desctable)
library(pander)
library(readxl)
library(inseeLocalData)
```

# Données de Vaccination

```{r, echo = F, message = F, warning = F}
week = 33

vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", week, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
  rename(codgeo = epci) %>%
  select(codgeo, taux_cumu_1_inj) %>%
  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
  plyr::rbind.fill(read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", week, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
  rename(codgeo = commune_residence) %>%
  select(codgeo, taux_cumu_1_inj) %>%
  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)))

vacc %>%
  desctable() %>%
  pander()
```

# Données de l'INSEE

```{r, echo = F, message = F, warning = F}
epci <- read_excel("data/Intercommunalite-Metropole_au_01-01-2021.xlsx",
                   range = "A6:D1260") %>%
  rename(codgeo = EPCI) %>%
  mutate(nivgeo = "EPCI")

doc_RP = read_excel("data/doc_RP.xlsx", sheet = "mesure_croisement") %>%
  filter(filtre_geo == "FHM" & GEO2021RP2018 == "x")

doc_FILOSOFI = read_excel("data/doc_FILOSOFI.xlsx", sheet = "mesure_croisement")

list_mesures = doc_FILOSOFI %>%
  select(mesure) %>%
  distinct()

doc_modalites = read_excel("data/doc_RP.xlsx", sheet = "var_modalite") %>%
  filter(variable %in% doc_RP$croisement) %>%
  arrange(variable)

# Donne toutes les extractions réalisées
modalites = doc_modalites %>%
  select(variable) %>%
  distinct() %>%
  # group_by(variable) %>%
  # summarise(chaine = paste(modalite, collapse = "+")) %>%
  # ungroup() %>%
  right_join(doc_RP %>%
               select(croisement) %>%
               distinct(),
             by = c("variable" = "croisement")) %>%
  group_by(variable) %>%
  mutate(nb_modalites = str_count(variable, "-")+1,
         chaine =paste0(rep("all", nb_modalites), collapse = ".")) %>%
  ungroup() %>%
  arrange(variable)

nb_croisements = dim(modalites)[1]
```

J'ai effectué toutes les extractions de FILOSOFI et de RP qui sont définies sur toutes la France et avec les données de 2018 et le découpage géographique de 2021. Cela représente 40 extractions (+ 2 concernant l'immigration). Toute la documentation concernant les extractions est présente dans le fichier de documentation.

```{r, eval = F, echo = F}
# changer no_crois de 1 à 35 et modifier les variables dans pivot wider à chaque fois

no_crois = 5

# croisement <- modalites$variable[no_crois]
croisement = "INATC-SEXE-AGE4_B-IRANR_4"
jeu_donnees <- "GEO2021RP2018"
# modalite <- modalites$chaine[no_crois]
modalite = "all.all.all.all"

sortie_test <- mapply(get_dataset,

                      # ce jeton est obsolète, il faut le changer sur le site de l'API
                      jeton = "76a9bb8d-a435-3de3-ae7f-1d42385e6e98",

                      jeu_donnees = jeu_donnees, 
                      croisement = croisement,
                      modalite = modalite,

                      # changer pour le type de territoire :
                      nivgeo = "COM",
                      # nivgeo = "EPCI",

                      # changer pour le type de territoire :
                      codgeo = postal_code$commune_residence,
                      # codgeo = epci$codgeo,

                      USE.NAMES = TRUE,
                      temporisation = 2) # pour éviter de faire trop de

donnees <- NULL

# Selon l'une ou l'autre extraction il faut utiliser l'un ou l'autre des codes suivants pour remettre un territoire par ligne et une variable insee par colonne. Si l'un ne fonctionne pas, il faut utiliser l'autre (Je ne comprends pas pourquoi).

for (i in 1:length(sortie_test)){
  if (i == 1){
    donnees <- plyr::rbind.fill(
      donnees,
      sortie_test[i]$`76a9bb8d-a435-3de3-ae7f-1d42385e6e98`$donnees %>%
        pivot_wider(id_cols = c(codgeo),
                    names_from = c(mesure, INATC, SEXE, AGE4_B, IRANR_4),
                    values_from = valeur)
    ) %>%
      distinct()
  } else {
    if (length(sortie_test[i]$`NA`) != 1){
      donnees <- plyr::rbind.fill(
        donnees,
        sortie_test[i]$`NA`$donnees %>%
          pivot_wider(id_cols = c(codgeo),
                      names_from = c(mesure, INATC, SEXE, AGE4_B, IRANR_4),
                      values_from = valeur)
      ) %>%
        distinct()
    }
  }
}

# for (i in 1:dim(sortie_test)[2]){
#   donnees <- plyr::rbind.fill(donnees,
#                               sortie_test[,i]$donnees %>%
#                                 pivot_wider(id_cols = c(codgeo),
#                                             names_from = c(mesure, INDICS_FILO_DISP_DET),
#                                             values_from = valeur))
# }
```

```{r, eval = F, echo = F}
# Les données sont stockées provisoirement par croisement et par type de territoire (commune ou EPCI)

write.csv2(donnees, file = "data/com_INATC-SEXE-AGE4_B-IRANR_4.csv")

# Une fois qu'on a extrait tout ce qu'on voulait, on peut passer à la suite.
```

```{r}
# Les extractions sont classées par thème : Logement, Emploi, Famille, Revenus, Activité, Formation, Population, Immigration, Géographie. Ces thèmes correspondent aux thèmes de l'INSEE.

STOCD <- read_delim("data/STOCD.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_STOCD.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `STOCD` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("STOCD_", .)) -> colnames(`STOCD`)

ANEMR2 <- read_delim("data/ANEMR2.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_ANEMR2.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `ANEMR2` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("ANEMR2_", .)) -> colnames(`ANEMR2`)

ANEMR3 <- read_delim("data/ANEMR3.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_ANEMR3.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `ANEMR3` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("ANEMR3_", .)) -> colnames(`ANEMR3`)

GARL <- read_delim("data/GARL.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_GARL.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `GARL` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("GARL_", .)) -> colnames(`GARL`)

NBPIR5P <- read_delim("data/NBPIR5P.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_NBPIR5P.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `NBPIR5P` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("NBPIR5P_", .)) -> colnames(`NBPIR5P`)

SUROCCHS1P <- read_delim("data/SUROCCHS1P.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_SUROCCHS1P.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `SUROCCHS1P` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("SUROCCHS1P_", .)) -> colnames(`SUROCCHS1P`)

`TYPLR-ACHL20` <- read_delim("data/TYPLR-ACHL20.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_TYPLR-ACHL20.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `TYPLR-ACHL20` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("TYPLR-ACHL20_", .)) -> colnames(`TYPLR-ACHL20`)

`TYPLR-CATL` <- read_delim("data/TYPLR-CATL.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_TYPLR-CATL.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `TYPLR-CATL` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("TYPLR-CATL_", .)) -> colnames(`TYPLR-CATL`)

`VOIT` <- read_delim("data/VOIT.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_VOIT.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `VOIT` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("VOIT_", .)) -> colnames(`VOIT`)

LOG = STOCD %>% select(-X1) %>%
  full_join(ANEMR2 %>% select(-X1)) %>%
  full_join(ANEMR3 %>% select(-X1)) %>%
  full_join(GARL %>% select(-X1)) %>%
  full_join(NBPIR5P %>% select(-X1)) %>%
  full_join(SUROCCHS1P %>% select(-X1)) %>%
  full_join(`TYPLR-ACHL20` %>% select(-X1)) %>%
  full_join(`TYPLR-CATL` %>% select(-X1)) %>%
  full_join(`VOIT` %>% select(-X1))
```

```{r}
CS1_6 <- read_delim("data/CS1_6.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_CS1_6.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `CS1_6` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("CS1_6_", .)) -> colnames(`CS1_6`)

`STATR-SEXE` <- read_delim("data/STATR-SEXE.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_STATR-SEXE.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `STATR-SEXE` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("STATR-SEXE_", .)) -> colnames(`STATR-SEXE`)

`STATR-TP` <- read_delim("data/STATR-TP.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_STATR-TP.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `STATR-TP` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("STATR-TP_", .)) -> colnames(`STATR-TP`)

`CS1_6-TACTR_2` <- read_delim("data/CS1_6-TACTR_2.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_CS1_6-TACTR_2.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `CS1_6-TACTR_2` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("CS1_6-TACTR_2_", .)) -> colnames(`CS1_6-TACTR_2`)

`SEXE-AGE3` <- read_delim("data/SEXE-AGE3.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_SEXE-AGE3.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `SEXE-AGE3` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("SEXE-AGE3_", .)) -> colnames(`SEXE-AGE3`)

TACTR <- read_delim("data/TACTR.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_TACTR.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `TACTR` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("TACTR_", .)) -> colnames(`TACTR`)

`TACTR_2-AGE4` <- read_delim("data/com_TACTR_2-AGE4.csv", ";", escape_double = FALSE, trim_ws = TRUE)

c("X1", "codgeo", `TACTR_2-AGE4` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("TACTR_2-AGE4_", .)) -> colnames(`TACTR_2-AGE4`)

`TACTR_2-SEXE-AGE3` <- read_delim("data/TACTR_2-SEXE-AGE3.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_TACTR_2-SEXE-AGE3.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `TACTR_2-SEXE-AGE3` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("TACTR_2-SEXE-AGE3_", .)) -> colnames(`TACTR_2-SEXE-AGE3`)

EMP = CS1_6 %>% select(-X1) %>%
  full_join(`STATR-SEXE` %>% select(-X1)) %>%
  full_join(`STATR-TP` %>% select(-X1)) %>%
  full_join(`CS1_6-TACTR_2` %>% select(-X1)) %>%
  full_join(`SEXE-AGE3` %>% select(-X1)) %>%
  full_join(TACTR %>% select(-X1)) %>%
  full_join(`TACTR_2-AGE4` %>% select(-X1)) %>%
  full_join(`TACTR_2-SEXE-AGE3` %>% select(-X1))
```

```{r}
`TP-SEXE-AGE3P` <- read_delim("data/TP-SEXE-AGE3P.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_TP-SEXE-AGE3P.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `TP-SEXE-AGE3P` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("TP-SEXE-AGE3P_", .)) -> colnames(`TP-SEXE-AGE3P`)

`EMPL-SEXE` <- read_delim("data/EMPL-SEXE.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_EMPL-SEXE.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `EMPL-SEXE` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("EMPL-SEXE_", .)) -> colnames(`EMPL-SEXE`)

`ILTR` <- read_delim("data/ILTR.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_ILTR.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `ILTR` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("ILTR_", .)) -> colnames(`ILTR`)

`TRANS_19` <- read_delim("data/TRANS_19.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_TRANS_19.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `TRANS_19` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("TRANS_19_", .)) -> colnames(`TRANS_19`)

ACT = `TP-SEXE-AGE3P` %>% select(-X1) %>%
  full_join(`EMPL-SEXE` %>% select(-X1)) %>%
  full_join(`ILTR` %>% select(-X1)) %>%
  full_join(`TRANS_19` %>% select(-X1))
```

```{r}
`CS1_8` <- read_delim("data/CS1_8.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_CS1_8.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `CS1_8` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("CS1_8_", .)) -> colnames(`CS1_8`)

`TF4` <- read_delim("data/TF4.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_TF4.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `TF4` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("TF4_", .)) -> colnames(`TF4`)

`TYPMR` <- read_delim("data/TYPMR.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_TYPMR.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `TYPMR` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("TYPMR_", .)) -> colnames(`TYPMR`)

`AGEMEN8_A` <- read_delim("data/AGEMEN8_A.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_AGEMEN8_A.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `AGEMEN8_A` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("AGEMEN8_A_", .)) -> colnames(`AGEMEN8_A`)

`AGEMEN8_A-COUPLE` <- read_delim("data/AGEMEN8_A-COUPLE.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_AGEMEN8_A-COUPLE.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `AGEMEN8_A-COUPLE` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("AGEMEN8_A-COUPLE_", .)) -> colnames(`AGEMEN8_A-COUPLE`)

`STAT_CONJ_19` <- read_delim("data/STAT_CONJ_19.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_STAT_CONJ_19.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `STAT_CONJ_19` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("STAT_CONJ_19_", .)) -> colnames(`STAT_CONJ_19`)

FAM = `CS1_8` %>% select(-X1) %>%
  full_join(`TF4` %>% select(-X1)) %>%
  full_join(`TYPMR` %>% select(-X1)) %>%
  full_join(`AGEMEN8_A` %>% select(-X1)) %>%
  full_join(`AGEMEN8_A-COUPLE` %>% select(-X1)) %>%
  full_join(`STAT_CONJ_19` %>% select(-X1))
```

```{r}
`AGESCOL-SEXE-ETUD` <- read_delim("data/AGESCOL-SEXE-ETUD.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_AGESCOL-SEXE-ETUD.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `AGESCOL-SEXE-ETUD` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("AGESCOL-SEXE-ETUD_", .)) -> colnames(`AGESCOL-SEXE-ETUD`)

`SEXE-DIPL_19` <- read_delim("data/SEXE-DIPL_19.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_SEXE-DIPL_19.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `SEXE-DIPL_19` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("SEXE-DIPL_19_", .)) -> colnames(`SEXE-DIPL_19`)

FOR = `AGESCOL-SEXE-ETUD` %>% select(-X1) %>%
  full_join(`SEXE-DIPL_19` %>% select(-X1))
```

```{r}
`CS1_8-AGEREMPLOI` <- read_delim("data/CS1_8-AGEREMPLOI.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_CS1_8-AGEREMPLOI.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `CS1_8-AGEREMPLOI` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("CS1_8-AGEREMPLOI_", .)) -> colnames(`CS1_8-AGEREMPLOI`)

`CS1_8-SEXE` <- read_delim("data/CS1_8-SEXE.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_CS1_8-SEXE.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `CS1_8-SEXE` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("CS1_8-SEXE_", .)) -> colnames(`CS1_8-SEXE`)

`IRANC-AGE5_55` <- read_delim("data/IRANC-AGE5_55.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_IRANC-AGE5_55.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `IRANC-AGE5_55` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("IRANC-AGE5_55_", .)) -> colnames(`IRANC-AGE5_55`)

`IRANR_2` <- read_delim("data/IRANR_2.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_IRANR_2.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `IRANR_2` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("IRANR_2_", .)) -> colnames(`IRANR_2`)

`SEXE-AGE15_15_90` <- read_delim("data/SEXE-AGE15_15_90.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_SEXE-AGE15_15_90.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `SEXE-AGE15_15_90` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("SEXE-AGE15_15_90_", .)) -> colnames(`SEXE-AGE15_15_90`)

`SEXE-AGE3_B` <- read_delim("data/SEXE-AGE3_B.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_SEXE-AGE3_B.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `SEXE-AGE3_B` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("SEXE-AGE3_B_", .)) -> colnames(`SEXE-AGE3_B`)

POP = `CS1_8-AGEREMPLOI` %>% select(-X1) %>%
  full_join(`CS1_8-SEXE` %>% select(-X1)) %>%
  full_join(`IRANC-AGE5_55` %>% select(-X1)) %>%
  full_join(`IRANR_2` %>% select(-X1)) %>%
  full_join(`SEXE-AGE15_15_90` %>% select(-X1)) %>%
  full_join(`SEXE-AGE3_B` %>% select(-X1))
```

```{r}
`INDICS_FILO_DEC_DET` <- read_delim("data/INDICS_FILO_DEC_DET.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_INDICS_FILO_DEC_DET.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `INDICS_FILO_DEC_DET` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("INDICS_FILO_DEC_DET_", .)) -> colnames(`INDICS_FILO_DEC_DET`)

`INDICS_FILO_DISP_DET-OCCTYPR` <- read_delim("data/INDICS_FILO_DISP_DET-OCCTYPR.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_INDICS_FILO_DISP_DET-OCCTYPR.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `INDICS_FILO_DISP_DET-OCCTYPR` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("INDICS_FILO_DISP_DET-OCCTYPR_", .)) -> colnames(`INDICS_FILO_DISP_DET-OCCTYPR`)

`INDICS_FILO_DISP_DET-TRAGERF` <- read_delim("data/INDICS_FILO_DISP_DET-TRAGERF.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_INDICS_FILO_DISP_DET-TRAGERF.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `INDICS_FILO_DISP_DET-TRAGERF` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("INDICS_FILO_DISP_DET-TRAGERF_", .)) -> colnames(`INDICS_FILO_DISP_DET-TRAGERF`)

`INDICS_FILO_DISP_DET` <- read_delim("data/INDICS_FILO_DISP_DET.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_INDICS_FILO_DISP_DET.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `INDICS_FILO_DISP_DET` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("INDICS_FILO_DISP_DET_", .)) -> colnames(`INDICS_FILO_DISP_DET`)

`INDICS_FILO_DISP` <- read_delim("data/INDICS_FILO_DISP.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_INDICS_FILO_DISP.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `INDICS_FILO_DISP` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("INDICS_FILO_DISP_", .)) -> colnames(`INDICS_FILO_DISP`)

REV = `INDICS_FILO_DEC_DET` %>% select(-X1) %>%
  full_join(`INDICS_FILO_DISP_DET-OCCTYPR` %>% select(-X1)) %>%
  full_join(`INDICS_FILO_DISP_DET-TRAGERF` %>% select(-X1)) %>%
  full_join(`INDICS_FILO_DISP_DET` %>% select(-X1)) %>%
  full_join(`INDICS_FILO_DISP` %>% select(-X1))
```

```{r}
`IMMI-CS1_8-SEXE` <- read_delim("data/IMMI-CS1_8-SEXE.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_IMMI-CS1_8-SEXE.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `IMMI-CS1_8-SEXE` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("IMMI-CS1_8-SEXE_", .)) -> colnames(`IMMI-CS1_8-SEXE`)

`INATC-SEXE-AGE4_B-IRANR_4` <- read_delim("data/INATC-SEXE-AGE4_B-IRANR_4.csv", ";", escape_double = FALSE, trim_ws = TRUE) %>%
  plyr::rbind.fill(
    read_delim("data/com_INATC-SEXE-AGE4_B-IRANR_4.csv", ";", escape_double = FALSE, trim_ws = TRUE)
  )

c("X1", "codgeo", `INATC-SEXE-AGE4_B-IRANR_4` %>%
    select(-c(X1, codgeo)) %>%
    colnames() %>%
    paste0("INATC-SEXE-AGE4_B-IRANR_4_", .)) -> colnames(`INATC-SEXE-AGE4_B-IRANR_4`)

IMM = `IMMI-CS1_8-SEXE` %>% select(-X1) %>%
  full_join(`INATC-SEXE-AGE4_B-IRANR_4` %>% select(-X1))
```

# Calcul des variables

```{r}
binarisation = function(liste, q = 0.5){
  mediane = quantile(liste, q, na.rm = T)[[1]]
  return(as.factor(simplify2array(lapply(liste-mediane,
                                         function(x){if_else(x < 0, 0, 1)}))))
}
```

## LOG

```{r}
LOG_brut = LOG %>%
  mutate(`1ry_res` = 100* `TYPLR-CATL_NBLOG_ENS_1` / `TYPLR-CATL_NBLOG_ENS_ENS`,
         `2ry_res` = 100* (`TYPLR-CATL_NBLOG_ENS_2` + `TYPLR-CATL_NBLOG_ENS_3`) / `TYPLR-CATL_NBLOG_ENS_ENS`,
         `Vacant_Home` = 100* `TYPLR-CATL_NBLOG_ENS_4` / `TYPLR-CATL_NBLOG_ENS_ENS`,
         `Houses` = 100* `TYPLR-CATL_NBLOG_1_ENS` / `TYPLR-CATL_NBLOG_ENS_ENS`,
         `Flats` = 100* `TYPLR-CATL_NBLOG_2_ENS` / `TYPLR-CATL_NBLOG_ENS_ENS`,
         `Nb_Rooms_1ry_res` = `TYPLR-CATL_NBPIECES_ENS_1` / `TYPLR-CATL_NBLOG_ENS_1`,
         `House_1ry_res` = 100* `TYPLR-CATL_NBLOG_1_1` / `TYPLR-CATL_NBLOG_ENS_1`,
         `Flat_1ry_res` = 100* `TYPLR-CATL_NBLOG_2_1` / `TYPLR-CATL_NBLOG_ENS_1`,
         `1ry_res_bf_1919` = 100* `TYPLR-ACHL20_NBLOG_ENS_A11` / `TYPLR-ACHL20_NBLOG_ENS_ENS`,
         `1ry_res_19-45` = 100* `TYPLR-ACHL20_NBLOG_ENS_A12` / `TYPLR-ACHL20_NBLOG_ENS_ENS`,
         `1ry_res_46-70` = 100* `TYPLR-ACHL20_NBLOG_ENS_B11` / `TYPLR-ACHL20_NBLOG_ENS_ENS`,
         `1ry_res_71-90` = 100* `TYPLR-ACHL20_NBLOG_ENS_B12` / `TYPLR-ACHL20_NBLOG_ENS_ENS`,
         `1ry_res_91-05` = 100* `TYPLR-ACHL20_NBLOG_ENS_C100` / `TYPLR-ACHL20_NBLOG_ENS_ENS`,
         `1ry_res_06-15` = 100* `TYPLR-ACHL20_NBLOG_ENS_C106P` / `TYPLR-ACHL20_NBLOG_ENS_ENS`,
         `HH_Moving_Time_lt2y` = 100* `ANEMR2_NBLOG_0` / `ANEMR2_NBLOG_ENS`,
         `HH_Moving_Time_2to4y` = 100* `ANEMR2_NBLOG_1` / `ANEMR2_NBLOG_ENS`,
         `HH_Moving_Time_5to9y` = 100* `ANEMR2_NBLOG_2` / `ANEMR2_NBLOG_ENS`,
         `HH_Moving_Time_10to19y` = 100* `ANEMR2_NBLOG_3` / `ANEMR2_NBLOG_ENS`,
         `HH_Moving_Time_20to29y` = 100* `ANEMR2_NBLOG_4` / `ANEMR2_NBLOG_ENS`,
         `HH_Moving_Time_gt30y` = 100* `ANEMR2_NBLOG_5` / `ANEMR2_NBLOG_ENS`,
         `1ry_res_Owner` = 100* `STOCD_NBLOG_10` / `STOCD_NBLOG_ENS`,
         `1ry_res_Tenant` = 100* `STOCD_NBLOG_21` / `STOCD_NBLOG_ENS`,
         `1ry_res_Social` = 100* `STOCD_NBLOG_22` / `STOCD_NBLOG_ENS`,
         `1ry_res_FreeAcc` = 100* `STOCD_NBLOG_23` / `STOCD_NBLOG_ENS`,
         `1ry_res_Carpark` = 100* `GARL_NBLOG_1` / `GARL_NBLOG_ENS`,
         `1ry_res_0car` = 100* `VOIT_NBLOG_0` / `VOIT_NBLOG_ENS`,
         `1ry_res_1car` = 100* `VOIT_NBLOG_1` / `VOIT_NBLOG_ENS`,
         `1ry_res_2car` = 100* `VOIT_NBLOG_2` / `VOIT_NBLOG_ENS`,
         `1ry_res_3+car` = 100* `VOIT_NBLOG_3` / `VOIT_NBLOG_ENS`,
         `Pop_per_1ry_res` = `STOCD_POP_ENS` / `STOCD_NBLOG_ENS`,
         `1ry_res_gt0car` = 100* (`VOIT_NBLOG_1` + `VOIT_NBLOG_2` + `VOIT_NBLOG_3`) / `VOIT_NBLOG_ENS`,
         `Pop_per_1ry_res_Owner` = `STOCD_POP_10` / `STOCD_NBLOG_10`,
         `Pop_per_1ry_res_Tenant` = `STOCD_POP_21` / `STOCD_NBLOG_21`,
         `Pop_per_1ry_res_Social` = `STOCD_POP_22` / `STOCD_NBLOG_22`,
         `Pop_per_1ry_res_FreeAcc` = `STOCD_POP_23` / `STOCD_NBLOG_23`,
         `1ry_res_Occupancy` = `STOCD_DUREE_ENS` /8765.82,
         `Owners_Occupancy` = `STOCD_DUREE_10` /8765.82,
         `Tenant_Occupancy` = `STOCD_DUREE_21` /8765.82,
         `Social_Occupancy` = `STOCD_DUREE_22` /8765.82,
         `FreeAcc_Occupancy` = `STOCD_DUREE_23` /8765.82,
         `Overcrowding_rate` = 100* `SUROCCHS1P_NBLOG_1` / `SUROCCHS1P_NBLOG_ENS`) %>%
  select(-colnames(LOG)[2:126]) %>%
  inner_join(vacc)
LOG_fact = LOG_brut %>%
  mutate(across(-c(codgeo, taux_cumu_1_inj), binarisation)) %>%
  mutate(taux_cumu_1_inj = binarisation(taux_cumu_1_inj, 0.25),
         taux_cumu_1_inj = as.factor(if_else(taux_cumu_1_inj == 1, 0, 1)))
```

## EMP

```{r}
EMP_brut = EMP %>%
  mutate(`1564_Workforce_rate` = 100* `TACTR_2-SEXE-AGE3_POP_ENS_ENS_ENS` / `SEXE-AGE3_POP_ENS_ENS`,
         `1524_Workforce_rate` = 100* `TACTR_2-SEXE-AGE3_POP_ENS_ENS_15` / `SEXE-AGE3_POP_ENS_15`,
         `2554_Workforce_rate` = 100* `TACTR_2-SEXE-AGE3_POP_ENS_ENS_25` / `SEXE-AGE3_POP_ENS_25`,
         `5564_Workforce_rate` = 100* `TACTR_2-SEXE-AGE3_POP_ENS_ENS_55` / `SEXE-AGE3_POP_ENS_55`,
         `1564_men_Workforce_rate` = 100* `TACTR_2-SEXE-AGE3_POP_ENS_1_ENS` / `SEXE-AGE3_POP_1_ENS`,
         `1524_men_Workforce_rate` = 100* `TACTR_2-SEXE-AGE3_POP_ENS_1_15` / `SEXE-AGE3_POP_1_15`,
         `2554_men_Workforce_rate` = 100* `TACTR_2-SEXE-AGE3_POP_ENS_1_25` / `SEXE-AGE3_POP_1_25`,
         `5564_men_Workforce_rate` = 100* `TACTR_2-SEXE-AGE3_POP_ENS_1_55` / `SEXE-AGE3_POP_1_55`,
         `1564_women_Workforce_rate` = 100* `TACTR_2-SEXE-AGE3_POP_ENS_2_ENS` / `SEXE-AGE3_POP_2_ENS`,
         `1524_women_Workforce_rate` = 100* `TACTR_2-SEXE-AGE3_POP_ENS_2_15` / `SEXE-AGE3_POP_2_15`,
         `2554_women_Workforce_rate` = 100* `TACTR_2-SEXE-AGE3_POP_ENS_2_25` / `SEXE-AGE3_POP_2_25`,
         `5564_women_Workforce_rate` = 100* `TACTR_2-SEXE-AGE3_POP_ENS_2_55` / `SEXE-AGE3_POP_2_55`,
         `1564_Employed_rate_amg_WF` = 100* `TACTR_2-SEXE-AGE3_POP_11_ENS_ENS` / `TACTR_2-SEXE-AGE3_POP_ENS_ENS_ENS`,
         `1524_Employed_rate_amg_WF` = 100* `TACTR_2-SEXE-AGE3_POP_11_ENS_15` / `TACTR_2-SEXE-AGE3_POP_ENS_ENS_15`,
         `2554_Employed_rate_amg_WF` = 100* `TACTR_2-SEXE-AGE3_POP_11_ENS_25` / `TACTR_2-SEXE-AGE3_POP_ENS_ENS_25`,
         `5564_Employed_rate_amg_WF` = 100* `TACTR_2-SEXE-AGE3_POP_11_ENS_55` / `TACTR_2-SEXE-AGE3_POP_ENS_ENS_55`,
         `1564_men_Employed_rate_amg_WF` = 100* `TACTR_2-SEXE-AGE3_POP_11_1_ENS` / `TACTR_2-SEXE-AGE3_POP_ENS_1_ENS`,
         `1524_men_Employed_rate_amg_WF` = 100* `TACTR_2-SEXE-AGE3_POP_11_1_15` / `TACTR_2-SEXE-AGE3_POP_ENS_1_15`,
         `2554_men_Employed_rate_amg_WF` = 100* `TACTR_2-SEXE-AGE3_POP_11_1_25` / `TACTR_2-SEXE-AGE3_POP_ENS_1_25`,
         `5564_men_Employed_rate_amg_WF` = 100* `TACTR_2-SEXE-AGE3_POP_11_1_55` / `TACTR_2-SEXE-AGE3_POP_ENS_1_55`,
         `1564_women_Employed_rate_amg_WF` = 100* `TACTR_2-SEXE-AGE3_POP_11_2_ENS` / `TACTR_2-SEXE-AGE3_POP_ENS_2_ENS`,
         `1524_women_Employed_rate_amg_WF` = 100* `TACTR_2-SEXE-AGE3_POP_11_2_15` / `TACTR_2-SEXE-AGE3_POP_ENS_2_15`,
         `2554_women_Employed_rate_amg_WF` = 100* `TACTR_2-SEXE-AGE3_POP_11_2_25` / `TACTR_2-SEXE-AGE3_POP_ENS_2_25`,
         `5564_women_Employed_rate_amg_WF` = 100* `TACTR_2-SEXE-AGE3_POP_11_2_55` / `TACTR_2-SEXE-AGE3_POP_ENS_2_55`,
         `1564_Unemployed_rate_amg_WF` = 100* `TACTR_2-SEXE-AGE3_POP_12_ENS_ENS` / `TACTR_2-SEXE-AGE3_POP_ENS_ENS_ENS`,
         `1524_Unemployed_rate_amg_WF` = 100* `TACTR_2-SEXE-AGE3_POP_12_ENS_15` / `TACTR_2-SEXE-AGE3_POP_ENS_ENS_15`,
         `2554_Unemployed_rate_amg_WF` = 100* `TACTR_2-SEXE-AGE3_POP_12_ENS_25` / `TACTR_2-SEXE-AGE3_POP_ENS_ENS_25`,
         `5564_Unemployed_rate_amg_WF` = 100* `TACTR_2-SEXE-AGE3_POP_12_ENS_55` / `TACTR_2-SEXE-AGE3_POP_ENS_ENS_55`,
         `1564_NonWorking_amg_WF` = 100* `TACTR_POP_12` / `TACTR_POP_ENS`,
         `1564_Student_amg_WF` = 100* `TACTR_POP_22` / `TACTR_POP_ENS`,
         `1564_Retired_amg_WF` = 100* `TACTR_POP_21` / `TACTR_POP_ENS`,
         `1564_OtherInactive_amg_WF` = 100* `TACTR_POP_26` / `TACTR_POP_ENS`,
         `1564_men_Unemplyed_amg_WF` = 100* `STATR-SEXE_POP_2_1` / `STATR-SEXE_POP_ENS_1`,
         `1564_women_Unemplyed_amg_WF` = 100* `STATR-SEXE_POP_2_2` / `STATR-SEXE_POP_ENS_2`,
         `1564_Student_amg_NW` = 100* `TACTR_POP_22` / (`TACTR_POP_ENS` - `TACTR_POP_11`),
         `1564_Retired_amg_NW` = 100* `TACTR_POP_21` / (`TACTR_POP_ENS` - `TACTR_POP_11`),
         `1564_OtherInactive_amg_NW` = 100* `TACTR_POP_26` / (`TACTR_POP_ENS` - `TACTR_POP_11`),
         `1564_NonWorking_amg_POP` = 100* (`TACTR_POP_ENS` - `TACTR_POP_11`) / `TACTR_POP_ENS`,
         `1564_Farmers_amg_WF` = 100* `CS1_6_NBEMP_1` / `CS1_6_NBEMP_ENS`,
         `1564_CraftsBusinessShopkeepers_amg_WF` = 100* `CS1_6_NBEMP_2` / `CS1_6_NBEMP_ENS`,
         `1564_HihgQualWorkers_amg_WF` = 100* `CS1_6_NBEMP_3` / `CS1_6_NBEMP_ENS`,
         `1564_IntermediateProf_amg_WF` = 100* `CS1_6_NBEMP_4` / `CS1_6_NBEMP_ENS`,
         `1564_BlueCollar_amg_WF` = 100* `CS1_6_NBEMP_6` / `CS1_6_NBEMP_ENS`,
         `1564_WhiteCollar_amg_WF` = 100* `CS1_6_NBEMP_5` / `CS1_6_NBEMP_ENS`,
         `1564_Farmers_amg_EmpWF` = 100* `CS1_6-TACTR_2_POP_1_ENS` / `CS1_6-TACTR_2_POP_ENS_ENS`,
         `1564_CraftsBusinessShopkeepers_amg_EmpWF` = 100* `CS1_6-TACTR_2_POP_2_ENS` / `CS1_6-TACTR_2_POP_ENS_ENS`,
         `1564_HihgQualWorkers_amg_EmpWF` = 100* `CS1_6-TACTR_2_POP_3_ENS` / `CS1_6-TACTR_2_POP_ENS_ENS`,
         `1564_IntermediateProf_amg_EmpWF` = 100* `CS1_6-TACTR_2_POP_4_ENS` / `CS1_6-TACTR_2_POP_ENS_ENS`,
         `1564_BlueCollar_amg_EmpWF` = 100* `CS1_6-TACTR_2_POP_6_ENS` / `CS1_6-TACTR_2_POP_ENS_ENS`,
         `1564_WhiteCollar_amg_EmpWF` = 100* `CS1_6-TACTR_2_POP_5_ENS` / `CS1_6-TACTR_2_POP_ENS_ENS`,
         `15+_men_amg_empWF` = 100* `SEXE-AGE3_POP_1_ENS` / `SEXE-AGE3_POP_ENS_ENS`,
         `15+_women_amg_empWF` = 100* `SEXE-AGE3_POP_2_ENS` / `SEXE-AGE3_POP_ENS_ENS`,
         `15+_Salaried_amg_empWF` = 100* `STATR-SEXE_POP_1_ENS` / `STATR-SEXE_POP_ENS_ENS`,
         `15+_NonSalaried_amg_empWF` = 100* `STATR-SEXE_POP_2_ENS` / `STATR-SEXE_POP_ENS_ENS`,
         `15+_FullTime_amg_empWF` = 100* `STATR-TP_POP_ENS_1` / `STATR-TP_POP_ENS_ENS`,
         `15+_men_amg_salWF` = 100* `STATR-SEXE_POP_1_1` / `STATR-SEXE_POP_1_ENS`,
         `15+_women_amg_salWF` = 100* `STATR-SEXE_POP_1_2` / `STATR-SEXE_POP_1_ENS`,
         `15+_men_amg_nonsalWF` = 100* `STATR-SEXE_POP_2_1` / `STATR-SEXE_POP_2_ENS`,
         `15+_women_amg_nonsalWF` = 100* `STATR-SEXE_POP_2_2` / `STATR-SEXE_POP_2_ENS`,
         `15+_men_amg_FullTimeWF` = 100* `STATR-TP_POP_1_1` / `STATR-TP_POP_ENS_1`,
         `15+_women_amg_FullTimeWF` = 100* `STATR-TP_POP_2_1` / `STATR-TP_POP_ENS_1`,
         `15+_FullTime_amg_salWF` = 100* `STATR-TP_POP_1_1` / `STATR-TP_POP_1_ENS`) %>%
  select(-colnames(EMP)[2:135]) %>%
  inner_join(vacc)
EMP_fact = EMP_brut %>%
  mutate(across(-c(codgeo, taux_cumu_1_inj), binarisation)) %>%
  mutate(taux_cumu_1_inj = binarisation(taux_cumu_1_inj, 0.25),
         taux_cumu_1_inj = as.factor(if_else(taux_cumu_1_inj == 1, 0, 1)))
```

## FAM

```{r}
FAM_brut = FAM %>%
  mutate(`SinglePerson_HH` = 100* (`TYPMR_NBLOG_11` + `TYPMR_NBLOG_12`) / `TYPMR_NBLOG_ENS`,
         `SingleMan_HH` = 100* `TYPMR_NBLOG_11` / `TYPMR_NBLOG_ENS`,
         `SingleWoman_HH` = 100* `TYPMR_NBLOG_12` / `TYPMR_NBLOG_ENS`,
         `OtherNoFamily_HH` = 100* `TYPMR_NBLOG_20` / `TYPMR_NBLOG_ENS`,
         `Family_HH` = 100* (`TYPMR_NBLOG_ENS` - `TYPMR_NBLOG_11` - `TYPMR_NBLOG_12` - `TYPMR_NBLOG_20`) / `TYPMR_NBLOG_ENS`,
         `NoChildFamily_HH` = 100* `TF4_NBLOG_1` / `TF4_NBLOG_ENS`,
         `ChildFamily_HH` = 100* `TF4_NBLOG_2` / `TF4_NBLOG_ENS`,
         `SingleParent_HH` = 100* (`TF4_NBLOG_3` + `TF4_NBLOG_4`) / `TF4_NBLOG_ENS`,
         `Farmer_HH` = 100* `CS1_8_NBLOG_1` / `CS1_8_NBLOG_ENS`,
         `CraftsBusinessShopkeepers_HH` = 100* `CS1_8_NBLOG_2` / `CS1_8_NBLOG_ENS`,
         `HighQualidied_HH` = 100* `CS1_8_NBLOG_3` / `CS1_8_NBLOG_ENS`,
         `Intermediate_HH` = 100* `CS1_8_NBLOG_4` / `CS1_8_NBLOG_ENS`,
         `BlueCollar_HH` = 100* `CS1_8_NBLOG_6` / `CS1_8_NBLOG_ENS`,
         `WhiteCollar_HH` = 100* `CS1_8_NBLOG_5` / `CS1_8_NBLOG_ENS`,
         `Retired_HH` = 100* `CS1_8_NBLOG_7` / `CS1_8_NBLOG_ENS`,
         `Other_HH` = 100* `CS1_8_NBLOG_8` / `CS1_8_NBLOG_ENS`,
         `15+_SinglePerson_HH` = 100* `AGEMEN8_A-COUPLE_POP_ENS_2` / `AGEMEN8_A-COUPLE_POP_ENS_ENS`,
         `Pop_SingleMan_HH` = 100* `TYPMR_POP_11` / `TYPMR_POP_ENS`,
         `Pop_SingleWoman_HH` = 100* `TYPMR_POP_12` / `TYPMR_POP_ENS`,
         `Pop_OtherNoFamily_HH` = 100* `TYPMR_POP_20` / `TYPMR_POP_ENS`,
         `Pop_Family_HH` = 100* (`TYPMR_POP_ENS` - `TYPMR_POP_11` - `TYPMR_POP_12` - `TYPMR_POP_20`) / `TYPMR_POP_ENS`,
         `Pop_NoChildFamily_HH` = 100* `TF4_POP_1` / `TF4_POP_ENS`,
         `Pop_ChildFamily_HH` = 100* `TF4_POP_2` / `TF4_POP_ENS`,
         `Pop_SingleParent_HH` = 100* (`TF4_POP_3` + `TF4_POP_4`) / `TF4_POP_ENS`,
         `Pop_Farmer_HH` = 100* `CS1_8_POP_1` / `CS1_8_POP_ENS`,
         `Pop_CraftsBusinessShopkeepers_HH` = 100* `CS1_8_POP_2` / `CS1_8_POP_ENS`,
         `Pop_HighQualidied_HH` = 100* `CS1_8_POP_3` / `CS1_8_POP_ENS`,
         `Pop_Intermediate_HH` = 100* `CS1_8_POP_4` / `CS1_8_POP_ENS`,
         `Pop_BlueCollar_HH` = 100* `CS1_8_POP_6` / `CS1_8_POP_ENS`,
         `Pop_WhiteCollar_HH` = 100* `CS1_8_POP_5` / `CS1_8_POP_ENS`,
         `Pop_Retired_HH` = 100* `CS1_8_POP_7` / `CS1_8_POP_ENS`,
         `Pop_Other_HH` = 100* `CS1_8_POP_8` / `CS1_8_POP_ENS`,
         `1524_amg_15+POP` = 100* (`AGEMEN8_A-COUPLE_POP_15_ENS` + `AGEMEN8_A-COUPLE_POP_20_ENS`) / `AGEMEN8_A-COUPLE_POP_ENS_ENS`,
         `2554_amg_15+POP` = 100* (`AGEMEN8_A-COUPLE_POP_25_ENS` + `AGEMEN8_A-COUPLE_POP_40_ENS`) / `AGEMEN8_A-COUPLE_POP_ENS_ENS`,
         `5579_amg_15+POP` = 100* (`AGEMEN8_A-COUPLE_POP_55_ENS` + `AGEMEN8_A-COUPLE_POP_65_ENS`) / `AGEMEN8_A-COUPLE_POP_ENS_ENS`,
         `80+_amg_15+POP` = 100* `AGEMEN8_A-COUPLE_POP_80_ENS` / `AGEMEN8_A-COUPLE_POP_ENS_ENS`,
         `15+_Single_amg_POP` = 100* `STAT_CONJ_19_POP_6` / `STAT_CONJ_19_POP_ENS`,
         `15+_Married_amg_POP` = 100* `STAT_CONJ_19_POP_1` / `STAT_CONJ_19_POP_ENS`,
         `15+_nonMarried_amg_POP` = 100* (`STAT_CONJ_19_POP_ENS` - `STAT_CONJ_19_POP_1`) / `STAT_CONJ_19_POP_ENS`,
         `1524_amg_HH` = 100* (`AGEMEN8_A_POPMEN_15` + `AGEMEN8_A_POPMEN_20`) / `AGEMEN8_A_POPMEN_ENS`,
         `2554_amg_HH` = 100* (`AGEMEN8_A_POPMEN_25` + `AGEMEN8_A_POPMEN_40`) / `AGEMEN8_A_POPMEN_ENS`,
         `5579_amg_HH` = 100* (`AGEMEN8_A_POPMEN_55` + `AGEMEN8_A_POPMEN_65`) / `AGEMEN8_A_POPMEN_ENS`,
         `80+_amg_HH` = 100* `AGEMEN8_A_POPMEN_80` / `AGEMEN8_A_POPMEN_ENS`,
         `1524_amg_Single` = 100* (`AGEMEN8_A_NPERSEULES_15` + `AGEMEN8_A_NPERSEULES_20`) / `AGEMEN8_A_NPERSEULES_ENS`,
         `2554_amg_Single` = 100* (`AGEMEN8_A_NPERSEULES_25` + `AGEMEN8_A_NPERSEULES_40`) / `AGEMEN8_A_NPERSEULES_ENS`,
         `5579_amg_Single` = 100* (`AGEMEN8_A_NPERSEULES_55` + `AGEMEN8_A_NPERSEULES_65`) / `AGEMEN8_A_NPERSEULES_ENS`,
         `80+_amg_Single` = 100* `AGEMEN8_A_NPERSEULES_80` / `AGEMEN8_A_NPERSEULES_ENS`,
         `Family_w_Children_amg_HH` = 100* (`TF4_NBLOG_2` + `TF4_NBLOG_3` + `TF4_NBLOG_4`) / `TF4_NBLOG_ENS`,
         `Single_Parent_Family_amg_HH` = 100* (`TF4_NBLOG_3` + `TF4_NBLOG_4`) / `TF4_NBLOG_ENS`,
         `Family_wo_Children_amg_HH` = 100* `TF4_NBLOG_1` / `TF4_NBLOG_ENS`) %>%
  select(-colnames(FAM)[2:96]) %>%
  inner_join(vacc)
FAM_fact = FAM_brut %>%
  mutate(across(-c(codgeo, taux_cumu_1_inj), binarisation)) %>%
  mutate(taux_cumu_1_inj = binarisation(taux_cumu_1_inj, 0.25),
         taux_cumu_1_inj = as.factor(if_else(taux_cumu_1_inj == 1, 0, 1)))
```

## REV

```{r}
REV_brut = REV %>%
  mutate(`D1_st_Living` = `INDICS_FILO_DISP_DET_D1_1`,
         `Median_st_Living` = `INDICS_FILO_DISP_MEDIANE_1`,
         `D9_st_Living` = `INDICS_FILO_DISP_DET_D9_1`,
         `Interdecile_91_Ratio` = `INDICS_FILO_DISP_DET_RD_1`,
         `Taxable_HH` = `INDICS_FILO_DEC_DET_PIMP_1`,
         `Poverty_amg_Owners` = `INDICS_FILO_DISP_DET-OCCTYPR_TP60_1_1`,
         `Poverty_amg_Tenants` = `INDICS_FILO_DISP_DET-OCCTYPR_TP60_1_2`,
         `-30_Poverty` = `INDICS_FILO_DISP_DET-TRAGERF_TP60_1_1`,
         `3039_Poverty` = `INDICS_FILO_DISP_DET-TRAGERF_TP60_1_2`,
         `4049_Poverty` = `INDICS_FILO_DISP_DET-TRAGERF_TP60_1_3`,
         `5059_Poverty` = `INDICS_FILO_DISP_DET-TRAGERF_TP60_1_4`,
         `6074_Poverty` = `INDICS_FILO_DISP_DET-TRAGERF_TP60_1_5`,
         `75+_Poverty` = `INDICS_FILO_DISP_DET-TRAGERF_TP60_1_6`,
         `Poverty` = `INDICS_FILO_DISP_DET_TP60_1`,
         `Activity_Income` = `INDICS_FILO_DISP_DET_PACT_1`,
         `Salary_Income` = `INDICS_FILO_DISP_DET_PTSA_1`,
         `Unemployment_Benef` = `INDICS_FILO_DISP_DET_PCHO_1`,
         `Self-Employment` = `INDICS_FILO_DISP_DET_PBEN_1`,
         `Pensions_Annuities` = `INDICS_FILO_DISP_DET_PPEN_1`,
         `Estate` = `INDICS_FILO_DISP_DET_PPAT_1`,
         `Social_Benef` = `INDICS_FILO_DISP_DET_PPSOC_1`,
         `Family_Benef` = `INDICS_FILO_DISP_DET_PPFAM_1`,
         `Social_Minima` = `INDICS_FILO_DISP_DET_PPMINI_1`,
         `Housing_Benef` = `INDICS_FILO_DISP_DET_PPLOGT_1`,
         `Tax` = `INDICS_FILO_DISP_DET_PIMPOT_1`) %>%
  select(-colnames(REV)[2:28]) %>%
  inner_join(vacc)
REV_fact = REV_brut %>%
  mutate(across(-c(codgeo, taux_cumu_1_inj), binarisation)) %>%
  mutate(taux_cumu_1_inj = binarisation(taux_cumu_1_inj, 0.25),
         taux_cumu_1_inj = as.factor(if_else(taux_cumu_1_inj == 1, 0, 1)))
```

## ACT

```{r}
ACT_brut = ACT %>%
  mutate(`Wk_Res_Municipality` = 100* `ILTR_POP_1` / `ILTR_POP_ENS`,
         `Wk_Res_County-Municipality` = 100* `ILTR_POP_2` / `ILTR_POP_ENS`,
         `Wk_Res_Region-County` = 100* `ILTR_POP_3` / `ILTR_POP_ENS`,
         `Wk_Res_Country-Region` = 100* `ILTR_POP_4` / `ILTR_POP_ENS`,
         `Wk_Dom_Com_Abroad` = 100* `ILTR_POP_5` / `ILTR_POP_ENS`,
         `noTransport_toWk` = 100* `TRANS_19_POP_1` / `TRANS_19_POP_ENS`,
         `Walk_toWk` = 100* `TRANS_19_POP_2` / `TRANS_19_POP_ENS`,
         `Bike_toWk` = 100* `TRANS_19_POP_3` / `TRANS_19_POP_ENS`,
         `Motorbike_toWk` = 100* `TRANS_19_POP_4` / `TRANS_19_POP_ENS`,
         `Drive_toWk` = 100* `TRANS_19_POP_5` / `TRANS_19_POP_ENS`,
         `PublicTrans_toWk` = 100* `TRANS_19_POP_6` / `TRANS_19_POP_ENS`,
         `15+_Men_amg_salWF` = 100* `TP-SEXE-AGE3P_NBSAL_ENS_1_ENS` / `TP-SEXE-AGE3P_NBSAL_ENS_ENS_ENS`,
         `15+_Women_amg_salWF` = 100* `TP-SEXE-AGE3P_NBSAL_ENS_2_ENS` / `TP-SEXE-AGE3P_NBSAL_ENS_ENS_ENS`,
         `15+_PermanentContract_amg_salWF` = 100* `EMPL-SEXE_NBEMP_16_ENS` / (`EMPL-SEXE_NBEMP_11_ENS` + `EMPL-SEXE_NBEMP_12_ENS` + `EMPL-SEXE_NBEMP_13_ENS` + `EMPL-SEXE_NBEMP_14_ENS` + `EMPL-SEXE_NBEMP_15_ENS`+ +`EMPL-SEXE_NBEMP_16_ENS`),
         `15+_ShortTermContract_amg_salWF` = 100* `EMPL-SEXE_NBEMP_15_ENS` / (`EMPL-SEXE_NBEMP_11_ENS` + `EMPL-SEXE_NBEMP_12_ENS` + `EMPL-SEXE_NBEMP_13_ENS` + `EMPL-SEXE_NBEMP_14_ENS` + `EMPL-SEXE_NBEMP_15_ENS`+ +`EMPL-SEXE_NBEMP_16_ENS`),
         `15+_InterimContract_amg_salWF` = 100* `EMPL-SEXE_NBEMP_12_ENS` / (`EMPL-SEXE_NBEMP_11_ENS` + `EMPL-SEXE_NBEMP_12_ENS` + `EMPL-SEXE_NBEMP_13_ENS` + `EMPL-SEXE_NBEMP_14_ENS` + `EMPL-SEXE_NBEMP_15_ENS`+ +`EMPL-SEXE_NBEMP_16_ENS`),
         `15+_SubsidizedWork_amg_salWF` = 100* `EMPL-SEXE_NBEMP_13_ENS` / (`EMPL-SEXE_NBEMP_11_ENS` + `EMPL-SEXE_NBEMP_12_ENS` + `EMPL-SEXE_NBEMP_13_ENS` + `EMPL-SEXE_NBEMP_14_ENS` + `EMPL-SEXE_NBEMP_15_ENS`+ +`EMPL-SEXE_NBEMP_16_ENS`),
         `15+_ApprenticeContract_amg_salWF` = 100* `EMPL-SEXE_NBEMP_11_ENS` / (`EMPL-SEXE_NBEMP_11_ENS` + `EMPL-SEXE_NBEMP_12_ENS` + `EMPL-SEXE_NBEMP_13_ENS` + `EMPL-SEXE_NBEMP_14_ENS` + `EMPL-SEXE_NBEMP_15_ENS`+ +`EMPL-SEXE_NBEMP_16_ENS`),
         `15+_SelfEmployed_amg_nonsalWF` = 100* `EMPL-SEXE_NBEMP_21_ENS` / (`EMPL-SEXE_NBEMP_21_ENS` + `EMPL-SEXE_NBEMP_22_ENS` + `EMPL-SEXE_NBEMP_23_ENS`),
         `15+_Employers_amg_nonsalWF` = 100* `EMPL-SEXE_NBEMP_22_ENS` / (`EMPL-SEXE_NBEMP_21_ENS` + `EMPL-SEXE_NBEMP_22_ENS` + `EMPL-SEXE_NBEMP_23_ENS`),
         `15+_caregivers_amg_nonsalWF` = 100* `EMPL-SEXE_NBEMP_23_ENS` / (`EMPL-SEXE_NBEMP_21_ENS` + `EMPL-SEXE_NBEMP_22_ENS` + `EMPL-SEXE_NBEMP_23_ENS`)) %>%
  select(-colnames(ACT)[2:119]) %>%
  inner_join(vacc)
ACT_fact = ACT_brut %>%
  mutate(across(-c(codgeo, taux_cumu_1_inj), binarisation)) %>%
  mutate(taux_cumu_1_inj = binarisation(taux_cumu_1_inj, 0.25),
         taux_cumu_1_inj = as.factor(if_else(taux_cumu_1_inj == 1, 0, 1)))
```

## FOR

```{r}
FOR_brut = FOR %>%
  mutate(`0205_School` = 100* `AGESCOL-SEXE-ETUD_POP_02_ENS_1` / `AGESCOL-SEXE-ETUD_POP_02_ENS_ENS`,
         `0610_School` = 100* `AGESCOL-SEXE-ETUD_POP_06_ENS_1` / `AGESCOL-SEXE-ETUD_POP_06_ENS_ENS`,
         `1114_School` = 100* `AGESCOL-SEXE-ETUD_POP_11_ENS_1` / `AGESCOL-SEXE-ETUD_POP_11_ENS_ENS`,
         `1517_School` = 100* `AGESCOL-SEXE-ETUD_POP_15_ENS_1` / `AGESCOL-SEXE-ETUD_POP_15_ENS_ENS`,
         `1824_School` = 100* `AGESCOL-SEXE-ETUD_POP_18_ENS_1` / `AGESCOL-SEXE-ETUD_POP_18_ENS_ENS`,
         `2529_School` = 100* `AGESCOL-SEXE-ETUD_POP_25_ENS_1` / `AGESCOL-SEXE-ETUD_POP_25_ENS_ENS`,
         `30+_School` = 100* `AGESCOL-SEXE-ETUD_POP_30_ENS_1` / `AGESCOL-SEXE-ETUD_POP_30_ENS_ENS`,
         `15+_NoDiploma_amg_WF` = 100* `SEXE-DIPL_19_POP_ENS_A` / `SEXE-DIPL_19_POP_ENS_ENS`,
         `15+_CertifGeneEducation_amg_WF` = 100* `SEXE-DIPL_19_POP_ENS_B` / `SEXE-DIPL_19_POP_ENS_ENS`,
         `15+_VocationalGraduate_amg_WF` = 100* `SEXE-DIPL_19_POP_ENS_C` / `SEXE-DIPL_19_POP_ENS_ENS`,
         `15+_HighSchoolGraduate_amg_WF` = 100* `SEXE-DIPL_19_POP_ENS_D` / `SEXE-DIPL_19_POP_ENS_ENS`,
         `15+_HSG+2_amg_WF` = 100* `SEXE-DIPL_19_POP_ENS_E` / `SEXE-DIPL_19_POP_ENS_ENS`,
         `15+_HSG+4_amg_WF` = 100* `SEXE-DIPL_19_POP_ENS_F` / `SEXE-DIPL_19_POP_ENS_ENS`,
         `15+_HSG+5+_amg_WF` = 100* `SEXE-DIPL_19_POP_ENS_G` / `SEXE-DIPL_19_POP_ENS_ENS`,
         `15+_HighEducation_amg_WF` = 100* (`SEXE-DIPL_19_POP_ENS_E` + `SEXE-DIPL_19_POP_ENS_F` + `SEXE-DIPL_19_POP_ENS_G`) / `SEXE-DIPL_19_POP_ENS_ENS`,
         `15+_men_NoDiploma_amg_mWF` = 100* `SEXE-DIPL_19_POP_1_A` / `SEXE-DIPL_19_POP_1_ENS`,
         `15+_men_VocationalGraduate_amg_mWF` = 100* `SEXE-DIPL_19_POP_1_C` / `SEXE-DIPL_19_POP_1_ENS`,
         `15+_men_HighSchoolGraduate_amg_mWF` = 100* `SEXE-DIPL_19_POP_1_D` / `SEXE-DIPL_19_POP_1_ENS`,
         `15+_men_HighEducation_amg_mWF` = 100* (`SEXE-DIPL_19_POP_1_E` + `SEXE-DIPL_19_POP_1_F` + `SEXE-DIPL_19_POP_1_G`) / `SEXE-DIPL_19_POP_1_ENS`,
         `15+_women_NoDiploma_amg_wWF` = 100* `SEXE-DIPL_19_POP_2_A` / `SEXE-DIPL_19_POP_2_ENS`,
         `15+_women_VocationalGraduate_amg_wWF` = 100* `SEXE-DIPL_19_POP_2_C` / `SEXE-DIPL_19_POP_2_ENS`,
         `15+_women_HighSchoolGraduate_amg_wWF` = 100* `SEXE-DIPL_19_POP_2_D` / `SEXE-DIPL_19_POP_2_ENS`,
         `15+_women_HighEducation_amg_wWF` = 100* (`SEXE-DIPL_19_POP_2_E` + `SEXE-DIPL_19_POP_2_F` + `SEXE-DIPL_19_POP_2_G`) / `SEXE-DIPL_19_POP_2_ENS`,
         `15+_MenOnWomen_NoDiploma` = 100* `SEXE-DIPL_19_POP_1_A` / `SEXE-DIPL_19_POP_2_A`,
         `15+_MenOnWomen_VocationalGraduate` = 100* `SEXE-DIPL_19_POP_1_C` / `SEXE-DIPL_19_POP_2_C`,
         `15+_MenOnWomen_HighSchoolGraduate` = 100* `SEXE-DIPL_19_POP_1_D` / `SEXE-DIPL_19_POP_2_D`,
         `15+_MenOnWomen_HighEducation` = 100* ((`SEXE-DIPL_19_POP_1_E` + `SEXE-DIPL_19_POP_1_F` + `SEXE-DIPL_19_POP_1_G`) / (`SEXE-DIPL_19_POP_2_E` + `SEXE-DIPL_19_POP_2_F` + `SEXE-DIPL_19_POP_2_G`))) %>%
  select(-colnames(FOR)[2:97]) %>%
  inner_join(vacc)
FOR_fact = FOR_brut %>%
  mutate(across(-c(codgeo, taux_cumu_1_inj), binarisation)) %>%
  mutate(taux_cumu_1_inj = binarisation(taux_cumu_1_inj, 0.25),
         taux_cumu_1_inj = as.factor(if_else(taux_cumu_1_inj == 1, 0, 1)))
```

## POP

```{r}
POP_brut = POP %>%
  mutate(`0014_amg_POP` = 100* `SEXE-AGE15_15_90_POP_ENS_00` / `SEXE-AGE15_15_90_POP_ENS_ENS`,
         `1529_amg_POP` = 100* `SEXE-AGE15_15_90_POP_ENS_00` / `SEXE-AGE15_15_90_POP_ENS_ENS`,
         `3044_amg_POP` = 100* `SEXE-AGE15_15_90_POP_ENS_30` / `SEXE-AGE15_15_90_POP_ENS_ENS`,
         `4559_amg_POP` = 100* `SEXE-AGE15_15_90_POP_ENS_45` / `SEXE-AGE15_15_90_POP_ENS_ENS`,
         `6074_amg_POP` = 100* `SEXE-AGE15_15_90_POP_ENS_60` / `SEXE-AGE15_15_90_POP_ENS_ENS`,
         `7589_amg_POP` = 100* `SEXE-AGE15_15_90_POP_ENS_75` / `SEXE-AGE15_15_90_POP_ENS_ENS`,
         `90+_amg_POP` = 100* `SEXE-AGE15_15_90_POP_ENS_90` / `SEXE-AGE15_15_90_POP_ENS_ENS`,
         `Men` = 100* `SEXE-AGE15_15_90_POP_1_ENS` / `SEXE-AGE15_15_90_POP_ENS_ENS`,
         `0019_amg_POP` = 100* `SEXE-AGE3_B_POP_ENS_00` / `SEXE-AGE3_B_POP_ENS_ENS`,
         `2064_amg_POP` = 100* `SEXE-AGE3_B_POP_ENS_20` / `SEXE-AGE3_B_POP_ENS_ENS`,
         `65+_amg_POP` = 100* `SEXE-AGE3_B_POP_ENS_65` / `SEXE-AGE3_B_POP_ENS_ENS`,
         `15+_Farmers_amg_POP` = 100* `CS1_8-SEXE_POP_1_ENS` / `CS1_8-SEXE_POP_ENS_ENS`,
         `15+_CraftsBusinessShopkeeper_amg_POP` = 100* `CS1_8-SEXE_POP_2_ENS` / `CS1_8-SEXE_POP_ENS_ENS`,
         `15+_ManagersHigherIntellectProf_amg_POP` = 100* `CS1_8-SEXE_POP_3_ENS` / `CS1_8-SEXE_POP_ENS_ENS`,
         `15+_IntermediateProf_amg_POP` = 100* `CS1_8-SEXE_POP_4_ENS` / `CS1_8-SEXE_POP_ENS_ENS`,
         `15+_WhiteCollar_amg_POP` = 100* `CS1_8-SEXE_POP_5_ENS` / `CS1_8-SEXE_POP_ENS_ENS`,
         `15+_BlueCollar_amg_POP` = 100* `CS1_8-SEXE_POP_6_ENS` / `CS1_8-SEXE_POP_ENS_ENS`,
         `15+_Retired_amg_POP` = 100* `CS1_8-SEXE_POP_7_ENS` / `CS1_8-SEXE_POP_ENS_ENS`,
         `15+_OtherNoActivity_amg_POP` = 100* `CS1_8-SEXE_POP_8_ENS` / `CS1_8-SEXE_POP_ENS_ENS`,
         `0014_men_amg_mPOP` = 100* `SEXE-AGE15_15_90_POP_1_00` / `SEXE-AGE15_15_90_POP_1_ENS`,
         `1529_men_amg_mPOP` = 100* `SEXE-AGE15_15_90_POP_1_15` / `SEXE-AGE15_15_90_POP_1_ENS`,
         `3044_men_amg_mPOP` = 100* `SEXE-AGE15_15_90_POP_1_30` / `SEXE-AGE15_15_90_POP_1_ENS`,
         `4559_men_amg_mPOP` = 100* `SEXE-AGE15_15_90_POP_1_45` / `SEXE-AGE15_15_90_POP_1_ENS`,
         `6074_men_amg_mPOP` = 100* `SEXE-AGE15_15_90_POP_1_60` / `SEXE-AGE15_15_90_POP_1_ENS`,
         `7589_men_amg_mPOP` = 100* `SEXE-AGE15_15_90_POP_1_75` / `SEXE-AGE15_15_90_POP_1_ENS`,
         `90+_men_amg_mPOP` = 100* `SEXE-AGE15_15_90_POP_1_90` / `SEXE-AGE15_15_90_POP_1_ENS`,
         `0019_men_amg_mPOP` = 100* `SEXE-AGE3_B_POP_1_00` / `SEXE-AGE3_B_POP_1_ENS`,
         `2064_men_amg_mPOP` = 100* `SEXE-AGE3_B_POP_1_20` / `SEXE-AGE3_B_POP_1_ENS`,
         `65+_men_amg_mPOP` = 100* `SEXE-AGE3_B_POP_1_65` / `SEXE-AGE3_B_POP_1_ENS`,
         `15+_men_Farmers_amg_mPOP` = 100* `CS1_8-SEXE_POP_1_1` / `CS1_8-SEXE_POP_ENS_1`,
         `15+_men_CraftsBusinessShopkeeper_amg_mPOP` = 100* `CS1_8-SEXE_POP_2_1` / `CS1_8-SEXE_POP_ENS_1`,
         `15+_men_ManagersHigherIntellectProf_amg_mPOP` = 100* `CS1_8-SEXE_POP_3_1` / `CS1_8-SEXE_POP_ENS_1`,
         `15+_men_IntermediateProf_amg_mPOP` = 100* `CS1_8-SEXE_POP_4_1` / `CS1_8-SEXE_POP_ENS_1`,
         `15+_men_WhiteCollar_amg_mPOP` = 100* `CS1_8-SEXE_POP_5_1` / `CS1_8-SEXE_POP_ENS_1`,
         `15+_men_BlueCollar_amg_mPOP` = 100* `CS1_8-SEXE_POP_6_1` / `CS1_8-SEXE_POP_ENS_1`,
         `15+_men_Retired_amg_mPOP` = 100* `CS1_8-SEXE_POP_7_1` / `CS1_8-SEXE_POP_ENS_1`,
         `15+_men_OtherNoActivity_amg_POP` = 100* `CS1_8-SEXE_POP_8_1` / `CS1_8-SEXE_POP_ENS_1`,
         `0014_women_amg_wPOP` = 100* `SEXE-AGE15_15_90_POP_2_00` / `SEXE-AGE15_15_90_POP_2_ENS`,
         `1529_women_amg_wPOP` = 100* `SEXE-AGE15_15_90_POP_2_15` / `SEXE-AGE15_15_90_POP_2_ENS`,
         `3044_women_amg_wPOP` = 100* `SEXE-AGE15_15_90_POP_2_30` / `SEXE-AGE15_15_90_POP_2_ENS`,
         `4559_women_amg_wPOP` = 100* `SEXE-AGE15_15_90_POP_2_45` / `SEXE-AGE15_15_90_POP_2_ENS`,
         `6074_women_amg_wPOP` = 100* `SEXE-AGE15_15_90_POP_2_60` / `SEXE-AGE15_15_90_POP_2_ENS`,
         `7589_women_amg_wPOP` = 100* `SEXE-AGE15_15_90_POP_2_75` / `SEXE-AGE15_15_90_POP_2_ENS`,
         `90+_women_amg_wPOP` = 100* `SEXE-AGE15_15_90_POP_2_90` / `SEXE-AGE15_15_90_POP_2_ENS`,
         `0019_women_amg_wPOP` = 100* `SEXE-AGE3_B_POP_2_00` / `SEXE-AGE3_B_POP_2_ENS`,
         `2064_women_amg_wPOP` = 100* `SEXE-AGE3_B_POP_2_20` / `SEXE-AGE3_B_POP_2_ENS`,
         `65+_women_amg_wPOP` = 100* `SEXE-AGE3_B_POP_2_65` / `SEXE-AGE3_B_POP_2_ENS`,
         `15+_women_Farmers_amg_wPOP` = 100* `CS1_8-SEXE_POP_1_2` / `CS1_8-SEXE_POP_ENS_2`,
         `15+_women_CraftsBusinessShopkeeper_amg_wPOP` = 100* `CS1_8-SEXE_POP_2_2` / `CS1_8-SEXE_POP_ENS_2`,
         `15+_women_ManagersHigherIntellectProf_amh_wPOP` = 100* `CS1_8-SEXE_POP_3_2` / `CS1_8-SEXE_POP_ENS_2`,
         `15+_women_IntermediateProf_amg_wPOP` = 100* `CS1_8-SEXE_POP_4_2` / `CS1_8-SEXE_POP_ENS_2`,
         `15+_women_WhiteCollar_amg_wPOP` = 100* `CS1_8-SEXE_POP_5_2` / `CS1_8-SEXE_POP_ENS_2`,
         `15+_women_BlueCollar_amg_wPOP` = 100* `CS1_8-SEXE_POP_6_2` / `CS1_8-SEXE_POP_ENS_2`,
         `15+_women_Retired_amg_wPOP` = 100* `CS1_8-SEXE_POP_7_2` / `CS1_8-SEXE_POP_ENS_2`,
         `15+_women_OtherNoActivity_amg_wPOP` = 100* `CS1_8-SEXE_POP_8_2` / `CS1_8-SEXE_POP_ENS_2`) %>%
  select(-colnames(POP)[2:123]) %>%
  inner_join(vacc)
POP_fact = POP_brut %>%
  mutate(across(-c(codgeo, taux_cumu_1_inj), binarisation)) %>%
  mutate(taux_cumu_1_inj = binarisation(taux_cumu_1_inj, 0.25),
         taux_cumu_1_inj = as.factor(if_else(taux_cumu_1_inj == 1, 0, 1)))
```

## IMM

```{r}
IMM_brut = IMM %>%
  mutate(`French_nlty` = 100* `INATC-SEXE-AGE4_B-IRANR_4_POP_1_ENS_ENS_ENS` / `INATC-SEXE-AGE4_B-IRANR_4_POP_ENS_ENS_ENS_ENS`,
         `Stranger` = 100* `INATC-SEXE-AGE4_B-IRANR_4_POP_2_ENS_ENS_ENS` / `INATC-SEXE-AGE4_B-IRANR_4_POP_ENS_ENS_ENS_ENS`,
         `Immigrant` = 100* `IMMI-CS1_8-SEXE_POP_1_ENS_ENS` / `IMMI-CS1_8-SEXE_POP_ENS_ENS_ENS`,
         `French_nlty_amg_Men` = 100* `INATC-SEXE-AGE4_B-IRANR_4_POP_1_1_ENS_ENS` / `INATC-SEXE-AGE4_B-IRANR_4_POP_ENS_1_ENS_ENS`,
         `Stranger_amg_Men` = 100* `INATC-SEXE-AGE4_B-IRANR_4_POP_2_1_ENS_ENS` / `INATC-SEXE-AGE4_B-IRANR_4_POP_ENS_1_ENS_ENS`,
         `Immigrant_amg_Men` = 100* `IMMI-CS1_8-SEXE_POP_1_ENS_1` / `IMMI-CS1_8-SEXE_POP_ENS_ENS_1`,
         `French_nlty_amg_Women` = 100* `INATC-SEXE-AGE4_B-IRANR_4_POP_1_2_ENS_ENS` / `INATC-SEXE-AGE4_B-IRANR_4_POP_ENS_2_ENS_ENS`,
         `Stranger_amg_Women` = 100* `INATC-SEXE-AGE4_B-IRANR_4_POP_2_2_ENS_ENS` / `INATC-SEXE-AGE4_B-IRANR_4_POP_ENS_2_ENS_ENS`,
         `Immigrant_amg_Women` = 100* `IMMI-CS1_8-SEXE_POP_1_ENS_2` / `IMMI-CS1_8-SEXE_POP_ENS_ENS_2`,
         `Res_Abroad_2017` = 100* `INATC-SEXE-AGE4_B-IRANR_4_POP_ENS_ENS_ENS_4` / `INATC-SEXE-AGE4_B-IRANR_4_POP_ENS_ENS_ENS_ENS`) %>%
  select(-colnames(IMM)[2:307]) %>%
  inner_join(vacc)
IMM_fact = IMM_brut %>%
  mutate(across(-c(codgeo, taux_cumu_1_inj), binarisation)) %>%
  mutate(taux_cumu_1_inj = binarisation(taux_cumu_1_inj, 0.25),
         taux_cumu_1_inj = as.factor(if_else(taux_cumu_1_inj == 1, 0, 1)))
```

## GEO

```{r}

GEO = read_csv("~/nas_backup_scripts_elr/INSEE_API/data/exportGeo_EPCI.csv") %>%

  mutate(SUPERFICIE = SUPERFICIE /100) %>%
  select(codgeo = SIREN, latitude = Y_CENTROID, longitude = X_CENTROID, superficie = SUPERFICIE) %>%
  plyr::rbind.fill(read_csv("~/nas_backup_scripts_elr/INSEE_API/data/exportGeo_ComArr.csv") %>%
                     select(codgeo = insee, superficie = surf_km2) %>%
                     mutate(superficie = case_when(codgeo == 75102 ~ 0.99,
                                                   codgeo == 69381 ~ 1.51,
                                                   codgeo == 75104 ~ 1.60,
                                                   codgeo == 75103 ~ 1.17,
                                                   codgeo == 75101 ~ 1.83,
                                                   codgeo == 13201 ~ 1.778,
                                                   codgeo == 69384 ~ 2.93,
                                                   codgeo == 75106 ~ 2.15,
                                                   codgeo == 75105 ~ 2.54,
                                                   codgeo == 75109 ~ 2.18,
                                                   codgeo == 75110 ~ 2.89,
                                                   codgeo == 13203 ~ 2.60,
                                                   codgeo == 13206 ~ 2.10,
                                                   codgeo == 13205 ~ 2.24,
                                                   codgeo == 13204 ~ 2.90,
                                                   T ~ superficie))) %>%
  inner_join(POP %>% select(codgeo, `SEXE-AGE3_B_POP_ENS_ENS`)) %>%
  mutate(densite = `SEXE-AGE3_B_POP_ENS_ENS` / superficie) %>%
  inner_join(vacc)

GEO_OM = GEO %>%
  filter(codgeo %in% c(GEO_gua$SIREN_EPCI, GEO_guy$SIREN_EPCI, GEO_mar$SIREN_EPCI, GEO_may$SIREN, GEO_reu$SIREN_EPCI)) %>%
  select(-c(latitude, longitude)) %>%
  plyr::rbind.fill(GEO %>%
                     filter(!(codgeo %in% c(GEO_gua$SIREN_EPCI, GEO_guy$SIREN_EPCI, GEO_mar$SIREN_EPCI, GEO_may$SIREN, GEO_reu$SIREN_EPCI))))

GEO_fact = GEO %>%
  filter(codgeo %in% c(GEO_gua$SIREN_EPCI, GEO_guy$SIREN_EPCI, GEO_mar$SIREN_EPCI, GEO_may$SIREN, GEO_reu$SIREN_EPCI)) %>%
  select(-c(latitude, longitude)) %>%
  plyr::rbind.fill(GEO %>%
                     filter(!(codgeo %in% c(GEO_gua$SIREN_EPCI, GEO_guy$SIREN_EPCI, GEO_mar$SIREN_EPCI, GEO_may$SIREN, GEO_reu$SIREN_EPCI)))) %>%
  select(codgeo, latitude, longitude, densite, taux_cumu_1_inj) %>%
  mutate(across(-c(codgeo, taux_cumu_1_inj), binarisation)) %>%
  mutate(taux_cumu_1_inj = binarisation(taux_cumu_1_inj, 0.25),
         taux_cumu_1_inj = as.factor(if_else(taux_cumu_1_inj == 1, 0, 1)))
```

```{r}
LOG_OR = questionr::odds.ratio(LOG_fact$`1ry_res`, LOG_fact$taux_cumu_1_inj) %>%
  rbind(questionr::odds.ratio(LOG_fact$`2ry_res`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`Vacant_Home`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`Houses`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`Flats`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`Nb_Rooms_1ry_res`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`House_1ry_res`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`Flat_1ry_res`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`1ry_res_bf_1919`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`1ry_res_19-45`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`1ry_res_46-70`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`1ry_res_71-90`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`1ry_res_91-05`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`1ry_res_06-15`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`HH_Moving_Time_lt2y`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`HH_Moving_Time_2to4y`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`HH_Moving_Time_5to9y`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`HH_Moving_Time_10to19y`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`HH_Moving_Time_20to29y`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`HH_Moving_Time_gt30y`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`1ry_res_Owner`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`1ry_res_Tenant`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`1ry_res_Social`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`1ry_res_FreeAcc`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`1ry_res_Carpark`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`1ry_res_0car`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`1ry_res_1car`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`1ry_res_2car`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`1ry_res_3+car`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`Pop_per_1ry_res`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`1ry_res_gt0car`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`Pop_per_1ry_res_Owner`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`Pop_per_1ry_res_Tenant`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`Pop_per_1ry_res_Social`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`Pop_per_1ry_res_FreeAcc`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`1ry_res_Occupancy`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`Owners_Occupancy`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`Tenant_Occupancy`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`Social_Occupancy`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`FreeAcc_Occupancy`, LOG_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(LOG_fact$`Overcrowding_rate`, LOG_fact$taux_cumu_1_inj)) %>%
  as.data.frame() %>%
  bind_cols(Variable = colnames(LOG_fact)[2:42]) %>%
  select(Variable, OR, `2.5 %`, `97.5 %`, p)
rownames(LOG_OR) = NULL
write_csv2(LOG_OR, "data/LOG_OR.csv")
```

```{r}
EMP_OR = questionr::odds.ratio(EMP_fact$`1564_Workforce_rate`, EMP_fact$taux_cumu_1_inj) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1524_Workforce_rate`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`2554_Workforce_rate`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`5564_Workforce_rate`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_men_Workforce_rate`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1524_men_Workforce_rate`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`2554_men_Workforce_rate`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`5564_men_Workforce_rate`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_women_Workforce_rate`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1524_women_Workforce_rate`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`2554_women_Workforce_rate`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`5564_women_Workforce_rate`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_Employed_rate_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1524_Employed_rate_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`2554_Employed_rate_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`5564_Employed_rate_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_men_Employed_rate_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1524_men_Employed_rate_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`2554_men_Employed_rate_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`5564_men_Employed_rate_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_women_Employed_rate_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1524_women_Employed_rate_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`2554_women_Employed_rate_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`5564_women_Employed_rate_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_Unemployed_rate_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1524_Unemployed_rate_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`2554_Unemployed_rate_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`5564_Unemployed_rate_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_NonWorking_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_Student_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_Retired_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_OtherInactive_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_men_Unemplyed_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_women_Unemplyed_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_Student_amg_NW`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_Retired_amg_NW`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_OtherInactive_amg_NW`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_NonWorking_amg_POP`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_Farmers_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_CraftsBusinessShopkeepers_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_HihgQualWorkers_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_IntermediateProf_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_BlueCollar_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_WhiteCollar_amg_WF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_Farmers_amg_EmpWF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_CraftsBusinessShopkeepers_amg_EmpWF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_HihgQualWorkers_amg_EmpWF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_IntermediateProf_amg_EmpWF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_BlueCollar_amg_EmpWF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`1564_WhiteCollar_amg_EmpWF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`15+_men_amg_empWF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`15+_women_amg_empWF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`15+_Salaried_amg_empWF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`15+_NonSalaried_amg_empWF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`15+_FullTime_amg_empWF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`15+_men_amg_salWF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`15+_women_amg_salWF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`15+_men_amg_nonsalWF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`15+_women_amg_nonsalWF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`15+_men_amg_FullTimeWF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`15+_women_amg_FullTimeWF`, EMP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(EMP_fact$`15+_FullTime_amg_salWF`, EMP_fact$taux_cumu_1_inj)) %>%
  as.data.frame() %>%
  bind_cols(Variable = colnames(EMP_fact)[2:63]) %>%
  select(Variable, OR, `2.5 %`, `97.5 %`, p)
rownames(EMP_OR) = NULL
write_csv2(EMP_OR, "data/EMP_OR.csv")
```

```{r}
FAM_OR = questionr::odds.ratio(FAM_fact$`SinglePerson_HH`, FAM_fact$taux_cumu_1_inj) %>%
  rbind(questionr::odds.ratio(FAM_fact$`SingleMan_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`SingleWoman_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`OtherNoFamily_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Family_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`NoChildFamily_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`ChildFamily_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`SingleParent_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Farmer_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`CraftsBusinessShopkeepers_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`HighQualidied_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Intermediate_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`BlueCollar_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`WhiteCollar_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Retired_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Other_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`15+_SinglePerson_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Pop_SingleMan_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Pop_SingleWoman_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Pop_OtherNoFamily_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Pop_Family_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Pop_NoChildFamily_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Pop_ChildFamily_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Pop_SingleParent_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Pop_Farmer_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Pop_CraftsBusinessShopkeepers_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Pop_HighQualidied_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Pop_Intermediate_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Pop_BlueCollar_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Pop_WhiteCollar_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Pop_Retired_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Pop_Other_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`1524_amg_15+POP`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`2554_amg_15+POP`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`5579_amg_15+POP`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`80+_amg_15+POP`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`15+_Single_amg_POP`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`15+_Married_amg_POP`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`15+_nonMarried_amg_POP`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`1524_amg_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`2554_amg_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`5579_amg_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`80+_amg_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`1524_amg_Single`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`2554_amg_Single`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`5579_amg_Single`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`80+_amg_Single`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Family_w_Children_amg_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Single_Parent_Family_amg_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FAM_fact$`Family_wo_Children_amg_HH`, FAM_fact$taux_cumu_1_inj)) %>%
  as.data.frame() %>%
  bind_cols(Variable = colnames(FAM_fact)[2:51]) %>%
  select(Variable, OR, `2.5 %`, `97.5 %`, p)
rownames(FAM_OR) = NULL
write_csv2(FAM_OR, "data/FAM_OR.csv")
```

```{r}
REV_OR = questionr::odds.ratio(REV_fact$`D1_st_Living`, REV_fact$taux_cumu_1_inj) %>%
  rbind(questionr::odds.ratio(REV_fact$`Median_st_Living`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`D9_st_Living`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`Interdecile_91_Ratio`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`Taxable_HH`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`Poverty_amg_Owners`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`Poverty_amg_Tenants`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`-30_Poverty`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`3039_Poverty`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`4049_Poverty`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`5059_Poverty`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`6074_Poverty`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`75+_Poverty`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`Poverty`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`Activity_Income`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`Salary_Income`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`Unemployment_Benef`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`Self-Employment`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`Pensions_Annuities`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`Estate`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`Social_Benef`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`Family_Benef`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`Social_Minima`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`Housing_Benef`, REV_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(REV_fact$`Tax`, REV_fact$taux_cumu_1_inj)) %>%
  as.data.frame() %>%
  bind_cols(Variable = colnames(REV_fact)[2:26]) %>%
  select(Variable, OR, `2.5 %`, `97.5 %`, p)
rownames(REV_OR) = NULL
write_csv2(REV_OR, "data/REV_OR.csv")
```

```{r}
ACT_OR = questionr::odds.ratio(ACT_fact$`Wk_Res_Municipality`, ACT_fact$taux_cumu_1_inj) %>%
  rbind(questionr::odds.ratio(ACT_fact$`Wk_Res_County-Municipality`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`Wk_Res_Region-County`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`Wk_Res_Country-Region`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`Wk_Dom_Com_Abroad`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`noTransport_toWk`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`Walk_toWk`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`Bike_toWk`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`Motorbike_toWk`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`Drive_toWk`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`PublicTrans_toWk`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`15+_Men_amg_salWF`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`15+_Women_amg_salWF`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`15+_PermanentContract_amg_salWF`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`15+_ShortTermContract_amg_salWF`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`15+_InterimContract_amg_salWF`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`15+_SubsidizedWork_amg_salWF`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`15+_ApprenticeContract_amg_salWF`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`15+_SelfEmployed_amg_nonsalWF`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`15+_Employers_amg_nonsalWF`, ACT_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(ACT_fact$`15+_caregivers_amg_nonsalWF`, ACT_fact$taux_cumu_1_inj)) %>%
  as.data.frame() %>%
  bind_cols(Variable = colnames(ACT_fact)[2:22]) %>%
  select(Variable, OR, `2.5 %`, `97.5 %`, p)
rownames(ACT_OR) = NULL
write_csv2(ACT_OR, "data/ACT_OR.csv")
```

```{r}
FOR_OR = questionr::odds.ratio(FOR_fact$`0205_School`, FOR_fact$taux_cumu_1_inj) %>%
  rbind(questionr::odds.ratio(FOR_fact$`0610_School`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`1114_School`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`1517_School`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`1824_School`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`2529_School`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`30+_School`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_NoDiploma_amg_WF`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_CertifGeneEducation_amg_WF`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_VocationalGraduate_amg_WF`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_HighSchoolGraduate_amg_WF`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_HSG+2_amg_WF`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_HSG+4_amg_WF`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_HSG+5+_amg_WF`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_HighEducation_amg_WF`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_men_NoDiploma_amg_mWF`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_men_VocationalGraduate_amg_mWF`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_men_HighSchoolGraduate_amg_mWF`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_men_HighEducation_amg_mWF`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_women_NoDiploma_amg_wWF`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_women_VocationalGraduate_amg_wWF`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_women_HighSchoolGraduate_amg_wWF`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_women_HighEducation_amg_wWF`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_MenOnWomen_NoDiploma`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_MenOnWomen_VocationalGraduate`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_MenOnWomen_HighSchoolGraduate`, FOR_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(FOR_fact$`15+_MenOnWomen_HighEducation`, FOR_fact$taux_cumu_1_inj)) %>%
  as.data.frame() %>%
  bind_cols(Variable = colnames(FOR_fact)[2:28]) %>%
  select(Variable, OR, `2.5 %`, `97.5 %`, p)
rownames(FOR_OR) = NULL
write_csv2(FOR_OR, "data/FOR_OR.csv")
```

```{r}
POP_OR = questionr::odds.ratio(POP_fact$`0014_amg_POP`, POP_fact$taux_cumu_1_inj) %>%
  rbind(questionr::odds.ratio(POP_fact$`1529_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`3044_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`4559_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`6074_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`7589_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`90+_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`Men`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`0019_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`2064_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`65+_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_Farmers_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_CraftsBusinessShopkeeper_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_ManagersHigherIntellectProf_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_IntermediateProf_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_WhiteCollar_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_BlueCollar_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_Retired_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_OtherNoActivity_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`0014_men_amg_mPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`1529_men_amg_mPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`3044_men_amg_mPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`4559_men_amg_mPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`6074_men_amg_mPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`7589_men_amg_mPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`90+_men_amg_mPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`0019_men_amg_mPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`2064_men_amg_mPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`65+_men_amg_mPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_men_Farmers_amg_mPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_men_CraftsBusinessShopkeeper_amg_mPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_men_ManagersHigherIntellectProf_amg_mPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_men_IntermediateProf_amg_mPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_men_WhiteCollar_amg_mPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_men_BlueCollar_amg_mPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_men_Retired_amg_mPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_men_OtherNoActivity_amg_POP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`0014_women_amg_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`1529_women_amg_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`3044_women_amg_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`4559_women_amg_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`6074_women_amg_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`7589_women_amg_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`90+_women_amg_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`0019_women_amg_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`2064_women_amg_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`65+_women_amg_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_women_Farmers_amg_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_women_CraftsBusinessShopkeeper_amg_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_women_ManagersHigherIntellectProf_amh_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_women_IntermediateProf_amg_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_women_WhiteCollar_amg_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_women_BlueCollar_amg_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_women_Retired_amg_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(POP_fact$`15+_women_OtherNoActivity_amg_wPOP`, POP_fact$taux_cumu_1_inj)) %>%
  as.data.frame() %>%
  bind_cols(Variable = colnames(POP_fact)[2:56]) %>%
  select(Variable, OR, `2.5 %`, `97.5 %`, p)
rownames(POP_OR) = NULL
write_csv2(POP_OR, "data/POP_OR.csv")
```

```{r}
IMM_OR = questionr::odds.ratio(IMM_fact$`French_nlty`, IMM_fact$taux_cumu_1_inj) %>%
  rbind(questionr::odds.ratio(IMM_fact$`Stranger`, IMM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(IMM_fact$`Immigrant`, IMM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(IMM_fact$`French_nlty_amg_Men`, IMM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(IMM_fact$`Stranger_amg_Men`, IMM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(IMM_fact$`Immigrant_amg_Men`, IMM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(IMM_fact$`French_nlty_amg_Women`, IMM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(IMM_fact$`Stranger_amg_Women`, IMM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(IMM_fact$`Immigrant_amg_Women`, IMM_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(IMM_fact$`Res_Abroad_2017`, IMM_fact$taux_cumu_1_inj)) %>%
  as.data.frame() %>%
  bind_cols(Variable = colnames(IMM_fact)[2:11]) %>%
  select(Variable, OR, `2.5 %`, `97.5 %`, p)
rownames(IMM_OR) = NULL
write_csv2(IMM_OR, "data/IMM_OR.csv")
```

```{r}
GEO_OR = questionr::odds.ratio(GEO_fact$latitude, GEO_fact$taux_cumu_1_inj) %>%
  rbind(questionr::odds.ratio(GEO_fact$longitude, GEO_fact$taux_cumu_1_inj)) %>%
  rbind(questionr::odds.ratio(GEO_fact$densite, GEO_fact$taux_cumu_1_inj)) %>%
  as.data.frame() %>%
  bind_cols(Variable = colnames(GEO_fact)[2:4]) %>%
  select(Variable, OR, `2.5 %`, `97.5 %`, p)
rownames(GEO_OR) = NULL
write_csv2(GEO_OR, "data/GEO_OR.csv")
```

```{r}
DF_OR =  LOG_OR %>% mutate(theme = "Logement", .after = Variable) %>%
  bind_rows(EMP_OR %>% mutate(theme = "Emploi", .after = Variable)) %>%
  bind_rows(FAM_OR %>% mutate(theme = "Famille", .after = Variable)) %>%
  bind_rows(REV_OR %>% mutate(theme = "Revenus", .after = Variable)) %>%
  bind_rows(ACT_OR %>% mutate(theme = "Activite", .after = Variable)) %>%
  bind_rows(FOR_OR %>% mutate(theme = "Formation", .after = Variable)) %>%
  bind_rows(POP_OR %>% mutate(theme = "Population", .after = Variable)) %>%
  bind_rows(IMM_OR %>% mutate(theme = "Immigration", .after = Variable)) %>%
  bind_rows(GEO_OR %>% mutate(theme = "Geographie", .after = Variable)) %>%
  group_by(theme) %>%
  mutate(id = row_number()) %>%
  ungroup() %>%
  mutate(inv_OR = 1/OR,
         `inv_2.5 %` = 1/`97.5 %`,
         `inv_97.5 %` = 1/`2.5 %`,
         `is_OR_>1` = OR > inv_OR,
         `max_OR-inv_OR` = if_else(`is_OR_>1`, OR, inv_OR)) %>%
  arrange(desc(`max_OR-inv_OR`))
```

# Manhattan

```{r}

axis_df = DF_OR %>%
  arrange(theme, id) %>%
  mutate (pos = row_number()) %>%
  group_by(theme) %>%
  summarise(center = (max(pos) + min(pos)) /2)

p = DF_OR_32 %>%
  arrange(theme, id) %>%
  mutate (pos = row_number()) %>%
  ggplot() +
  aes(x = pos, y = -log10(p), variable = Variable) +
  geom_point(aes(color = theme), alpha = 0.8, size = 1.3) +
  scale_color_manual(values = rep(c("grey", "skyblue"), 5)[1:9]) +
  scale_x_continuous(label = axis_df$theme,
                     breaks = axis_df$center, guide = guide_axis(angle = 45)) +
  ggrepel::geom_label_repel(data = subset(DF_OR_32%>%
                                            arrange(theme, id) %>%
                                            mutate (pos = row_number(),
                                                    theme = as.factor(theme)),
                                          -log10(p) > 61),
                            aes(label = Variable), size = 3) +
  theme_bw() +
  # geom_point(data = subset(DF_OR %>%
  #                            arrange(theme, id) %>%
  #                            mutate (pos = row_number(),
  #                                    theme = as.factor(theme)) %>% filter(p < 0.0001/dim(DF_OR)[1])), color = "orange", size = 2) +
  theme(legend.position = "none",
        panel.border = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  labs(title = paste("Manhattan plot on the P-value week ", week),
       x = "")

plotly::ggplotly(p)

ggsave(filename = "manh_p_32.png", path = "plots")
```

# Données à la date souhaitée

```{r}
make_data_covid = function(wk){
  vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
    rename(codgeo = commune_residence) %>%
    select(codgeo, taux_cumu_1_inj) %>%
    mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))

  vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
    rename(codgeo = epci) %>%
    select(codgeo, taux_cumu_1_inj) %>%
    mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
    plyr::rbind.fill(vacc_com)

  LOG_1107 = LOG_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
  EMP_1107 = EMP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
  FAM_1107 = FAM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
  REV_1107 = REV_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
  ACT_1107 = ACT_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
  FOR_1107 = FOR_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
  POP_1107 = POP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
  IMM_1107 = IMM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
  GEO_1107 = GEO_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))

  LOG_OR_1107 = questionr::odds.ratio(LOG_1107$`1ry_res`, LOG_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(LOG_1107$`2ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Vacant_Home`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Houses`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Flats`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Nb_Rooms_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`House_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Flat_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_bf_1919`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_19-45`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_46-70`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_71-90`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_91-05`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_06-15`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_lt2y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_2to4y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_5to9y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_10to19y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_20to29y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_gt30y`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Carpark`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_0car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_1car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_2car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_3+car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_gt0car`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Owners_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Tenant_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Social_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`FreeAcc_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(LOG_1107$`Overcrowding_rate`, LOG_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(LOG_1107)[2:42]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(LOG_OR) = NULL
  # write_csv2(LOG_OR, "data/LOG_OR.csv")

  EMP_OR_1107 = questionr::odds.ratio(EMP_1107$`1564_Workforce_rate`, EMP_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1524_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`2554_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`5564_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1524_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`2554_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`5564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1524_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`2554_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`5564_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1524_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`2554_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`5564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1524_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`2554_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`5564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1524_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`2554_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`5564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1524_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`2554_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`5564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_Student_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_Retired_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_OtherInactive_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_Student_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_Retired_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_OtherInactive_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_POP`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_Farmers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_CraftsBusinessShopkeepers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_HihgQualWorkers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_IntermediateProf_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_BlueCollar_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_WhiteCollar_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_Farmers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_CraftsBusinessShopkeepers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_HihgQualWorkers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_IntermediateProf_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_BlueCollar_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`1564_WhiteCollar_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_Salaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_NonSalaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(EMP_1107)[2:63]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(EMP_OR) = NULL
  # write_csv2(EMP_OR, "data/EMP_OR.csv")

  FAM_OR_1107 = questionr::odds.ratio(FAM_1107$`SinglePerson_HH`, FAM_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(FAM_1107$`SingleMan_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`SingleWoman_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Farmer_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`HighQualidied_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Intermediate_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`WhiteCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`15+_SinglePerson_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleMan_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleWoman_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_Farmer_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_HighQualidied_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_Intermediate_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_WhiteCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Pop_Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`15+_Single_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`15+_Married_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`15+_nonMarried_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Family_w_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Single_Parent_Family_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FAM_1107$`Family_wo_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(FAM_1107)[2:51]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(FAM_OR) = NULL
  # write_csv2(FAM_OR, "data/FAM_OR.csv")

  REV_OR_1107 = questionr::odds.ratio(REV_1107$`D1_st_Living`, REV_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(REV_1107$`Median_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`D9_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Interdecile_91_Ratio`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Taxable_HH`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Owners`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Tenants`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`-30_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`3039_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`4049_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`5059_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`6074_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`75+_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Poverty`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Activity_Income`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Salary_Income`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Unemployment_Benef`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Self-Employment`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Pensions_Annuities`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Estate`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Social_Benef`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Family_Benef`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Social_Minima`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Housing_Benef`, REV_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(REV_1107$`Tax`, REV_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(REV_1107)[2:26]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(REV_OR) = NULL
  # write_csv2(REV_OR, "data/REV_OR.csv")

  ACT_OR_1107 = questionr::odds.ratio(ACT_1107$`Wk_Res_Municipality`, ACT_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_County-Municipality`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_Region-County`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_Country-Region`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Wk_Dom_Com_Abroad`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`noTransport_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Walk_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Bike_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Motorbike_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`Drive_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`PublicTrans_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`15+_Men_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`15+_Women_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`15+_PermanentContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`15+_ShortTermContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`15+_InterimContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`15+_SubsidizedWork_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`15+_ApprenticeContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`15+_SelfEmployed_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`15+_Employers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(ACT_1107$`15+_caregivers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(ACT_1107)[2:22]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(ACT_OR) = NULL
  # write_csv2(ACT_OR, "data/ACT_OR.csv")

  FOR_OR_1107 = questionr::odds.ratio(FOR_1107$`0205_School`, FOR_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(FOR_1107$`0610_School`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`1114_School`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`1517_School`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`1824_School`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`2529_School`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`30+_School`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_NoDiploma_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_CertifGeneEducation_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_VocationalGraduate_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_HighSchoolGraduate_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+2_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+4_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+5+_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_HighEducation_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_men_NoDiploma_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_men_VocationalGraduate_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_men_HighSchoolGraduate_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_men_HighEducation_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_women_NoDiploma_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_women_VocationalGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighSchoolGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighEducation_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_NoDiploma`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_VocationalGraduate`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_HighSchoolGraduate`, FOR_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_HighEducation`, FOR_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(FOR_1107)[2:28]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(FOR_OR) = NULL
  # write_csv2(FOR_OR, "data/FOR_OR.csv")

  POP_OR_1107 = questionr::odds.ratio(POP_1107$`0014_amg_POP`, POP_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(POP_1107$`1529_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`3044_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`4559_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`6074_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`7589_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`90+_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`Men`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`0019_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`2064_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`65+_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_Farmers_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_CraftsBusinessShopkeeper_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_ManagersHigherIntellectProf_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_IntermediateProf_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_WhiteCollar_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_BlueCollar_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_Retired_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_OtherNoActivity_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`0014_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`1529_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`3044_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`4559_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`6074_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`7589_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`90+_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`0019_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`2064_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`65+_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_men_Farmers_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_men_CraftsBusinessShopkeeper_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_men_ManagersHigherIntellectProf_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_men_IntermediateProf_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_men_WhiteCollar_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_men_BlueCollar_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_men_Retired_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_men_OtherNoActivity_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`0014_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`1529_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`3044_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`4559_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`6074_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`7589_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`90+_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`0019_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`2064_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`65+_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_women_Farmers_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_women_CraftsBusinessShopkeeper_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_women_ManagersHigherIntellectProf_amh_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_women_IntermediateProf_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_women_WhiteCollar_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_women_BlueCollar_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_women_Retired_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(POP_1107$`15+_women_OtherNoActivity_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(POP_1107)[2:56]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(POP_OR) = NULL
  # write_csv2(POP_OR, "data/POP_OR.csv")

  IMM_OR_1107 = questionr::odds.ratio(IMM_1107$`French_nlty`, IMM_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(IMM_1107$`Stranger`, IMM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(IMM_1107$`Immigrant`, IMM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(IMM_1107$`French_nlty_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(IMM_1107$`French_nlty_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(IMM_1107$`Res_Abroad_2017`, IMM_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(IMM_1107)[2:11]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(IMM_OR) = NULL
  # write_csv2(IMM_OR, "data/IMM_OR.csv")

  GEO_OR_1107 = questionr::odds.ratio(GEO_1107$latitude, GEO_1107$taux_cumu_1_inj) %>%
    rbind(questionr::odds.ratio(GEO_1107$longitude, GEO_1107$taux_cumu_1_inj)) %>%
    rbind(questionr::odds.ratio(GEO_1107$densite, GEO_1107$taux_cumu_1_inj)) %>%
    as.data.frame() %>%
    bind_cols(Variable = colnames(GEO_1107)[2:4]) %>%
    select(Variable, OR, `2.5 %`, `97.5 %`, p)
  rownames(GEO_OR) = NULL
  # write_csv2(GEO_OR, "data/GEO_OR.csv")

  DF_OR_1107 = LOG_OR_1107 %>% mutate(theme = "Logement", .after = Variable) %>%
    bind_rows(EMP_OR_1107 %>% mutate(theme = "Emploi", .after = Variable)) %>%
    bind_rows(FAM_OR_1107 %>% mutate(theme = "Famille", .after = Variable)) %>%
    bind_rows(REV_OR_1107 %>% mutate(theme = "Revenus", .after = Variable)) %>%
    bind_rows(ACT_OR_1107 %>% mutate(theme = "Activite", .after = Variable)) %>%
    bind_rows(FOR_OR_1107 %>% mutate(theme = "Formation", .after = Variable)) %>%
    bind_rows(POP_OR_1107 %>% mutate(theme = "Population", .after = Variable)) %>%
    bind_rows(IMM_OR_1107 %>% mutate(theme = "Immigration", .after = Variable)) %>%
    bind_rows(GEO_OR_1107 %>% mutate(theme = "Geographie", .after = Variable)) %>%
    group_by(theme) %>%
    mutate(id = row_number()) %>%
    ungroup() %>%
    mutate(inv_OR = 1/OR,
           `inv_2.5 %` = 1/`97.5 %`,
           `inv_97.5 %` = 1/`2.5 %`,
           `is_OR_>1` = OR > inv_OR,
           `max_OR-inv_OR` = if_else(`is_OR_>1`, OR, inv_OR)) %>%
    arrange(desc(`max_OR-inv_OR`))
  write_csv(DF_OR_1107, paste0("data/DF_OR_", wk, ".csv"))
}
```

### 2021-09-08 code/manhattan_animated.Rmd
Add code
code for API extraction, data transformation and manhattan plot (animated or not)

---
title: "Manhattan Plot"
author: "Emmanuel LECOEUR"
date: "03/09/2021"
output: html_document
---

```{r, echo = F, message = F, warning = F}
library(tidyverse)
library(plotly)
library(gapminder)
```

```{r, echo = F, message = F, warning = F}
df_OR = read_csv("data/DF_OR_27.csv") %>%
  arrange(theme, id) %>%
  mutate (pos = row_number(),
          week = 27) %>%
  bind_rows(read_csv("data/DF_OR_32.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 32)) %>%
  bind_rows(read_csv("data/DF_OR_05.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 05)) %>%
  bind_rows(read_csv("data/DF_OR_07.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 07)) %>%
  bind_rows(read_csv("data/DF_OR_09.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 09)) %>%
  bind_rows(read_csv("data/DF_OR_11.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 11)) %>%
  bind_rows(read_csv("data/DF_OR_12.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 12)) %>%
  bind_rows(read_csv("data/DF_OR_15.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 15)) %>%
  bind_rows(read_csv("data/DF_OR_17.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 17)) %>%
  bind_rows(read_csv("data/DF_OR_19.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 19)) %>%
  bind_rows(read_csv("data/DF_OR_21.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 21)) %>%
  bind_rows(read_csv("data/DF_OR_24.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 24)) %>%
  bind_rows(read_csv("data/DF_OR_23.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 23)) %>%
  bind_rows(read_csv("data/DF_OR_26.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 26)) %>%
  bind_rows(read_csv("data/DF_OR_29.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 29)) %>%
  bind_rows(read_csv("data/DF_OR_30.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 30)) %>%
  bind_rows(read_csv("data/DF_OR_32.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 32)) %>%
  bind_rows(read_csv("data/DF_OR_02.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 02)) %>%
  bind_rows(read_csv("data/DF_OR_04.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 04)) %>%
  bind_rows(read_csv("data/DF_OR_14.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 14)) %>%
  bind_rows(read_csv("data/DF_OR_18.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 18)) %>%
  bind_rows(read_csv("data/DF_OR_31.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 31)) %>%
  bind_rows(read_csv("data/DF_OR_33.csv") %>%
              arrange(theme, id) %>%
              mutate (pos = row_number(),
                        week = 33)) %>%
  mutate(`is_OR_>1` = if_else(`is_OR_>1`, "OR", "1/OR"))
```

```{r}
df_OR %>%
  filter(week == 33) %>%
  arrange(OR) %>%
  mutate(pos2 = row_number()) %>%
  select(Variable, pos2) %>%
  inner_join(df_OR)
```

Pour construire les graphiques suivants, chaque variable a été dichotomisée par rapport à la médiane (`1` pour supérieur à la médiane et `0` pour inférieur à la médiane).

Pour chaque semaine de l'année 2021, les 25 % des territoires les moins vaccinés sont étiquetés `1` et les autres `0`.

On calcule l'odds ratio pour chaque variable. Cela permet de repérer les variables qui agissent le plus sur le taux de vaccination.

Dans ls graphique suivants, chaque variable a une position fixe sur l'axe des abscisses.

L'axe des ordonnées représente le maximum entre l'odds ratio et son inverse. Ainsi une variable qui agit fortement sur le taux de vaccination aura une position élevée sur le graphque indépendamment de l'influence positive ou négative de son influence. Les variables sont classées par thématique.

La grosseur de chaque point est proportionnelle à l'opposé du logarithme de la p-value.

Puis pour connaitre l'influebce de chaque variable, on ne trace uniquement l'odds ratio et enfin son inverse.

```{r, echo = F, message = F, warning = F}
fig = df_OR %>%
  filter(week == 33) %>%
  arrange(OR) %>%
  mutate(pos2 = row_number()) %>%
  select(Variable, pos) %>%
  inner_join(df_OR) %>%
  plot_ly(
    x = ~pos,
    y = ~`max_OR-inv_OR`,
    size = ~-log10(p),
    color = ~theme,
    frame = ~week,
    text = ~Variable,
    hooverinfo = "text",
    type = "scatter",
    mode = "markers"
  )
fig
```

```{r, echo = F, message = F, warning = F}
fig = df_OR %>%
  filter(week == 33) %>%
  arrange(OR) %>%
  mutate(pos2 = row_number()) %>%
  select(Variable, pos2) %>%
  inner_join(df_OR) %>%
  plot_ly(
    x = ~pos2,
    y = ~`OR`,
    size = ~-log10(p),
    color = ~theme,
    frame = ~week,
    text = ~Variable,
    hooverinfo = "text",
    type = "scatter",
    mode = "markers"
  )
fig
```

```{r, echo = F, message = F, warning = F}
fig = df_OR %>%
  filter(week == 33) %>%
  arrange(OR) %>%
  mutate(pos2 = row_number()) %>%
  select(Variable, pos2) %>%
  inner_join(df_OR) %>%
  plot_ly(
    x = ~pos2,
    y = ~`inv_OR`,
    size = ~-log10(p),
    color = ~theme,
    frame = ~week,
    text = ~Variable,
    hooverinfo = "text",
    type = "scatter",
    mode = "markers"
  )
fig
```

### 2021-09-08 code/INSEE_vaccination_COVID.Rmd
update code and fix bugs

@@
 
-GEO_fact = GEO %>%
-  filter(codgeo %in% c(GEO_gua$SIREN_EPCI, GEO_guy$SIREN_EPCI, GEO_mar$SIREN_EPCI, GEO_may$SIREN, GEO_reu$SIREN_EPCI)) %>%
-  select(-c(latitude, longitude)) %>%
-  plyr::rbind.fill(GEO %>%
-                     filter(!(codgeo %in% c(GEO_gua$SIREN_EPCI, GEO_guy$SIREN_EPCI, GEO_mar$SIREN_EPCI, GEO_may$SIREN, GEO_reu$SIREN_EPCI)))) %>%
+GEO_OM$lat01 <- (GEO_OM$latitude - min(GEO_OM$latitude, na.rm = T)) / (max(GEO_OM$latitude, na.rm = T) - min(GEO_OM$latitude, na.rm = T))
+GEO_OM$lon01 <- (GEO_OM$longitude - min(GEO_OM$longitude, na.rm = T)) / (max(GEO_OM$longitude, na.rm = T) - min(GEO_OM$longitude, na.rm = T))
+
+GEO_OM = GEO_OM %>%
+  mutate(`SO-NE` = lat01+lon01,
+         `NO-SE` = lon01-lat01)
+
+GEO_fact = GEO_OM %>%
   select(codgeo, latitude, longitude, densite, taux_cumu_1_inj) %>%
@@
   rbind(questionr::odds.ratio(GEO_fact$densite, GEO_fact$taux_cumu_1_inj)) %>%
+  rbind(questionr::odds.ratio(GEO_fact$`SO-NE`, GEO_fact$taux_cumu_1_inj)) %>%
+  rbind(questionr::odds.ratio(GEO_fact$`NO-SE`, GEO_fact$taux_cumu_1_inj)) %>%
   as.data.frame() %>%
-  bind_cols(Variable = colnames(GEO_fact)[2:4]) %>%
+  bind_cols(Variable = colnames(GEO_fact)[2:6]) %>%
   select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
 make_data_covid = function(wk){
+
+  if (wk/10 <1){
+    wk = paste0("0", wk)
+  }
+
   vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
@@
     rbind(questionr::odds.ratio(GEO_1107$densite, GEO_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(GEO_fact$`SO-NE`, GEO_fact$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(GEO_fact$`NO-SE`, GEO_fact$taux_cumu_1_inj)) %>%
     as.data.frame() %>%
-    bind_cols(Variable = colnames(GEO_1107)[2:4]) %>%
+    bind_cols(Variable = colnames(GEO_1107)[2:6]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)

### 2021-09-08 code/manhattan_animated.Rmd
update code and fix bugs

@@
 ```{r, echo = F, message = F, warning = F}
-df_OR = read_csv("data/DF_OR_27.csv") %>%
+LOG_fact = read_csv("data/LOG_fact.csv", col_type = list(.default = col_factor()))
+EMP_fact = read_csv("data/EMP_fact.csv", col_type = list(.default = col_factor()))
+ACT_fact = read_csv("data/ACT_fact.csv", col_type = list(.default = col_factor()))
+REV_fact = read_csv("data/REV_fact.csv", col_type = list(.default = col_factor()))
+POP_fact = read_csv("data/POP_fact.csv", col_type = list(.default = col_factor()))
+FOR_fact = read_csv("data/FOR_fact.csv", col_type = list(.default = col_factor()))
+IMM_fact = read_csv("data/IMM_fact.csv", col_type = list(.default = col_factor()))
+GEO_fact = read_csv("data/GEO_fact.csv", col_type = list(.default = col_factor()))
+FAM_fact = read_csv("data/FAM_fact.csv", col_type = list(.default = col_factor()))
+```
+
+```{r, echo = F, message = F, warning = F}
+binarisation = function(liste, q = 0.5){
+  mediane = quantile(liste, q, na.rm = T)[[1]]
+  return(as.factor(simplify2array(lapply(liste-mediane,
+                                         function(x){if_else(x < 0, 0, 1)}))))
+}
+
+make_data_covid = function(wk){
+
+  if (wk/10 <1){
+    wk = paste0("0", wk)
+  }
+
+  vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+    mutate(codgeo = as.factor(commune_residence)) %>%
+    select(codgeo, taux_cumu_1_inj) %>%
+    mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
+
+  vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+    mutate(codgeo = as.factor(epci)) %>%
+    select(codgeo, taux_cumu_1_inj) %>%
+    mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+    plyr::rbind.fill(vacc_com)
+
+  LOG_1107 = LOG_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+  EMP_1107 = EMP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+  FAM_1107 = FAM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+  REV_1107 = REV_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+  ACT_1107 = ACT_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+  FOR_1107 = FOR_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+  POP_1107 = POP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+  IMM_1107 = IMM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+  GEO_1107 = GEO_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+
+  LOG_OR_1107 = questionr::odds.ratio(LOG_1107$`1ry_res`, LOG_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`2ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Vacant_Home`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Houses`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Flats`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Nb_Rooms_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`House_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Flat_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_bf_1919`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_19-45`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_46-70`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_71-90`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_91-05`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_06-15`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_lt2y`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_2to4y`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_5to9y`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_10to19y`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_20to29y`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_gt30y`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Carpark`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_0car`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_1car`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_2car`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_3+car`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_gt0car`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Owners_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Tenant_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Social_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`FreeAcc_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Overcrowding_rate`, LOG_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(LOG_1107)[2:42]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(LOG_OR_1107) = NULL
+  # write_csv2(LOG_OR, "data/LOG_OR.csv")
+
+  EMP_OR_1107 = questionr::odds.ratio(EMP_1107$`1564_Workforce_rate`, EMP_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1524_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`2554_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`5564_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1524_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`2554_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`5564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1524_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`2554_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`5564_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1524_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`2554_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`5564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1524_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`2554_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`5564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1524_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`2554_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`5564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1524_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`2554_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`5564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_Student_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_Retired_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_OtherInactive_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_Student_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_Retired_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_OtherInactive_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_POP`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_Farmers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_CraftsBusinessShopkeepers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_HihgQualWorkers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_IntermediateProf_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_BlueCollar_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_WhiteCollar_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_Farmers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_CraftsBusinessShopkeepers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_HihgQualWorkers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_IntermediateProf_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_BlueCollar_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_WhiteCollar_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_Salaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_NonSalaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(EMP_1107)[2:63]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(EMP_OR_1107) = NULL
+  # write_csv2(EMP_OR, "data/EMP_OR.csv")
+
+  FAM_OR_1107 = questionr::odds.ratio(FAM_1107$`SinglePerson_HH`, FAM_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`SingleMan_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`SingleWoman_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Farmer_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`HighQualidied_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Intermediate_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`WhiteCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`15+_SinglePerson_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleMan_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleWoman_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_Farmer_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_HighQualidied_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_Intermediate_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_WhiteCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`15+_Single_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`15+_Married_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`15+_nonMarried_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Family_w_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Single_Parent_Family_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Family_wo_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(FAM_1107)[2:51]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(FAM_OR_1107) = NULL
+  # write_csv2(FAM_OR, "data/FAM_OR.csv")
+
+  REV_OR_1107 = questionr::odds.ratio(REV_1107$`D1_st_Living`, REV_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Median_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`D9_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Interdecile_91_Ratio`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Taxable_HH`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Owners`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Tenants`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`-30_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`3039_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`4049_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`5059_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`6074_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`75+_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Activity_Income`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Salary_Income`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Unemployment_Benef`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Self-Employment`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Pensions_Annuities`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Estate`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Social_Benef`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Family_Benef`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Social_Minima`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Housing_Benef`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Tax`, REV_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(REV_1107)[2:26]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(REV_OR_1107) = NULL
+  # write_csv2(REV_OR, "data/REV_OR.csv")
+
+  ACT_OR_1107 = questionr::odds.ratio(ACT_1107$`Wk_Res_Municipality`, ACT_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_County-Municipality`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_Region-County`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_Country-Region`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`Wk_Dom_Com_Abroad`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`noTransport_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`Walk_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`Bike_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`Motorbike_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`Drive_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`PublicTrans_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_Men_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_Women_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_PermanentContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_ShortTermContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_InterimContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_SubsidizedWork_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_ApprenticeContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_SelfEmployed_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_Employers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_caregivers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(ACT_1107)[2:22]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(ACT_OR_1107) = NULL
+  # write_csv2(ACT_OR, "data/ACT_OR.csv")
+
+  FOR_OR_1107 = questionr::odds.ratio(FOR_1107$`0205_School`, FOR_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`0610_School`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`1114_School`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`1517_School`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`1824_School`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`2529_School`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`30+_School`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_NoDiploma_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_CertifGeneEducation_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_VocationalGraduate_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_HighSchoolGraduate_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+2_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+4_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+5+_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_HighEducation_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_men_NoDiploma_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_men_VocationalGraduate_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_men_HighSchoolGraduate_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_men_HighEducation_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_women_NoDiploma_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_women_VocationalGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighSchoolGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighEducation_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_NoDiploma`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_VocationalGraduate`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_HighSchoolGraduate`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_HighEducation`, FOR_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(FOR_1107)[2:28]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(FOR_OR_1107) = NULL
+  # write_csv2(FOR_OR, "data/FOR_OR.csv")
+
+  POP_OR_1107 = questionr::odds.ratio(POP_1107$`0014_amg_POP`, POP_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(POP_1107$`1529_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`3044_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`4559_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`6074_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`7589_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`90+_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`Men`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`0019_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`2064_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`65+_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_Farmers_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_CraftsBusinessShopkeeper_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_ManagersHigherIntellectProf_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_IntermediateProf_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_WhiteCollar_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_BlueCollar_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_Retired_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_OtherNoActivity_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`0014_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`1529_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`3044_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`4559_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`6074_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`7589_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`90+_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`0019_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`2064_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`65+_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_men_Farmers_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_men_CraftsBusinessShopkeeper_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_men_ManagersHigherIntellectProf_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_men_IntermediateProf_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_men_WhiteCollar_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_men_BlueCollar_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_men_Retired_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_men_OtherNoActivity_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`0014_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`1529_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`3044_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`4559_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`6074_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`7589_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`90+_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`0019_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`2064_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`65+_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_women_Farmers_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_women_CraftsBusinessShopkeeper_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_women_ManagersHigherIntellectProf_amh_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_women_IntermediateProf_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_women_WhiteCollar_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_women_BlueCollar_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_women_Retired_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_women_OtherNoActivity_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(POP_1107)[2:56]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(POP_OR_1107) = NULL
+  # write_csv2(POP_OR, "data/POP_OR.csv")
+
+  IMM_OR_1107 = questionr::odds.ratio(IMM_1107$`French_nlty`, IMM_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`Stranger`, IMM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`Immigrant`, IMM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`French_nlty_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`French_nlty_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`Res_Abroad_2017`, IMM_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(IMM_1107)[2:11]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(IMM_OR_1107) = NULL
+  # write_csv2(IMM_OR, "data/IMM_OR.csv")
+
+  GEO_OR_1107 = questionr::odds.ratio(GEO_1107$latitude, GEO_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(GEO_1107$longitude, GEO_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(GEO_1107$densite, GEO_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(GEO_fact$`SO-NE`, GEO_fact$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(GEO_fact$`NO-SE`, GEO_fact$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(GEO_1107)[2:6]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(GEO_OR_1107) = NULL
+  # write_csv2(GEO_OR, "data/GEO_OR.csv")
+
+  DF_OR_1107 = LOG_OR_1107 %>% mutate(theme = "Logement", .after = Variable) %>%
+    bind_rows(EMP_OR_1107 %>% mutate(theme = "Emploi", .after = Variable)) %>%
+    bind_rows(FAM_OR_1107 %>% mutate(theme = "Famille", .after = Variable)) %>%
+    bind_rows(REV_OR_1107 %>% mutate(theme = "Revenus", .after = Variable)) %>%
+    bind_rows(ACT_OR_1107 %>% mutate(theme = "Activite", .after = Variable)) %>%
+    bind_rows(FOR_OR_1107 %>% mutate(theme = "Formation", .after = Variable)) %>%
+    bind_rows(POP_OR_1107 %>% mutate(theme = "Population", .after = Variable)) %>%
+    bind_rows(IMM_OR_1107 %>% mutate(theme = "Immigration", .after = Variable)) %>%
+    bind_rows(GEO_OR_1107 %>% mutate(theme = "Geographie", .after = Variable)) %>%
+    group_by(theme) %>%
+    mutate(id = row_number()) %>%
+    ungroup() %>%
+    mutate(inv_OR = 1/OR,
+           `inv_2.5 %` = 1/`97.5 %`,
+           `inv_97.5 %` = 1/`2.5 %`,
+           `is_OR_>1` = OR > inv_OR,
+           `max_OR-inv_OR` = if_else(`is_OR_>1`, OR, inv_OR)) %>%
+    arrange(desc(`max_OR-inv_OR`))
+  return(DF_OR_1107)
+}
+```
+
+```{r, echo = F, message = F, warning = F}
+data = NULL
+for (i in 2:33){
+  data = bind_rows(
+    data,
+    make_data_covid(i) %>%
       arrange(theme, id) %>%
       mutate (pos = row_number(),
-          week = 27) %>%
-  bind_rows(read_csv("data/DF_OR_32.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 32)) %>%
-  bind_rows(read_csv("data/DF_OR_05.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 05)) %>%
-  bind_rows(read_csv("data/DF_OR_07.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 07)) %>%
-  bind_rows(read_csv("data/DF_OR_09.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 09)) %>%
-  bind_rows(read_csv("data/DF_OR_11.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 11)) %>%
-  bind_rows(read_csv("data/DF_OR_12.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 12)) %>%
-  bind_rows(read_csv("data/DF_OR_15.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 15)) %>%
-  bind_rows(read_csv("data/DF_OR_17.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 17)) %>%
-  bind_rows(read_csv("data/DF_OR_19.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 19)) %>%
-  bind_rows(read_csv("data/DF_OR_21.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 21)) %>%
-  bind_rows(read_csv("data/DF_OR_24.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 24)) %>%
-  bind_rows(read_csv("data/DF_OR_23.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 23)) %>%
-  bind_rows(read_csv("data/DF_OR_26.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 26)) %>%
-  bind_rows(read_csv("data/DF_OR_29.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 29)) %>%
-  bind_rows(read_csv("data/DF_OR_30.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 30)) %>%
-  bind_rows(read_csv("data/DF_OR_32.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 32)) %>%
-  bind_rows(read_csv("data/DF_OR_02.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 02)) %>%
-  bind_rows(read_csv("data/DF_OR_04.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 04)) %>%
-  bind_rows(read_csv("data/DF_OR_14.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 14)) %>%
-  bind_rows(read_csv("data/DF_OR_18.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 18)) %>%
-  bind_rows(read_csv("data/DF_OR_31.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 31)) %>%
-  bind_rows(read_csv("data/DF_OR_33.csv") %>%
-              arrange(theme, id) %>%
-              mutate (pos = row_number(),
-                        week = 33)) %>%
-  mutate(`is_OR_>1` = if_else(`is_OR_>1`, "OR", "1/OR"))
-```
-
-```{r}
-df_OR %>%
-  filter(week == 33) %>%
-  arrange(OR) %>%
-  mutate(pos2 = row_number()) %>%
-  select(Variable, pos2) %>%
-  inner_join(df_OR)
+              week = i)
+  )
+}
 ```
@@
 ```{r, echo = F, message = F, warning = F}
-fig = df_OR %>%
+fig = data %>%
   filter(week == 33) %>%
@@
   select(Variable, pos) %>%
-  inner_join(df_OR) %>%
+  inner_join(data) %>%
   plot_ly(
@@
   select(Variable, pos2) %>%
-  inner_join(df_OR) %>%
+  inner_join(data) %>%
   plot_ly(

### 2021-09-10 code/manhattan_animated.Rmd
update manhattan_animated.RMD
add median and IQR for each variable
add non cumulated animations for whole
add cumulative animations by age

@@
 library(gapminder)
+library(desctable)
+library(pander)
 ```
@@
 
-make_data_covid = function(wk){
+make_data_covid = function(wk, variable = "taux_cumu_1_inj", classe_age = "tous"){
 
@@
 
+  if (classe_age == "tous"){
     vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
       mutate(codgeo = as.factor(commune_residence)) %>%
-    select(codgeo, taux_cumu_1_inj) %>%
       mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
@@
       mutate(codgeo = as.factor(epci)) %>%
-    select(codgeo, taux_cumu_1_inj) %>%
       mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
       plyr::rbind.fill(vacc_com)
+  }else{
+    vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", classe_age, "&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+      mutate(codgeo = as.factor(commune_residence)) %>%
+      mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
 
+    vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&refine.classe_age=", classe_age, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+      mutate(codgeo = as.factor(epci)) %>%
+      mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+      plyr::rbind.fill(vacc_com)
+  }
+
+  vacc$taux_cumu_1_inj[is.na(vacc$taux_cumu_1_inj)] <- 0
+
+  if (variable == "taux_cumu_1_inj"){
     LOG_1107 = LOG_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
@@
     GEO_1107 = GEO_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+  }else if (variable == "taux_1_inj"){
+    LOG_1107 = LOG_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+    EMP_1107 = EMP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+    FAM_1107 = FAM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+    REV_1107 = REV_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+    ACT_1107 = ACT_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+    FOR_1107 = FOR_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+    POP_1107 = POP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+    IMM_1107 = IMM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+    GEO_1107 = GEO_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+  }
 
@@
     rbind(questionr::odds.ratio(GEO_1107$densite, GEO_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(GEO_fact$`SO-NE`, GEO_fact$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(GEO_fact$`NO-SE`, GEO_fact$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(GEO_1107$`SO-NE`, GEO_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(GEO_1107$`NO-SE`, GEO_1107$taux_cumu_1_inj)) %>%
     as.data.frame() %>%
@@
 
+# les territoires étudiés
+
+## Les EPCI
+
 ```{r, echo = F, message = F, warning = F}
-data = NULL
-for (i in 2:33){
-  data = bind_rows(
-    data,
-    make_data_covid(i) %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
-  )
-}
+read.csv2("data/POP.csv") %>%
+  select(codgeo, SEXE.AGE15_15_90_POP_ENS_ENS) %>%
+  rename(Population = SEXE.AGE15_15_90_POP_ENS_ENS) %>%
+  select(Population) %>%
+  desctable(stats = list("N" = length, "Mean" = mean)) %>%
+  pander()
 ```
+## Les communes des métropoles de Paris, Lyon, Marseille
+
+```{r, echo = F, message = F, warning = F}
+read.csv2("data/com_POP.csv") %>%
+  select(codgeo, SEXE.AGE15_15_90_POP_ENS_ENS) %>%
+  rename(Population = SEXE.AGE15_15_90_POP_ENS_ENS) %>%
+  select(Population) %>%
+  desctable(stats = list("N" = length, "Mean" = mean)) %>%
+  pander()
+```
+
+# Les variables utilisées pour l'étude
+
+## Thématique Logement
+
+```{r, echo = F, message = F, warning = F}
+read.csv2("data/LOG_brut.csv") %>%
+  select(-c(codgeo, taux_cumu_1_inj)) %>%
+  desctable(stats = list("N" = length, "Med" = median, "IQR" = IQR)) %>%
+  pander()
+```
+
+## Thématique Emploi
+
+```{r, echo = F, message = F, warning = F}
+read.csv2("data/EMP_brut.csv") %>%
+  select(-c(codgeo, taux_cumu_1_inj)) %>%
+  desctable(stats = list("N" = length, "Med" = median, "IQR" = IQR)) %>%
+  pander()
+```
+
+## Thématique Famille
+
+```{r, echo = F, message = F, warning = F}
+read.csv2("data/FAM_brut.csv") %>%
+  select(-c(codgeo, taux_cumu_1_inj)) %>%
+  desctable(stats = list("N" = length, "Med" = median, "IQR" = IQR)) %>%
+  pander()
+```
+
+## Thématique Revenus
+
+```{r, echo = F, message = F, warning = F}
+read.csv2("data/REV_brut.csv") %>%
+  select(-c(codgeo, taux_cumu_1_inj)) %>%
+  desctable(stats = list("N" = length, "Med" = median, "IQR" = IQR)) %>%
+  pander()
+```
+
+## Thématique Activité
+
+```{r, echo = F, message = F, warning = F}
+read.csv2("data/ACT_brut.csv") %>%
+  select(-c(codgeo, taux_cumu_1_inj)) %>%
+  desctable(stats = list("N" = length, "Med" = median, "IQR" = IQR)) %>%
+  pander()
+```
+
+## Thématique Formation
+
+```{r, echo = F, message = F, warning = F}
+read.csv2("data/FOR_brut.csv") %>%
+  select(-c(codgeo, taux_cumu_1_inj)) %>%
+  desctable(stats = list("N" = length, "Med" = median, "IQR" = IQR)) %>%
+  pander()
+```
+
+## Thématique Population
+
+```{r, echo = F, message = F, warning = F}
+read.csv2("data/POP_brut.csv") %>%
+  select(-c(codgeo, taux_cumu_1_inj)) %>%
+  desctable(stats = list("N" = length, "Med" = median, "IQR" = IQR)) %>%
+  pander()
+```
+
+## Thématique Logement
+
+```{r, echo = F, message = F, warning = F}
+read.csv2("data/LOG_brut.csv") %>%
+  select(-c(codgeo, taux_cumu_1_inj)) %>%
+  desctable(stats = list("N" = length, "Med" = median, "IQR" = IQR)) %>%
+  pander()
+```
+
+## Thématique Immigration
+
+```{r, echo = F, message = F, warning = F}
+read.csv2("data/IMM_brut.csv") %>%
+  select(-c(codgeo, taux_cumu_1_inj)) %>%
+  desctable(stats = list("N" = length, "Med" = median, "IQR" = IQR)) %>%
+  pander()
+```
+
+## Thématique Géographie
+
+```{r, echo = F, message = F, warning = F}
+read.csv("data/GEO_brut.csv") %>%
+  select(-c(codgeo, taux_cumu_1_inj, X, SEXE.AGE3_B_POP_ENS_ENS, lat01, lon01, superficie)) %>%
+  desctable(stats = list("N" = length, "Med" = median, "IQR" = IQR)) %>%
+  pander()
+```
+
+# Manhattan
 
@@
 
-La grosseur de chaque point est proportionnelle à l'opposé du logarithme de la p-value.
+La grosseur de chaque point est proportionnelle à $-\log_{10}(p)$.
 
 Puis pour connaitre l'influebce de chaque variable, on ne trace uniquement l'odds ratio et enfin son inverse.
+
+## Données cumulées
+
+```{r, echo = F, message = F, warning = F}
+data = NULL
+for (i in 2:33){
+  data = bind_rows(
+    data,
+    make_data_covid(i) %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+```
 
@@
 fig = data %>%
+  filter(week == 27) %>%
+  arrange(OR) %>%
+  mutate(asc_OR = row_number()) %>%
+  select(Variable, asc_OR) %>%
+  inner_join(data) %>%
+  plot_ly(
+    x = ~asc_OR,
+    y = ~`max_OR-inv_OR`,
+    size = ~-log10(p),
+    color = ~theme,
+    frame = ~week,
+    text = ~Variable,
+    hooverinfo = "text",
+    type = "scatter",
+    mode = "markers"
+  )
+fig
+```
+
+## Données à la semaine non cumulées
+
+```{r, echo = F, message = F, warning = F}
+data = NULL
+for (i in 2:33){
+  data = bind_rows(
+    data,
+    make_data_covid(i, variable = "taux_1_inj") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+```
+
+```{r, echo = F, message = F, warning = F}
+fig = data %>%
   filter(week == 33) %>%
@@
   mutate(pos2 = row_number()) %>%
-  select(Variable, pos2) %>%
+  select(Variable, pos) %>%
   inner_join(data) %>%
   plot_ly(
-    x = ~pos2,
-    y = ~`OR`,
+    x = ~pos,
+    y = ~`max_OR-inv_OR`,
     size = ~-log10(p),
@@
 fig = data %>%
-  filter(week == 33) %>%
+  filter(week == 27) %>%
   arrange(OR) %>%
-  mutate(pos2 = row_number()) %>%
-  select(Variable, pos2) %>%
+  mutate(asc_OR = row_number()) %>%
+  select(Variable, asc_OR) %>%
   inner_join(data) %>%
   plot_ly(
-    x = ~pos2,
-    y = ~`inv_OR`,
+    x = ~asc_OR,
+    y = ~`max_OR-inv_OR`,
     size = ~-log10(p),
@@
 ```
+
+# Par classe d'âge
+
+## 0 - 19 ans
+
+```{r, echo = F, message = F, warning = F}
+data = NULL
+for (i in 18:33){
+  data = bind_rows(
+    data,
+    make_data_covid(i, classe_age = "00-19") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+
+# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
+#   filter(classe_age != "00-19") %>%
+#   group_by(epci) %>%
+#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
+#   ungroup()
+```
+
+```{r, echo = F, message = F, warning = F}
+fig = data %>%
+  filter(week == 33) %>%
+  arrange(OR) %>%
+  mutate(pos2 = row_number()) %>%
+  select(Variable, pos) %>%
+  inner_join(data) %>%
+  plot_ly(
+    x = ~pos,
+    y = ~`max_OR-inv_OR`,
+    size = ~-log10(p),
+    color = ~theme,
+    frame = ~week,
+    text = ~Variable,
+    hooverinfo = "text",
+    type = "scatter",
+    mode = "markers"
+  )
+fig
+```
+
+```{r, echo = F, message = F, warning = F}
+fig = data %>%
+  filter(week == 27) %>%
+  arrange(OR) %>%
+  mutate(asc_OR = row_number()) %>%
+  select(Variable, asc_OR) %>%
+  inner_join(data) %>%
+  plot_ly(
+    x = ~asc_OR,
+    y = ~`max_OR-inv_OR`,
+    size = ~-log10(p),
+    color = ~theme,
+    frame = ~week,
+    text = ~Variable,
+    hooverinfo = "text",
+    type = "scatter",
+    mode = "markers"
+  )
+fig
+```
+
+## 20 - 39 ans
+
+```{r, echo = F, message = F, warning = F}
+data = NULL
+for (i in 2:33){
+  data = bind_rows(
+    data,
+    make_data_covid(i, classe_age = "20-39") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+
+# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
+#   filter(classe_age != "00-19") %>%
+#   group_by(epci) %>%
+#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
+#   ungroup()
+```
+
+```{r, echo = F, message = F, warning = F}
+fig = data %>%
+  filter(week == 33) %>%
+  arrange(OR) %>%
+  mutate(pos2 = row_number()) %>%
+  select(Variable, pos) %>%
+  inner_join(data) %>%
+  plot_ly(
+    x = ~pos,
+    y = ~`max_OR-inv_OR`,
+    size = ~-log10(p),
+    color = ~theme,
+    frame = ~week,
+    text = ~Variable,
+    hooverinfo = "text",
+    type = "scatter",
+    mode = "markers"
+  )
+fig
+```
+
+```{r, echo = F, message = F, warning = F}
+fig = data %>%
+  filter(week == 27) %>%
+  arrange(OR) %>%
+  mutate(asc_OR = row_number()) %>%
+  select(Variable, asc_OR) %>%
+  inner_join(data) %>%
+  plot_ly(
+    x = ~asc_OR,
+    y = ~`max_OR-inv_OR`,
+    size = ~-log10(p),
+    color = ~theme,
+    frame = ~week,
+    text = ~Variable,
+    hooverinfo = "text",
+    type = "scatter",
+    mode = "markers"
+  )
+fig
+```
+
+## 40 - 54 ans
+
+```{r, echo = F, message = F, warning = F}
+data = NULL
+for (i in 2:33){
+  data = bind_rows(
+    data,
+    make_data_covid(i, classe_age = "40-54") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+
+# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
+#   filter(classe_age != "00-19") %>%
+#   group_by(epci) %>%
+#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
+#   ungroup()
+```
+
+```{r, echo = F, message = F, warning = F}
+fig = data %>%
+  filter(week == 33) %>%
+  arrange(OR) %>%
+  mutate(pos2 = row_number()) %>%
+  select(Variable, pos) %>%
+  inner_join(data) %>%
+  plot_ly(
+    x = ~pos,
+    y = ~`max_OR-inv_OR`,
+    size = ~-log10(p),
+    color = ~theme,
+    frame = ~week,
+    text = ~Variable,
+    hooverinfo = "text",
+    type = "scatter",
+    mode = "markers"
+  )
+fig
+```
+
+```{r, echo = F, message = F, warning = F}
+fig = data %>%
+  filter(week == 27) %>%
+  arrange(OR) %>%
+  mutate(asc_OR = row_number()) %>%
+  select(Variable, asc_OR) %>%
+  inner_join(data) %>%
+  plot_ly(
+    x = ~asc_OR,
+    y = ~`max_OR-inv_OR`,
+    size = ~-log10(p),
+    color = ~theme,
+    frame = ~week,
+    text = ~Variable,
+    hooverinfo = "text",
+    type = "scatter",
+    mode = "markers"
+  )
+fig
+```
+
+## 55 - 64 ans
+
+```{r, echo = F, message = F, warning = F}
+data = NULL
+for (i in 2:33){
+  data = bind_rows(
+    data,
+    make_data_covid(i, classe_age = "55-64") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+
+# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
+#   filter(classe_age != "00-19") %>%
+#   group_by(epci) %>%
+#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
+#   ungroup()
+```
+
+```{r, echo = F, message = F, warning = F}
+fig = data %>%
+  filter(week == 33) %>%
+  arrange(OR) %>%
+  mutate(pos2 = row_number()) %>%
+  select(Variable, pos) %>%
+  inner_join(data) %>%
+  plot_ly(
+    x = ~pos,
+    y = ~`max_OR-inv_OR`,
+    size = ~-log10(p),
+    color = ~theme,
+    frame = ~week,
+    text = ~Variable,
+    hooverinfo = "text",
+    type = "scatter",
+    mode = "markers"
+  )
+fig
+```
+
+```{r, echo = F, message = F, warning = F}
+fig = data %>%
+  filter(week == 27) %>%
+  arrange(OR) %>%
+  mutate(asc_OR = row_number()) %>%
+  select(Variable, asc_OR) %>%
+  inner_join(data) %>%
+  plot_ly(
+    x = ~asc_OR,
+    y = ~`max_OR-inv_OR`,
+    size = ~-log10(p),
+    color = ~theme,
+    frame = ~week,
+    text = ~Variable,
+    hooverinfo = "text",
+    type = "scatter",
+    mode = "markers"
+  )
+fig
+```
+
+## 65 - 74 ans
+
+```{r, echo = F, message = F, warning = F}
+data = NULL
+for (i in 2:33){
+  data = bind_rows(
+    data,
+    make_data_covid(i, classe_age = "65-74") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+
+# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
+#   filter(classe_age != "00-19") %>%
+#   group_by(epci) %>%
+#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
+#   ungroup()
+```
+
+```{r, echo = F, message = F, warning = F}
+fig = data %>%
+  filter(week == 33) %>%
+  arrange(OR) %>%
+  mutate(pos2 = row_number()) %>%
+  select(Variable, pos) %>%
+  inner_join(data) %>%
+  plot_ly(
+    x = ~pos,
+    y = ~`max_OR-inv_OR`,
+    size = ~-log10(p),
+    color = ~theme,
+    frame = ~week,
+    text = ~Variable,
+    hooverinfo = "text",
+    type = "scatter",
+    mode = "markers"
+  )
+fig
+```
+
+```{r, echo = F, message = F, warning = F}
+fig = data %>%
+  filter(week == 27) %>%
+  arrange(OR) %>%
+  mutate(asc_OR = row_number()) %>%
+  select(Variable, asc_OR) %>%
+  inner_join(data) %>%
+  plot_ly(
+    x = ~asc_OR,
+    y = ~`max_OR-inv_OR`,
+    size = ~-log10(p),
+    color = ~theme,
+    frame = ~week,
+    text = ~Variable,
+    hooverinfo = "text",
+    type = "scatter",
+    mode = "markers"
+  )
+fig
+```
+
+## 75 ans et plus
+
+```{r, echo = F, message = F, warning = F}
+data = NULL
+for (i in 2:33){
+  data = bind_rows(
+    data,
+    make_data_covid(i, classe_age = "75+et+%2B") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+
+# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
+#   filter(classe_age != "00-19") %>%
+#   group_by(epci) %>%
+#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
+#   ungroup()
+```
+
+```{r, echo = F, message = F, warning = F}
+fig = data %>%
+  filter(week == 33) %>%
+  arrange(OR) %>%
+  mutate(pos2 = row_number()) %>%
+  select(Variable, pos) %>%
+  inner_join(data) %>%
+  plot_ly(
+    x = ~pos,
+    y = ~`max_OR-inv_OR`,
+    size = ~-log10(p),
+    color = ~theme,
+    frame = ~week,
+    text = ~Variable,
+    hooverinfo = "text",
+    type = "scatter",
+    mode = "markers"
+  )
+fig
+```
+
+```{r, echo = F, message = F, warning = F}
+fig = data %>%
+  filter(week == 27) %>%
+  arrange(OR) %>%
+  mutate(asc_OR = row_number()) %>%
+  select(Variable, asc_OR) %>%
+  inner_join(data) %>%
+  plot_ly(
+    x = ~asc_OR,
+    y = ~`max_OR-inv_OR`,
+    size = ~-log10(p),
+    color = ~theme,
+    frame = ~week,
+    text = ~Variable,
+    hooverinfo = "text",
+    type = "scatter",
+    mode = "markers"
+  )
+fig
+```

### 2021-09-13 code/manhattan_animated.Rmd
update manhattan_animated.rmd

@@
 date: "03/09/2021"
-output: html_document
+output:
+   html_document:
+    toc: true
+    toc_float: true
 ---
@@
 library(pander)
+library(rAmCharts)
 ```
@@
 }
+
+# fonction qui sort les OR à une date : possibilité de prendre en cumul ou à la semaine et possibilité de choisir la tranche d'âge
 
@@
 }
+
+# extraction des données et calcul des OR pour des données cumulées sur une sous période d"limitée
+
+make_data_covid_cumul = function(wks, variable = "taux_1_inj", classe_age = "tous"){
+
+  vacc_tot = NULL
+
+  for (wk in wks){
+    if (wk/10 <1){
+      wk = paste0("0", wk)
+    }
+
+    vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+      mutate(codgeo = as.factor(commune_residence)) %>%
+      mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
+
+    vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+      mutate(codgeo = as.factor(epci)) %>%
+      mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+      plyr::rbind.fill(vacc_com)
+
+    vacc$taux_cumu_1_inj[is.na(vacc$taux_cumu_1_inj)] <- 0
+
+    vacc_tot = plyr::rbind.fill(vacc_tot, vacc)
+  }
+
+  vacc = vacc_tot %>%
+    filter(classe_age != "00-19") %>%
+    group_by(codgeo) %>%
+    summarise(effectif_1_inj = sum(effectif_1_inj),
+              population_carto = sum(population_carto)) %>%
+    ungroup() %>%
+    mutate(taux_1_inj = effectif_1_inj / population_carto)
+
+  if (variable == "taux_cumu_1_inj"){
+    LOG_1107 = LOG_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+    EMP_1107 = EMP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+    FAM_1107 = FAM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+    REV_1107 = REV_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+    ACT_1107 = ACT_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+    FOR_1107 = FOR_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+    POP_1107 = POP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+    IMM_1107 = IMM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+    GEO_1107 = GEO_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+  }else if (variable == "taux_1_inj"){
+    LOG_1107 = LOG_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+    EMP_1107 = EMP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+    FAM_1107 = FAM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+    REV_1107 = REV_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+    ACT_1107 = ACT_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+    FOR_1107 = FOR_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+    POP_1107 = POP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+    IMM_1107 = IMM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+    GEO_1107 = GEO_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+  }
+
+  LOG_OR_1107 = questionr::odds.ratio(LOG_1107$`1ry_res`, LOG_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`2ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Vacant_Home`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Houses`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Flats`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Nb_Rooms_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`House_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Flat_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_bf_1919`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_19-45`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_46-70`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_71-90`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_91-05`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_06-15`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_lt2y`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_2to4y`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_5to9y`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_10to19y`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_20to29y`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_gt30y`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Carpark`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_0car`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_1car`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_2car`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_3+car`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_gt0car`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Owners_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Tenant_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Social_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`FreeAcc_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Overcrowding_rate`, LOG_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(LOG_1107)[2:42]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(LOG_OR_1107) = NULL
+  # write_csv2(LOG_OR, "data/LOG_OR.csv")
+
+  EMP_OR_1107 = questionr::odds.ratio(EMP_1107$`1564_Workforce_rate`, EMP_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1524_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`2554_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`5564_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1524_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`2554_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`5564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1524_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`2554_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`5564_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1524_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`2554_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`5564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1524_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`2554_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`5564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1524_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`2554_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`5564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1524_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`2554_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`5564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_Student_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_Retired_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_OtherInactive_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_Student_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_Retired_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_OtherInactive_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_POP`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_Farmers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_CraftsBusinessShopkeepers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_HihgQualWorkers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_IntermediateProf_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_BlueCollar_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_WhiteCollar_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_Farmers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_CraftsBusinessShopkeepers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_HihgQualWorkers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_IntermediateProf_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_BlueCollar_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`1564_WhiteCollar_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_Salaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_NonSalaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(EMP_1107)[2:63]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(EMP_OR_1107) = NULL
+  # write_csv2(EMP_OR, "data/EMP_OR.csv")
+
+  FAM_OR_1107 = questionr::odds.ratio(FAM_1107$`SinglePerson_HH`, FAM_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`SingleMan_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`SingleWoman_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Farmer_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`HighQualidied_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Intermediate_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`WhiteCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`15+_SinglePerson_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleMan_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleWoman_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_Farmer_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_HighQualidied_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_Intermediate_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_WhiteCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`15+_Single_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`15+_Married_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`15+_nonMarried_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Family_w_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Single_Parent_Family_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Family_wo_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(FAM_1107)[2:51]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(FAM_OR_1107) = NULL
+  # write_csv2(FAM_OR, "data/FAM_OR.csv")
+
+  REV_OR_1107 = questionr::odds.ratio(REV_1107$`D1_st_Living`, REV_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Median_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`D9_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Interdecile_91_Ratio`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Taxable_HH`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Owners`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Tenants`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`-30_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`3039_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`4049_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`5059_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`6074_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`75+_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Activity_Income`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Salary_Income`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Unemployment_Benef`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Self-Employment`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Pensions_Annuities`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Estate`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Social_Benef`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Family_Benef`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Social_Minima`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Housing_Benef`, REV_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(REV_1107$`Tax`, REV_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(REV_1107)[2:26]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(REV_OR_1107) = NULL
+  # write_csv2(REV_OR, "data/REV_OR.csv")
+
+  ACT_OR_1107 = questionr::odds.ratio(ACT_1107$`Wk_Res_Municipality`, ACT_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_County-Municipality`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_Region-County`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_Country-Region`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`Wk_Dom_Com_Abroad`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`noTransport_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`Walk_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`Bike_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`Motorbike_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`Drive_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`PublicTrans_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_Men_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_Women_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_PermanentContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_ShortTermContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_InterimContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_SubsidizedWork_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_ApprenticeContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_SelfEmployed_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_Employers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(ACT_1107$`15+_caregivers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(ACT_1107)[2:22]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(ACT_OR_1107) = NULL
+  # write_csv2(ACT_OR, "data/ACT_OR.csv")
+
+  FOR_OR_1107 = questionr::odds.ratio(FOR_1107$`0205_School`, FOR_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`0610_School`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`1114_School`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`1517_School`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`1824_School`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`2529_School`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`30+_School`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_NoDiploma_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_CertifGeneEducation_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_VocationalGraduate_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_HighSchoolGraduate_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+2_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+4_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+5+_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_HighEducation_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_men_NoDiploma_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_men_VocationalGraduate_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_men_HighSchoolGraduate_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_men_HighEducation_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_women_NoDiploma_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_women_VocationalGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighSchoolGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighEducation_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_NoDiploma`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_VocationalGraduate`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_HighSchoolGraduate`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_HighEducation`, FOR_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(FOR_1107)[2:28]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(FOR_OR_1107) = NULL
+  # write_csv2(FOR_OR, "data/FOR_OR.csv")
+
+  POP_OR_1107 = questionr::odds.ratio(POP_1107$`0014_amg_POP`, POP_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(POP_1107$`1529_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`3044_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`4559_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`6074_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`7589_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`90+_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`Men`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`0019_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`2064_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`65+_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_Farmers_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_CraftsBusinessShopkeeper_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_ManagersHigherIntellectProf_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_IntermediateProf_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_WhiteCollar_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_BlueCollar_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_Retired_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_OtherNoActivity_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`0014_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`1529_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`3044_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`4559_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`6074_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`7589_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`90+_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`0019_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`2064_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`65+_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_men_Farmers_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_men_CraftsBusinessShopkeeper_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_men_ManagersHigherIntellectProf_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_men_IntermediateProf_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_men_WhiteCollar_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_men_BlueCollar_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_men_Retired_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_men_OtherNoActivity_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`0014_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`1529_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`3044_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`4559_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`6074_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`7589_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`90+_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`0019_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`2064_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`65+_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_women_Farmers_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_women_CraftsBusinessShopkeeper_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_women_ManagersHigherIntellectProf_amh_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_women_IntermediateProf_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_women_WhiteCollar_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_women_BlueCollar_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_women_Retired_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_women_OtherNoActivity_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(POP_1107)[2:56]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(POP_OR_1107) = NULL
+  # write_csv2(POP_OR, "data/POP_OR.csv")
+
+  IMM_OR_1107 = questionr::odds.ratio(IMM_1107$`French_nlty`, IMM_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`Stranger`, IMM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`Immigrant`, IMM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`French_nlty_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`French_nlty_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(IMM_1107$`Res_Abroad_2017`, IMM_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(IMM_1107)[2:11]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(IMM_OR_1107) = NULL
+  # write_csv2(IMM_OR, "data/IMM_OR.csv")
+
+  GEO_OR_1107 = questionr::odds.ratio(GEO_1107$latitude, GEO_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(GEO_1107$longitude, GEO_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(GEO_1107$densite, GEO_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(GEO_1107$`SO-NE`, GEO_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(GEO_1107$`NO-SE`, GEO_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(GEO_1107)[2:6]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(GEO_OR_1107) = NULL
+  # write_csv2(GEO_OR, "data/GEO_OR.csv")
+
+  DF_OR_1107 = LOG_OR_1107 %>% mutate(theme = "Logement", .after = Variable) %>%
+    bind_rows(EMP_OR_1107 %>% mutate(theme = "Emploi", .after = Variable)) %>%
+    bind_rows(FAM_OR_1107 %>% mutate(theme = "Famille", .after = Variable)) %>%
+    bind_rows(REV_OR_1107 %>% mutate(theme = "Revenus", .after = Variable)) %>%
+    bind_rows(ACT_OR_1107 %>% mutate(theme = "Activite", .after = Variable)) %>%
+    bind_rows(FOR_OR_1107 %>% mutate(theme = "Formation", .after = Variable)) %>%
+    bind_rows(POP_OR_1107 %>% mutate(theme = "Population", .after = Variable)) %>%
+    bind_rows(IMM_OR_1107 %>% mutate(theme = "Immigration", .after = Variable)) %>%
+    bind_rows(GEO_OR_1107 %>% mutate(theme = "Geographie", .after = Variable)) %>%
+    group_by(theme) %>%
+    mutate(id = row_number()) %>%
+    ungroup() %>%
+    mutate(inv_OR = 1/OR,
+           `inv_2.5 %` = 1/`97.5 %`,
+           `inv_97.5 %` = 1/`2.5 %`,
+           `is_OR_>1` = OR > inv_OR,
+           `max_OR-inv_OR` = if_else(`is_OR_>1`, OR, inv_OR)) %>%
+    arrange(desc(`max_OR-inv_OR`))
+  return(DF_OR_1107)
+}
 ```
@@
 
-## Thématique Logement
-
-```{r, echo = F, message = F, warning = F}
-read.csv2("data/LOG_brut.csv") %>%
-  select(-c(codgeo, taux_cumu_1_inj)) %>%
-  desctable(stats = list("N" = length, "Med" = median, "IQR" = IQR)) %>%
-  pander()
-```
-
 ## Thématique Immigration
@@
 data = NULL
-for (i in 2:33){
+for (i in 2:34){
   data = bind_rows(
@@
 
-# Par classe d'âge
+# Par classe d'âge : données cumulées
 
@@
 data = NULL
-for (i in 18:33){
+for (i in 18:34){
   data = bind_rows(
@@
 ```
+
+# Données données cumulées restreintes de la semaine 22 à 27
+
+```{r, message = F, echo = F, warning = F}
+data = make_data_covid_cumul(22:28)
+
+axis_df = data %>%
+  arrange(theme, id) %>%
+  mutate (pos = row_number()) %>%
+  group_by(theme) %>%
+  summarise(center = (max(pos) + min(pos)) /2)
+
+p = data %>%
+  arrange(theme, id) %>%
+  mutate (pos = row_number()) %>%
+  ggplot() +
+  aes(x = pos, y = -log10(p), variable = Variable, OR = OR) +
+  geom_point(aes(color = theme), alpha = 0.8, size = 1.3) +
+  # scale_color_manual(values = rep(c("grey", "skyblue"), 5)[1:9]) +
+  scale_x_continuous(label = axis_df$theme,
+                     breaks = axis_df$center, guide = guide_axis(angle = 45)) +
+  # ggrepel::geom_label_repel(data = subset(DF_OR_32%>%
+  #                                           arrange(theme, id) %>%
+  #                                           mutate (pos = row_number(),
+  #                                                   theme = as.factor(theme)),
+  #                                         -log10(p) > 61),
+  #                           aes(label = Variable), size = 3) +
+  theme_bw() +
+  # geom_point(data = subset(DF_OR %>%
+  #                            arrange(theme, id) %>%
+  #                            mutate (pos = row_number(),
+  #                                    theme = as.factor(theme)) %>% filter(p < 0.0001/dim(DF_OR)[1])), color = "orange", size = 2) +
+  theme(legend.position = "none",
+        panel.border = element_blank(),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank()) +
+  labs(title = paste("Manhattan plot on the P-value, weeks 28 to 34"),
+       x = "")
+
+plotly::ggplotly(p) %>%
+  layout(showlegend = FALSE, xaxis = list(tickangle=45))
+```
+
+# Données données cumulées restreintes de la semaine 28 à 34
+
+```{r, message = F, echo = F, warning = F}
+data = make_data_covid_cumul(28:34)
+
+axis_df = data %>%
+  arrange(theme, id) %>%
+  mutate (pos = row_number()) %>%
+  group_by(theme) %>%
+  summarise(center = (max(pos) + min(pos)) /2)
+
+p = data %>%
+  arrange(theme, id) %>%
+  mutate (pos = row_number()) %>%
+  ggplot() +
+  aes(x = pos, y = -log10(p), variable = Variable, OR = OR) +
+  geom_point(aes(color = theme), alpha = 0.8, size = 1.3) +
+  # scale_color_manual(values = rep(c("grey", "skyblue"), 5)[1:9]) +
+  scale_x_continuous(label = axis_df$theme,
+                     breaks = axis_df$center, guide = guide_axis(angle = 45)) +
+  # ggrepel::geom_label_repel(data = subset(DF_OR_32%>%
+  #                                           arrange(theme, id) %>%
+  #                                           mutate (pos = row_number(),
+  #                                                   theme = as.factor(theme)),
+  #                                         -log10(p) > 61),
+  #                           aes(label = Variable), size = 3) +
+  theme_bw() +
+  # geom_point(data = subset(DF_OR %>%
+  #                            arrange(theme, id) %>%
+  #                            mutate (pos = row_number(),
+  #                                    theme = as.factor(theme)) %>% filter(p < 0.0001/dim(DF_OR)[1])), color = "orange", size = 2) +
+  theme(legend.position = "none",
+        panel.border = element_blank(),
+        panel.grid.major.x = element_blank(),
+        panel.grid.minor.x = element_blank()) +
+  labs(title = paste("Manhattan plot on the P-value, weeks 28 to 34"),
+       x = "")
+
+plotly::ggplotly(p) %>%
+  layout(showlegend = FALSE, xaxis = list(tickangle=45))
+```
+
+# Couverture vaccinale par tranche d'âge
+
+```{r, message = F, warning = F, echo = F}
+data = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
+  plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-27&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-34&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")))
+data = data %>%
+  filter(classe_age != "TOUT_AGE") %>%
+  group_by(semaine_injection, classe_age) %>%
+  summarise(population_carto = sum(population_carto),
+            effectif_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T)) %>%
+  ungroup() %>%
+  mutate(taux_cumu_1_inj = round(100* effectif_cumu_1_inj / population_carto, 2)) %>%
+  pivot_wider(id_cols = semaine_injection, names_from = classe_age, values_from = taux_cumu_1_inj)
+# pivot_wider(id_cols = classe_age, names_from = semaine_injection, values_from = taux_cumu_1_inj)
+data %>%
+  pander()
+data %>%
+  amBarplot(x = "semaine_injection", y = c("00-19", "20-39", "40-54", "55-64", "65-74", "75 et +")) %>%
+  # amBarplot(x = "classe_age", y = c("2021-22", "2021-27", "2021-34")) %>%
+  amOptions(legend = TRUE, export = TRUE)
+```

### 2021-09-16 code/manhattan_animated.Rmd
updated data by week

@@
 
+  wk1 = wk-1
+
   if (wk/10 <1){
     wk = paste0("0", wk)
+  }
+
+  if (wk1/10 <1){
+    wk1 = paste0("0", wk1)
   }
@@
   vacc$taux_cumu_1_inj[is.na(vacc$taux_cumu_1_inj)] <- 0
+  vacc$taux_1_inj[is.na(vacc$taux_cumu_1_inj)] <- 0
 
@@
   }else if (variable == "taux_1_inj"){
+
+    if (classe_age == "tous"){
+      vacc_com1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk1, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+        mutate(codgeo = as.factor(commune_residence)) %>%
+        mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
+
+      vacc1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk1, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+        mutate(codgeo = as.factor(epci)) %>%
+        mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+        plyr::rbind.fill(vacc_com1)
+    }else{
+      vacc_com1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", classe_age, "&refine.semaine_injection=2021-", wk1, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+        mutate(codgeo = as.factor(commune_residence)) %>%
+        mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
+
+      vacc1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk1, "&refine.classe_age=", classe_age, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+        mutate(codgeo = as.factor(epci)) %>%
+        mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+        plyr::rbind.fill(vacc_com1)
+    }
+
+    vacc1$taux_cumu_1_inj[is.na(vacc1$taux_cumu_1_inj)] <- 0
+    vacc1$taux_1_inj[is.na(vacc1$taux_cumu_1_inj)] <- 0
+
+    vacc = vacc %>%
+      inner_join(vacc1, by = "codgeo") %>%
+      mutate(pop = population_carto.x - effectif_cumu_1_inj.y,
+             taux_1_inj = pop / effectif_1_inj.x)
+
     LOG_1107 = LOG_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
@@
 
+  wk1 = wks[1] - 1
+
+  if (wk1/10 <1){
+      wk1 = paste0("0", wk1)
+  }
+
+  vacc_com1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk1, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+      mutate(codgeo = as.factor(commune_residence)) %>%
+      mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
+
+    vacc1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk1, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+      mutate(codgeo = as.factor(epci)) %>%
+      mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+      plyr::rbind.fill(vacc_com1) %>%
+      filter(!(classe_age %in% c("00-19", "TOUT_AGE"))) %>%
+      select(codgeo, classe_age, population_carto, effectif_cumu_1_inj) %>%
+      group_by(codgeo) %>%
+      summarise(population_carto = sum(population_carto),
+                effectif_cumu_1_inj = sum(effectif_cumu_1_inj)) %>%
+      ungroup()
+
   for (wk in wks){
@@
 
-  vacc = vacc_tot %>%
-    filter(classe_age != "00-19") %>%
+    vacc_agg = vacc_tot %>%
+      select(codgeo, classe_age, population_carto, effectif_1_inj) %>%
+      filter(!(classe_age %in% c("00-19", "TOUT_AGE"))) %>%
       group_by(codgeo) %>%
-    summarise(effectif_1_inj = sum(effectif_1_inj),
-              population_carto = sum(population_carto)) %>%
-    ungroup() %>%
-    mutate(taux_1_inj = effectif_1_inj / population_carto)
+      summarise(effectif_1_inj = sum(effectif_1_inj, na.rm = T)) %>%
+      ungroup()
+
+  vacc = vacc_agg %>%
+    inner_join(vacc1) %>%
+    mutate(taux_1_inj = effectif_1_inj/(population_carto - effectif_cumu_1_inj))
 
@@
     data,
-    make_data_covid(i, classe_age = "00-19") %>%
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "00-19") %>%
       arrange(theme, id) %>%
@@
     data,
-    make_data_covid(i, classe_age = "20-39") %>%
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "20-39") %>%
       arrange(theme, id) %>%
@@
     data,
-    make_data_covid(i, classe_age = "40-54") %>%
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "40-54") %>%
       arrange(theme, id) %>%
@@
     data,
-    make_data_covid(i, classe_age = "55-64") %>%
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "55-64") %>%
       arrange(theme, id) %>%
@@
     data,
-    make_data_covid(i, classe_age = "65-74") %>%
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "65-74") %>%
       arrange(theme, id) %>%
@@
     data,
-    make_data_covid(i, classe_age = "75+et+%2B") %>%
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "75+et+%2B") %>%
       arrange(theme, id) %>%
@@
 ```{r, message = F, echo = F, warning = F}
-data = make_data_covid_cumul(22:28)
+data = make_data_covid_cumul(22:27)
 
@@
   # amBarplot(x = "classe_age", y = c("2021-22", "2021-27", "2021-34")) %>%
-  amOptions(legend = TRUE, export = TRUE)
-```
+  amOptions(legend = TRUE, export = TRUE, main = "Couverture vaccinale par tranche d'âge et par semaine")
+```

### 2021-09-23 code/manhattan_animated.Rmd
Add files via upload

@@
 ```{r, echo = F, message = F, warning = F}
+last_week = 35
+
 LOG_fact = read_csv("data/LOG_fact.csv", col_type = list(.default = col_factor()))
@@
 read.csv("data/GEO_brut.csv") %>%
-  select(-c(codgeo, taux_cumu_1_inj, X, SEXE.AGE3_B_POP_ENS_ENS, lat01, lon01, superficie)) %>%
+  select(-c(codgeo, taux_cumu_1_inj, SEXE.AGE3_B_POP_ENS_ENS, lat01, lon01, superficie)) %>%
+  mutate(latitude = 41+35/60+30/3600+(51+2/60+18/3600-41-35/60-30/3600)*(latitude-6069383)/(7101616-6069383),
+         longitude = -4-38/60-16/3600+(9+31/60+15/3600+4+38/60+16/3600)*(longitude+4+38/60+16/3600)/(1232484-131265)) %>%
   desctable(stats = list("N" = length, "Med" = median, "IQR" = IQR)) %>%
@@
 # Manhattan
+
+## Dates clés de la vaccination en France
+
+- **6 février 2021 (S05)** : La vaccination a été ouverte à l'ensemble des professionnels de santé et du secteur médico-social, aux aides à domicile intervenant auprès de personnes vulnérables et aux pompiers quel que soit leur âge.
+- **19 février 2021 (S07)** : La vaccination est ouverte aux personnes de 50 à 64 ans inclus à risque de formes graves de Covid-19, comme par exemple le diabète ou l'obésité, qui peuvent être vaccinées dans leurs structures de soins, notamment à l'hôpital.
+Depuis le 25 février 2021, elles peuvent se faire vacciner directement chez un médecin de ville.
+- **2 mars 2021 (S09)** : les personnes âgées de plus de 75 ans peuvent être vaccinées par le vaccin AstraZeneca chez un médecin de ville (spécialiste ou médecin généraliste).
+- **15 mars 2021 (S11)** : la vaccination en pharmacie est possible pour les personnes de plus de 50 ans atteintes de comorbidités.
+Les patients éligibles au vaccin AstraZeneca n'auront pas besoin d'une prescription médicale et pourront se rendre directement en officine.
+- **25 mars 2021 (S12)** : toutes les personnes âgées de 70 ans et plus peuvent obtenir des rendez-vous en centre de vaccination pour y recevoir le vaccin Moderna ou Pfizer-BioNtech à partir du samedi 27 mars 2021.
+Celles qui sont éligibles au vaccin AstraZeneca peuvent être vaccinées chez un pharmacien ou un médecin de ville (médecin généraliste, médecin spécialiste, ou médecin du travail).
+- **12 avril 2021 (S15)** : les personnes de 55 ans et plus quel que soit leur lieu de vie et leur état de santé (avec ou sans comorbidités) peuvent être vaccinées chez un pharmacien, un infirmier ou un médecin de ville (médecin généraliste, médecin spécialiste, ou médecin du travail) avec le vaccin Vaxzevria (AstraZeneca).
+- **16 avril 2021 (S15)** : les personnes de 60 à 69 ans et plus bénéficient de l'extension de la campagne vaccinale par Pfizer et Moderna (en centre de vaccination).
+- **1er mai 2021 (S17)** : les personnes de plus de 18 à 49 ans souffrant de comorbidité(s) peuvent être vaccinées en centre de vaccination par Pfizer et Moderna, sur déclaration de leur(s) comorbidité(s) et sans avoir à présenter une prescription médicale.
+- **10 mai 2021 (S19)** : les personnes de 50 ans et plus quel que soit leur lieu de vie et leur état de santé (avec ou sans comorbidités) peuvent être vaccinées en centre de vaccination par Pfizer et Moderna.
+- **12 mai 2021 (S19)** : toutes les personnes de 18 à 49 ans peuvent prendre rendez-vous pour se faire vacciner en centre de vaccination pour des injections avec les vaccins Pfizer-BioNTech ou Moderna ayant lieu le jour même ou le lendemain.
+- **27 mai 2021 (S21)** : toutes les personnes majeures peuvent prendre rendez-vous pour se faire vacciner en centre de vaccination pour des injections avec les vaccins Pfizer-BioNTech ou Moderna à compter du 31 mai 2021.
+- **15 juin 2021 (S24)** : les 12 à 17 ans inclus ans peuvent se faire vacciner avec le vaccin Pfizer-BioNTech en centre de vaccination.
+Le 24 juillet 2021, l'Agence européenne du médicament (EMA) a délivré une autorisation du vaccin Moderna sur lequel la HAS a rendu un avis favorable le 28 juillet.
+- **12 juillet 2021 (S28)** : annonce du président le la république concernant la mise en place du pass sanitaire.
+- **9 août 2021 (S32)** : mise en place de l'obligation du passe sanitaire dans les lieux concernés.
+- **1er septembre 2021 (S35)** : une campagne de rappel est mise en place pour stimuler le système immunitaire des plus vulnérables : les résidents d'EHPAD et d'USLD, les personnes de 65 ans et plus vivant à domicile, les personnes souffrant de comorbidité(s), les personnes atteintes de pathologies à haut risque de forme grave, les personnes ayant été vaccinées avec le vaccin Janssen.
+- **15 septembre 2021 (S37)** : l'obligation vaccinale concernerait tous les personnels des établissements de santé, établissements d'hébergement pour personnes âgées dépendantes (Ehpad) et établissements pour personnes en situation de handicap et tous les professionnels ou les bénévoles en contact avec des personnes âgées ou vulnérables, y compris à domicile.
+Cette mesure a fait l'objet d'un projet de loi relatif à la gestion de la crise sanitaire examiné par le Parlement depuis le 20 juillet 2021.
+
+## Protocole
 
@@
 
-Puis pour connaitre l'influebce de chaque variable, on ne trace uniquement l'odds ratio et enfin son inverse.
+Puis pour connaître l'influence de chaque variable, on ne trace uniquement l'odds ratio et enfin son inverse.
+
+Une variable tracée avec un triangle pointe en gaut indique que plus la valeur de la variable est élevée, plus le territoire est vacciné.
+À l'inverse, si la variable est symbolisée avec un triangle pointe en bas, une valeur élevée de la variable indique un territoire moins vacciné.
 
@@
 data = NULL
-for (i in 2:34){
+for (i in 2:last_week){
   data = bind_rows(
@@
 ```{r, echo = F, message = F, warning = F}
+ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
+
 fig = data %>%
-  filter(week == 33) %>%
-  arrange(OR) %>%
-  mutate(pos2 = row_number()) %>%
-  select(Variable, pos) %>%
-  inner_join(data) %>%
+  mutate(shape = if_else(OR > 1, 0, 1)) %>%
+  # filter(week == 33) %>%
+  # arrange(OR) %>%
+  # mutate(pos2 = row_number()) %>%
+  # select(Variable, pos) %>%
+  # inner_join(data) %>%
   plot_ly(
@@
     text = ~Variable,
+    alpha = 0.75,
+    symbol = ~shape,
+    symbols = c(220, 219),
     hooverinfo = "text",
@@
     mode = "markers"
-  )
+  ) %>%
+  layout(
+    xaxis = list(title = "Variable"),
+    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
 fig
@@
 
-```{r, echo = F, message = F, warning = F}
-fig = data %>%
-  filter(week == 27) %>%
-  arrange(OR) %>%
-  mutate(asc_OR = row_number()) %>%
-  select(Variable, asc_OR) %>%
-  inner_join(data) %>%
-  plot_ly(
-    x = ~asc_OR,
-    y = ~`max_OR-inv_OR`,
-    size = ~-log10(p),
-    color = ~theme,
-    frame = ~week,
-    text = ~Variable,
-    hooverinfo = "text",
-    type = "scatter",
-    mode = "markers"
-  )
-fig
-```
-
 ## Données à la semaine non cumulées
@@
 
-```{r, echo = F, message = F, warning = F}
+```{r, echo = F, message = F, warning = F, eval = F}
+ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
+
 fig = data %>%
-  filter(week == 27) %>%
-  arrange(OR) %>%
-  mutate(asc_OR = row_number()) %>%
-  select(Variable, asc_OR) %>%
-  inner_join(data) %>%
+  mutate(shape = if_else(OR > 1, 220, 219)) %>%
+  # filter(week == 33) %>%
+  # arrange(OR) %>%
+  # mutate(pos2 = row_number()) %>%
+  # select(Variable, pos) %>%
+  # inner_join(data) %>%
   plot_ly(
-    x = ~asc_OR,
+    x = ~pos,
     y = ~`max_OR-inv_OR`,
@@
     text = ~Variable,
+    symbol = ~shape,
+    symbols = c(220, 119),
     hooverinfo = "text",
@@
     mode = "markers"
-  )
+  ) %>%
+  layout(scene = list(
+    xaxis = list(title = "Variable"),
+    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim))))
 fig
@@
 
-# Par classe d'âge : données cumulées
+# Par classe d'âge
 
@@
 
+### données à la semaine
+
 ```{r, echo = F, message = F, warning = F}
 data = NULL
-for (i in 18:34){
+for (i in 18:last_week){
   data = bind_rows(
@@
     mode = "markers"
+  ) %>%
+  layout(
+    xaxis = list(title = "Variable"),
+    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
+fig
+```
+
+### données cumulées
+
+```{r, echo = F, message = F, warning = F}
+data = NULL
+for (i in 18:last_week){
+  data = bind_rows(
+    data,
+    make_data_covid(i, classe_age = "00-19") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
   )
-fig
-```
-
-```{r, echo = F, message = F, warning = F}
+}
+```
+
+```{r, echo = F, message = F, warning = F}
+ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
+
 fig = data %>%
-  filter(week == 27) %>%
-  arrange(OR) %>%
-  mutate(asc_OR = row_number()) %>%
-  select(Variable, asc_OR) %>%
-  inner_join(data) %>%
+  mutate(shape = if_else(OR > 1, 0, 1)) %>%
+  # filter(week == 33) %>%
+  # arrange(OR) %>%
+  # mutate(pos2 = row_number()) %>%
+  # select(Variable, pos) %>%
+  # inner_join(data) %>%
   plot_ly(
-    x = ~asc_OR,
+    x = ~pos,
     y = ~`max_OR-inv_OR`,
@@
 
+### données à la semaine
+
 ```{r, echo = F, message = F, warning = F}
 data = NULL
-for (i in 2:34){
+for (i in 2:last_week){
   data = bind_rows(
@@
     mode = "markers"
+  ) %>%
+  layout(
+    xaxis = list(title = "Variable"),
+    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
+fig
+```
+
+### données cumulées
+
+```{r, echo = F, message = F, warning = F}
+data = NULL
+for (i in 2:last_week){
+  data = bind_rows(
+    data,
+    make_data_covid(i, classe_age = "20-39") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
   )
-fig
-```
-
-```{r, echo = F, message = F, warning = F}
+}
+```
+
+```{r, echo = F, message = F, warning = F}
+ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
+
 fig = data %>%
-  filter(week == 27) %>%
-  arrange(OR) %>%
-  mutate(asc_OR = row_number()) %>%
-  select(Variable, asc_OR) %>%
-  inner_join(data) %>%
+  mutate(shape = if_else(OR > 1, 0, 1)) %>%
+  # filter(week == 33) %>%
+  # arrange(OR) %>%
+  # mutate(pos2 = row_number()) %>%
+  # select(Variable, pos) %>%
+  # inner_join(data) %>%
   plot_ly(
-    x = ~asc_OR,
+    x = ~pos,
     y = ~`max_OR-inv_OR`,
@@
 
+### Données à la semaine
+
 ```{r, echo = F, message = F, warning = F}
 data = NULL
-for (i in 2:34){
+for (i in 2:last_week){
   data = bind_rows(
@@
     mode = "markers"
+  ) %>%
+  layout(
+    xaxis = list(title = "Variable"),
+    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
+fig
+```
+
+### Données cumulées
+
+```{r, echo = F, message = F, warning = F}
+data = NULL
+for (i in 2:last_week){
+  data = bind_rows(
+    data,
+    make_data_covid(i, classe_age = "20-39") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
   )
-fig
-```
-
-```{r, echo = F, message = F, warning = F}
+}
+```
+
+```{r, echo = F, message = F, warning = F}
+ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
+
 fig = data %>%
-  filter(week == 27) %>%
-  arrange(OR) %>%
-  mutate(asc_OR = row_number()) %>%
-  select(Variable, asc_OR) %>%
-  inner_join(data) %>%
+  mutate(shape = if_else(OR > 1, 0, 1)) %>%
+  # filter(week == 33) %>%
+  # arrange(OR) %>%
+  # mutate(pos2 = row_number()) %>%
+  # select(Variable, pos) %>%
+  # inner_join(data) %>%
   plot_ly(
-    x = ~asc_OR,
+    x = ~pos,
     y = ~`max_OR-inv_OR`,
@@
 
-# Données données cumulées restreintes de la semaine 22 à 27
-
-```{r, message = F, echo = F, warning = F}
+<!-- # Données cumulées restreintes de la semaine 22 à 27 -->
+
+```{r, message = F, echo = F, warning = F, eval = F}
 data = make_data_covid_cumul(22:27)
@@
 
-# Données données cumulées restreintes de la semaine 28 à 34
-
-```{r, message = F, echo = F, warning = F}
+<!-- # Données cumulées restreintes de la semaine 28 à 34 -->
+
+```{r, message = F, echo = F, warning = F, eval = F}
 data = make_data_covid_cumul(28:34)
@@
 
-p = data %>%
+pl = data %>%
   arrange(theme, id) %>%
-  mutate (pos = row_number()) %>%
+  mutate (pos = row_number(),
+          max = if_else(OR > 1, "OR", "inv(OR)")) %>%
   ggplot() +
-  aes(x = pos, y = -log10(p), variable = Variable, OR = OR) +
-  geom_point(aes(color = theme), alpha = 0.8, size = 1.3) +
+  aes(x = pos, y = `max_OR-inv_OR`, size = -log10(p), variable = Variable, Max = max) +
+  geom_point(aes(color = theme), alpha = 0.5) +
   # scale_color_manual(values = rep(c("grey", "skyblue"), 5)[1:9]) +
@@
 
-plotly::ggplotly(p) %>%
-  layout(showlegend = FALSE, xaxis = list(tickangle=45))
+plotly::ggplotly(pl) %>%
+  layout(showlegend = FALSE, xaxis = list(tickangle=45), yaxis = list(title = "max(OR, 1/OR)"))
 ```
@@
   plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-27&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-34&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")))
+  plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-34&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-31&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")))
 data = data %>%

### 2021-09-24 code/manhattan_animated.Rmd
fixed errors relative to shapes

@@
     symbol = ~shape,
-    symbols = c(220, 219),
+    symbols = c(219, 220),
     hooverinfo = "text",
@@
     symbol = ~shape,
-    symbols = c(220, 119),
+    symbols = c(219, 220),
     hooverinfo = "text",
@@
 ```
+
+<!-- === -->
+```{r, eval = F}
+vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", "00-19", "&refine.semaine_injection=2021-", "31", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+      mutate(codgeo = as.factor(commune_residence)) %>%
+      mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
+
+    vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", "31", "&refine.classe_age=", "00-19", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+      mutate(codgeo = as.factor(epci)) %>%
+      mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+      plyr::rbind.fill(vacc_com)
+
+test = vacc %>% inner_join(LOG_fact %>%
+                      select(codgeo, Overcrowding_rate)) %>%
+  mutate(taux_1_inj = binarisation(as.numeric(taux_1_inj), 0.25))
+
+summary(test$Overcrowding_rate)
+summary(test$taux_1_inj)
+```
+
+<!-- === -->
 
@@
 ```
+
+```{r, eval = F}
+data = NULL
+for (i in 2:last_week){
+  data = bind_rows(
+    data,
+    make_data_covid(i) %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+```
+
+```{r, eval = F}
+data1 = data
+```
+
+```{r, eval = F}
+data = data1 %>%
+  # filter(Variable %in% c("NO-SE",
+  #                        "Overcrowding_rate",
+  #                        "Interdecile_91_Ratio",
+  #                        "Unemployment_Benef",
+  #                        "Immigrant",
+  #                        "Pop_NoChildFamily_HH")) %>%
+  filter(week >= 22) %>%
+  mutate(ban = as.factor(if_else(week <27, 0, 1)))
+p = data %>%
+  # filter(ban == 0) %>%
+  ggplot() +
+  aes(x = week, y = log(`max_OR-inv_OR`), color = Variable, alpha = 0.5) +
+  geom_point(size = 0.5) +
+  # geom_vline(aes(xintercept = 26.5)) +
+  geom_smooth(aes(fill = ban), size = 0.5, method = "lm", se = F)+
+  theme_bw() +
+  theme(legend.position = "none") 
+# ggplotly(p)
+
+# plot(data$`max_OR-inv_OR`,
+#      type="n",
+#      ylim=c(00,12),
+#      xlab="Week",
+#      ylab="log(Interdecile_91_Ratio)",
+#      bty="l",
+#      xaxt="n")
+# rect(26.5,0,34,12,col=grey(0.9),border=F)
+# points(log(data$`max_OR-inv_OR`[data$ban==0]),cex=0.7)
+```

### 2021-09-28 code/manhattan_animated.Rmd
correct errors and add some features

--- 2021-09-23 code/manhattan_animated.Rmd
@@
 ---
-title: "Manhattan Plot"
+title: "Données de vaccination et "
 author: "Emmanuel LECOEUR"
@@
 ```{r, echo = F, message = F, warning = F}
+# knitr::opts_chunk$set(echo = F, warning = F, message = F)
+```
+
+```{r, echo = F, message = F, warning = F}
 library(tidyverse)
@@
 
-LOG_fact = read_csv("data/LOG_fact.csv", col_type = list(.default = col_factor()))
-EMP_fact = read_csv("data/EMP_fact.csv", col_type = list(.default = col_factor()))
-ACT_fact = read_csv("data/ACT_fact.csv", col_type = list(.default = col_factor()))
-REV_fact = read_csv("data/REV_fact.csv", col_type = list(.default = col_factor()))
-POP_fact = read_csv("data/POP_fact.csv", col_type = list(.default = col_factor()))
-FOR_fact = read_csv("data/FOR_fact.csv", col_type = list(.default = col_factor()))
-IMM_fact = read_csv("data/IMM_fact.csv", col_type = list(.default = col_factor()))
-GEO_fact = read_csv("data/GEO_fact.csv", col_type = list(.default = col_factor()))
-FAM_fact = read_csv("data/FAM_fact.csv", col_type = list(.default = col_factor()))
+LOG_fact = read_csv("data/LOG_fact.csv")
+EMP_fact = read_csv("data/EMP_fact.csv")
+ACT_fact = read_csv("data/ACT_fact.csv")
+REV_fact = read_csv("data/REV_fact.csv")
+POP_fact = read_csv("data/POP_fact.csv")
+FOR_fact = read_csv("data/FOR_fact.csv")
+IMM_fact = read_csv("data/IMM_fact.csv")
+GEO_fact = read_csv("data/GEO_fact.csv")
+FAM_fact = read_csv("data/FAM_fact.csv")
 ```
@@
     vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-      mutate(codgeo = as.factor(commune_residence)) %>%
+      mutate(codgeo = as.numeric(commune_residence)) %>%
       mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
@@
     vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-      mutate(codgeo = as.factor(epci)) %>%
+      mutate(codgeo = as.numeric(epci)) %>%
       mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
@@
     vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", classe_age, "&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-      mutate(codgeo = as.factor(commune_residence)) %>%
+      mutate(codgeo = as.numeric(commune_residence)) %>%
       mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
@@
     vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&refine.classe_age=", classe_age, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-      mutate(codgeo = as.factor(epci)) %>%
+      mutate(codgeo = as.numeric(epci)) %>%
       mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
@@
   if (variable == "taux_cumu_1_inj"){
-    LOG_1107 = LOG_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-    EMP_1107 = EMP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-    FAM_1107 = FAM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-    REV_1107 = REV_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-    ACT_1107 = ACT_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-    FOR_1107 = FOR_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-    POP_1107 = POP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-    IMM_1107 = IMM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-    GEO_1107 = GEO_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+    LOG_1107 = LOG_fact %>%
+      select(-taux_cumu_1_inj) %>%
+      inner_join(vacc) %>%
+      mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)),
+             across(-c(codgeo, taux_cumu_1_inj), function(x){
+               return(factor(x, levels = c(0,1), labels = c(0,1)))}))
+    EMP_1107 = EMP_fact %>%
+      select(-taux_cumu_1_inj) %>%
+      inner_join(vacc) %>%
+      mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)),
+             across(-c(codgeo, taux_cumu_1_inj), function(x){
+               return(factor(x, levels = c(0,1), labels = c(0,1)))}))
+    FAM_1107 = FAM_fact %>%
+      select(-taux_cumu_1_inj) %>%
+      inner_join(vacc) %>%
+      mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)),
+             across(-c(codgeo, taux_cumu_1_inj), function(x){
+               return(factor(x, levels = c(0,1), labels = c(0,1)))}))
+    REV_1107 = REV_fact %>%
+      select(-taux_cumu_1_inj) %>%
+      inner_join(vacc) %>%
+      mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)),
+             across(-c(codgeo, taux_cumu_1_inj), function(x){
+               return(factor(x, levels = c(0,1), labels = c(0,1)))}))
+    ACT_1107 = ACT_fact %>%
+      select(-taux_cumu_1_inj) %>%
+      inner_join(vacc) %>%
+      mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)),
+             across(-c(codgeo, taux_cumu_1_inj), function(x){
+               return(factor(x, levels = c(0,1), labels = c(0,1)))}))
+    FOR_1107 = FOR_fact %>%
+      select(-taux_cumu_1_inj) %>%
+      inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)),
+                                  across(-c(codgeo, taux_cumu_1_inj), function(x){
+                                    return(factor(x, levels = c(0,1), labels = c(0,1)))}))
+    POP_1107 = POP_fact %>%
+      select(-taux_cumu_1_inj) %>%
+      inner_join(vacc) %>%
+      mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)),
+             across(-c(codgeo, taux_cumu_1_inj), function(x){
+               return(factor(x, levels = c(0,1), labels = c(0,1)))}))
+    IMM_1107 = IMM_fact %>%
+      select(-taux_cumu_1_inj) %>%
+      inner_join(vacc) %>%
+      mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)),
+             across(-c(codgeo, taux_cumu_1_inj), function(x){
+               return(factor(x, levels = c(0,1), labels = c(0,1)))}))
+    GEO_1107 = GEO_fact %>%
+      select(-taux_cumu_1_inj) %>%
+      inner_join(vacc) %>%
+      mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)),
+             across(-c(codgeo, taux_cumu_1_inj), function(x){
+               return(factor(x, levels = c(0,1), labels = c(0,1)))}))
   }else if (variable == "taux_1_inj"){
@@
       vacc_com1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk1, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-        mutate(codgeo = as.factor(commune_residence)) %>%
+        mutate(codgeo = as.numeric(commune_residence)) %>%
         mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
@@
       vacc1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk1, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-        mutate(codgeo = as.factor(epci)) %>%
+        mutate(codgeo = as.numeric(epci)) %>%
         mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
@@
       vacc_com1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", classe_age, "&refine.semaine_injection=2021-", wk1, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-        mutate(codgeo = as.factor(commune_residence)) %>%
+        mutate(codgeo = as.numeric(commune_residence)) %>%
         mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
@@
       vacc1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk1, "&refine.classe_age=", classe_age, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-        mutate(codgeo = as.factor(epci)) %>%
+        mutate(codgeo = as.numeric(epci)) %>%
         mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
@@
 
-# les territoires étudiés
-
-## Les EPCI
+# Les données
+
+## Les EPCI + les communes de des métropoles de Paris, Lyon et Marseille.
 
@@
 read.csv2("data/POP.csv") %>%
+  plyr::rbind.fill(read.csv2("data/com_POP.csv")) %>%
   select(codgeo, SEXE.AGE15_15_90_POP_ENS_ENS) %>%
@@
   select(Population) %>%
-  desctable(stats = list("N" = length, "Mean" = mean)) %>%
+  desctable(stats = list("N" = length, "Med" = median, "IQR" = IQR)) %>%
   pander()
 ```
-## Les communes des métropoles de Paris, Lyon, Marseille
-
-```{r, echo = F, message = F, warning = F}
-read.csv2("data/com_POP.csv") %>%
-  select(codgeo, SEXE.AGE15_15_90_POP_ENS_ENS) %>%
-  rename(Population = SEXE.AGE15_15_90_POP_ENS_ENS) %>%
-  select(Population) %>%
-  desctable(stats = list("N" = length, "Mean" = mean)) %>%
+
+## Les données de vaccination : Taux de vaccination cumulées par tranche d'âge
+
+Les tableaux suivants donnent les taux de vaccination totaux par tranche d'âge pour plusieurs semaines clés.
+
+### **Semaine 27** : juste avant l'annonce du passe sanitaire en France
+
+```{r, echo = F, message = F, warning = F}
+read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-27&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"),
+          col_type = list(
+            date_reference = col_date(format = ""),
+            semaine_injection = col_character(),
+            epci = col_double(),
+            libelle_epci = col_character(),
+            population_carto = col_double(),
+            classe_age = col_character(),
+            libelle_classe_age = col_character(),
+            effectif_1_inj = col_double(),
+            effectif_termine = col_double(),
+            effectif_cumu_1_inj = col_double(),
+            effectif_cumu_termine = col_double(),
+            taux_1_inj = col_character(),
+            taux_termine = col_character(),
+            taux_cumu_1_inj = col_character(),
+            taux_cumu_termine = col_character(),
+            date = col_date(format = ""),
+            reg_code = col_double()
+          )) %>%
+  mutate(codgeo = epci) %>%
+  plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-27&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"),
+                             col_type = list(
+                               date_reference = col_date(format = ""),
+                               semaine_injection = col_character(),
+                               commune_residence = col_double(),
+                               libelle_commune = col_character(),
+                               population_carto = col_double(),
+                               classe_age = col_character(),
+                               libelle_classe_age = col_character(),
+                               effectif_1_inj = col_double(),
+                               effectif_termine = col_double(),
+                               effectif_cumu_1_inj = col_double(),
+                               effectif_cumu_termine = col_double(),
+                               taux_1_inj = col_character(),
+                               taux_termine = col_character(),
+                               taux_cumu_1_inj = col_character(),
+                               taux_cumu_termine = col_character(),
+                               date = col_date(format = ""),
+                               reg_code = col_double()
+                             )) %>%
+                     mutate(codgeo = commune_residence)) %>%
+  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+  # test$taux_cumu_1_inj[is.na(test$taux_cumu_1_inj)] <- 0
+  # test %>%
+  pivot_wider(id_cols = codgeo,
+              names_from = classe_age,
+              values_from = taux_cumu_1_inj) %>%
+  select(7, 5, 2, 3, 6, 4, 8) %>%
+  desctable() %>%
+  pander()
+```
+
+### **Semaine 31** : juste avant l'obligation du passe sanitaire en France
+
+```{r, message = F, echo = F, warning = F}
+read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-31&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"),
+          col_type = list(
+            date_reference = col_date(format = ""),
+            semaine_injection = col_character(),
+            epci = col_double(),
+            libelle_epci = col_character(),
+            population_carto = col_double(),
+            classe_age = col_character(),
+            libelle_classe_age = col_character(),
+            effectif_1_inj = col_double(),
+            effectif_termine = col_double(),
+            effectif_cumu_1_inj = col_double(),
+            effectif_cumu_termine = col_double(),
+            taux_1_inj = col_character(),
+            taux_termine = col_character(),
+            taux_cumu_1_inj = col_character(),
+            taux_cumu_termine = col_character(),
+            date = col_date(format = ""),
+            reg_code = col_double()
+          )) %>%
+  mutate(codgeo = epci) %>%
+  plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-31&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"),
+                             col_type = list(
+                               date_reference = col_date(format = ""),
+                               semaine_injection = col_character(),
+                               commune_residence = col_double(),
+                               libelle_commune = col_character(),
+                               population_carto = col_double(),
+                               classe_age = col_character(),
+                               libelle_classe_age = col_character(),
+                               effectif_1_inj = col_double(),
+                               effectif_termine = col_double(),
+                               effectif_cumu_1_inj = col_double(),
+                               effectif_cumu_termine = col_double(),
+                               taux_1_inj = col_character(),
+                               taux_termine = col_character(),
+                               taux_cumu_1_inj = col_character(),
+                               taux_cumu_termine = col_character(),
+                               date = col_date(format = ""),
+                               reg_code = col_double()
+                             )) %>%
+                     mutate(codgeo = commune_residence)) %>%
+  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+  # test$taux_cumu_1_inj[is.na(test$taux_cumu_1_inj)] <- 0
+  # test %>%
+  pivot_wider(id_cols = codgeo,
+              names_from = classe_age,
+              values_from = taux_cumu_1_inj) %>%
+  select(8,2,6,4,7,5) %>%
+  desctable() %>%
+  pander()
+```
+
+### **Semaine 35** : le plus récent
+
+```{r, warning = F, echo = F, message = F}
+read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-35&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"),
+          col_type = list(
+            date_reference = col_date(format = ""),
+            semaine_injection = col_character(),
+            epci = col_double(),
+            libelle_epci = col_character(),
+            population_carto = col_double(),
+            classe_age = col_character(),
+            libelle_classe_age = col_character(),
+            effectif_1_inj = col_double(),
+            effectif_termine = col_double(),
+            effectif_cumu_1_inj = col_double(),
+            effectif_cumu_termine = col_double(),
+            taux_1_inj = col_character(),
+            taux_termine = col_character(),
+            taux_cumu_1_inj = col_character(),
+            taux_cumu_termine = col_character(),
+            date = col_date(format = ""),
+            reg_code = col_double()
+          )) %>%
+  mutate(codgeo = epci) %>%
+  plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-35&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"),
+                             col_type = list(
+                               date_reference = col_date(format = ""),
+                               semaine_injection = col_character(),
+                               commune_residence = col_double(),
+                               libelle_commune = col_character(),
+                               population_carto = col_double(),
+                               classe_age = col_character(),
+                               libelle_classe_age = col_character(),
+                               effectif_1_inj = col_double(),
+                               effectif_termine = col_double(),
+                               effectif_cumu_1_inj = col_double(),
+                               effectif_cumu_termine = col_double(),
+                               taux_1_inj = col_character(),
+                               taux_termine = col_character(),
+                               taux_cumu_1_inj = col_character(),
+                               taux_cumu_termine = col_character(),
+                               date = col_date(format = ""),
+                               reg_code = col_double()
+                             )) %>%
+                     mutate(codgeo = commune_residence)) %>%
+  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+  # test$taux_cumu_1_inj[is.na(test$taux_cumu_1_inj)] <- 0
+  # test %>%
+  pivot_wider(id_cols = codgeo,
+              names_from = classe_age,
+              values_from = taux_cumu_1_inj) %>%
+  select(6,2,3,7,4,5,8) %>%
+  desctable() %>%
   pander()
@@
 data = NULL
-for (i in 2:last_week){
+for (i in 22:last_week){
   data = bind_rows(
@@
 
-## Données à la semaine non cumulées
-
-```{r, echo = F, message = F, warning = F}
+### Distributions des Odds ratios
+
+```{r, message = F, echo = F, warning = F}
+data %>%
+  filter(week %in% c(22, 27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  ggplot() +
+  aes(x = `max_OR-inv_OR`, y = ..density.., color = week) +
+  geom_density(kernel = "gaussian") +
+  theme_bw() +
+  labs(title = "Distribution of max(OR, 1/OR) over every variable",
+       x = "max(OR, 1/OR)")
+
+# data %>%
+#   filter(week %in% c(27, 31, 35)) %>%
+#   mutate(week = factor(week)) %>%
+#   ggplot() +
+#   aes(x = log(`max_OR-inv_OR`), y = ..density.., color = week) +
+#   geom_density(kernel = "gaussian") +
+#   theme_bw() +
+#   labs(title = "Distribution of log(max(OR, 1/OR)) over every variable",
+#        x = "log(max(OR, 1/OR))")
+```
+
+### Test de Wilcoxon
+
+```{r, message = F, echo = F, warning = F}
+w1 = data %>%
+  filter(week %in% c(27, 31)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w2 = data %>%
+  filter(week %in% c(31, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w3 = data %>%
+  filter(week %in% c(27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+data.frame(Comparison = c("wk27_wk31", "wk31_wk35", "wk27_wk35"),
+           method = c(w1$method, w2$method, w3$method), p.value = c(w1$p.value, w2$p.value, w3$p.value)) %>%
+  pander()
+```
+
+<!-- === -->
+```{r, eval = F, echo = F}
+vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", "TOUT_AGE", "&refine.semaine_injection=2021-", "35", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  mutate(codgeo = as.factor(commune_residence)) %>%
+  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
+
+vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", "35", "&refine.classe_age=", "TOUT_AGE", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  mutate(codgeo = as.factor(epci)) %>%
+  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+  plyr::rbind.fill(vacc_com)
+
+test = vacc %>% inner_join(LOG_fact %>%
+                             select(codgeo, Overcrowding_rate)) %>%
+  mutate(taux_cumu_1_inj = binarisation(as.numeric(taux_cumu_1_inj), 0.25))
+
+summary(test$Overcrowding_rate[test$taux_cumu_1_inj == 1])
+summary(test$Overcrowding_rate[test$taux_cumu_1_inj == 0])
+
+table(test$Overcrowding_rate, test$taux_cumu_1_inj)
+
+questionr::odds.ratio(test$Overcrowding_rate, test$taux_cumu_1_inj)
+```
+
+<!-- ## Données à la semaine non cumulées -->
+
+```{r, echo = F, message = F, warning = F, eval = F}
 data = NULL
@@
 
-```{r, echo = F, message = F, warning = F}
+```{r, echo = F, message = F, warning = F, eval = F}
+ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
+
+fig = data %>%
+  mutate(shape = if_else(OR > 1, 0, 1)) %>%
+  # filter(week == 33) %>%
+  # arrange(OR) %>%
+  # mutate(pos2 = row_number()) %>%
+  # select(Variable, pos) %>%
+  # inner_join(data) %>%
+  plot_ly(
+    x = ~pos,
+    y = ~`max_OR-inv_OR`,
+    size = ~-log10(p),
+    color = ~theme,
+    frame = ~week,
+    text = ~Variable,
+    alpha = 0.75,
+    symbol = ~shape,
+    symbols = c(219, 220),
+    hooverinfo = "text",
+    type = "scatter",
+    mode = "markers"
+  ) %>%
+  layout(
+    xaxis = list(title = "Variable"),
+    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
+fig
+```
+
+```{r, echo = F, message = F, warning = F, eval = F}
+ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
+
+fig = data %>%
+  mutate(shape = if_else(OR > 1, 220, 219)) %>%
+  # filter(week == 33) %>%
+  # arrange(OR) %>%
+  # mutate(pos2 = row_number()) %>%
+  # select(Variable, pos) %>%
+  # inner_join(data) %>%
+  plot_ly(
+    x = ~pos,
+    y = ~`max_OR-inv_OR`,
+    size = ~-log10(p),
+    color = ~theme,
+    frame = ~week,
+    text = ~Variable,
+    symbol = ~shape,
+    symbols = c(219, 220),
+    hooverinfo = "text",
+    type = "scatter",
+    mode = "markers"
+  ) %>%
+  layout(scene = list(
+    xaxis = list(title = "Variable"),
+    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim))))
+fig
+```
+
+# Par classe d'âge - données cumulées
+
+## 0 - 19 ans
+
+<!-- ### Données à la semaine -->
+
+```{r, echo = F, message = F, warning = F, eval = F}
+data = NULL
+for (i in 22:last_week){
+  data = bind_rows(
+    data,
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "00-19") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+
+# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
+#   filter(classe_age != "00-19") %>%
+#   group_by(epci) %>%
+#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
+#   ungroup()
+```
+
+```{r, echo = F, message = F, warning = F, eval = F}
 ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
@@
 
-```{r, echo = F, message = F, warning = F, eval = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 220, 219)) %>%
-  # filter(week == 33) %>%
-  # arrange(OR) %>%
-  # mutate(pos2 = row_number()) %>%
-  # select(Variable, pos) %>%
-  # inner_join(data) %>%
-  plot_ly(
-    x = ~pos,
-    y = ~`max_OR-inv_OR`,
-    size = ~-log10(p),
-    color = ~theme,
-    frame = ~week,
-    text = ~Variable,
-    symbol = ~shape,
-    symbols = c(220, 119),
-    hooverinfo = "text",
-    type = "scatter",
-    mode = "markers"
-  ) %>%
-  layout(scene = list(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim))))
-fig
-```
-
-# Par classe d'âge
-
-## 0 - 19 ans
-
-### données à la semaine
+<!-- === -->
+```{r, eval = F, echo = F}
+vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", "00-19", "&refine.semaine_injection=2021-", "35", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  mutate(codgeo = as.numeric(commune_residence)) %>%
+  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
+
+vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", "35", "&refine.classe_age=", "00-19", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  mutate(codgeo = as.numeric(epci)) %>%
+  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+  plyr::rbind.fill(vacc_com)
+
+test = vacc %>% inner_join(LOG_fact %>%
+                             select(codgeo, Overcrowding_rate)) %>%
+  mutate(taux_cumu_1_inj = binarisation(as.numeric(taux_cumu_1_inj), 0.25))
+
+summary(factor(test$Overcrowding_rate, levels = c(0,1), labels = c(0,1)))
+summary(test$taux_cumu_1_inj)
+
+table(test$Overcrowding_rate, test$taux_cumu_1_inj)
+
+questionr::odds.ratio(factor(test$Overcrowding_rate, levels = c(0,1), labels = c(0,1)), test$taux_cumu_1_inj)
+```
+
+<!-- === -->
+
+<!-- ### Données cumulées -->
 
@@
 data = NULL
-for (i in 18:last_week){
+for (i in 22:last_week){
   data = bind_rows(
     data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "00-19") %>%
+    make_data_covid(i, classe_age = "00-19") %>%
       arrange(theme, id) %>%
@@
 }
-
-# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
-#   filter(classe_age != "00-19") %>%
-#   group_by(epci) %>%
-#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
-#   ungroup()
 ```
@@
 
-### données cumulées
-
-```{r, echo = F, message = F, warning = F}
+### Distributions des Odds ratios
+
+```{r, message = F, echo = F, warning = F}
+data %>%
+  filter(week %in% c(22, 27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  ggplot() +
+  aes(x = `max_OR-inv_OR`, y = ..density.., color = week) +
+  geom_density(kernel = "gaussian") +
+  theme_bw() +
+  labs(title = "Distribution of max(OR, 1/OR) over every variable",
+       x = "max(OR, 1/OR)")
+
+# data %>%
+#   filter(week %in% c(27, 31, 35)) %>%
+#   mutate(week = factor(week)) %>%
+#   ggplot() +
+#   aes(x = log(`max_OR-inv_OR`), y = ..density.., color = week) +
+#   geom_density(kernel = "gaussian") +
+#   theme_bw() +
+#   labs(title = "Distribution of log(max(OR, 1/OR)) over every variable",
+#        x = "log(max(OR, 1/OR))")
+```
+
+### Test de Wilcoxon
+
+```{r, message = F, echo = F, warning = F}
+w1 = data %>%
+  filter(week %in% c(27, 31)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w2 = data %>%
+  filter(week %in% c(31, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w3 = data %>%
+  filter(week %in% c(27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+data.frame(Comparison = c("wk27_wk31", "wk31_wk35", "wk27_wk35"),
+           method = c(w1$method, w2$method, w3$method), p.value = c(w1$p.value, w2$p.value, w3$p.value)) %>%
+  pander()
+```
+
+## 20 - 39 ans
+
+<!-- ### Données à la semaine -->
+
+```{r, echo = F, message = F, warning = F, eval = F}
 data = NULL
-for (i in 18:last_week){
+for (i in 22:last_week){
   data = bind_rows(
     data,
-    make_data_covid(i, classe_age = "00-19") %>%
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "20-39") %>%
       arrange(theme, id) %>%
@@
 }
-```
-
-```{r, echo = F, message = F, warning = F}
+
+# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
+#   filter(classe_age != "00-19") %>%
+#   group_by(epci) %>%
+#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
+#   ungroup()
+```
+
+```{r, echo = F, message = F, warning = F, eval = F}
 ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
@@
 
-## 20 - 39 ans
-
-### données à la semaine
+<!-- ### Données cumulées -->
 
@@
 data = NULL
-for (i in 2:last_week){
+for (i in 22:last_week){
   data = bind_rows(
     data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "20-39") %>%
+    make_data_covid(i, classe_age = "20-39") %>%
       arrange(theme, id) %>%
@@
 
-### données cumulées
-
-```{r, echo = F, message = F, warning = F}
+### Distributions des Odds ratios
+
+```{r, message = F, echo = F, warning = F}
+data %>%
+  filter(week %in% c(22, 27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  ggplot() +
+  aes(x = `max_OR-inv_OR`, y = ..density.., color = week) +
+  geom_density(kernel = "gaussian") +
+  theme_bw() +
+  labs(title = "Distribution of max(OR, 1/OR) over every variable",
+       x = "max(OR, 1/OR)")
+
+# data %>%
+#   filter(week %in% c(27, 31, 35)) %>%
+#   mutate(week = factor(week)) %>%
+#   ggplot() +
+#   aes(x = log(`max_OR-inv_OR`), y = ..density.., color = week) +
+#   geom_density(kernel = "gaussian") +
+#   theme_bw() +
+#   labs(title = "Distribution of log(max(OR, 1/OR)) over every variable",
+#        x = "log(max(OR, 1/OR))")
+```
+
+### Test de Wilcoxon
+
+```{r, message = F, echo = F, warning = F}
+w1 = data %>%
+  filter(week %in% c(27, 31)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w2 = data %>%
+  filter(week %in% c(31, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w3 = data %>%
+  filter(week %in% c(27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+data.frame(Comparison = c("wk27_wk31", "wk31_wk35", "wk27_wk35"),
+           method = c(w1$method, w2$method, w3$method), p.value = c(w1$p.value, w2$p.value, w3$p.value)) %>%
+  pander()
+```
+
+```{r, eval = F, echo = F}
+vacc_com = read_csv2(
+  url(
+    paste0(
+      "https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=",
+      "75+et+%2B",
+      "&refine.semaine_injection=2021-",
+      "35",
+      "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  mutate(codgeo = as.numeric(commune_residence)) %>%
+  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
+
+vacc = read_csv2(
+  url(
+    paste0(
+      "https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-",
+      "35",
+      "&refine.classe_age=",
+      "75+et+%2B",
+      "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  mutate(codgeo = as.numeric(epci)) %>%
+  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+  plyr::rbind.fill(vacc_com)
+
+test = vacc %>% inner_join(GEO_fact %>%
+                             select(codgeo, `NO-SE`, latitude)) %>%
+  mutate(taux_cumu_1_inj = binarisation(as.numeric(taux_cumu_1_inj), 0.25),
+         `NO-SE` = as.factor(`NO-SE`))
+
+summary(test$`NO-SE`)
+summary(test$taux_cumu_1_inj)
+
+table(test$`NO-SE`, test$taux_cumu_1_inj)
+
+questionr::odds.ratio(test$`NO-SE`, test$taux_cumu_1_inj)
+```
+
+## 40 - 54 ans
+
+<!-- ### Données à la semaine -->
+
+```{r, echo = F, message = F, warning = F, eval = F}
 data = NULL
-for (i in 2:last_week){
+for (i in 22:last_week){
   data = bind_rows(
     data,
-    make_data_covid(i, classe_age = "20-39") %>%
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "40-54") %>%
       arrange(theme, id) %>%
@@
 
-## 40 - 54 ans
-
-### Données à la semaine
+<!-- ### Données cumulées -->
 
@@
 data = NULL
-for (i in 2:last_week){
+for (i in 22:last_week){
   data = bind_rows(
     data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "40-54") %>%
+    make_data_covid(i, classe_age = "40-54") %>%
       arrange(theme, id) %>%
@@
 
-### Données cumulées
-
-```{r, echo = F, message = F, warning = F}
+### Distributions des Odds ratios
+
+```{r, message = F, echo = F, warning = F}
+data %>%
+  filter(week %in% c(22, 27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  ggplot() +
+  aes(x = `max_OR-inv_OR`, y = ..density.., color = week) +
+  geom_density(kernel = "gaussian") +
+  theme_bw() +
+  labs(title = "Distribution of max(OR, 1/OR) over every variable",
+       x = "max(OR, 1/OR)")
+
+# data %>%
+#   filter(week %in% c(27, 31, 35)) %>%
+#   mutate(week = factor(week)) %>%
+#   ggplot() +
+#   aes(x = log(`max_OR-inv_OR`), y = ..density.., color = week) +
+#   geom_density(kernel = "gaussian") +
+#   theme_bw() +
+#   labs(title = "Distribution of log(max(OR, 1/OR)) over every variable",
+#        x = "log(max(OR, 1/OR))")
+```
+
+### Test de Wilcoxon
+
+```{r, message = F, echo = F, warning = F}
+w1 = data %>%
+  filter(week %in% c(27, 31)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w2 = data %>%
+  filter(week %in% c(31, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w3 = data %>%
+  filter(week %in% c(27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+data.frame(Comparison = c("wk27_wk31", "wk31_wk35", "wk27_wk35"),
+           method = c(w1$method, w2$method, w3$method), p.value = c(w1$p.value, w2$p.value, w3$p.value)) %>%
+  pander()
+```
+
+## 55 - 64 ans
+
+<!-- ### Données à la semaine -->
+
+```{r, echo = F, message = F, warning = F, eval = F}
 data = NULL
-for (i in 2:last_week){
+for (i in 22:last_week){
   data = bind_rows(
     data,
-    make_data_covid(i, classe_age = "20-39") %>%
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "55-64") %>%
       arrange(theme, id) %>%
@@
 
-## 55 - 64 ans
-
-### Données à la semaine
+<!-- ### Données cumulées -->
 
@@
 data = NULL
-for (i in 2:last_week){
+for (i in 22:last_week){
   data = bind_rows(
     data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "55-64") %>%
+    make_data_covid(i, classe_age = "55-64") %>%
       arrange(theme, id) %>%
@@
 
-### Données cumulées
-
-```{r, echo = F, message = F, warning = F}
+### Distributions des Odds ratios
+
+```{r, message = F, echo = F, warning = F}
+data %>%
+  filter(week %in% c(22, 27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  ggplot() +
+  aes(x = `max_OR-inv_OR`, y = ..density.., color = week) +
+  geom_density(kernel = "gaussian") +
+  theme_bw() +
+  labs(title = "Distribution of max(OR, 1/OR) over every variable",
+       x = "max(OR, 1/OR)")
+
+# data %>%
+#   filter(week %in% c(27, 31, 35)) %>%
+#   mutate(week = factor(week)) %>%
+#   ggplot() +
+#   aes(x = log(`max_OR-inv_OR`), y = ..density.., color = week) +
+#   geom_density(kernel = "gaussian") +
+#   theme_bw() +
+#   labs(title = "Distribution of log(max(OR, 1/OR)) over every variable",
+#        x = "log(max(OR, 1/OR))")
+```
+
+### Test de Wilcoxon
+
+```{r, message = F, echo = F, warning = F}
+w1 = data %>%
+  filter(week %in% c(27, 31)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w2 = data %>%
+  filter(week %in% c(31, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w3 = data %>%
+  filter(week %in% c(27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+data.frame(Comparison = c("wk27_wk31", "wk31_wk35", "wk27_wk35"),
+           method = c(w1$method, w2$method, w3$method), p.value = c(w1$p.value, w2$p.value, w3$p.value)) %>%
+  pander()
+```
+
+## 65 - 74 ans
+
+<!-- ### Données à la semaine -->
+
+```{r, echo = F, message = F, warning = F, eval = F}
 data = NULL
-for (i in 2:last_week){
+for (i in 22:last_week){
   data = bind_rows(
     data,
-    make_data_covid(i, classe_age = "20-39") %>%
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "65-74") %>%
       arrange(theme, id) %>%
@@
 
-## 65 - 74 ans
-
-### Données à la semaine
+<!-- ### Données cumulées -->
 
@@
 data = NULL
-for (i in 2:last_week){
+for (i in 22:last_week){
   data = bind_rows(
     data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "65-74") %>%
+    make_data_covid(i, classe_age = "65-74") %>%
       arrange(theme, id) %>%
@@
 
-### Données cumulées
-
-```{r, echo = F, message = F, warning = F}
+### Distributions des Odds ratios
+
+```{r, message = F, echo = F, warning = F}
+data %>%
+  filter(week %in% c(22, 27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  ggplot() +
+  aes(x = `max_OR-inv_OR`, y = ..density.., color = week) +
+  geom_density(kernel = "gaussian") +
+  theme_bw() +
+  labs(title = "Distribution of max(OR, 1/OR) over every variable",
+       x = "max(OR, 1/OR)")
+
+# data %>%
+#   filter(week %in% c(27, 31, 35)) %>%
+#   mutate(week = factor(week)) %>%
+#   ggplot() +
+#   aes(x = log(`max_OR-inv_OR`), y = ..density.., color = week) +
+#   geom_density(kernel = "gaussian") +
+#   theme_bw() +
+#   labs(title = "Distribution of log(max(OR, 1/OR)) over every variable",
+#        x = "log(max(OR, 1/OR))")
+```
+
+### Test de Wilcoxon
+
+```{r, message = F, echo = F, warning = F}
+w1 = data %>%
+  filter(week %in% c(27, 31)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w2 = data %>%
+  filter(week %in% c(31, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w3 = data %>%
+  filter(week %in% c(27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+data.frame(Comparison = c("wk27_wk31", "wk31_wk35", "wk27_wk35"),
+           method = c(w1$method, w2$method, w3$method), p.value = c(w1$p.value, w2$p.value, w3$p.value)) %>%
+  pander()
+```
+
+## 75 ans et plus
+
+<!-- ### Données à la semaine -->
+
+```{r, echo = F, message = F, warning = F, eval = F}
 data = NULL
-for (i in 2:last_week){
+for (i in 22:last_week){
   data = bind_rows(
     data,
-    make_data_covid(i, classe_age = "20-39") %>%
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "75+et+%2B") %>%
       arrange(theme, id) %>%
@@
 
-## 75 ans et plus
-
-### Données à la semaine
+<!-- ### Données cumulées -->
 
@@
 data = NULL
-for (i in 2:last_week){
+for (i in 22:last_week){
   data = bind_rows(
     data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "75+et+%2B") %>%
+    make_data_covid(i, classe_age = "75+et+%2B") %>%
       arrange(theme, id) %>%
@@
 
-### Données cumulées
-
-```{r, echo = F, message = F, warning = F}
-data = NULL
-for (i in 2:last_week){
-  data = bind_rows(
-    data,
-    make_data_covid(i, classe_age = "20-39") %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
-  )
-}
-```
-
-```{r, echo = F, message = F, warning = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 0, 1)) %>%
-  # filter(week == 33) %>%
-  # arrange(OR) %>%
-  # mutate(pos2 = row_number()) %>%
-  # select(Variable, pos) %>%
-  # inner_join(data) %>%
-  plot_ly(
-    x = ~pos,
-    y = ~`max_OR-inv_OR`,
-    size = ~-log10(p),
-    color = ~theme,
-    frame = ~week,
-    text = ~Variable,
-    alpha = 0.75,
-    symbol = ~shape,
-    symbols = c(220, 219),
-    hooverinfo = "text",
-    type = "scatter",
-    mode = "markers"
-  ) %>%
-  layout(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
-fig
+### Distributions des Odds ratios
+
+```{r, message = F, echo = F, warning = F}
+data %>%
+  filter(week %in% c(22, 27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  ggplot() +
+  aes(x = `max_OR-inv_OR`, y = ..density.., color = week) +
+  geom_density(kernel = "gaussian") +
+  theme_bw() +
+  labs(title = "Distribution of max(OR, 1/OR) over every variable",
+       x = "max(OR, 1/OR)")
+
+# data %>%
+#   filter(week %in% c(22, 27, 35)) %>%
+#   mutate(week = factor(week)) %>%
+#   ggplot() +
+#   aes(x = log(`max_OR-inv_OR`), y = ..density.., color = week) +
+#   geom_density(kernel = "gaussian") +
+#   theme_bw() +
+#   labs(title = "Distribution of log(max(OR, 1/OR)) over every variable",
+#        x = "log(max(OR, 1/OR))")
+```
+
+### Test de Wilcoxon
+
+```{r, message = F, echo = F, warning = F}
+w1 = data %>%
+  filter(week %in% c(27, 31)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w2 = data %>%
+  filter(week %in% c(31, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w3 = data %>%
+  filter(week %in% c(27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+data.frame(Comparison = c("wk27_wk31", "wk31_wk35", "wk27_wk35"),
+           method = c(w1$method, w2$method, w3$method), p.value = c(w1$p.value, w2$p.value, w3$p.value)) %>%
+  pander()
 ```
@@
 ```
+
+```{r, eval = F, echo = F}
+data = NULL
+for (i in 2:last_week){
+  data = bind_rows(
+    data,
+    make_data_covid(i) %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+```
+
+```{r, eval = F, echo = F}
+data1 = data
+```
+
+```{r, eval = F, echo = F}
+data = data1 %>%
+  # filter(Variable %in% c("NO-SE",
+  #                        "Overcrowding_rate",
+  #                        "Interdecile_91_Ratio",
+  #                        "Unemployment_Benef",
+  #                        "Immigrant",
+  #                        "Pop_NoChildFamily_HH")) %>%
+  filter(week >= 22) %>%
+  mutate(ban = as.factor(if_else(week <27, 0, 1)))
+p = data %>%
+  # filter(ban == 0) %>%
+  ggplot() +
+  aes(x = week, y = log(`max_OR-inv_OR`), color = Variable, alpha = 0.5) +
+  geom_point(size = 0.5) +
+  # geom_vline(aes(xintercept = 26.5)) +
+  geom_smooth(aes(fill = ban), size = 0.5, method = "lm", se = F)+
+  theme_bw() +
+  theme(legend.position = "none") 
+# ggplotly(p)
+
+# plot(data$`max_OR-inv_OR`,
+#      type="n",
+#      ylim=c(00,12),
+#      xlab="Week",
+#      ylab="log(Interdecile_91_Ratio)",
+#      bty="l",
+#      xaxt="n")
+# rect(26.5,0,34,12,col=grey(0.9),border=F)
+# points(log(data$`max_OR-inv_OR`[data$ban==0]),cex=0.7)
+```

### 2021-09-29 code/manhattan_animated.Rmd
Add correlations

@@
 FAM_fact = read_csv("data/FAM_fact.csv")
-```
-
-```{r, echo = F, message = F, warning = F}
+
+# LOG_brut = 
+# EMP_brut = read_csv2("data/EMP_brut.csv")
+# ACT_brut = read_csv2("data/ACT_brut.csv")
+# REV_brut = read_csv2("data/REV_brut.csv")
+# POP_brut = read_csv2("data/POP_brut.csv")
+# FOR_brut = read_csv2("data/FOR_brut.csv")
+# IMM_brut = read_csv2("data/IMM_brut.csv")
+# GEO_brut = read_csv("data/GEO_brut.csv")
+# FAM_brut = read_csv2("data/FAM_brut.csv")
+```
+
+```{r, echo = F, message = F, warning = F}
+get_upper_tri <- function(cormat){
+    cormat[lower.tri(cormat)]<- NA
+    return(cormat)
+  }
+
+reorder_cormat <- function(cormat){
+# Utiliser la corrélation entre les variables
+  # comme mésure de distance
+dd <- as.dist((1-cormat)/2)
+hc <- hclust(dd)
+cormat <-cormat[hc$order, hc$order]
+}
+
 binarisation = function(liste, q = 0.5){
@@
   vacc$taux_1_inj[is.na(vacc$taux_cumu_1_inj)] <- 0
+
+  vacc = unique(vacc)
 
@@
     rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Tenants`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`-30_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`3039_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`4049_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`5059_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`6074_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`75+_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(REV_1107$`-30_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(REV_1107$`3039_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(REV_1107$`4049_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(REV_1107$`5059_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(REV_1107$`6074_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(REV_1107$`75+_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(REV_1107$`Poverty`, REV_1107$taux_cumu_1_inj)) %>%
@@
     as.data.frame() %>%
-    bind_cols(Variable = colnames(REV_1107)[2:26]) %>%
+    bind_cols(Variable = colnames(REV_1107)[c(2:8, 15:26)]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
     rbind(questionr::odds.ratio(ACT_1107$`15+_Women_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_PermanentContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_ShortTermContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_InterimContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_SubsidizedWork_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_ApprenticeContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_SelfEmployed_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_Employers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_caregivers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(ACT_1107$`15+_PermanentContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(ACT_1107$`15+_ShortTermContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(ACT_1107$`15+_InterimContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(ACT_1107$`15+_SubsidizedWork_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(ACT_1107$`15+_ApprenticeContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(ACT_1107$`15+_SelfEmployed_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(ACT_1107$`15+_Employers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(ACT_1107$`15+_caregivers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
     as.data.frame() %>%
-    bind_cols(Variable = colnames(ACT_1107)[2:22]) %>%
+    bind_cols(Variable = colnames(ACT_1107)[2:14]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
 
-  IMM_OR_1107 = questionr::odds.ratio(IMM_1107$`French_nlty`, IMM_1107$taux_cumu_1_inj) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`Stranger`, IMM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`Immigrant`, IMM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`French_nlty_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
+  IMM_OR_1107 = questionr::odds.ratio(IMM_1107$`Immigrant`, IMM_1107$taux_cumu_1_inj) %>%
+    # rbind(questionr::odds.ratio(IMM_1107$`French_nlty_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`French_nlty_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(IMM_1107$`French_nlty_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`Res_Abroad_2017`, IMM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(IMM_1107$`Res_Abroad_2017`, IMM_1107$taux_cumu_1_inj)) %>%
     as.data.frame() %>%
-    bind_cols(Variable = colnames(IMM_1107)[2:11]) %>%
+    bind_cols(Variable = colnames(IMM_1107)[c(2, 5, 8)]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
     as.data.frame() %>%
-    bind_cols(Variable = colnames(GEO_1107)[2:6]) %>%
+    bind_cols(Variable = c(colnames(GEO_1107)[2:4], "SO-NE", "NO-SE")) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
 
-  DF_OR_1107 = LOG_OR_1107 %>% mutate(theme = "Logement", .after = Variable) %>%
-    bind_rows(EMP_OR_1107 %>% mutate(theme = "Emploi", .after = Variable)) %>%
-    bind_rows(FAM_OR_1107 %>% mutate(theme = "Famille", .after = Variable)) %>%
-    bind_rows(REV_OR_1107 %>% mutate(theme = "Revenus", .after = Variable)) %>%
-    bind_rows(ACT_OR_1107 %>% mutate(theme = "Activite", .after = Variable)) %>%
-    bind_rows(FOR_OR_1107 %>% mutate(theme = "Formation", .after = Variable)) %>%
+  DF_OR_1107 = LOG_OR_1107 %>% mutate(theme = "Housing", .after = Variable) %>%
+    bind_rows(EMP_OR_1107 %>% mutate(theme = "Employment", .after = Variable)) %>%
+    bind_rows(FAM_OR_1107 %>% mutate(theme = "Family", .after = Variable)) %>%
+    bind_rows(REV_OR_1107 %>% mutate(theme = "Revenue", .after = Variable)) %>%
+    bind_rows(ACT_OR_1107 %>% mutate(theme = "Activity", .after = Variable)) %>%
+    bind_rows(FOR_OR_1107 %>% mutate(theme = "School", .after = Variable)) %>%
     bind_rows(POP_OR_1107 %>% mutate(theme = "Population", .after = Variable)) %>%
     bind_rows(IMM_OR_1107 %>% mutate(theme = "Immigration", .after = Variable)) %>%
-    bind_rows(GEO_OR_1107 %>% mutate(theme = "Geographie", .after = Variable)) %>%
+    bind_rows(GEO_OR_1107 %>% mutate(theme = "Geography", .after = Variable)) %>%
     group_by(theme) %>%
@@
 
-# extraction des données et calcul des OR pour des données cumulées sur une sous période d"limitée
-
-make_data_covid_cumul = function(wks, variable = "taux_1_inj", classe_age = "tous"){
-
-  vacc_tot = NULL
-
-  wk1 = wks[1] - 1
-
-  if (wk1/10 <1){
-    wk1 = paste0("0", wk1)
-  }
-
-  vacc_com1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk1, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-    mutate(codgeo = as.factor(commune_residence)) %>%
-    mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
-
-  vacc1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk1, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-    mutate(codgeo = as.factor(epci)) %>%
-    mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
-    plyr::rbind.fill(vacc_com1) %>%
-    filter(!(classe_age %in% c("00-19", "TOUT_AGE"))) %>%
-    select(codgeo, classe_age, population_carto, effectif_cumu_1_inj) %>%
-    group_by(codgeo) %>%
-    summarise(population_carto = sum(population_carto),
-              effectif_cumu_1_inj = sum(effectif_cumu_1_inj)) %>%
-    ungroup()
-
-  for (wk in wks){
-    if (wk/10 <1){
-      wk = paste0("0", wk)
-    }
-
-    vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-      mutate(codgeo = as.factor(commune_residence)) %>%
-      mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
-
-    vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-      mutate(codgeo = as.factor(epci)) %>%
-      mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
-      plyr::rbind.fill(vacc_com)
-
-    vacc$taux_cumu_1_inj[is.na(vacc$taux_cumu_1_inj)] <- 0
-
-    vacc_tot = plyr::rbind.fill(vacc_tot, vacc)
-  }
-
-  vacc_agg = vacc_tot %>%
-    select(codgeo, classe_age, population_carto, effectif_1_inj) %>%
-    filter(!(classe_age %in% c("00-19", "TOUT_AGE"))) %>%
-    group_by(codgeo) %>%
-    summarise(effectif_1_inj = sum(effectif_1_inj, na.rm = T)) %>%
-    ungroup()
-
-  vacc = vacc_agg %>%
-    inner_join(vacc1) %>%
-    mutate(taux_1_inj = effectif_1_inj/(population_carto - effectif_cumu_1_inj))
-
-  if (variable == "taux_cumu_1_inj"){
-    LOG_1107 = LOG_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-    EMP_1107 = EMP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-    FAM_1107 = FAM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-    REV_1107 = REV_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-    ACT_1107 = ACT_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-    FOR_1107 = FOR_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-    POP_1107 = POP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-    IMM_1107 = IMM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-    GEO_1107 = GEO_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-  }else if (variable == "taux_1_inj"){
-    LOG_1107 = LOG_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-    EMP_1107 = EMP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-    FAM_1107 = FAM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-    REV_1107 = REV_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-    ACT_1107 = ACT_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-    FOR_1107 = FOR_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-    POP_1107 = POP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-    IMM_1107 = IMM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-    GEO_1107 = GEO_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-  }
-
-  LOG_OR_1107 = questionr::odds.ratio(LOG_1107$`1ry_res`, LOG_1107$taux_cumu_1_inj) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`2ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Vacant_Home`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Houses`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Flats`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Nb_Rooms_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`House_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Flat_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_bf_1919`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_19-45`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_46-70`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_71-90`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_91-05`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_06-15`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_lt2y`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_2to4y`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_5to9y`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_10to19y`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_20to29y`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_gt30y`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Carpark`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_0car`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_1car`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_2car`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_3+car`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_gt0car`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Owners_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Tenant_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Social_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`FreeAcc_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Overcrowding_rate`, LOG_1107$taux_cumu_1_inj)) %>%
-    as.data.frame() %>%
-    bind_cols(Variable = colnames(LOG_1107)[2:42]) %>%
-    select(Variable, OR, `2.5 %`, `97.5 %`, p)
-  rownames(LOG_OR_1107) = NULL
-  # write_csv2(LOG_OR, "data/LOG_OR.csv")
-
-  EMP_OR_1107 = questionr::odds.ratio(EMP_1107$`1564_Workforce_rate`, EMP_1107$taux_cumu_1_inj) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1524_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`2554_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`5564_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1524_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`2554_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`5564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1524_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`2554_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`5564_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1524_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`2554_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`5564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1524_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`2554_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`5564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1524_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`2554_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`5564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1524_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`2554_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`5564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_Student_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_Retired_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_OtherInactive_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_Student_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_Retired_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_OtherInactive_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_POP`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_Farmers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_CraftsBusinessShopkeepers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_HihgQualWorkers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_IntermediateProf_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_BlueCollar_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_WhiteCollar_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_Farmers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_CraftsBusinessShopkeepers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_HihgQualWorkers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_IntermediateProf_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_BlueCollar_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_WhiteCollar_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_Salaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_NonSalaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    as.data.frame() %>%
-    bind_cols(Variable = colnames(EMP_1107)[2:63]) %>%
-    select(Variable, OR, `2.5 %`, `97.5 %`, p)
-  rownames(EMP_OR_1107) = NULL
-  # write_csv2(EMP_OR, "data/EMP_OR.csv")
-
-  FAM_OR_1107 = questionr::odds.ratio(FAM_1107$`SinglePerson_HH`, FAM_1107$taux_cumu_1_inj) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`SingleMan_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`SingleWoman_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Farmer_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`HighQualidied_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Intermediate_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`WhiteCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`15+_SinglePerson_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleMan_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleWoman_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_Farmer_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_HighQualidied_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_Intermediate_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_WhiteCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`15+_Single_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`15+_Married_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`15+_nonMarried_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Family_w_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Single_Parent_Family_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Family_wo_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    as.data.frame() %>%
-    bind_cols(Variable = colnames(FAM_1107)[2:51]) %>%
-    select(Variable, OR, `2.5 %`, `97.5 %`, p)
-  rownames(FAM_OR_1107) = NULL
-  # write_csv2(FAM_OR, "data/FAM_OR.csv")
-
-  REV_OR_1107 = questionr::odds.ratio(REV_1107$`D1_st_Living`, REV_1107$taux_cumu_1_inj) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Median_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`D9_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Interdecile_91_Ratio`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Taxable_HH`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Owners`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Tenants`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`-30_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`3039_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`4049_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`5059_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`6074_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`75+_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Activity_Income`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Salary_Income`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Unemployment_Benef`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Self-Employment`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Pensions_Annuities`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Estate`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Social_Benef`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Family_Benef`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Social_Minima`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Housing_Benef`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Tax`, REV_1107$taux_cumu_1_inj)) %>%
-    as.data.frame() %>%
-    bind_cols(Variable = colnames(REV_1107)[2:26]) %>%
-    select(Variable, OR, `2.5 %`, `97.5 %`, p)
-  rownames(REV_OR_1107) = NULL
-  # write_csv2(REV_OR, "data/REV_OR.csv")
-
-  ACT_OR_1107 = questionr::odds.ratio(ACT_1107$`Wk_Res_Municipality`, ACT_1107$taux_cumu_1_inj) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_County-Municipality`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_Region-County`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_Country-Region`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`Wk_Dom_Com_Abroad`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`noTransport_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`Walk_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`Bike_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`Motorbike_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`Drive_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`PublicTrans_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_Men_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_Women_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_PermanentContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_ShortTermContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_InterimContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_SubsidizedWork_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_ApprenticeContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_SelfEmployed_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_Employers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_caregivers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    as.data.frame() %>%
-    bind_cols(Variable = colnames(ACT_1107)[2:22]) %>%
-    select(Variable, OR, `2.5 %`, `97.5 %`, p)
-  rownames(ACT_OR_1107) = NULL
-  # write_csv2(ACT_OR, "data/ACT_OR.csv")
-
-  FOR_OR_1107 = questionr::odds.ratio(FOR_1107$`0205_School`, FOR_1107$taux_cumu_1_inj) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`0610_School`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`1114_School`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`1517_School`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`1824_School`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`2529_School`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`30+_School`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_NoDiploma_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_CertifGeneEducation_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_VocationalGraduate_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_HighSchoolGraduate_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+2_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+4_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+5+_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_HighEducation_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_men_NoDiploma_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_men_VocationalGraduate_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_men_HighSchoolGraduate_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_men_HighEducation_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_women_NoDiploma_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_women_VocationalGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighSchoolGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighEducation_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_NoDiploma`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_VocationalGraduate`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_HighSchoolGraduate`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_HighEducation`, FOR_1107$taux_cumu_1_inj)) %>%
-    as.data.frame() %>%
-    bind_cols(Variable = colnames(FOR_1107)[2:28]) %>%
-    select(Variable, OR, `2.5 %`, `97.5 %`, p)
-  rownames(FOR_OR_1107) = NULL
-  # write_csv2(FOR_OR, "data/FOR_OR.csv")
-
-  POP_OR_1107 = questionr::odds.ratio(POP_1107$`0014_amg_POP`, POP_1107$taux_cumu_1_inj) %>%
-    rbind(questionr::odds.ratio(POP_1107$`1529_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`3044_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`4559_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`6074_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`7589_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`90+_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`Men`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`0019_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`2064_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`65+_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_Farmers_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_CraftsBusinessShopkeeper_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_ManagersHigherIntellectProf_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_IntermediateProf_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_WhiteCollar_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_BlueCollar_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_Retired_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_OtherNoActivity_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`0014_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`1529_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`3044_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`4559_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`6074_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`7589_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`90+_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`0019_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`2064_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`65+_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_men_Farmers_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_men_CraftsBusinessShopkeeper_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_men_ManagersHigherIntellectProf_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_men_IntermediateProf_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_men_WhiteCollar_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_men_BlueCollar_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_men_Retired_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_men_OtherNoActivity_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`0014_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`1529_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`3044_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`4559_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`6074_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`7589_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`90+_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`0019_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`2064_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`65+_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_women_Farmers_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_women_CraftsBusinessShopkeeper_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_women_ManagersHigherIntellectProf_amh_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_women_IntermediateProf_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_women_WhiteCollar_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_women_BlueCollar_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_women_Retired_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_women_OtherNoActivity_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    as.data.frame() %>%
-    bind_cols(Variable = colnames(POP_1107)[2:56]) %>%
-    select(Variable, OR, `2.5 %`, `97.5 %`, p)
-  rownames(POP_OR_1107) = NULL
-  # write_csv2(POP_OR, "data/POP_OR.csv")
-
-  IMM_OR_1107 = questionr::odds.ratio(IMM_1107$`French_nlty`, IMM_1107$taux_cumu_1_inj) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`Stranger`, IMM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`Immigrant`, IMM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`French_nlty_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`French_nlty_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`Res_Abroad_2017`, IMM_1107$taux_cumu_1_inj)) %>%
-    as.data.frame() %>%
-    bind_cols(Variable = colnames(IMM_1107)[2:11]) %>%
-    select(Variable, OR, `2.5 %`, `97.5 %`, p)
-  rownames(IMM_OR_1107) = NULL
-  # write_csv2(IMM_OR, "data/IMM_OR.csv")
-
-  GEO_OR_1107 = questionr::odds.ratio(GEO_1107$latitude, GEO_1107$taux_cumu_1_inj) %>%
-    rbind(questionr::odds.ratio(GEO_1107$longitude, GEO_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(GEO_1107$densite, GEO_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(GEO_1107$`SO-NE`, GEO_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(GEO_1107$`NO-SE`, GEO_1107$taux_cumu_1_inj)) %>%
-    as.data.frame() %>%
-    bind_cols(Variable = colnames(GEO_1107)[2:6]) %>%
-    select(Variable, OR, `2.5 %`, `97.5 %`, p)
-  rownames(GEO_OR_1107) = NULL
-  # write_csv2(GEO_OR, "data/GEO_OR.csv")
-
-  DF_OR_1107 = LOG_OR_1107 %>% mutate(theme = "Logement", .after = Variable) %>%
-    bind_rows(EMP_OR_1107 %>% mutate(theme = "Emploi", .after = Variable)) %>%
-    bind_rows(FAM_OR_1107 %>% mutate(theme = "Famille", .after = Variable)) %>%
-    bind_rows(REV_OR_1107 %>% mutate(theme = "Revenus", .after = Variable)) %>%
-    bind_rows(ACT_OR_1107 %>% mutate(theme = "Activite", .after = Variable)) %>%
-    bind_rows(FOR_OR_1107 %>% mutate(theme = "Formation", .after = Variable)) %>%
-    bind_rows(POP_OR_1107 %>% mutate(theme = "Population", .after = Variable)) %>%
-    bind_rows(IMM_OR_1107 %>% mutate(theme = "Immigration", .after = Variable)) %>%
-    bind_rows(GEO_OR_1107 %>% mutate(theme = "Geographie", .after = Variable)) %>%
-    group_by(theme) %>%
-    mutate(id = row_number()) %>%
-    ungroup() %>%
-    mutate(inv_OR = 1/OR,
-           `inv_2.5 %` = 1/`97.5 %`,
-           `inv_97.5 %` = 1/`2.5 %`,
-           `is_OR_>1` = OR > inv_OR,
-           `max_OR-inv_OR` = if_else(`is_OR_>1`, OR, inv_OR)) %>%
-    arrange(desc(`max_OR-inv_OR`))
-  return(DF_OR_1107)
-}
+# # extraction des données et calcul des OR pour des données cumulées sur une sous période d"limitée
+# 
+# make_data_covid_cumul = function(wks, variable = "taux_1_inj", classe_age = "tous"){
+#   
+#   vacc_tot = NULL
+#   
+#   wk1 = wks[1] - 1
+#   
+#   if (wk1/10 <1){
+#     wk1 = paste0("0", wk1)
+#   }
+#   
+#   vacc_com1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk1, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+#     mutate(codgeo = as.factor(commune_residence)) %>%
+#     mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
+#   
+#   vacc1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk1, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+#     mutate(codgeo = as.factor(epci)) %>%
+#     mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+#     plyr::rbind.fill(vacc_com1) %>%
+#     filter(!(classe_age %in% c("00-19", "TOUT_AGE"))) %>%
+#     select(codgeo, classe_age, population_carto, effectif_cumu_1_inj) %>%
+#     group_by(codgeo) %>%
+#     summarise(population_carto = sum(population_carto),
+#               effectif_cumu_1_inj = sum(effectif_cumu_1_inj)) %>%
+#     ungroup()
+#   
+#   
+#   for (wk in wks){
+#     if (wk/10 <1){
+#       wk = paste0("0", wk)
+#     }
+#     
+#     
+#     
+#     vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+#       mutate(codgeo = as.factor(commune_residence)) %>%
+#       mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
+#     
+#     vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+#       mutate(codgeo = as.factor(epci)) %>%
+#       mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+#       plyr::rbind.fill(vacc_com)
+#     
+#     vacc$taux_cumu_1_inj[is.na(vacc$taux_cumu_1_inj)] <- 0
+#     
+#     vacc_tot = plyr::rbind.fill(vacc_tot, vacc)
+#   }
+#   
+#   vacc_agg = vacc_tot %>%
+#     select(codgeo, classe_age, population_carto, effectif_1_inj) %>%
+#     filter(!(classe_age %in% c("00-19", "TOUT_AGE"))) %>%
+#     group_by(codgeo) %>%
+#     summarise(effectif_1_inj = sum(effectif_1_inj, na.rm = T)) %>%
+#     ungroup()
+#   
+#   vacc = vacc_agg %>%
+#     inner_join(vacc1) %>%
+#     mutate(taux_1_inj = effectif_1_inj/(population_carto - effectif_cumu_1_inj))
+#   
+#   if (variable == "taux_cumu_1_inj"){
+#     LOG_1107 = LOG_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+#     EMP_1107 = EMP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+#     FAM_1107 = FAM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+#     REV_1107 = REV_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+#     ACT_1107 = ACT_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+#     FOR_1107 = FOR_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+#     POP_1107 = POP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+#     IMM_1107 = IMM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+#     GEO_1107 = GEO_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
+#   }else if (variable == "taux_1_inj"){
+#     LOG_1107 = LOG_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+#     EMP_1107 = EMP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+#     FAM_1107 = FAM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+#     REV_1107 = REV_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+#     ACT_1107 = ACT_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+#     FOR_1107 = FOR_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+#     POP_1107 = POP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+#     IMM_1107 = IMM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+#     GEO_1107 = GEO_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+#   }
+#   
+#   LOG_OR_1107 = questionr::odds.ratio(LOG_1107$`1ry_res`, LOG_1107$taux_cumu_1_inj) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`2ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`Vacant_Home`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`Houses`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`Flats`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`Nb_Rooms_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`House_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`Flat_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_bf_1919`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_19-45`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_46-70`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_71-90`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_91-05`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_06-15`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_lt2y`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_2to4y`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_5to9y`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_10to19y`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_20to29y`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_gt30y`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Carpark`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_0car`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_1car`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_2car`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_3+car`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_gt0car`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`Owners_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`Tenant_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`Social_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`FreeAcc_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(LOG_1107$`Overcrowding_rate`, LOG_1107$taux_cumu_1_inj)) %>%
+#     as.data.frame() %>%
+#     bind_cols(Variable = colnames(LOG_1107)[2:42]) %>%
+#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
+#   rownames(LOG_OR_1107) = NULL
+#   # write_csv2(LOG_OR, "data/LOG_OR.csv")
+#   
+#   EMP_OR_1107 = questionr::odds.ratio(EMP_1107$`1564_Workforce_rate`, EMP_1107$taux_cumu_1_inj) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1524_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`2554_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`5564_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1524_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`2554_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`5564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1524_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`2554_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`5564_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1524_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`2554_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`5564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1524_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`2554_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`5564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1524_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`2554_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`5564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1524_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`2554_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`5564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_Student_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_Retired_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_OtherInactive_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_men_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_women_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_Student_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_Retired_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_OtherInactive_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_POP`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_Farmers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_CraftsBusinessShopkeepers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_HihgQualWorkers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_IntermediateProf_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_BlueCollar_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_WhiteCollar_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_Farmers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_CraftsBusinessShopkeepers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_HihgQualWorkers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_IntermediateProf_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_BlueCollar_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`1564_WhiteCollar_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`15+_Salaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`15+_NonSalaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
+#     as.data.frame() %>%
+#     bind_cols(Variable = colnames(EMP_1107)[2:63]) %>%
+#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
+#   rownames(EMP_OR_1107) = NULL
+#   # write_csv2(EMP_OR, "data/EMP_OR.csv")
+#   
+#   FAM_OR_1107 = questionr::odds.ratio(FAM_1107$`SinglePerson_HH`, FAM_1107$taux_cumu_1_inj) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`SingleMan_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`SingleWoman_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Farmer_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`HighQualidied_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Intermediate_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`WhiteCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`15+_SinglePerson_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleMan_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleWoman_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Pop_OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Pop_Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Pop_NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Pop_ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Pop_Farmer_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Pop_CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Pop_HighQualidied_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Pop_Intermediate_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Pop_BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Pop_WhiteCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Pop_Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Pop_Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`1524_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`2554_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`5579_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`80+_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`15+_Single_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`15+_Married_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`15+_nonMarried_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`1524_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`2554_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`5579_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`80+_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`1524_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`2554_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`5579_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`80+_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Family_w_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Single_Parent_Family_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FAM_1107$`Family_wo_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+#     as.data.frame() %>%
+#     bind_cols(Variable = colnames(FAM_1107)[2:51]) %>%
+#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
+#   rownames(FAM_OR_1107) = NULL
+#   # write_csv2(FAM_OR, "data/FAM_OR.csv")
+#   
+#   REV_OR_1107 = questionr::odds.ratio(REV_1107$`D1_st_Living`, REV_1107$taux_cumu_1_inj) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`Median_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`D9_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`Interdecile_91_Ratio`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`Taxable_HH`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Owners`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Tenants`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`-30_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`3039_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`4049_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`5059_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`6074_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`75+_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`Activity_Income`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`Salary_Income`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`Unemployment_Benef`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`Self-Employment`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`Pensions_Annuities`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`Estate`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`Social_Benef`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`Family_Benef`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`Social_Minima`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`Housing_Benef`, REV_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(REV_1107$`Tax`, REV_1107$taux_cumu_1_inj)) %>%
+#     as.data.frame() %>%
+#     bind_cols(Variable = colnames(REV_1107)[2:26]) %>%
+#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
+#   rownames(REV_OR_1107) = NULL
+#   # write_csv2(REV_OR, "data/REV_OR.csv")
+#   
+#   ACT_OR_1107 = questionr::odds.ratio(ACT_1107$`Wk_Res_Municipality`, ACT_1107$taux_cumu_1_inj) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_County-Municipality`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_Region-County`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_Country-Region`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`Wk_Dom_Com_Abroad`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`noTransport_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`Walk_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`Bike_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`Motorbike_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`Drive_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`PublicTrans_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`15+_Men_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`15+_Women_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`15+_PermanentContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`15+_ShortTermContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`15+_InterimContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`15+_SubsidizedWork_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`15+_ApprenticeContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`15+_SelfEmployed_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`15+_Employers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(ACT_1107$`15+_caregivers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
+#     as.data.frame() %>%
+#     bind_cols(Variable = colnames(ACT_1107)[2:22]) %>%
+#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
+#   rownames(ACT_OR_1107) = NULL
+#   # write_csv2(ACT_OR, "data/ACT_OR.csv")
+#   
+#   FOR_OR_1107 = questionr::odds.ratio(FOR_1107$`0205_School`, FOR_1107$taux_cumu_1_inj) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`0610_School`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`1114_School`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`1517_School`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`1824_School`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`2529_School`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`30+_School`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_NoDiploma_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_CertifGeneEducation_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_VocationalGraduate_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_HighSchoolGraduate_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+2_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+4_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+5+_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_HighEducation_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_men_NoDiploma_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_men_VocationalGraduate_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_men_HighSchoolGraduate_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_men_HighEducation_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_women_NoDiploma_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_women_VocationalGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighSchoolGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighEducation_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_NoDiploma`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_VocationalGraduate`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_HighSchoolGraduate`, FOR_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_HighEducation`, FOR_1107$taux_cumu_1_inj)) %>%
+#     as.data.frame() %>%
+#     bind_cols(Variable = colnames(FOR_1107)[2:28]) %>%
+#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
+#   rownames(FOR_OR_1107) = NULL
+#   # write_csv2(FOR_OR, "data/FOR_OR.csv")
+#   
+#   POP_OR_1107 = questionr::odds.ratio(POP_1107$`0014_amg_POP`, POP_1107$taux_cumu_1_inj) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`1529_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`3044_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`4559_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`6074_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`7589_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`90+_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`Men`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`0019_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`2064_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`65+_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_Farmers_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_CraftsBusinessShopkeeper_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_ManagersHigherIntellectProf_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_IntermediateProf_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_WhiteCollar_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_BlueCollar_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_Retired_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_OtherNoActivity_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`0014_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`1529_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`3044_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`4559_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`6074_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`7589_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`90+_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`0019_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`2064_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`65+_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_men_Farmers_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_men_CraftsBusinessShopkeeper_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_men_ManagersHigherIntellectProf_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_men_IntermediateProf_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_men_WhiteCollar_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_men_BlueCollar_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_men_Retired_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_men_OtherNoActivity_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`0014_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`1529_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`3044_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`4559_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`6074_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`7589_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`90+_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`0019_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`2064_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`65+_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_women_Farmers_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_women_CraftsBusinessShopkeeper_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_women_ManagersHigherIntellectProf_amh_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_women_IntermediateProf_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_women_WhiteCollar_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_women_BlueCollar_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_women_Retired_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(POP_1107$`15+_women_OtherNoActivity_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+#     as.data.frame() %>%
+#     bind_cols(Variable = colnames(POP_1107)[2:56]) %>%
+#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
+#   rownames(POP_OR_1107) = NULL
+#   # write_csv2(POP_OR, "data/POP_OR.csv")
+#   
+#   IMM_OR_1107 = questionr::odds.ratio(IMM_1107$`French_nlty`, IMM_1107$taux_cumu_1_inj) %>%
+#     rbind(questionr::odds.ratio(IMM_1107$`Stranger`, IMM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(IMM_1107$`Immigrant`, IMM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(IMM_1107$`French_nlty_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(IMM_1107$`French_nlty_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(IMM_1107$`Res_Abroad_2017`, IMM_1107$taux_cumu_1_inj)) %>%
+#     as.data.frame() %>%
+#     bind_cols(Variable = colnames(IMM_1107)[2:11]) %>%
+#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
+#   rownames(IMM_OR_1107) = NULL
+#   # write_csv2(IMM_OR, "data/IMM_OR.csv")
+#   
+#   
+#   GEO_OR_1107 = questionr::odds.ratio(GEO_1107$latitude, GEO_1107$taux_cumu_1_inj) %>%
+#     rbind(questionr::odds.ratio(GEO_1107$longitude, GEO_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(GEO_1107$densite, GEO_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(GEO_1107$`SO-NE`, GEO_1107$taux_cumu_1_inj)) %>%
+#     rbind(questionr::odds.ratio(GEO_1107$`NO-SE`, GEO_1107$taux_cumu_1_inj)) %>%
+#     as.data.frame() %>%
+#     bind_cols(Variable = colnames(GEO_1107)[2:6]) %>%
+#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
+#   rownames(GEO_OR_1107) = NULL
+#   # write_csv2(GEO_OR, "data/GEO_OR.csv")
+#   
+#   
+#   DF_OR_1107 = LOG_OR_1107 %>% mutate(theme = "Logement", .after = Variable) %>%
+#     bind_rows(EMP_OR_1107 %>% mutate(theme = "Emploi", .after = Variable)) %>%
+#     bind_rows(FAM_OR_1107 %>% mutate(theme = "Famille", .after = Variable)) %>%
+#     bind_rows(REV_OR_1107 %>% mutate(theme = "Revenus", .after = Variable)) %>%
+#     bind_rows(ACT_OR_1107 %>% mutate(theme = "Activite", .after = Variable)) %>%
+#     bind_rows(FOR_OR_1107 %>% mutate(theme = "Formation", .after = Variable)) %>%
+#     bind_rows(POP_OR_1107 %>% mutate(theme = "Population", .after = Variable)) %>%
+#     bind_rows(IMM_OR_1107 %>% mutate(theme = "Immigration", .after = Variable)) %>%
+#     bind_rows(GEO_OR_1107 %>% mutate(theme = "Geographie", .after = Variable)) %>%
+#     group_by(theme) %>%
+#     mutate(id = row_number()) %>%
+#     ungroup() %>%
+#     mutate(inv_OR = 1/OR,
+#            `inv_2.5 %` = 1/`97.5 %`,
+#            `inv_97.5 %` = 1/`2.5 %`,
+#            `is_OR_>1` = OR > inv_OR,
+#            `max_OR-inv_OR` = if_else(`is_OR_>1`, OR, inv_OR)) %>%
+#     arrange(desc(`max_OR-inv_OR`))
+#   return(DF_OR_1107)
+# }
 ```
@@
               values_from = taux_cumu_1_inj) %>%
-  select(8,2,6,4,7,5) %>%
+  select(8,2,6,4,7,5,3) %>%
   desctable() %>%
@@
 
+On a représenté les matrices de corrélation sous forme de Heatmap.
+
+Les variables corrélées entre elles à plus de 95 % sont représentées sous forme de graphe.
+
 ## Thématique Logement
@@
 
+```{r, echo = F, message = F, warning = F}
+data_b = read_csv2("data/LOG_brut.csv") %>% select(-taux_cumu_1_inj)
+
+data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  ggplot() +
+  aes(x = Var1, y = Var2, fill = value) +
+  geom_tile(color = "white") +
+  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1,1), space = "Lab", name="Pearson\nCorrelation") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(vjust = 1, size = 12, hjust = 1, angle = 45),
+        axis.text.y = element_text(vjust = 1, size = 12, hjust = 1)) +
+  coord_fixed()
+```
+
+```{r, echo = F, message = F, warning = F}
+seuil = 0.95
+
+library(visNetwork)
+
+database = data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  filter(Var1 != Var2 & (value > seuil | value < -seuil)) %>%
+  data.frame()
+
+nodes = data.frame(label = database$Var1) %>%
+  bind_rows(data.frame(label = database$Var2)) %>%
+  unique() %>%
+  mutate(id = row_number())
+
+edges = database %>%
+  inner_join(nodes, by = c("Var1" = "label")) %>%
+  rename(from = id) %>%
+  inner_join(nodes, by = c("Var2" = "label")) %>%
+  rename(to = id) %>%
+  select(from, to)
+
+visNetwork(nodes, edges) %>%
+  visOptions(highlightNearest = TRUE)
+```
+
 ## Thématique Emploi
@@
 
+```{r, echo = F, message = F, warning = F}
+data_b = read_csv2("data/EMP_brut.csv") %>% select(-taux_cumu_1_inj)
+
+data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  ggplot() +
+  aes(x = Var1, y = Var2, fill = value) +
+  geom_tile(color = "white") +
+  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1,1), space = "Lab", name="Pearson\nCorrelation") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(vjust = 1, size = 12, hjust = 1, angle = 45),
+        axis.text.y = element_text(vjust = 1, size = 12, hjust = 1)) +
+  coord_fixed()
+```
+
+```{r, echo = F, message = F, warning = F}
+database = data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  filter(Var1 != Var2 & (value > seuil | value < -seuil)) %>%
+  data.frame()
+
+nodes = data.frame(label = database$Var1) %>%
+  bind_rows(data.frame(label = database$Var2)) %>%
+  unique() %>%
+  mutate(id = row_number())
+
+edges = database %>%
+  inner_join(nodes, by = c("Var1" = "label")) %>%
+  rename(from = id) %>%
+  inner_join(nodes, by = c("Var2" = "label")) %>%
+  rename(to = id) %>%
+  select(from, to)
+
+visNetwork(nodes, edges) %>%
+  visOptions(highlightNearest = TRUE)
+```
+
 ## Thématique Famille
@@
 
+```{r, echo = F, message = F, warning = F}
+data_b = read_csv2("data/FAM_brut.csv") %>% select(-taux_cumu_1_inj)
+
+data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  ggplot() +
+  aes(x = Var1, y = Var2, fill = value) +
+  geom_tile(color = "white") +
+  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1,1), space = "Lab", name="Pearson\nCorrelation") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(vjust = 1, size = 12, hjust = 1, angle = 45),
+        axis.text.y = element_text(vjust = 1, size = 12, hjust = 1)) +
+  coord_fixed()
+```
+
+```{r, echo = F, message = F, warning = F}
+database = data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  filter(Var1 != Var2 & (value > seuil | value < -seuil)) %>%
+  data.frame()
+
+nodes = data.frame(label = database$Var1) %>%
+  bind_rows(data.frame(label = database$Var2)) %>%
+  unique() %>%
+  mutate(id = row_number())
+
+edges = database %>%
+  inner_join(nodes, by = c("Var1" = "label")) %>%
+  rename(from = id) %>%
+  inner_join(nodes, by = c("Var2" = "label")) %>%
+  rename(to = id) %>%
+  select(from, to)
+
+visNetwork(nodes, edges) %>%
+  visOptions(highlightNearest = TRUE)
+```
+
 ## Thématique Revenus
@@
 
+```{r, echo = F, message = F, warning = F}
+data_b = read_csv2("data/REV_brut.csv") %>% select(-c(taux_cumu_1_inj,
+                                                      `Poverty_amg_Owners`,
+                                                      `-30_Poverty`,
+                                                      `3039_Poverty`,
+                                                      `4049_Poverty`,
+                                                      `5059_Poverty`,
+                                                      `6074_Poverty`,
+                                                      `75+_Poverty`))
+
+data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  ggplot() +
+  aes(x = Var1, y = Var2, fill = value) +
+  geom_tile(color = "white") +
+  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1,1), space = "Lab", name="Pearson\nCorrelation") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(vjust = 1, size = 12, hjust = 1, angle = 45),
+        axis.text.y = element_text(vjust = 1, size = 12, hjust = 1)) +
+  coord_fixed()
+```
+
+```{r, echo = F, message = F, warning = F}
+database = data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  filter(Var1 != Var2 & (value > seuil | value < -seuil)) %>%
+  data.frame()
+
+nodes = data.frame(label = database$Var1) %>%
+  bind_rows(data.frame(label = database$Var2)) %>%
+  unique() %>%
+  mutate(id = row_number())
+
+edges = database %>%
+  inner_join(nodes, by = c("Var1" = "label")) %>%
+  rename(from = id) %>%
+  inner_join(nodes, by = c("Var2" = "label")) %>%
+  rename(to = id) %>%
+  select(from, to)
+
+visNetwork(nodes, edges) %>%
+  visOptions(highlightNearest = TRUE)
+```
+
 ## Thématique Activité
@@
 
+```{r, echo = F, message = F, warning = F}
+data_b = read_csv2("data/ACT_brut.csv") %>% select(-c(taux_cumu_1_inj,
+                                                      `15+_PermanentContract_amg_salWF`,
+                                                      `15+_ShortTermContract_amg_salWF`,
+                                                      `15+_InterimContract_amg_salWF`,
+                                                      `15+_SubsidizedWork_amg_salWF`,
+                                                      `15+_ApprenticeContract_amg_salWF`,
+                                                      `15+_SelfEmployed_amg_nonsalWF`,
+                                                      `15+_Employers_amg_nonsalWF`,
+                                                      `15+_caregivers_amg_nonsalWF`))
+
+data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  ggplot() +
+  aes(x = Var1, y = Var2, fill = value) +
+  geom_tile(color = "white") +
+  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1,1), space = "Lab", name="Pearson\nCorrelation") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(vjust = 1, size = 12, hjust = 1, angle = 45),
+        axis.text.y = element_text(vjust = 1, size = 12, hjust = 1)) +
+  coord_fixed()
+```
+
+```{r, echo = F, message = F, warning = F}
+database = data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  filter(Var1 != Var2 & (value > seuil | value < -seuil)) %>%
+  data.frame()
+
+nodes = data.frame(label = database$Var1) %>%
+  bind_rows(data.frame(label = database$Var2)) %>%
+  unique() %>%
+  mutate(id = row_number())
+
+edges = database %>%
+  inner_join(nodes, by = c("Var1" = "label")) %>%
+  rename(from = id) %>%
+  inner_join(nodes, by = c("Var2" = "label")) %>%
+  rename(to = id) %>%
+  select(from, to)
+
+visNetwork(nodes, edges) %>%
+  visOptions(highlightNearest = TRUE)
+```
+
 ## Thématique Formation
@@
 
+```{r, echo = F, message = F, warning = F}
+data_b = read_csv2("data/FOR_brut.csv") %>% select(-taux_cumu_1_inj)
+
+data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  ggplot() +
+  aes(x = Var1, y = Var2, fill = value) +
+  geom_tile(color = "white") +
+  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1,1), space = "Lab", name="Pearson\nCorrelation") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(vjust = 1, size = 12, hjust = 1, angle = 45),
+        axis.text.y = element_text(vjust = 1, size = 12, hjust = 1)) +
+  coord_fixed()
+```
+
+```{r, echo = F, message = F, warning = F}
+database = data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  filter(Var1 != Var2 & (value > seuil | value < -seuil)) %>%
+  data.frame()
+
+nodes = data.frame(label = database$Var1) %>%
+  bind_rows(data.frame(label = database$Var2)) %>%
+  unique() %>%
+  mutate(id = row_number())
+
+edges = database %>%
+  inner_join(nodes, by = c("Var1" = "label")) %>%
+  rename(from = id) %>%
+  inner_join(nodes, by = c("Var2" = "label")) %>%
+  rename(to = id) %>%
+  select(from, to)
+
+visNetwork(nodes, edges) %>%
+  visOptions(highlightNearest = TRUE)
+```
+
 ## Thématique Population
@@
 
+```{r, echo = F, message = F, warning = F}
+data_b = read_csv2("data/POP_brut.csv") %>% select(-taux_cumu_1_inj)
+
+data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  ggplot() +
+  aes(x = Var1, y = Var2, fill = value) +
+  geom_tile(color = "white") +
+  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1,1), space = "Lab", name="Pearson\nCorrelation") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(vjust = 1, size = 12, hjust = 1, angle = 45),
+        axis.text.y = element_text(vjust = 1, size = 12, hjust = 1)) +
+  coord_fixed()
+```
+
+```{r, echo = F, message = F, warning = F}
+database = data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  filter(Var1 != Var2 & (value > seuil | value < -seuil)) %>%
+  data.frame()
+
+nodes = data.frame(label = database$Var1) %>%
+  bind_rows(data.frame(label = database$Var2)) %>%
+  unique() %>%
+  mutate(id = row_number())
+
+edges = database %>%
+  inner_join(nodes, by = c("Var1" = "label")) %>%
+  rename(from = id) %>%
+  inner_join(nodes, by = c("Var2" = "label")) %>%
+  rename(to = id) %>%
+  select(from, to)
+
+visNetwork(nodes, edges) %>%
+  visOptions(highlightNearest = TRUE)
+```
+
 ## Thématique Immigration
@@
 
+```{r, echo = F, message = F, warning = F}
+data_b = read_csv2("data/IMM_brut.csv") %>% select(codgeo,
+                                                   Immigrant,
+                                                   Immigrant_amg_Men,
+                                                   Immigrant_amg_Women)
+
+data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  ggplot() +
+  aes(x = Var1, y = Var2, fill = value) +
+  geom_tile(color = "white") +
+  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1,1), space = "Lab", name="Pearson\nCorrelation") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(vjust = 1, size = 12, hjust = 1, angle = 45),
+        axis.text.y = element_text(vjust = 1, size = 12, hjust = 1)) +
+  coord_fixed()
+```
+
+```{r, echo = F, message = F, warning = F}
+database = data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  filter(Var1 != Var2 & (value > seuil | value < -seuil)) %>%
+  data.frame()
+
+nodes = data.frame(label = database$Var1) %>%
+  bind_rows(data.frame(label = database$Var2)) %>%
+  unique() %>%
+  mutate(id = row_number())
+
+edges = database %>%
+  inner_join(nodes, by = c("Var1" = "label")) %>%
+  rename(from = id) %>%
+  inner_join(nodes, by = c("Var2" = "label")) %>%
+  rename(to = id) %>%
+  select(from, to)
+
+visNetwork(nodes, edges) %>%
+  visOptions(highlightNearest = TRUE)
+```
+
 ## Thématique Géographie
@@
 read.csv("data/GEO_brut.csv") %>%
-  select(-c(codgeo, taux_cumu_1_inj, SEXE.AGE3_B_POP_ENS_ENS, lat01, lon01, superficie)) %>%
-  mutate(latitude = 41+35/60+30/3600+(51+2/60+18/3600-41-35/60-30/3600)*(latitude-6069383)/(7101616-6069383),
-         longitude = -4-38/60-16/3600+(9+31/60+15/3600+4+38/60+16/3600)*(longitude+4+38/60+16/3600)/(1232484-131265)) %>%
+  select(-c(codgeo, taux_cumu_1_inj, lat01, lon01)) %>%
   desctable(stats = list("N" = length, "Med" = median, "IQR" = IQR)) %>%
@@
 ```
+
+```{r, echo = F, message = F, warning = F}
+data_b = read_csv("data/GEO_brut.csv") %>% select(codgeo, latitude, longitude, densite, `SO-NE`, `NO-SE`)
+
+data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  ggplot() +
+  aes(x = Var1, y = Var2, fill = value) +
+  geom_tile(color = "white") +
+  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1,1), space = "Lab", name="Pearson\nCorrelation") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(vjust = 1, size = 12, hjust = 1, angle = 45),
+        axis.text.y = element_text(vjust = 1, size = 12, hjust = 1)) +
+  coord_fixed()
+```
+
+```{r, echo = F, message = F, warning = F}
+database = data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  filter(Var1 != Var2 & (value > seuil | value < -seuil)) %>%
+  data.frame()
+
+nodes = data.frame(label = database$Var1) %>%
+  bind_rows(data.frame(label = database$Var2)) %>%
+  unique() %>%
+  mutate(id = row_number())
+
+edges = database %>%
+  inner_join(nodes, by = c("Var1" = "label")) %>%
+  rename(from = id) %>%
+  inner_join(nodes, by = c("Var2" = "label")) %>%
+  rename(to = id) %>%
+  select(from, to)
+
+visNetwork(nodes, edges) %>%
+  visOptions(highlightNearest = TRUE)
+```
+
+## Traitement des données manquantes
+
+On retire de l'étude les variables ayant plus de 5% de données manquantes : c'est à dire les variables dont le N est inférieur à 1492 observations.
 
@@
 data = NULL
-for (i in 22:last_week){
-  data = bind_rows(
+for (i in c(27, 31, 35)){
+  data = plyr::rbind.fill(
     data,
@@
 data %>%
-  filter(week %in% c(22, 27, 35)) %>%
   mutate(week = factor(week)) %>%
@@
 data = NULL
-for (i in 22:last_week){
+for (i in c(27, 31, 35)){
   data = bind_rows(
@@
 data %>%
-  filter(week %in% c(22, 27, 35)) %>%
+  filter(week %in% c(27, 31, 35)) %>%
   mutate(week = factor(week)) %>%
@@
 
-summary(test$`NO-SE`)
+summary(as.factor(test$`NO-SE`))
 summary(test$taux_cumu_1_inj)

### 2021-10-06 code/manhattan_animated.Rmd

@@
   LOG_OR_1107 = questionr::odds.ratio(LOG_1107$`1ry_res`, LOG_1107$taux_cumu_1_inj) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`2ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(LOG_1107$`2ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(LOG_1107$`Vacant_Home`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Houses`, LOG_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(LOG_1107$`Houses`, LOG_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(LOG_1107$`Flats`, LOG_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(LOG_1107$`Nb_Rooms_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`House_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Flat_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(LOG_1107$`House_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(LOG_1107$`Flat_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_bf_1919`, LOG_1107$taux_cumu_1_inj)) %>%
@@
     rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_gt0car`, LOG_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(LOG_1107$`1ry_res_gt0car`, LOG_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
@@
     rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Owners_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Tenant_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(LOG_1107$`Owners_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(LOG_1107$`Tenant_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(LOG_1107$`Social_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`FreeAcc_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Overcrowding_rate`, LOG_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(LOG_1107$`FreeAcc_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(LOG_1107$`Overcrowding_rate`, LOG_1107$taux_cumu_1_inj)) %>%
     as.data.frame() %>%
-    bind_cols(Variable = colnames(LOG_1107)[2:42]) %>%
+    bind_cols(Variable = colnames(LOG_1107)[c(2, 4, 6:7, 10:31, 33:36, 40)]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
     rbind(questionr::odds.ratio(EMP_1107$`1564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1524_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`1524_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(EMP_1107$`2554_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`5564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`5564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(EMP_1107$`1564_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
@@
     rbind(questionr::odds.ratio(EMP_1107$`5564_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1524_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`2554_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`5564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`1564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`1524_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`2554_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`5564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`1564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(EMP_1107$`1524_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`2554_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`2554_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(EMP_1107$`5564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`1564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(EMP_1107$`1524_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`2554_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`2554_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(EMP_1107$`5564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
@@
     rbind(questionr::odds.ratio(EMP_1107$`1524_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`2554_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`2554_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(EMP_1107$`5564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(EMP_1107$`1564_Student_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
@@
     rbind(questionr::odds.ratio(EMP_1107$`1564_OtherInactive_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_men_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_women_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`1564_men_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`1564_women_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(EMP_1107$`1564_Student_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
@@
     rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_Salaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`15+_Salaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(EMP_1107$`15+_NonSalaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
     as.data.frame() %>%
-    bind_cols(Variable = colnames(EMP_1107)[2:63]) %>%
+    bind_cols(Variable = colnames(EMP_1107)[c(2:6, 8, 10:13, 19, 21, 23, 25:27, 29, 31:33, 36:53, 55, 57, 59, 63)]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
     rbind(questionr::odds.ratio(FAM_1107$`OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(FAM_1107$`NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
@@
     rbind(questionr::odds.ratio(FAM_1107$`15+_SinglePerson_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleMan_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleWoman_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleMan_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleWoman_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Pop_OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Pop_Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Pop_NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Pop_ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(FAM_1107$`Pop_Farmer_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_HighQualidied_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_Intermediate_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Pop_CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Pop_HighQualidied_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Pop_Intermediate_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Pop_BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(FAM_1107$`Pop_WhiteCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Pop_Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Pop_Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(FAM_1107$`1524_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
@@
     rbind(questionr::odds.ratio(FAM_1107$`15+_Married_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`15+_nonMarried_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`15+_nonMarried_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`1524_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`2554_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`5579_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`80+_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(FAM_1107$`1524_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
@@
     rbind(questionr::odds.ratio(FAM_1107$`80+_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Family_w_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Single_Parent_Family_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Family_wo_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Family_w_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Single_Parent_Family_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Family_wo_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
     as.data.frame() %>%
-    bind_cols(Variable = colnames(FAM_1107)[2:51]) %>%
+    bind_cols(Variable = colnames(FAM_1107)[c(2:5, 7:18, 26, 31, 34:39, 45:48)]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
     rbind(questionr::odds.ratio(REV_1107$`Activity_Income`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Salary_Income`, REV_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(REV_1107$`Salary_Income`, REV_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(REV_1107$`Unemployment_Benef`, REV_1107$taux_cumu_1_inj)) %>%
@@
     rbind(questionr::odds.ratio(REV_1107$`Social_Minima`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Housing_Benef`, REV_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(REV_1107$`Housing_Benef`, REV_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(REV_1107$`Tax`, REV_1107$taux_cumu_1_inj)) %>%
     as.data.frame() %>%
-    bind_cols(Variable = colnames(REV_1107)[c(2:8, 15:26)]) %>%
+    bind_cols(Variable = colnames(REV_1107)[c(2:8, 15:16, 18:24, 26)]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
     rbind(questionr::odds.ratio(ACT_1107$`15+_Men_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(ACT_1107$`15+_Women_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(ACT_1107$`15+_Women_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
     # rbind(questionr::odds.ratio(ACT_1107$`15+_PermanentContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
@@
     as.data.frame() %>%
-    bind_cols(Variable = colnames(ACT_1107)[2:14]) %>%
+    bind_cols(Variable = colnames(ACT_1107)[2:13]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
     rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+2_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+4_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+5+_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+4_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+5+_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(FOR_1107$`15+_HighEducation_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_men_NoDiploma_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_men_VocationalGraduate_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FOR_1107$`15+_men_NoDiploma_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FOR_1107$`15+_men_VocationalGraduate_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(FOR_1107$`15+_men_HighSchoolGraduate_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_men_HighEducation_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_women_NoDiploma_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_women_VocationalGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighSchoolGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FOR_1107$`15+_men_HighEducation_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FOR_1107$`15+_women_NoDiploma_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FOR_1107$`15+_women_VocationalGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighSchoolGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighEducation_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
@@
     as.data.frame() %>%
-    bind_cols(Variable = colnames(FOR_1107)[2:28]) %>%
+    bind_cols(Variable = colnames(FOR_1107)[c(2:13, 16, 19, 24:28)]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
 
-  POP_OR_1107 = questionr::odds.ratio(POP_1107$`0014_amg_POP`, POP_1107$taux_cumu_1_inj) %>%
-    rbind(questionr::odds.ratio(POP_1107$`1529_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`3044_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+  POP_OR_1107 = questionr::odds.ratio(POP_1107$`3044_amg_POP`, POP_1107$taux_cumu_1_inj) %>%
     rbind(questionr::odds.ratio(POP_1107$`4559_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`6074_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`7589_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`6074_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`7589_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(POP_1107$`90+_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
@@
     rbind(questionr::odds.ratio(POP_1107$`15+_BlueCollar_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_Retired_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`15+_Retired_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(POP_1107$`15+_OtherNoActivity_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`0014_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`0014_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(POP_1107$`1529_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`3044_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`4559_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`6074_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`7589_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`3044_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`4559_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`6074_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`7589_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(POP_1107$`90+_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`0019_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`2064_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`65+_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_men_Farmers_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_men_CraftsBusinessShopkeeper_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_men_ManagersHigherIntellectProf_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`0019_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`2064_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`65+_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`15+_men_Farmers_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`15+_men_CraftsBusinessShopkeeper_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`15+_men_ManagersHigherIntellectProf_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(POP_1107$`15+_men_IntermediateProf_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(POP_1107$`15+_men_WhiteCollar_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_men_BlueCollar_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_men_Retired_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`15+_men_BlueCollar_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`15+_men_Retired_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(POP_1107$`15+_men_OtherNoActivity_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`0014_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`0014_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(POP_1107$`1529_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`3044_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`4559_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`6074_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`7589_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`90+_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`0019_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`2064_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`65+_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_women_Farmers_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`3044_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`4559_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`6074_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`7589_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`90+_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`0019_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`2064_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`65+_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`15+_women_Farmers_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(POP_1107$`15+_women_CraftsBusinessShopkeeper_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_women_ManagersHigherIntellectProf_amh_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_women_IntermediateProf_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`15+_women_ManagersHigherIntellectProf_amh_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`15+_women_IntermediateProf_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(POP_1107$`15+_women_WhiteCollar_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(POP_1107$`15+_women_BlueCollar_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_women_Retired_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(POP_1107$`15+_women_OtherNoActivity_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`15+_women_Retired_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(POP_1107$`15+_women_OtherNoActivity_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
     as.data.frame() %>%
-    bind_cols(Variable = colnames(POP_1107)[2:56]) %>%
+    bind_cols(Variable = colnames(POP_1107)[c(4:5, 8:18, 20, 22, 27, 34:35, 38, 40, 50, 53:54)]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
     # rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
     # rbind(questionr::odds.ratio(IMM_1107$`French_nlty_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
     # rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
     # rbind(questionr::odds.ratio(IMM_1107$`Res_Abroad_2017`, IMM_1107$taux_cumu_1_inj)) %>%
     as.data.frame() %>%
-    bind_cols(Variable = colnames(IMM_1107)[c(2, 5, 8)]) %>%
+    bind_cols(Variable = colnames(IMM_1107)[4]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
 
-## Traitement des données manquantes
+## Traitement des données manquantes et des fortes corrélations
 
 On retire de l'étude les variables ayant plus de 5% de données manquantes : c'est à dire les variables dont le N est inférieur à 1492 observations.
+
+De plus, quand deux variables sont fortement corrélées (à plus de 95%), on n'en garde qu'une des deux.
+
+Ces deux tris successifs permettent de réduire le nombre de variables de l'étude à **178 variables**.
 
@@
   plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-27&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-34&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-35&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
   plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-31&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")))

### 2021-10-08 code/essais_Florence.R
essais code florence

@@ -1,0 +1,326 @@
+#### INITIALIZATIONS ####
+
+# rm(list = ls())
+library("epitools")
+
+library("RColorBrewer")
+
+#### INSEE AND GEO DATA ####
+
+# Activity data
+dat.ACT <- read.csv("../data/INSEE_transformed/ACT_brut.csv", sep = ";", dec = ",")
+head(dat.ACT)
+# Remove last column 
+dat.ACT <- dat.ACT[, 1:(ncol(dat.ACT)-1)]
+
+# Employment data
+dat.EMP <- read.csv("../data/INSEE_transformed/EMP_brut.csv", sep = ";", dec = ",")
+head(dat.EMP)
+# Remove last column 
+dat.EMP <- dat.EMP[, 1:(ncol(dat.EMP)-1)]
+
+# Family data
+dat.FAM <- read.csv("../data/INSEE_transformed/FAM_brut.csv", sep = ";", dec = ",")
+head(dat.FAM)
+# Remove last column 
+dat.FAM <- dat.FAM[, 1:(ncol(dat.FAM)-1)]
+
+# Education data
+dat.FOR <- read.csv("../data/INSEE_transformed/FOR_brut.csv", sep = ";", dec = ",")
+head(dat.FOR)
+# Remove last column 
+dat.FOR <- dat.FOR[, 1:(ncol(dat.FOR)-1)]
+
+# Geographic data -- MISSING
+# dat.GEO <- read.csv("../data/INSEE_transformed/GEO_brut.csv", sep = ";", dec = ",")
+#tail(dat.GEO)
+# Remove last column 
+# dat.GEO <- dat.GEO[, -5]
+
+dat.GEO <- read.csv("../data/geographic/exportGeo_EPCI.csv")
+dat.GEO <- dat.GEO[, -1]
+head(dat.GEO)
+names(dat.GEO) <- c("long", "lat", "surf", "codgeo")
+# Compute diagonal values
+dat.GEO$SONE <- dat.GEO$lat + dat.GEO$long
+dat.GEO$SENO <- dat.GEO$lat - dat.GEO$long
+
+# Immigration data 
+dat.IMM <- read.csv("../data/INSEE_transformed/IMM_brut.csv", sep = ";", dec = ",")
+head(dat.IMM)
+# Remove last column 
+dat.IMM <- dat.IMM[, 1:(ncol(dat.IMM)-1)]
+
+# Housing data
[…]

### 2021-10-08 code/geo_communes.R

@@ -1,0 +1,30 @@
+# Load EPCI information
+epci.info <- read.csv("../data/geographic/EPCI_composition-communale.csv")
+# Turn into dico
+comm <- epci.info$EPCI
+names(comm) <- as.character(epci.info$CODGEO)
+
+# Load arrondissement information
+arr.info <- read.csv("../data/geographic/arrondissement2021.csv")
+head(arr.info)
+arr.info$codeEPCI <- comm[as.character(arr.info$CHEFLIEU)]
+
+# Append to our dictionnary
+comm <- c(epci.info$EPCI, arr.info$codeEPCI)
+names(comm) <- c(as.character(epci.info$CODGEO), as.character(arr.info$ARR))
+
+
+arr.info[arr.info$ARR == "75110", ]
+
+# Load Communes information
+vaccCom <- read.csv("../data/ameli_vaccination/vaccCom.csv", sep = ";")
+names(vaccCom)[c(3, 4)] <- c("codgeo", "libelle_geo")
+
+
+unique(vaccCom$codgeo)
+vaccCom$epci <- comm[as.character(vaccCom$codgeo)]
+vaccCom$epci
+
+
+head(vaccCom)
+unique(vaccCom$codgeo)

### 2021-10-09 code/0_INSEE_predictors.R
en cours de restructuration en plusieurs fichiers

@@ -1,0 +1,273 @@
+#### INITIALIZATIONS ####
+
+## PARAMETERS
+
+# Threshold for correlation in the variables
+thrCor <- 0.95
+
+
+## FUNCTIONS
+
+# Function to check correlations
+checkCor <- function(dat){
+  cor.dat <- cor(dat, use = "pairwise.complete.obs")
+  diag(cor.dat) <- NA
+  # Turn into binary depending on position wrt threshold
+  cor.dat2 <- 1*(abs(cor.dat) > thrCor)
+  # Remove diagonal
+  diag(cor.dat2) <- 0
+  print(sum(cor.dat2))
+  
+  # Trim table to only show lines with correlations
+  rs <- rowSums(cor.dat2)
+  keep <- (rs > 0)
+  cor.dat[keep, keep] # Output
+}
+
+#### LOAD INSEE AND GEO DATA ####
+
+#---------------------------------------------------------------------------------------
+# Activity data
+dat.ACT <- read.csv("../data/INSEE_transformed/ACT_brut.csv", sep = ";", dec = ",")
+head(dat.ACT)
+# Remove last column 
+dat.ACT <- dat.ACT[, 1:(ncol(dat.ACT)-1)]
+# Check correlations
+cor.ACT <- checkCor(dat.ACT[, -1])
+cor.ACT
+image(cor.ACT)
+heatmap(cor.ACT, Rowv = NA, Colv = NA, cexRow = 0.7, cexCol = 0.7)
+# We can remove the following ones
+rm.ACT <- c("X15._Men_amg_salWF", "X15._SelfEmployed_amg_nonsalWF")
+
+#---------------------------------------------------------------------------------------
+# Employment data
+dat.EMP <- read.csv("../data/INSEE_transformed/EMP_brut.csv", sep = ";", dec = ",")
+head(dat.EMP)
+# Remove last column 
+dat.EMP <- dat.EMP[, 1:(ncol(dat.EMP)-1)]
+# Check correlations
+cor.EMP <- checkCor(dat.EMP[, -1])
+cor.EMP
+image(cor.EMP)
+heatmap(1 * (abs(cor.EMP) > thrCor), cexRow = 0.7, cexCol = 0.7)
+
+network <- graph_from_adjacency_matrix(1 * (abs(cor.EMP) > thrCor), weighted = TRUE, mode="undirected", diag = FALSE)
+plot(network, vertex.label.cex=0.7, vertex.size = 6)
+
+# We can remove the following ones
[…]

### 2021-10-09 code/essais_Florence.R

@@ -1,119 +1,13 @@
 #### INITIALIZATIONS ####
 
-# rm(list = ls())
+rm(list = ls())
 library("epitools")
 
 library("RColorBrewer")
 
-#### INSEE AND GEO DATA ####
+library("igraph")
 
-# Activity data
-dat.ACT <- read.csv("../data/INSEE_transformed/ACT_brut.csv", sep = ";", dec = ",")
-head(dat.ACT)
-# Remove last column 
-dat.ACT <- dat.ACT[, 1:(ncol(dat.ACT)-1)]
 
-# Employment data
-dat.EMP <- read.csv("../data/INSEE_transformed/EMP_brut.csv", sep = ";", dec = ",")
-head(dat.EMP)
-# Remove last column 
-dat.EMP <- dat.EMP[, 1:(ncol(dat.EMP)-1)]
-
-# Family data
-dat.FAM <- read.csv("../data/INSEE_transformed/FAM_brut.csv", sep = ";", dec = ",")
-head(dat.FAM)
-# Remove last column 
-dat.FAM <- dat.FAM[, 1:(ncol(dat.FAM)-1)]
-
-# Education data
-dat.FOR <- read.csv("../data/INSEE_transformed/FOR_brut.csv", sep = ";", dec = ",")
-head(dat.FOR)
-# Remove last column 
-dat.FOR <- dat.FOR[, 1:(ncol(dat.FOR)-1)]
-
-# Geographic data -- MISSING
-# dat.GEO <- read.csv("../data/INSEE_transformed/GEO_brut.csv", sep = ";", dec = ",")
-#tail(dat.GEO)
-# Remove last column 
-# dat.GEO <- dat.GEO[, -5]
-
-dat.GEO <- read.csv("../data/geographic/exportGeo_EPCI.csv")
-dat.GEO <- dat.GEO[, -1]
-head(dat.GEO)
-names(dat.GEO) <- c("long", "lat", "surf", "codgeo")
-# Compute diagonal values
-dat.GEO$SONE <- dat.GEO$lat + dat.GEO$long
-dat.GEO$SENO <- dat.GEO$lat - dat.GEO$long
-
-# Immigration data 
-dat.IMM <- read.csv("../data/INSEE_transformed/IMM_brut.csv", sep = ";", dec = ",")
-head(dat.IMM)
-# Remove last column 
-dat.IMM <- dat.IMM[, 1:(ncol(dat.IMM)-1)]
-
[…]

### 2021-10-11 code/manhattan_animated.Rmd
Add files via upload

@@
 ---
-title: "Données de vaccination et "
+title: "Données de vaccination et Etude socioéconomique"
 author: "Emmanuel LECOEUR"
@@
 
+metro = read_csv("data/exportGeo_EPCI.csv") %>%
+  rename(codgeo = SIREN) %>%
+  plyr::rbind.fill(read_csv("data/exportGeo_ComArr.csv") %>%
+                     rename(codgeo = insee))
+
 # LOG_brut = 
@@
   mediane = quantile(liste, q, na.rm = T)[[1]]
-  return(as.factor(simplify2array(lapply(liste-mediane,
-                                         function(x){if_else(x < 0, 0, 1)}))))
+  return(factor(simplify2array(lapply(liste-mediane,
+                                      function(x){if_else(x < 0, 0, 1)})), ordered = T))
 }
@@
 
-  vacc$taux_cumu_1_inj[is.na(vacc$taux_cumu_1_inj)] <- 0
-  vacc$taux_1_inj[is.na(vacc$taux_cumu_1_inj)] <- 0
+  # vacc$taux_cumu_1_inj[is.na(vacc$taux_cumu_1_inj)] <- 0
+  # vacc$taux_1_inj[is.na(vacc$taux_cumu_1_inj)] <- 0
 
@@
 
-    vacc1$taux_cumu_1_inj[is.na(vacc1$taux_cumu_1_inj)] <- 0
-    vacc1$taux_1_inj[is.na(vacc1$taux_cumu_1_inj)] <- 0
+    # vacc1$taux_cumu_1_inj[is.na(vacc1$taux_cumu_1_inj)] <- 0
+    # vacc1$taux_1_inj[is.na(vacc1$taux_cumu_1_inj)] <- 0
 
@@
     rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(LOG_1107$`1ry_res_gt0car`, LOG_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`1ry_res_gt0car`, LOG_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
@@
     # rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(LOG_1107$`Owners_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(LOG_1107$`Tenant_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Owners_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Tenant_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(LOG_1107$`Social_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(LOG_1107$`FreeAcc_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(LOG_1107$`Overcrowding_rate`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`FreeAcc_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(LOG_1107$`Overcrowding_rate`, LOG_1107$taux_cumu_1_inj)) %>%
     as.data.frame() %>%
-    bind_cols(Variable = colnames(LOG_1107)[c(2, 4, 6:7, 10:31, 33:36, 40)]) %>%
+    bind_cols(Variable = colnames(LOG_1107)[c(2, 4, 6:7, 10:32, 34:36, 38:42)]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
     # rbind(questionr::odds.ratio(EMP_1107$`2554_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(EMP_1107$`5564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`5564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
     # rbind(questionr::odds.ratio(EMP_1107$`1564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
@@
     rbind(questionr::odds.ratio(EMP_1107$`5564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`1564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`1564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(EMP_1107$`1524_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(EMP_1107$`2554_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`5564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`2554_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`5564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
     # rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
@@
     rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
     # rbind(questionr::odds.ratio(EMP_1107$`15+_Salaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
@@
     # rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
@@
     as.data.frame() %>%
-    bind_cols(Variable = colnames(EMP_1107)[c(2:6, 8, 10:13, 19, 21, 23, 25:27, 29, 31:33, 36:53, 55, 57, 59, 63)]) %>%
+    bind_cols(Variable = colnames(EMP_1107)[c(2:6, 8, 10:13, 17, 19, 21, 23, 25, 27:28, 31:33, 36:52, 55, 58:59, 63)]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
     # rbind(questionr::odds.ratio(FAM_1107$`Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(FAM_1107$`ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
@@
     # rbind(questionr::odds.ratio(FAM_1107$`Pop_Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(FAM_1107$`Pop_NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
     # rbind(questionr::odds.ratio(FAM_1107$`Pop_ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
     # rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_Farmer_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Pop_Farmer_HH`, FAM_1107$taux_cumu_1_inj)) %>%
     # rbind(questionr::odds.ratio(FAM_1107$`Pop_CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
@@
     # rbind(questionr::odds.ratio(FAM_1107$`Pop_BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`Pop_WhiteCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`Pop_WhiteCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
     # rbind(questionr::odds.ratio(FAM_1107$`Pop_Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(FAM_1107$`Pop_Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`Pop_Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`1524_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`2554_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`5579_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`80+_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(FAM_1107$`15+_Single_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FAM_1107$`15+_Married_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(FAM_1107$`15+_nonMarried_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(FAM_1107$`1524_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(FAM_1107$`2554_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(FAM_1107$`5579_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(FAM_1107$`80+_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FAM_1107$`15+_Married_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`15+_nonMarried_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`1524_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`2554_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`5579_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FAM_1107$`80+_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(FAM_1107$`1524_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
@@
     as.data.frame() %>%
-    bind_cols(Variable = colnames(FAM_1107)[c(2:5, 7:18, 26, 31, 34:39, 45:48)]) %>%
+    bind_cols(Variable = colnames(FAM_1107)[c(2:5, 8:18, 23, 33, 38, 40:48)]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
     rbind(questionr::odds.ratio(REV_1107$`Taxable_HH`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Owners`, REV_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Owners`, REV_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Tenants`, REV_1107$taux_cumu_1_inj)) %>%
@@
     # rbind(questionr::odds.ratio(REV_1107$`75+_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(REV_1107$`Poverty`, REV_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(REV_1107$`Poverty`, REV_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(REV_1107$`Activity_Income`, REV_1107$taux_cumu_1_inj)) %>%
@@
     as.data.frame() %>%
-    bind_cols(Variable = colnames(REV_1107)[c(2:8, 15:16, 18:24, 26)]) %>%
+    bind_cols(Variable = colnames(REV_1107)[c(2:6, 8, 16, 18:24, 26)]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
     # rbind(questionr::odds.ratio(FOR_1107$`15+_women_VocationalGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighSchoolGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
-    rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighEducation_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighSchoolGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
+    # rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighEducation_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_NoDiploma`, FOR_1107$taux_cumu_1_inj)) %>%
@@
     as.data.frame() %>%
-    bind_cols(Variable = colnames(FOR_1107)[c(2:13, 16, 19, 24:28)]) %>%
+    bind_cols(Variable = colnames(FOR_1107)[c(2:13, 16, 19, 23, 25:28)]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
     rbind(questionr::odds.ratio(POP_1107$`4559_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(POP_1107$`6074_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`6074_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
     # rbind(questionr::odds.ratio(POP_1107$`7589_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
@@
     rbind(questionr::odds.ratio(POP_1107$`15+_BlueCollar_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(POP_1107$`15+_Retired_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_Retired_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
     rbind(questionr::odds.ratio(POP_1107$`15+_OtherNoActivity_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
@@
     # rbind(questionr::odds.ratio(POP_1107$`15+_women_Retired_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-    # rbind(questionr::odds.ratio(POP_1107$`15+_women_OtherNoActivity_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(POP_1107$`15+_women_OtherNoActivity_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
     as.data.frame() %>%
-    bind_cols(Variable = colnames(POP_1107)[c(4:5, 8:18, 20, 22, 27, 34:35, 38, 40, 50, 53:54)]) %>%
+    bind_cols(Variable = colnames(POP_1107)[c(4:6, 8:20, 22, 27, 34:35, 38, 40, 50, 53:54, 56)]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
     as.data.frame() %>%
-    bind_cols(Variable = c(colnames(GEO_1107)[2:4], "SO-NE", "NO-SE")) %>%
+    bind_cols(Variable = colnames(GEO_1107)[c(2:4, 7:8)]) %>%
     select(Variable, OR, `2.5 %`, `97.5 %`, p)
@@
 ```{r, echo = F, message = F, warning = F}
-read.csv2("data/POP.csv") %>%
+pop = read.csv2("data/POP.csv") %>%
   plyr::rbind.fill(read.csv2("data/com_POP.csv")) %>%
   select(codgeo, SEXE.AGE15_15_90_POP_ENS_ENS) %>%
-  rename(Population = SEXE.AGE15_15_90_POP_ENS_ENS) %>%
+  rename(Population = SEXE.AGE15_15_90_POP_ENS_ENS)
+pop %>%
   select(Population) %>%
@@
 Les tableaux suivants donnent les taux de vaccination totaux par tranche d'âge pour plusieurs semaines clés.
+
+On a retiré les codes insee de Mayotte puisqu'ils ne sont pas répertoriés dans l'extraction de l'insee, nous avons aussi retiré les codes suivants
+
+- 999999999, 75999, 69999, 13999 : patients dont la répartition n'est pas possible.
+
+- On ne garde aussi que les codes insee de métropole.
+On retire les 3 codes des EPCI de la métropole du grand Paris, la métropole de lyon et la métropole d'Aix-Marseille car ces données feraient doublon puisque nous avons les données de vaccinations à l'échelle de la commune pour ces EPCI.
+
+Vertaines données de vaccination sont manquantes par souci d'anonymisation sur des territoires trop peu peuplés.
 
@@
                      mutate(codgeo = commune_residence)) %>%
-  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj),
+         taux_cumu_1_inj = if_else(is.na(taux_cumu_1_inj), 0, taux_cumu_1_inj)) %>%
   # test$taux_cumu_1_inj[is.na(test$taux_cumu_1_inj)] <- 0
@@
               values_from = taux_cumu_1_inj) %>%
-  select(7, 5, 2, 3, 6, 4, 8) %>%
+  inner_join(pop %>% select(codgeo)) %>%
+  select(5,6,2,8,3,4,7) %>%
   desctable() %>%
@@
               values_from = taux_cumu_1_inj) %>%
-  select(8,2,6,4,7,5,3) %>%
+  inner_join(pop %>% select(codgeo)) %>%
+  select(5,6,2,3,7,4,8) %>%
   desctable() %>%
@@
               values_from = taux_cumu_1_inj) %>%
-  select(6,2,3,7,4,5,8) %>%
+  inner_join(pop %>% select(codgeo)) %>%
+  select(2,7,4,6,8,5,3) %>%
   desctable() %>%
@@
 ```{r, echo = F, message = F, warning = F}
-read.csv2("data/LOG_brut.csv") %>%
+read.csv("data/LOG_brut.csv") %>%
   select(-c(codgeo, taux_cumu_1_inj)) %>%
@@
 ```{r, echo = F, message = F, warning = F}
-data_b = read_csv2("data/LOG_brut.csv") %>% select(-taux_cumu_1_inj)
+data_b = read_csv("data/LOG_brut.csv") %>% select(-taux_cumu_1_inj)
 
@@
 ```{r, echo = F, message = F, warning = F}
-read.csv2("data/EMP_brut.csv") %>%
+read.csv("data/EMP_brut.csv") %>%
   select(-c(codgeo, taux_cumu_1_inj)) %>%
@@
 ```{r, echo = F, message = F, warning = F}
-data_b = read_csv2("data/EMP_brut.csv") %>% select(-taux_cumu_1_inj)
+data_b = read_csv("data/EMP_brut.csv") %>% select(-taux_cumu_1_inj)
 
@@
 ```{r, echo = F, message = F, warning = F}
-read.csv2("data/FAM_brut.csv") %>%
+read.csv("data/FAM_brut.csv") %>%
   select(-c(codgeo, taux_cumu_1_inj)) %>%
@@
 ```{r, echo = F, message = F, warning = F}
-data_b = read_csv2("data/FAM_brut.csv") %>% select(-taux_cumu_1_inj)
+data_b = read_csv("data/FAM_brut.csv") %>% select(-taux_cumu_1_inj)
 
@@
 ```{r, echo = F, message = F, warning = F}
-read.csv2("data/REV_brut.csv") %>%
+read.csv("data/REV_brut.csv") %>%
   select(-c(codgeo, taux_cumu_1_inj)) %>%
@@
 ```{r, echo = F, message = F, warning = F}
-data_b = read_csv2("data/REV_brut.csv") %>% select(-c(taux_cumu_1_inj,
+data_b = read_csv("data/REV_brut.csv") %>% select(-c(taux_cumu_1_inj,
                                                      `Poverty_amg_Owners`,
@@
 ```{r, echo = F, message = F, warning = F}
-read.csv2("data/ACT_brut.csv") %>%
+read.csv("data/ACT_brut.csv") %>%
   select(-c(codgeo, taux_cumu_1_inj)) %>%
@@
 ```{r, echo = F, message = F, warning = F}
-data_b = read_csv2("data/ACT_brut.csv") %>% select(-c(taux_cumu_1_inj,
+data_b = read_csv("data/ACT_brut.csv") %>% select(-c(taux_cumu_1_inj,
                                                      `15+_PermanentContract_amg_salWF`,
@@
 ```{r, echo = F, message = F, warning = F}
-read.csv2("data/FOR_brut.csv") %>%
+read.csv("data/FOR_brut.csv") %>%
   select(-c(codgeo, taux_cumu_1_inj)) %>%
@@
 ```{r, echo = F, message = F, warning = F}
-data_b = read_csv2("data/FOR_brut.csv") %>% select(-taux_cumu_1_inj)
+data_b = read_csv("data/FOR_brut.csv") %>% select(-taux_cumu_1_inj)
 
@@
 ```{r, echo = F, message = F, warning = F}
-read.csv2("data/POP_brut.csv") %>%
+read.csv("data/POP_brut.csv") %>%
   select(-c(codgeo, taux_cumu_1_inj)) %>%
@@
 ```{r, echo = F, message = F, warning = F}
-data_b = read_csv2("data/POP_brut.csv") %>% select(-taux_cumu_1_inj)
+data_b = read_csv("data/POP_brut.csv") %>% select(-taux_cumu_1_inj)
 
@@
 ```{r, echo = F, message = F, warning = F}
-read.csv2("data/IMM_brut.csv") %>%
+read.csv("data/IMM_brut.csv") %>%
   select(-c(codgeo, taux_cumu_1_inj)) %>%
@@
 ```{r, echo = F, message = F, warning = F}
-data_b = read_csv2("data/IMM_brut.csv") %>% select(codgeo,
+data_b = read_csv("data/IMM_brut.csv") %>% select(codgeo,
                                                   Immigrant,
@@
 
-Ces deux tris successifs permettent de réduire le nombre de variables de l'étude à **178 variables**.
+Ces deux tris successifs permettent de réduire le nombre de variables de l'étude à **181 variables** à partir des 302 variables d'origine.
+
+## Variables retenues dans l'étude
+
+```{r, warning = F, echo = F, message = F}
+read.csv("data/LOG_brut.csv") %>%
+  select(c(1, 2, 4, 6:7, 10:32, 34:36, 38:42)) %>%
+  inner_join(read.csv("data/EMP_brut.csv") %>%
+               select(c(1, 2:6, 8, 10:13, 17, 19, 21, 23, 25, 27:28, 31:33, 36:52, 55, 58:59, 63))) %>%
+  inner_join(read.csv("data/FAM_brut.csv") %>%
+               select(c(1, 2:5, 8:18, 23, 33, 38, 40:48))) %>%
+  inner_join(read.csv("data/REV_brut.csv") %>%
+               select(c(1, 2:6, 8, 16, 18:24, 26))) %>%
+  inner_join(read.csv("data/ACT_brut.csv") %>%
+               select(c(1, 2:13))) %>%
+  inner_join(read.csv("data/FOR_brut.csv") %>%
+               select(c(1, 2:13, 16, 19, 23, 25:28))) %>%
+  inner_join(read.csv("data/POP_brut.csv") %>%
+               select(c(1, 4:6, 8:20, 22, 27, 34:35, 38, 40, 50, 53:54, 56))) %>%
+  inner_join(read.csv("data/IMM_brut.csv") %>%
+               select(1, 4)) %>%
+  inner_join(read.csv("data/GEO_brut.csv") %>%
+               select(c(1, 2:4, 8:9))) %>%
+  select(-1) %>%
+  desctable() %>%
+  pander()
+```
 
@@
 ```{r, echo = F, message = F, warning = F}
+ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
+
+fig = data %>%
+  mutate(shape = if_else(OR > 1, 24, 25)) %>%
+  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
+         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
+         value = (sup-inf))
+# filter(week == 33) %>%
+# arrange(OR) %>%
+# mutate(pos2 = row_number()) %>%
+# select(Variable, pos) %>%
+# inner_join(data) %>%
+
+plot_ly(
+  fig,
+  x = ~pos,
+  y = ~`max_OR-inv_OR`,
+  size = ~-log10(p),
+  color = ~theme,
+  frame = ~week,
+  text = ~Variable,
+  alpha = 0.75,
+  symbol = ~shape,
+  symbols = c(219, 219),
+  hooverinfo = "text",
+  type = "scatter",
+  mode = "markers"
+  # error_y = list(array = ~inf,
+  #                arrayminus = ~sup,
+  #                symmetric = FALSE,
+  #                type = "data")
+) %>%
+  layout(
+    xaxis = list(title = "Variable"),
+    yaxis = list(title = "max(OR, 1/OR)"))
+
+for (wk in c(27, 31, 35)){
+  print(
+    fig %>%
+      filter(week == wk) %>%
+      ggplot() +
+      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
+      geom_pointrange() +
+      theme_minimal() +
+      labs(title = paste("OR for the whole population, week", wk),
+           x = "",
+           y = "max(OR, 1/OR)")
+  )
+}
+```
+
+```{r, eval = F, warning = F, message = F, echo = F}
+plot_ly(data.frame(x=c(1,2,3,4),
+                   y=c(2,1,3,4),
+                   array = c(0.1, 0.2, 0.1, 0.1),
+                   arrayminus = c(0.2, 0.4, 1, 0.2)),
+        x = ~x,
+        y = ~y,
+        type = "scatter",
+        mode = "markers",
+        error_y = list(type = "data",
+                       symmetric = F,
+                       array = ~array,
+                       arrayminus = ~arrayminus))
+```
+
+### Distributions des Odds ratios
+
+```{r, message = F, echo = F, warning = F}
+data %>%
+  mutate(week = factor(week)) %>%
+  ggplot() +
+  aes(x = `max_OR-inv_OR`, y = ..density.., color = week) +
+  geom_density(kernel = "gaussian") +
+  theme_bw() +
+  labs(title = "Distribution of max(OR, 1/OR) over every variable",
+       x = "max(OR, 1/OR)")
+
+# data %>%
+#   filter(week %in% c(27, 31, 35)) %>%
+#   mutate(week = factor(week)) %>%
+#   ggplot() +
+#   aes(x = log(`max_OR-inv_OR`), y = ..density.., color = week) +
+#   geom_density(kernel = "gaussian") +
+#   theme_bw() +
+#   labs(title = "Distribution of log(max(OR, 1/OR)) over every variable",
+#        x = "log(max(OR, 1/OR))")
+```
+
+### Test de Wilcoxon
+
+```{r, message = F, echo = F, warning = F}
+w1 = data %>%
+  filter(week %in% c(27, 31)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w2 = data %>%
+  filter(week %in% c(31, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w3 = data %>%
+  filter(week %in% c(27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+data.frame(Comparison = c("wk27_wk31", "wk31_wk35", "wk27_wk35"),
+           method = c(w1$method, w2$method, w3$method), p.value = c(w1$p.value, w2$p.value, w3$p.value)) %>%
+  pander()
+```
+
+<!-- === -->
+```{r, eval = F, echo = F}
+vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", "TOUT_AGE", "&refine.semaine_injection=2021-", "35", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  mutate(codgeo = as.factor(commune_residence)) %>%
+  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
+
+vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", "35", "&refine.classe_age=", "TOUT_AGE", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  mutate(codgeo = as.factor(epci)) %>%
+  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+  plyr::rbind.fill(vacc_com)
+
+test = vacc %>% inner_join(LOG_fact %>%
+                             select(codgeo, Overcrowding_rate) %>%
+                             mutate(codgeo = as.factor(codgeo))) %>%
+  mutate(taux_cumu_1_inj = binarisation(as.numeric(taux_cumu_1_inj), 0.25))
+
+summary(test$Overcrowding_rate[test$taux_cumu_1_inj == 1])
+summary(test$Overcrowding_rate[test$taux_cumu_1_inj == 0])
+
+table(test$Overcrowding_rate, test$taux_cumu_1_inj)
+
+questionr::odds.ratio(test$Overcrowding_rate, test$taux_cumu_1_inj)
+```
+
+<!-- ## Données à la semaine non cumulées -->
+
+```{r, echo = F, message = F, warning = F, eval = F}
+data = NULL
+for (i in 2:last_week){
+  data = bind_rows(
+    data,
+    make_data_covid(i, variable = "taux_1_inj") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+```
+
+```{r, echo = F, message = F, warning = F, eval = F}
+ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
+
+fig = data %>%
+  mutate(shape = if_else(OR > 1, 0, 1)) %>%
+  # filter(week == 33) %>%
+  # arrange(OR) %>%
+  # mutate(pos2 = row_number()) %>%
+  # select(Variable, pos) %>%
+  # inner_join(data) %>%
+  plot_ly(
+    x = ~pos,
+    y = ~`max_OR-inv_OR`,
+    size = ~-log10(p),
+    color = ~theme,
+    frame = ~week,
+    text = ~Variable,
+    alpha = 0.75,
+    symbol = ~shape,
+    symbols = c(219, 220),
+    hooverinfo = "text",
+    type = "scatter",
+    mode = "markers"
+  ) %>%
+  layout(
+    xaxis = list(title = "Variable"),
+    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
+fig
+```
+
+```{r, echo = F, message = F, warning = F, eval = F}
+ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
+
+fig = data %>%
+  mutate(shape = if_else(OR > 1, 220, 219)) %>%
+  # filter(week == 33) %>%
+  # arrange(OR) %>%
+  # mutate(pos2 = row_number()) %>%
+  # select(Variable, pos) %>%
+  # inner_join(data) %>%
+  plot_ly(
+    x = ~pos,
+    y = ~`max_OR-inv_OR`,
+    size = ~-log10(p),
+    color = ~theme,
+    frame = ~week,
+    text = ~Variable,
+    symbol = ~shape,
+    symbols = c(219, 220),
+    hooverinfo = "text",
+    type = "scatter",
+    mode = "markers"
+  ) %>%
+  layout(scene = list(
+    xaxis = list(title = "Variable"),
+    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim))))
+fig
+```
+
+# Par classe d'âge - données cumulées
+
+## 0 - 19 ans
+
+<!-- ### Données à la semaine -->
+
+```{r, echo = F, message = F, warning = F, eval = F}
+data = NULL
+for (i in 22:last_week){
+  data = bind_rows(
+    data,
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "00-19") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+
+# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
+#   filter(classe_age != "00-19") %>%
+#   group_by(epci) %>%
+#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
+#   ungroup()
+```
+
+```{r, echo = F, message = F, warning = F, eval = F}
 ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
@@
 
+<!-- === -->
+```{r, eval = F, echo = F}
+vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", "00-19", "&refine.semaine_injection=2021-", "35", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  mutate(codgeo = as.numeric(commune_residence)) %>%
+  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
+
+vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", "35", "&refine.classe_age=", "00-19", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  mutate(codgeo = as.numeric(epci)) %>%
+  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+  plyr::rbind.fill(vacc_com)
+
+test = vacc %>% inner_join(LOG_fact %>%
+                             select(codgeo, Overcrowding_rate)) %>%
+  mutate(taux_cumu_1_inj = binarisation(as.numeric(taux_cumu_1_inj), 0.25))
+
+summary(factor(test$Overcrowding_rate, levels = c(0,1), labels = c(0,1)))
+summary(test$taux_cumu_1_inj)
+
+table(test$Overcrowding_rate, test$taux_cumu_1_inj)
+
+questionr::odds.ratio(factor(test$Overcrowding_rate, levels = c(0,1), labels = c(0,1)), test$taux_cumu_1_inj)
+```
+
+<!-- === -->
+
+<!-- ### Données cumulées -->
+
+```{r, echo = F, message = F, warning = F}
+data = NULL
+for (i in c(27, 31, 35)){
+  data = bind_rows(
+    data,
+    make_data_covid(i, classe_age = "00-19") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+```
+
+```{r, echo = F, message = F, warning = F}
+ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
+
+fig = data %>%
+  mutate(shape = if_else(OR > 1, 24, 25)) %>%
+  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
+         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
+         value = (sup-inf))
+# filter(week == 33) %>%
+# arrange(OR) %>%
+# mutate(pos2 = row_number()) %>%
+# select(Variable, pos) %>%
+# inner_join(data) %>%
+
+plot_ly(
+  fig,
+  x = ~pos,
+  y = ~`max_OR-inv_OR`,
+  size = ~-log10(p),
+  color = ~theme,
+  frame = ~week,
+  text = ~Variable,
+  alpha = 0.75,
+  symbol = ~shape,
+  symbols = c(220, 219),
+  hooverinfo = "text",
+  type = "scatter",
+  mode = "markers"
+  # error_y = list(array = ~inf,
+  #                arrayminus = ~sup,
+  #                symmetric = FALSE,
+  #                type = "data")
+) %>%
+  layout(
+    xaxis = list(title = "Variable"),
+    yaxis = list(title = "max(OR, 1/OR)"))
+
+for (wk in c(27, 31, 35)){
+  print(
+    fig %>%
+      filter(week == wk) %>%
+      ggplot() +
+      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
+      geom_pointrange() +
+      theme_minimal() +
+      labs(title = paste("OR for the whole population, week", wk),
+           x = "",
+           y = "max(OR, 1/OR)")
+  )
+}
+```
+
 ### Distributions des Odds ratios
@@
 data %>%
+  filter(week %in% c(27, 31, 35)) %>%
   mutate(week = factor(week)) %>%
@@
 
-<!-- === -->
-```{r, eval = F, echo = F}
-vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", "TOUT_AGE", "&refine.semaine_injection=2021-", "35", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.factor(commune_residence)) %>%
-  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
-
-vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", "35", "&refine.classe_age=", "TOUT_AGE", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.factor(epci)) %>%
-  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
-  plyr::rbind.fill(vacc_com)
-
-test = vacc %>% inner_join(LOG_fact %>%
-                             select(codgeo, Overcrowding_rate)) %>%
-  mutate(taux_cumu_1_inj = binarisation(as.numeric(taux_cumu_1_inj), 0.25))
-
-summary(test$Overcrowding_rate[test$taux_cumu_1_inj == 1])
-summary(test$Overcrowding_rate[test$taux_cumu_1_inj == 0])
-
-table(test$Overcrowding_rate, test$taux_cumu_1_inj)
-
-questionr::odds.ratio(test$Overcrowding_rate, test$taux_cumu_1_inj)
-```
-
-<!-- ## Données à la semaine non cumulées -->
-
-```{r, echo = F, message = F, warning = F, eval = F}
-data = NULL
-for (i in 2:last_week){
-  data = bind_rows(
-    data,
-    make_data_covid(i, variable = "taux_1_inj") %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
-  )
-}
-```
-
-```{r, echo = F, message = F, warning = F, eval = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 0, 1)) %>%
-  # filter(week == 33) %>%
-  # arrange(OR) %>%
-  # mutate(pos2 = row_number()) %>%
-  # select(Variable, pos) %>%
-  # inner_join(data) %>%
-  plot_ly(
-    x = ~pos,
-    y = ~`max_OR-inv_OR`,
-    size = ~-log10(p),
-    color = ~theme,
-    frame = ~week,
-    text = ~Variable,
-    alpha = 0.75,
-    symbol = ~shape,
-    symbols = c(219, 220),
-    hooverinfo = "text",
-    type = "scatter",
-    mode = "markers"
-  ) %>%
-  layout(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
-fig
-```
-
-```{r, echo = F, message = F, warning = F, eval = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 220, 219)) %>%
-  # filter(week == 33) %>%
-  # arrange(OR) %>%
-  # mutate(pos2 = row_number()) %>%
-  # select(Variable, pos) %>%
-  # inner_join(data) %>%
-  plot_ly(
-    x = ~pos,
-    y = ~`max_OR-inv_OR`,
-    size = ~-log10(p),
-    color = ~theme,
-    frame = ~week,
-    text = ~Variable,
-    symbol = ~shape,
-    symbols = c(219, 220),
-    hooverinfo = "text",
-    type = "scatter",
-    mode = "markers"
-  ) %>%
-  layout(scene = list(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim))))
-fig
-```
-
-# Par classe d'âge - données cumulées
-
-## 0 - 19 ans
+## 20 - 39 ans
 
@@
     data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "00-19") %>%
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "20-39") %>%
       arrange(theme, id) %>%
@@
 
-<!-- === -->
-```{r, eval = F, echo = F}
-vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", "00-19", "&refine.semaine_injection=2021-", "35", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.numeric(commune_residence)) %>%
-  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
-
-vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", "35", "&refine.classe_age=", "00-19", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.numeric(epci)) %>%
-  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
-  plyr::rbind.fill(vacc_com)
-
-test = vacc %>% inner_join(LOG_fact %>%
-                             select(codgeo, Overcrowding_rate)) %>%
-  mutate(taux_cumu_1_inj = binarisation(as.numeric(taux_cumu_1_inj), 0.25))
-
-summary(factor(test$Overcrowding_rate, levels = c(0,1), labels = c(0,1)))
-summary(test$taux_cumu_1_inj)
-
-table(test$Overcrowding_rate, test$taux_cumu_1_inj)
-
-questionr::odds.ratio(factor(test$Overcrowding_rate, levels = c(0,1), labels = c(0,1)), test$taux_cumu_1_inj)
-```
-
-<!-- === -->
-
 <!-- ### Données cumulées -->
@@
     data,
-    make_data_covid(i, classe_age = "00-19") %>%
+    make_data_covid(i, classe_age = "20-39") %>%
       arrange(theme, id) %>%
@@
 fig = data %>%
-  mutate(shape = if_else(OR > 1, 0, 1)) %>%
+  mutate(shape = if_else(OR > 1, 24, 25)) %>%
+  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
+         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
+         value = (sup-inf))
 # filter(week == 33) %>%
@@
 # inner_join(data) %>%
+
 plot_ly(
+  fig,
   x = ~pos,
@@
   symbol = ~shape,
-    symbols = c(220, 219),
+  symbols = c(219, 219),
   hooverinfo = "text",
@@
   mode = "markers"
+  # error_y = list(array = ~inf,
+  #                arrayminus = ~sup,
+  #                symmetric = FALSE,
+  #                type = "data")
 ) %>%
@@
     xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
-fig
+    yaxis = list(title = "max(OR, 1/OR)"))
+
+for (wk in c(27, 31, 35)){
+  print(
+    fig %>%
+      filter(week == wk) %>%
+      ggplot() +
+      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
+      geom_pointrange() +
+      theme_minimal() +
+      labs(title = paste("OR for the whole population, week", wk),
+           x = "",
+           y = "max(OR, 1/OR)")
+  )
+}
 ```
@@
 data %>%
-  filter(week %in% c(27, 31, 35)) %>%
   mutate(week = factor(week)) %>%
@@
 
-## 20 - 39 ans
-
-<!-- ### Données à la semaine -->
-
-```{r, echo = F, message = F, warning = F, eval = F}
-data = NULL
-for (i in 22:last_week){
-  data = bind_rows(
-    data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "20-39") %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
-  )
-}
-
-# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
-#   filter(classe_age != "00-19") %>%
-#   group_by(epci) %>%
-#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
-#   ungroup()
-```
-
-```{r, echo = F, message = F, warning = F, eval = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 0, 1)) %>%
-  # filter(week == 33) %>%
-  # arrange(OR) %>%
-  # mutate(pos2 = row_number()) %>%
-  # select(Variable, pos) %>%
-  # inner_join(data) %>%
-  plot_ly(
-    x = ~pos,
-    y = ~`max_OR-inv_OR`,
-    size = ~-log10(p),
-    color = ~theme,
-    frame = ~week,
-    text = ~Variable,
-    alpha = 0.75,
-    symbol = ~shape,
-    symbols = c(220, 219),
-    hooverinfo = "text",
-    type = "scatter",
-    mode = "markers"
-  ) %>%
-  layout(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
-fig
-```
-
-<!-- ### Données cumulées -->
-
-```{r, echo = F, message = F, warning = F}
-data = NULL
-for (i in c(27, 31, 35)){
-  data = bind_rows(
-    data,
-    make_data_covid(i, classe_age = "20-39") %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
-  )
-}
-```
-
-```{r, echo = F, message = F, warning = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 0, 1)) %>%
-  # filter(week == 33) %>%
-  # arrange(OR) %>%
-  # mutate(pos2 = row_number()) %>%
-  # select(Variable, pos) %>%
-  # inner_join(data) %>%
-  plot_ly(
-    x = ~pos,
-    y = ~`max_OR-inv_OR`,
-    size = ~-log10(p),
-    color = ~theme,
-    frame = ~week,
-    text = ~Variable,
-    alpha = 0.75,
-    symbol = ~shape,
-    symbols = c(220, 219),
-    hooverinfo = "text",
-    type = "scatter",
-    mode = "markers"
-  ) %>%
-  layout(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
-fig
-```
-
-### Distributions des Odds ratios
-
-```{r, message = F, echo = F, warning = F}
-data %>%
-  mutate(week = factor(week)) %>%
-  ggplot() +
-  aes(x = `max_OR-inv_OR`, y = ..density.., color = week) +
-  geom_density(kernel = "gaussian") +
-  theme_bw() +
-  labs(title = "Distribution of max(OR, 1/OR) over every variable",
-       x = "max(OR, 1/OR)")
-
-# data %>%
-#   filter(week %in% c(27, 31, 35)) %>%
-#   mutate(week = factor(week)) %>%
-#   ggplot() +
-#   aes(x = log(`max_OR-inv_OR`), y = ..density.., color = week) +
-#   geom_density(kernel = "gaussian") +
-#   theme_bw() +
-#   labs(title = "Distribution of log(max(OR, 1/OR)) over every variable",
-#        x = "log(max(OR, 1/OR))")
-```
-
-### Test de Wilcoxon
-
-```{r, message = F, echo = F, warning = F}
-w1 = data %>%
-  filter(week %in% c(27, 31)) %>%
-  mutate(week = factor(week)) %>%
-  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
-
-w2 = data %>%
-  filter(week %in% c(31, 35)) %>%
-  mutate(week = factor(week)) %>%
-  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
-
-w3 = data %>%
-  filter(week %in% c(27, 35)) %>%
-  mutate(week = factor(week)) %>%
-  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
-
-data.frame(Comparison = c("wk27_wk31", "wk31_wk35", "wk27_wk35"),
-           method = c(w1$method, w2$method, w3$method), p.value = c(w1$p.value, w2$p.value, w3$p.value)) %>%
-  pander()
-```
-
 ```{r, eval = F, echo = F}
@@
       "&refine.semaine_injection=2021-",
-      "35",
+      "27",
       "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
@@
       "https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-",
-      "35",
+      "27",
       "&refine.classe_age=",
@@
 
-test = vacc %>% inner_join(GEO_fact %>%
-                             select(codgeo, `NO-SE`, latitude)) %>%
+test = vacc %>% inner_join(LOG_fact %>%
+                             select(codgeo, Overcrowding_rate)) %>%
   mutate(taux_cumu_1_inj = binarisation(as.numeric(taux_cumu_1_inj), 0.25),
-         `NO-SE` = as.factor(`NO-SE`))
-
-summary(as.factor(test$`NO-SE`))
+         Overcrowding_rate = as.factor(Overcrowding_rate))
+
+summary(as.factor(test$Overcrowding_rate))
 summary(test$taux_cumu_1_inj)
 
-table(test$`NO-SE`, test$taux_cumu_1_inj)
-
-questionr::odds.ratio(test$`NO-SE`, test$taux_cumu_1_inj)
+table(test$Overcrowding_rate, test$taux_cumu_1_inj)
+
+questionr::odds.ratio(test$Overcrowding_rate, test$taux_cumu_1_inj)
 ```
@@
 
+# Taux de vaccinations selon les modalités des 3 variables les plus discriminantes
+
+```{r, echo = F, message = F, warning = F}
+vacct = NULL
+
+for (wk in c(27, 31, 35)){
+vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  mutate(codgeo = as.numeric(commune_residence)) %>%
+  mutate(week = wk) %>%
+  select(codgeo, classe_age, population_carto, effectif_cumu_1_inj, week)
+
+vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  mutate(codgeo = as.numeric(epci)) %>%
+  mutate(week = wk) %>%
+  select(codgeo, classe_age, population_carto, effectif_cumu_1_inj, week) %>%
+  plyr::rbind.fill(vacc_com)
+
+vacct = vacct %>% plyr::rbind.fill(vacc)
+}
+
+dfocus = read_csv("data/LOG_fact.csv") %>%
+  select(codgeo, Overcrowding_rate) %>%
+  inner_join(read_csv("data/REV_fact.csv") %>%
+               select(codgeo, Unemployment_Benef, Interdecile_91_Ratio)) %>%
+  inner_join(vacct) %>%
+  pivot_longer(cols = c(Overcrowding_rate, Unemployment_Benef, Interdecile_91_Ratio),
+               names_to = "Variable",
+               values_to = "half")
+```
+
+```{r, echo = F, message = F, warning = F}
+
+  dfocus %>%
+  filter(!is.na(half)) %>%
+  group_by(classe_age, week, Variable, half) %>%
+  summarise(population_carto = sum(population_carto, na.rm = T),
+            effectif_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T)) %>%
+  ungroup() %>%
+  mutate(taux_cumu_1_inj = effectif_cumu_1_inj/population_carto,
+         Variable = paste(Variable, half)) %>%
+    plot_ly(
+      x = ~week,
+      y = ~taux_cumu_1_inj,
+      color = ~Variable,
+      symbol = ~half,
+      mode = "lines+markers",
+      frame = ~classe_age 
+    )
+
+```
+
 # Couverture vaccinale par tranche d'âge

### 2021-10-18 code/manhattan_animated.Rmd
update RMD

@@
 fig = data %>%
-  mutate(shape = if_else(OR > 1, 24, 25)) %>%
+  mutate(shape = if_else(OR > 1, 219, 220)) %>%
   mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
@@
   symbol = ~shape,
-  symbols = c(219, 219),
+  symbols = c(219, 220),
   hooverinfo = "text",
@@
 ```{r, eval = F, echo = F}
-vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", "00-19", "&refine.semaine_injection=2021-", "35", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", "TOUT_AGE", "&refine.semaine_injection=2021-", "27", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
   mutate(codgeo = as.numeric(commune_residence)) %>%
@@
 
-vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", "35", "&refine.classe_age=", "00-19", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", "27", "&refine.classe_age=", "TOUT_AGE", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
   mutate(codgeo = as.numeric(epci)) %>%
@@
 
-table(test$Overcrowding_rate, test$taux_cumu_1_inj)
+(t=table(test$Overcrowding_rate, test$taux_cumu_1_inj))
 
 questionr::odds.ratio(factor(test$Overcrowding_rate, levels = c(0,1), labels = c(0,1)), test$taux_cumu_1_inj)
+epitools::oddsratio(x = t, method = "fisher")
 ```
@@
   symbol = ~shape,
-  symbols = c(220, 219),
+  symbols = c(219, 220),
   hooverinfo = "text",
@@
 fig = data %>%
+  mutate(shape = if_else(OR > 1, 219, 220)) %>%
+  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
+         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
+         value = (sup-inf))
+# filter(week == 33) %>%
+# arrange(OR) %>%
+# mutate(pos2 = row_number()) %>%
+# select(Variable, pos) %>%
+# inner_join(data) %>%
+
+plot_ly(
+  fig,
+  x = ~pos,
+  y = ~`max_OR-inv_OR`,
+  size = ~-log10(p),
+  color = ~theme,
+  frame = ~week,
+  text = ~Variable,
+  alpha = 0.75,
+  symbol = ~shape,
+  symbols = c(219, 220),
+  hooverinfo = "text",
+  type = "scatter",
+  mode = "markers"
+  # error_y = list(array = ~inf,
+  #                arrayminus = ~sup,
+  #                symmetric = FALSE,
+  #                type = "data")
+) %>%
+  layout(
+    xaxis = list(title = "Variable"),
+    yaxis = list(title = "max(OR, 1/OR)"))
+
+for (wk in c(27, 31, 35)){
+  print(
+    fig %>%
+      filter(week == wk) %>%
+      ggplot() +
+      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
+      geom_pointrange() +
+      theme_minimal() +
+      labs(title = paste("OR for the whole population, week", wk),
+           x = "",
+           y = "max(OR, 1/OR)")
+  )
+}
+```
+
+### Distributions des Odds ratios
+
+```{r, message = F, echo = F, warning = F}
+data %>%
+  mutate(week = factor(week)) %>%
+  ggplot() +
+  aes(x = `max_OR-inv_OR`, y = ..density.., color = week) +
+  geom_density(kernel = "gaussian") +
+  theme_bw() +
+  labs(title = "Distribution of max(OR, 1/OR) over every variable",
+       x = "max(OR, 1/OR)")
+
+# data %>%
+#   filter(week %in% c(27, 31, 35)) %>%
+#   mutate(week = factor(week)) %>%
+#   ggplot() +
+#   aes(x = log(`max_OR-inv_OR`), y = ..density.., color = week) +
+#   geom_density(kernel = "gaussian") +
+#   theme_bw() +
+#   labs(title = "Distribution of log(max(OR, 1/OR)) over every variable",
+#        x = "log(max(OR, 1/OR))")
+```
+
+### Test de Wilcoxon
+
+```{r, message = F, echo = F, warning = F}
+w1 = data %>%
+  filter(week %in% c(27, 31)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w2 = data %>%
+  filter(week %in% c(31, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w3 = data %>%
+  filter(week %in% c(27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+data.frame(Comparison = c("wk27_wk31", "wk31_wk35", "wk27_wk35"),
+           method = c(w1$method, w2$method, w3$method), p.value = c(w1$p.value, w2$p.value, w3$p.value)) %>%
+  pander()
+```
+
+```{r, eval = F, echo = F}
+vacc_com = read_csv2(
+  url(
+    paste0(
+      "https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=",
+      "75+et+%2B",
+      "&refine.semaine_injection=2021-",
+      "27",
+      "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  mutate(codgeo = as.numeric(commune_residence)) %>%
+  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
+
+vacc = read_csv2(
+  url(
+    paste0(
+      "https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-",
+      "27",
+      "&refine.classe_age=",
+      "75+et+%2B",
+      "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  mutate(codgeo = as.numeric(epci)) %>%
+  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
+  plyr::rbind.fill(vacc_com)
+
+test = vacc %>% inner_join(LOG_fact %>%
+                             select(codgeo, Overcrowding_rate)) %>%
+  mutate(taux_cumu_1_inj = binarisation(as.numeric(taux_cumu_1_inj), 0.25),
+         Overcrowding_rate = as.factor(Overcrowding_rate))
+
+summary(as.factor(test$Overcrowding_rate))
+summary(test$taux_cumu_1_inj)
+
+table(test$Overcrowding_rate, test$taux_cumu_1_inj)
+
+questionr::odds.ratio(test$Overcrowding_rate, test$taux_cumu_1_inj)
+```
+
+## 40 - 54 ans
+
+<!-- ### Données à la semaine -->
+
+```{r, echo = F, message = F, warning = F, eval = F}
+data = NULL
+for (i in 22:last_week){
+  data = bind_rows(
+    data,
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "40-54") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+
+# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
+#   filter(classe_age != "00-19") %>%
+#   group_by(epci) %>%
+#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
+#   ungroup()
+```
+
+```{r, echo = F, message = F, warning = F, eval = F}
+ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
+
+fig = data %>%
   mutate(shape = if_else(OR > 1, 24, 25)) %>%
@@
 
+<!-- ### Données cumulées -->
+
+```{r, echo = F, message = F, warning = F}
+data = NULL
+for (i in c(27, 31, 35)){
+  data = bind_rows(
+    data,
+    make_data_covid(i, classe_age = "40-54") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+```
+
+```{r, echo = F, message = F, warning = F}
+ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
+
+fig = data %>%
+  mutate(shape = if_else(OR > 1, 219, 220)) %>%
+  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
+         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
+         value = (sup-inf))
+# filter(week == 33) %>%
+# arrange(OR) %>%
+# mutate(pos2 = row_number()) %>%
+# select(Variable, pos) %>%
+# inner_join(data) %>%
+
+plot_ly(
+  fig,
+  x = ~pos,
+  y = ~`max_OR-inv_OR`,
+  size = ~-log10(p),
+  color = ~theme,
+  frame = ~week,
+  text = ~Variable,
+  alpha = 0.75,
+  symbol = ~shape,
+  symbols = c(219, 220),
+  hooverinfo = "text",
+  type = "scatter",
+  mode = "markers"
+  # error_y = list(array = ~inf,
+  #                arrayminus = ~sup,
+  #                symmetric = FALSE,
+  #                type = "data")
+) %>%
+  layout(
+    xaxis = list(title = "Variable"),
+    yaxis = list(title = "max(OR, 1/OR)"))
+
+for (wk in c(27, 31, 35)){
+  print(
+    fig %>%
+      filter(week == wk) %>%
+      ggplot() +
+      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
+      geom_pointrange() +
+      theme_minimal() +
+      labs(title = paste("OR for the whole population, week", wk),
+           x = "",
+           y = "max(OR, 1/OR)")
+  )
+}
+```
+
 ### Distributions des Odds ratios
@@
 
-```{r, eval = F, echo = F}
-vacc_com = read_csv2(
-  url(
-    paste0(
-      "https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=",
-      "75+et+%2B",
-      "&refine.semaine_injection=2021-",
-      "27",
-      "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.numeric(commune_residence)) %>%
-  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
-
-vacc = read_csv2(
-  url(
-    paste0(
-      "https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-",
-      "27",
-      "&refine.classe_age=",
-      "75+et+%2B",
-      "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.numeric(epci)) %>%
-  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
-  plyr::rbind.fill(vacc_com)
-
-test = vacc %>% inner_join(LOG_fact %>%
-                             select(codgeo, Overcrowding_rate)) %>%
-  mutate(taux_cumu_1_inj = binarisation(as.numeric(taux_cumu_1_inj), 0.25),
-         Overcrowding_rate = as.factor(Overcrowding_rate))
-
-summary(as.factor(test$Overcrowding_rate))
-summary(test$taux_cumu_1_inj)
-
-table(test$Overcrowding_rate, test$taux_cumu_1_inj)
-
-questionr::odds.ratio(test$Overcrowding_rate, test$taux_cumu_1_inj)
-```
-
-## 40 - 54 ans
+## 55 - 64 ans
 
@@
     data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "40-54") %>%
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "55-64") %>%
       arrange(theme, id) %>%
@@
     data,
-    make_data_covid(i, classe_age = "40-54") %>%
+    make_data_covid(i, classe_age = "55-64") %>%
       arrange(theme, id) %>%
@@
 ```{r, echo = F, message = F, warning = F}
+ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
+
+fig = data %>%
+  mutate(shape = if_else(OR > 1, 219, 220)) %>%
+  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
+         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
+         value = (sup-inf))
+# filter(week == 33) %>%
+# arrange(OR) %>%
+# mutate(pos2 = row_number()) %>%
+# select(Variable, pos) %>%
+# inner_join(data) %>%
+
+plot_ly(
+  fig,
+  x = ~pos,
+  y = ~`max_OR-inv_OR`,
+  size = ~-log10(p),
+  color = ~theme,
+  frame = ~week,
+  text = ~Variable,
+  alpha = 0.75,
+  symbol = ~shape,
+  symbols = c(219, 220),
+  hooverinfo = "text",
+  type = "scatter",
+  mode = "markers"
+  # error_y = list(array = ~inf,
+  #                arrayminus = ~sup,
+  #                symmetric = FALSE,
+  #                type = "data")
+) %>%
+  layout(
+    xaxis = list(title = "Variable"),
+    yaxis = list(title = "max(OR, 1/OR)"))
+
+for (wk in c(27, 31, 35)){
+  print(
+    fig %>%
+      filter(week == wk) %>%
+      ggplot() +
+      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
+      geom_pointrange() +
+      theme_minimal() +
+      labs(title = paste("OR for the whole population, week", wk),
+           x = "",
+           y = "max(OR, 1/OR)")
+  )
+}
+```
+
+### Distributions des Odds ratios
+
+```{r, message = F, echo = F, warning = F}
+data %>%
+  mutate(week = factor(week)) %>%
+  ggplot() +
+  aes(x = `max_OR-inv_OR`, y = ..density.., color = week) +
+  geom_density(kernel = "gaussian") +
+  theme_bw() +
+  labs(title = "Distribution of max(OR, 1/OR) over every variable",
+       x = "max(OR, 1/OR)")
+
+# data %>%
+#   filter(week %in% c(27, 31, 35)) %>%
+#   mutate(week = factor(week)) %>%
+#   ggplot() +
+#   aes(x = log(`max_OR-inv_OR`), y = ..density.., color = week) +
+#   geom_density(kernel = "gaussian") +
+#   theme_bw() +
+#   labs(title = "Distribution of log(max(OR, 1/OR)) over every variable",
+#        x = "log(max(OR, 1/OR))")
+```
+
+### Test de Wilcoxon
+
+```{r, message = F, echo = F, warning = F}
+w1 = data %>%
+  filter(week %in% c(27, 31)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w2 = data %>%
+  filter(week %in% c(31, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w3 = data %>%
+  filter(week %in% c(27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+data.frame(Comparison = c("wk27_wk31", "wk31_wk35", "wk27_wk35"),
+           method = c(w1$method, w2$method, w3$method), p.value = c(w1$p.value, w2$p.value, w3$p.value)) %>%
+  pander()
+```
+
+## 65 - 74 ans
+
+<!-- ### Données à la semaine -->
+
+```{r, echo = F, message = F, warning = F, eval = F}
+data = NULL
+for (i in 22:last_week){
+  data = bind_rows(
+    data,
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "65-74") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+
+# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
+#   filter(classe_age != "00-19") %>%
+#   group_by(epci) %>%
+#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
+#   ungroup()
+```
+
+```{r, echo = F, message = F, warning = F, eval = F}
 ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
@@
 
+<!-- ### Données cumulées -->
+
+```{r, echo = F, message = F, warning = F}
+data = NULL
+for (i in c(27, 31, 35)){
+  data = bind_rows(
+    data,
+    make_data_covid(i, classe_age = "65-74") %>%
+      arrange(theme, id) %>%
+      mutate (pos = row_number(),
+              week = i)
+  )
+}
+```
+
+```{r, echo = F, message = F, warning = F}
+ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
+
+fig = data %>%
+  mutate(shape = if_else(OR > 1, 219, 220)) %>%
+  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
+         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
+         value = (sup-inf))
+# filter(week == 33) %>%
+# arrange(OR) %>%
+# mutate(pos2 = row_number()) %>%
+# select(Variable, pos) %>%
+# inner_join(data) %>%
+
+plot_ly(
+  fig,
+  x = ~pos,
+  y = ~`max_OR-inv_OR`,
+  size = ~-log10(p),
+  color = ~theme,
+  frame = ~week,
+  text = ~Variable,
+  alpha = 0.75,
+  symbol = ~shape,
+  symbols = c(219, 220),
+  hooverinfo = "text",
+  type = "scatter",
+  mode = "markers"
+  # error_y = list(array = ~inf,
+  #                arrayminus = ~sup,
+  #                symmetric = FALSE,
+  #                type = "data")
+) %>%
+  layout(
+    xaxis = list(title = "Variable"),
+    yaxis = list(title = "max(OR, 1/OR)"))
+
+for (wk in c(27, 31, 35)){
+  print(
+    fig %>%
+      filter(week == wk) %>%
+      ggplot() +
+      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
+      geom_pointrange() +
+      theme_minimal() +
+      labs(title = paste("OR for the whole population, week", wk),
+           x = "",
+           y = "max(OR, 1/OR)")
+  )
+}
+```
+
 ### Distributions des Odds ratios
@@
 
-## 55 - 64 ans
+## 75 ans et plus
 
@@
     data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "55-64") %>%
+    make_data_covid(i, variable = "taux_1_inj", classe_age = "75+et+%2B") %>%
       arrange(theme, id) %>%
@@
     data,
-    make_data_covid(i, classe_age = "55-64") %>%
+    make_data_covid(i, classe_age = "75+et+%2B") %>%
       arrange(theme, id) %>%
@@
   symbol = ~shape,
-  symbols = c(219, 219),
-  hooverinfo = "text",
-  type = "scatter",
-  mode = "markers"
-  # error_y = list(array = ~inf,
-  #                arrayminus = ~sup,
-  #                symmetric = FALSE,
-  #                type = "data")
-) %>%
-  layout(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)"))
-
-for (wk in c(27, 31, 35)){
-  print(
-    fig %>%
-      filter(week == wk) %>%
-      ggplot() +
-      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
-      geom_pointrange() +
-      theme_minimal() +
-      labs(title = paste("OR for the whole population, week", wk),
-           x = "",
-           y = "max(OR, 1/OR)")
-  )
-}
-```
-
-### Distributions des Odds ratios
-
-```{r, message = F, echo = F, warning = F}
-data %>%
-  mutate(week = factor(week)) %>%
-  ggplot() +
-  aes(x = `max_OR-inv_OR`, y = ..density.., color = week) +
-  geom_density(kernel = "gaussian") +
-  theme_bw() +
-  labs(title = "Distribution of max(OR, 1/OR) over every variable",
-       x = "max(OR, 1/OR)")
-
-# data %>%
-#   filter(week %in% c(27, 31, 35)) %>%
-#   mutate(week = factor(week)) %>%
-#   ggplot() +
-#   aes(x = log(`max_OR-inv_OR`), y = ..density.., color = week) +
-#   geom_density(kernel = "gaussian") +
-#   theme_bw() +
-#   labs(title = "Distribution of log(max(OR, 1/OR)) over every variable",
-#        x = "log(max(OR, 1/OR))")
-```
-
-### Test de Wilcoxon
-
-```{r, message = F, echo = F, warning = F}
-w1 = data %>%
-  filter(week %in% c(27, 31)) %>%
-  mutate(week = factor(week)) %>%
-  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
-
-w2 = data %>%
-  filter(week %in% c(31, 35)) %>%
-  mutate(week = factor(week)) %>%
-  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
-
-w3 = data %>%
-  filter(week %in% c(27, 35)) %>%
-  mutate(week = factor(week)) %>%
-  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
-
-data.frame(Comparison = c("wk27_wk31", "wk31_wk35", "wk27_wk35"),
-           method = c(w1$method, w2$method, w3$method), p.value = c(w1$p.value, w2$p.value, w3$p.value)) %>%
-  pander()
-```
-
-## 65 - 74 ans
-
-<!-- ### Données à la semaine -->
-
-```{r, echo = F, message = F, warning = F, eval = F}
-data = NULL
-for (i in 22:last_week){
-  data = bind_rows(
-    data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "65-74") %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
-  )
-}
-
-# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
-#   filter(classe_age != "00-19") %>%
-#   group_by(epci) %>%
-#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
-#   ungroup()
-```
-
-```{r, echo = F, message = F, warning = F, eval = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 24, 25)) %>%
-  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
-         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
-         value = (sup-inf))
-# filter(week == 33) %>%
-# arrange(OR) %>%
-# mutate(pos2 = row_number()) %>%
-# select(Variable, pos) %>%
-# inner_join(data) %>%
-
-plot_ly(
-  fig,
-  x = ~pos,
-  y = ~`max_OR-inv_OR`,
-  size = ~-log10(p),
-  color = ~theme,
-  frame = ~week,
-  text = ~Variable,
-  alpha = 0.75,
-  symbol = ~shape,
-  symbols = c(219, 219),
-  hooverinfo = "text",
-  type = "scatter",
-  mode = "markers"
-  # error_y = list(array = ~inf,
-  #                arrayminus = ~sup,
-  #                symmetric = FALSE,
-  #                type = "data")
-) %>%
-  layout(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)"))
-
-for (wk in c(27, 31, 35)){
-  print(
-    fig %>%
-      filter(week == wk) %>%
-      ggplot() +
-      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
-      geom_pointrange() +
-      theme_minimal() +
-      labs(title = paste("OR for the whole population, week", wk),
-           x = "",
-           y = "max(OR, 1/OR)")
-  )
-}
-```
-
-<!-- ### Données cumulées -->
-
-```{r, echo = F, message = F, warning = F}
-data = NULL
-for (i in c(27, 31, 35)){
-  data = bind_rows(
-    data,
-    make_data_covid(i, classe_age = "65-74") %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
-  )
-}
-```
-
-```{r, echo = F, message = F, warning = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 24, 25)) %>%
-  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
-         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
-         value = (sup-inf))
-# filter(week == 33) %>%
-# arrange(OR) %>%
-# mutate(pos2 = row_number()) %>%
-# select(Variable, pos) %>%
-# inner_join(data) %>%
-
-plot_ly(
-  fig,
-  x = ~pos,
-  y = ~`max_OR-inv_OR`,
-  size = ~-log10(p),
-  color = ~theme,
-  frame = ~week,
-  text = ~Variable,
-  alpha = 0.75,
-  symbol = ~shape,
-  symbols = c(219, 219),
-  hooverinfo = "text",
-  type = "scatter",
-  mode = "markers"
-  # error_y = list(array = ~inf,
-  #                arrayminus = ~sup,
-  #                symmetric = FALSE,
-  #                type = "data")
-) %>%
-  layout(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)"))
-
-for (wk in c(27, 31, 35)){
-  print(
-    fig %>%
-      filter(week == wk) %>%
-      ggplot() +
-      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
-      geom_pointrange() +
-      theme_minimal() +
-      labs(title = paste("OR for the whole population, week", wk),
-           x = "",
-           y = "max(OR, 1/OR)")
-  )
-}
-```
-
-### Distributions des Odds ratios
-
-```{r, message = F, echo = F, warning = F}
-data %>%
-  mutate(week = factor(week)) %>%
-  ggplot() +
-  aes(x = `max_OR-inv_OR`, y = ..density.., color = week) +
-  geom_density(kernel = "gaussian") +
-  theme_bw() +
-  labs(title = "Distribution of max(OR, 1/OR) over every variable",
-       x = "max(OR, 1/OR)")
-
-# data %>%
-#   filter(week %in% c(27, 31, 35)) %>%
-#   mutate(week = factor(week)) %>%
-#   ggplot() +
-#   aes(x = log(`max_OR-inv_OR`), y = ..density.., color = week) +
-#   geom_density(kernel = "gaussian") +
-#   theme_bw() +
-#   labs(title = "Distribution of log(max(OR, 1/OR)) over every variable",
-#        x = "log(max(OR, 1/OR))")
-```
-
-### Test de Wilcoxon
-
-```{r, message = F, echo = F, warning = F}
-w1 = data %>%
-  filter(week %in% c(27, 31)) %>%
-  mutate(week = factor(week)) %>%
-  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
-
-w2 = data %>%
-  filter(week %in% c(31, 35)) %>%
-  mutate(week = factor(week)) %>%
-  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
-
-w3 = data %>%
-  filter(week %in% c(27, 35)) %>%
-  mutate(week = factor(week)) %>%
-  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
-
-data.frame(Comparison = c("wk27_wk31", "wk31_wk35", "wk27_wk35"),
-           method = c(w1$method, w2$method, w3$method), p.value = c(w1$p.value, w2$p.value, w3$p.value)) %>%
-  pander()
-```
-
-## 75 ans et plus
-
-<!-- ### Données à la semaine -->
-
-```{r, echo = F, message = F, warning = F, eval = F}
-data = NULL
-for (i in 22:last_week){
-  data = bind_rows(
-    data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "75+et+%2B") %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
-  )
-}
-
-# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
-#   filter(classe_age != "00-19") %>%
-#   group_by(epci) %>%
-#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
-#   ungroup()
-```
-
-```{r, echo = F, message = F, warning = F, eval = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 24, 25)) %>%
-  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
-         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
-         value = (sup-inf))
-# filter(week == 33) %>%
-# arrange(OR) %>%
-# mutate(pos2 = row_number()) %>%
-# select(Variable, pos) %>%
-# inner_join(data) %>%
-
-plot_ly(
-  fig,
-  x = ~pos,
-  y = ~`max_OR-inv_OR`,
-  size = ~-log10(p),
-  color = ~theme,
-  frame = ~week,
-  text = ~Variable,
-  alpha = 0.75,
-  symbol = ~shape,
-  symbols = c(219, 219),
-  hooverinfo = "text",
-  type = "scatter",
-  mode = "markers"
-  # error_y = list(array = ~inf,
-  #                arrayminus = ~sup,
-  #                symmetric = FALSE,
-  #                type = "data")
-) %>%
-  layout(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)"))
-
-for (wk in c(27, 31, 35)){
-  print(
-    fig %>%
-      filter(week == wk) %>%
-      ggplot() +
-      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
-      geom_pointrange() +
-      theme_minimal() +
-      labs(title = paste("OR for the whole population, week", wk),
-           x = "",
-           y = "max(OR, 1/OR)")
-  )
-}
-```
-
-<!-- ### Données cumulées -->
-
-```{r, echo = F, message = F, warning = F}
-data = NULL
-for (i in c(27, 31, 35)){
-  data = bind_rows(
-    data,
-    make_data_covid(i, classe_age = "75+et+%2B") %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
-  )
-}
-```
-
-```{r, echo = F, message = F, warning = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 24, 25)) %>%
-  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
-         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
-         value = (sup-inf))
-# filter(week == 33) %>%
-# arrange(OR) %>%
-# mutate(pos2 = row_number()) %>%
-# select(Variable, pos) %>%
-# inner_join(data) %>%
-
-plot_ly(
-  fig,
-  x = ~pos,
-  y = ~`max_OR-inv_OR`,
-  size = ~-log10(p),
-  color = ~theme,
-  frame = ~week,
-  text = ~Variable,
-  alpha = 0.75,
-  symbol = ~shape,
-  symbols = c(219, 219),
+  symbols = c(219, 220),
   hooverinfo = "text",
@@
 ```
+
+<!-- # Données de vaccination nationales -->
+
+```{r, echo = F, warning = F, message = F, eval = F}
+wk = 37
+
+vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  mutate(codgeo = as.numeric(commune_residence)) %>%
+  mutate(week = wk) %>%
+  select(codgeo, classe_age, population_carto, effectif_cumu_1_inj, week)
+
+vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  mutate(codgeo = as.numeric(epci)) %>%
+  mutate(week = wk) %>%
+  select(codgeo, classe_age, population_carto, effectif_cumu_1_inj, week) %>%
+  plyr::rbind.fill(vacc_com)
+
+vacc %>%
+  filter(!is.na(effectif_cumu_1_inj)) %>%
+  group_by(classe_age) %>%
+  summarise(pop = sum(population_carto, na.rm = T),
+            tot_vacc = sum(effectif_cumu_1_inj, na.rm = T)) %>%
+  ungroup() %>%
+  mutate(tx_vacc = tot_vacc/pop)
+```

### 2021-11-05 plots/manhattan_animated.Rmd
last version of the rmd
add final plots

--- 2021-10-18 code/manhattan_animated.Rmd
@@
 
-```{r, echo = F, message = F, warning = F}
+```{r, options, echo = F, message = F, warning = F}
 # knitr::opts_chunk$set(echo = F, warning = F, message = F)
@@
 
-```{r, echo = F, message = F, warning = F}
+```{r, libraries, echo = F, message = F, warning = F}
 library(tidyverse)
@@
 
-```{r, echo = F, message = F, warning = F}
+```{r, insee-data, echo = F, message = F, warning = F}
 last_week = 35
@@
 
-```{r, echo = F, message = F, warning = F}
+```{r, functions, echo = F, message = F, warning = F}
+# useful functions for correlation matrix
 get_upper_tri <- function(cormat){
@@
 binarisation = function(liste, q = 0.5){
+  # dichotomisation od a numeric variable between a quantile threshold
   mediane = quantile(liste, q, na.rm = T)[[1]]
@@
 
-  if (variable == "taux_cumu_1_inj"){
+  if (variable == "taux_cumu_1_inj"){ # dans la pratique on sera toujours dans ce cas
     LOG_1107 = LOG_fact %>%
-      select(-taux_cumu_1_inj) %>%
-      inner_join(vacc) %>%
-      mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)),
+      select(-taux_cumu_1_inj) %>% # suppression d'une variable
+      inner_join(vacc) %>% # jointure naturelle
+      mutate(
+        # Application de la fonction binarisation avec le seuil de 0.25 et mise en facteurs des variables
+        taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)), 
              across(-c(codgeo, taux_cumu_1_inj), function(x){
@@
   }
+
+  # calcul des OR - j'aurais très probablement pu faire tout ca en beaucoup moins de lignes mais j'avoue que je ne me suis pas vraiment penché sur la question.
 
@@
 
+  # combinaison des tables
+
   DF_OR_1107 = LOG_OR_1107 %>% mutate(theme = "Housing", .after = Variable) %>%
@@
 }
-
-# # extraction des données et calcul des OR pour des données cumulées sur une sous période d"limitée
-# 
-# make_data_covid_cumul = function(wks, variable = "taux_1_inj", classe_age = "tous"){
-#   
-#   vacc_tot = NULL
-#   
-#   wk1 = wks[1] - 1
-#   
-#   if (wk1/10 <1){
-#     wk1 = paste0("0", wk1)
-#   }
-#   
-#   vacc_com1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk1, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-#     mutate(codgeo = as.factor(commune_residence)) %>%
-#     mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
-#   
-#   vacc1 = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk1, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-#     mutate(codgeo = as.factor(epci)) %>%
-#     mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
-#     plyr::rbind.fill(vacc_com1) %>%
-#     filter(!(classe_age %in% c("00-19", "TOUT_AGE"))) %>%
-#     select(codgeo, classe_age, population_carto, effectif_cumu_1_inj) %>%
-#     group_by(codgeo) %>%
-#     summarise(population_carto = sum(population_carto),
-#               effectif_cumu_1_inj = sum(effectif_cumu_1_inj)) %>%
-#     ungroup()
-#   
-#   
-#   for (wk in wks){
-#     if (wk/10 <1){
-#       wk = paste0("0", wk)
-#     }
-#     
-#     
-#     
-#     vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-#       mutate(codgeo = as.factor(commune_residence)) %>%
-#       mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
-#     
-#     vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-#       mutate(codgeo = as.factor(epci)) %>%
-#       mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
-#       plyr::rbind.fill(vacc_com)
-#     
-#     vacc$taux_cumu_1_inj[is.na(vacc$taux_cumu_1_inj)] <- 0
-#     
-#     vacc_tot = plyr::rbind.fill(vacc_tot, vacc)
-#   }
-#   
-#   vacc_agg = vacc_tot %>%
-#     select(codgeo, classe_age, population_carto, effectif_1_inj) %>%
-#     filter(!(classe_age %in% c("00-19", "TOUT_AGE"))) %>%
-#     group_by(codgeo) %>%
-#     summarise(effectif_1_inj = sum(effectif_1_inj, na.rm = T)) %>%
-#     ungroup()
-#   
-#   vacc = vacc_agg %>%
-#     inner_join(vacc1) %>%
-#     mutate(taux_1_inj = effectif_1_inj/(population_carto - effectif_cumu_1_inj))
-#   
-#   if (variable == "taux_cumu_1_inj"){
-#     LOG_1107 = LOG_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-#     EMP_1107 = EMP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-#     FAM_1107 = FAM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-#     REV_1107 = REV_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-#     ACT_1107 = ACT_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-#     FOR_1107 = FOR_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-#     POP_1107 = POP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-#     IMM_1107 = IMM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-#     GEO_1107 = GEO_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)))
-#   }else if (variable == "taux_1_inj"){
-#     LOG_1107 = LOG_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-#     EMP_1107 = EMP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-#     FAM_1107 = FAM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-#     REV_1107 = REV_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-#     ACT_1107 = ACT_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-#     FOR_1107 = FOR_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-#     POP_1107 = POP_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-#     IMM_1107 = IMM_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-#     GEO_1107 = GEO_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-#   }
-#   
-#   LOG_OR_1107 = questionr::odds.ratio(LOG_1107$`1ry_res`, LOG_1107$taux_cumu_1_inj) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`2ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`Vacant_Home`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`Houses`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`Flats`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`Nb_Rooms_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`House_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`Flat_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_bf_1919`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_19-45`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_46-70`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_71-90`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_91-05`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_06-15`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_lt2y`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_2to4y`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_5to9y`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_10to19y`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_20to29y`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`HH_Moving_Time_gt30y`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Carpark`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_0car`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_1car`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_2car`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_3+car`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_gt0car`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Owner`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Tenant`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_Social`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`Pop_per_1ry_res_FreeAcc`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`1ry_res_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`Owners_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`Tenant_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`Social_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`FreeAcc_Occupancy`, LOG_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(LOG_1107$`Overcrowding_rate`, LOG_1107$taux_cumu_1_inj)) %>%
-#     as.data.frame() %>%
-#     bind_cols(Variable = colnames(LOG_1107)[2:42]) %>%
-#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
-#   rownames(LOG_OR_1107) = NULL
-#   # write_csv2(LOG_OR, "data/LOG_OR.csv")
-#   
-#   EMP_OR_1107 = questionr::odds.ratio(EMP_1107$`1564_Workforce_rate`, EMP_1107$taux_cumu_1_inj) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1524_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`2554_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`5564_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1524_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`2554_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`5564_men_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1524_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`2554_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`5564_women_Workforce_rate`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1524_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`2554_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`5564_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1524_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`2554_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`5564_men_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1524_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`2554_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`5564_women_Employed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1524_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`2554_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`5564_Unemployed_rate_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_Student_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_Retired_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_OtherInactive_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_men_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_women_Unemplyed_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_Student_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_Retired_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_OtherInactive_amg_NW`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_NonWorking_amg_POP`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_Farmers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_CraftsBusinessShopkeepers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_HihgQualWorkers_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_IntermediateProf_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_BlueCollar_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_WhiteCollar_amg_WF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_Farmers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_CraftsBusinessShopkeepers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_HihgQualWorkers_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_IntermediateProf_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_BlueCollar_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`1564_WhiteCollar_amg_EmpWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`15+_Salaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`15+_NonSalaried_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_empWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_nonsalWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`15+_men_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`15+_women_amg_FullTimeWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(EMP_1107$`15+_FullTime_amg_salWF`, EMP_1107$taux_cumu_1_inj)) %>%
-#     as.data.frame() %>%
-#     bind_cols(Variable = colnames(EMP_1107)[2:63]) %>%
-#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
-#   rownames(EMP_OR_1107) = NULL
-#   # write_csv2(EMP_OR, "data/EMP_OR.csv")
-#   
-#   FAM_OR_1107 = questionr::odds.ratio(FAM_1107$`SinglePerson_HH`, FAM_1107$taux_cumu_1_inj) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`SingleMan_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`SingleWoman_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Farmer_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`HighQualidied_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Intermediate_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`WhiteCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`15+_SinglePerson_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleMan_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleWoman_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Pop_OtherNoFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Pop_Family_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Pop_NoChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Pop_ChildFamily_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Pop_SingleParent_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Pop_Farmer_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Pop_CraftsBusinessShopkeepers_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Pop_HighQualidied_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Pop_Intermediate_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Pop_BlueCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Pop_WhiteCollar_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Pop_Retired_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Pop_Other_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`1524_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`2554_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`5579_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`80+_amg_15+POP`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`15+_Single_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`15+_Married_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`15+_nonMarried_amg_POP`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`1524_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`2554_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`5579_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`80+_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`1524_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`2554_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`5579_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`80+_amg_Single`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Family_w_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Single_Parent_Family_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FAM_1107$`Family_wo_Children_amg_HH`, FAM_1107$taux_cumu_1_inj)) %>%
-#     as.data.frame() %>%
-#     bind_cols(Variable = colnames(FAM_1107)[2:51]) %>%
-#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
-#   rownames(FAM_OR_1107) = NULL
-#   # write_csv2(FAM_OR, "data/FAM_OR.csv")
-#   
-#   REV_OR_1107 = questionr::odds.ratio(REV_1107$`D1_st_Living`, REV_1107$taux_cumu_1_inj) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`Median_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`D9_st_Living`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`Interdecile_91_Ratio`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`Taxable_HH`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Owners`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`Poverty_amg_Tenants`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`-30_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`3039_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`4049_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`5059_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`6074_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`75+_Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`Poverty`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`Activity_Income`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`Salary_Income`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`Unemployment_Benef`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`Self-Employment`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`Pensions_Annuities`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`Estate`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`Social_Benef`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`Family_Benef`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`Social_Minima`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`Housing_Benef`, REV_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(REV_1107$`Tax`, REV_1107$taux_cumu_1_inj)) %>%
-#     as.data.frame() %>%
-#     bind_cols(Variable = colnames(REV_1107)[2:26]) %>%
-#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
-#   rownames(REV_OR_1107) = NULL
-#   # write_csv2(REV_OR, "data/REV_OR.csv")
-#   
-#   ACT_OR_1107 = questionr::odds.ratio(ACT_1107$`Wk_Res_Municipality`, ACT_1107$taux_cumu_1_inj) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_County-Municipality`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_Region-County`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`Wk_Res_Country-Region`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`Wk_Dom_Com_Abroad`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`noTransport_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`Walk_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`Bike_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`Motorbike_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`Drive_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`PublicTrans_toWk`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`15+_Men_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`15+_Women_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`15+_PermanentContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`15+_ShortTermContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`15+_InterimContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`15+_SubsidizedWork_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`15+_ApprenticeContract_amg_salWF`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`15+_SelfEmployed_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`15+_Employers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(ACT_1107$`15+_caregivers_amg_nonsalWF`, ACT_1107$taux_cumu_1_inj)) %>%
-#     as.data.frame() %>%
-#     bind_cols(Variable = colnames(ACT_1107)[2:22]) %>%
-#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
-#   rownames(ACT_OR_1107) = NULL
-#   # write_csv2(ACT_OR, "data/ACT_OR.csv")
-#   
-#   FOR_OR_1107 = questionr::odds.ratio(FOR_1107$`0205_School`, FOR_1107$taux_cumu_1_inj) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`0610_School`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`1114_School`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`1517_School`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`1824_School`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`2529_School`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`30+_School`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_NoDiploma_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_CertifGeneEducation_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_VocationalGraduate_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_HighSchoolGraduate_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+2_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+4_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_HSG+5+_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_HighEducation_amg_WF`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_men_NoDiploma_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_men_VocationalGraduate_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_men_HighSchoolGraduate_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_men_HighEducation_amg_mWF`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_women_NoDiploma_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_women_VocationalGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighSchoolGraduate_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_women_HighEducation_amg_wWF`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_NoDiploma`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_VocationalGraduate`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_HighSchoolGraduate`, FOR_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(FOR_1107$`15+_MenOnWomen_HighEducation`, FOR_1107$taux_cumu_1_inj)) %>%
-#     as.data.frame() %>%
-#     bind_cols(Variable = colnames(FOR_1107)[2:28]) %>%
-#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
-#   rownames(FOR_OR_1107) = NULL
-#   # write_csv2(FOR_OR, "data/FOR_OR.csv")
-#   
-#   POP_OR_1107 = questionr::odds.ratio(POP_1107$`0014_amg_POP`, POP_1107$taux_cumu_1_inj) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`1529_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`3044_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`4559_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`6074_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`7589_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`90+_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`Men`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`0019_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`2064_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`65+_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_Farmers_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_CraftsBusinessShopkeeper_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_ManagersHigherIntellectProf_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_IntermediateProf_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_WhiteCollar_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_BlueCollar_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_Retired_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_OtherNoActivity_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`0014_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`1529_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`3044_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`4559_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`6074_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`7589_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`90+_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`0019_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`2064_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`65+_men_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_men_Farmers_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_men_CraftsBusinessShopkeeper_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_men_ManagersHigherIntellectProf_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_men_IntermediateProf_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_men_WhiteCollar_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_men_BlueCollar_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_men_Retired_amg_mPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_men_OtherNoActivity_amg_POP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`0014_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`1529_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`3044_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`4559_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`6074_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`7589_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`90+_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`0019_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`2064_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`65+_women_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_women_Farmers_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_women_CraftsBusinessShopkeeper_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_women_ManagersHigherIntellectProf_amh_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_women_IntermediateProf_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_women_WhiteCollar_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_women_BlueCollar_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_women_Retired_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(POP_1107$`15+_women_OtherNoActivity_amg_wPOP`, POP_1107$taux_cumu_1_inj)) %>%
-#     as.data.frame() %>%
-#     bind_cols(Variable = colnames(POP_1107)[2:56]) %>%
-#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
-#   rownames(POP_OR_1107) = NULL
-#   # write_csv2(POP_OR, "data/POP_OR.csv")
-#   
-#   IMM_OR_1107 = questionr::odds.ratio(IMM_1107$`French_nlty`, IMM_1107$taux_cumu_1_inj) %>%
-#     rbind(questionr::odds.ratio(IMM_1107$`Stranger`, IMM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(IMM_1107$`Immigrant`, IMM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(IMM_1107$`French_nlty_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Men`, IMM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(IMM_1107$`French_nlty_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(IMM_1107$`Stranger_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(IMM_1107$`Immigrant_amg_Women`, IMM_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(IMM_1107$`Res_Abroad_2017`, IMM_1107$taux_cumu_1_inj)) %>%
-#     as.data.frame() %>%
-#     bind_cols(Variable = colnames(IMM_1107)[2:11]) %>%
-#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
-#   rownames(IMM_OR_1107) = NULL
-#   # write_csv2(IMM_OR, "data/IMM_OR.csv")
-#   
-#   
-#   GEO_OR_1107 = questionr::odds.ratio(GEO_1107$latitude, GEO_1107$taux_cumu_1_inj) %>%
-#     rbind(questionr::odds.ratio(GEO_1107$longitude, GEO_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(GEO_1107$densite, GEO_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(GEO_1107$`SO-NE`, GEO_1107$taux_cumu_1_inj)) %>%
-#     rbind(questionr::odds.ratio(GEO_1107$`NO-SE`, GEO_1107$taux_cumu_1_inj)) %>%
-#     as.data.frame() %>%
-#     bind_cols(Variable = colnames(GEO_1107)[2:6]) %>%
-#     select(Variable, OR, `2.5 %`, `97.5 %`, p)
-#   rownames(GEO_OR_1107) = NULL
-#   # write_csv2(GEO_OR, "data/GEO_OR.csv")
-#   
-#   
-#   DF_OR_1107 = LOG_OR_1107 %>% mutate(theme = "Logement", .after = Variable) %>%
-#     bind_rows(EMP_OR_1107 %>% mutate(theme = "Emploi", .after = Variable)) %>%
-#     bind_rows(FAM_OR_1107 %>% mutate(theme = "Famille", .after = Variable)) %>%
-#     bind_rows(REV_OR_1107 %>% mutate(theme = "Revenus", .after = Variable)) %>%
-#     bind_rows(ACT_OR_1107 %>% mutate(theme = "Activite", .after = Variable)) %>%
-#     bind_rows(FOR_OR_1107 %>% mutate(theme = "Formation", .after = Variable)) %>%
-#     bind_rows(POP_OR_1107 %>% mutate(theme = "Population", .after = Variable)) %>%
-#     bind_rows(IMM_OR_1107 %>% mutate(theme = "Immigration", .after = Variable)) %>%
-#     bind_rows(GEO_OR_1107 %>% mutate(theme = "Geographie", .after = Variable)) %>%
-#     group_by(theme) %>%
-#     mutate(id = row_number()) %>%
-#     ungroup() %>%
-#     mutate(inv_OR = 1/OR,
-#            `inv_2.5 %` = 1/`97.5 %`,
-#            `inv_97.5 %` = 1/`2.5 %`,
-#            `is_OR_>1` = OR > inv_OR,
-#            `max_OR-inv_OR` = if_else(`is_OR_>1`, OR, inv_OR)) %>%
-#     arrange(desc(`max_OR-inv_OR`))
-#   return(DF_OR_1107)
-# }
 ```
@@
 
-```{r, echo = F, message = F, warning = F}
+```{r, pop-epci-insee, echo = F, message = F, warning = F}
 pop = read.csv2("data/POP.csv") %>%
@@
 
-```{r, echo = F, message = F, warning = F}
+```{r, s27, echo = F, message = F, warning = F}
 read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-27&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"),
@@
          taux_cumu_1_inj = if_else(is.na(taux_cumu_1_inj), 0, taux_cumu_1_inj)) %>%
-  # test$taux_cumu_1_inj[is.na(test$taux_cumu_1_inj)] <- 0
-  # test %>%
-  pivot_wider(id_cols = codgeo,
+  filter(!(codgeo %in% c(999999999, 200054807, 200054781, 200046977))) %>%
+  select(codgeo, classe_age, taux_cumu_1_inj) %>%
+  pivot_wider(# reshape
+    id_cols = codgeo,
               names_from = classe_age,
@@
   inner_join(pop %>% select(codgeo)) %>%
-  select(5,6,2,8,3,4,7) %>%
+  select(5,6,7,2,3,4,8) %>%
   desctable() %>%
@@
 
-```{r, message = F, echo = F, warning = F}
+```{r, s31, message = F, echo = F, warning = F}
 read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-31&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"),
@@
          taux_cumu_1_inj = if_else(is.na(taux_cumu_1_inj), 0, taux_cumu_1_inj)) %>%
-  # test$taux_cumu_1_inj[is.na(test$taux_cumu_1_inj)] <- 0
-  # test %>%
+  filter(!(codgeo %in% c(999999999, 200054807, 200054781, 200046977))) %>%
+  select(codgeo, classe_age, taux_cumu_1_inj) %>%
   pivot_wider(id_cols = codgeo,
@@
   inner_join(pop %>% select(codgeo)) %>%
-  select(5,6,2,3,7,4,8) %>%
+  select(3,4,8,6,7,2,5) %>%
   desctable() %>%
@@
 
-```{r, warning = F, echo = F, message = F}
+```{r, s35, warning = F, echo = F, message = F}
 read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-35&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"),
@@
   inner_join(pop %>% select(codgeo)) %>%
-  select(2,7,4,6,8,5,3) %>%
+  select(4,6,5,2,3,7,8) %>%
   desctable() %>%
@@
 
-```{r, echo = F, message = F, warning = F}
+```{r, desctable-log, echo = F, message = F, warning = F}
 read.csv("data/LOG_brut.csv") %>%
@@
 
-```{r, echo = F, message = F, warning = F}
+```{r, corr-log, echo = F, message = F, warning = F}
 data_b = read_csv("data/LOG_brut.csv") %>% select(-taux_cumu_1_inj)
@@
 
-```{r, echo = F, message = F, warning = F}
+```{r, network-log, echo = F, message = F, warning = F}
 seuil = 0.95
@@
 for (wk in c(27, 31, 35)){
-  print(
+  if (wk == 35){
+    assign(paste0("p", wk),
            fig %>%
@@
              theme_minimal() +
-      labs(title = paste("OR for the whole population, week", wk),
+             labs(title = paste("OR for the whole population - week", wk),
                   x = "",
-           y = "max(OR, 1/OR)")
-  )
-}
-```
-
-```{r, eval = F, warning = F, message = F, echo = F}
-plot_ly(data.frame(x=c(1,2,3,4),
-                   y=c(2,1,3,4),
-                   array = c(0.1, 0.2, 0.1, 0.1),
-                   arrayminus = c(0.2, 0.4, 1, 0.2)),
-        x = ~x,
-        y = ~y,
-        type = "scatter",
-        mode = "markers",
-        error_y = list(type = "data",
-                       symmetric = F,
-                       array = ~array,
-                       arrayminus = ~arrayminus))
+                  y = "max(OR, 1/OR)"))
+  }else{
+    assign(paste0("p", wk),
+           fig %>%
+             filter(week == wk) %>%
+             ggplot() +
+             aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
+             geom_pointrange() +
+             theme_minimal() +
+             theme(legend.position = "none") +
+             labs(title = paste("OR for the whole population - week", wk),
+                  x = "",
+                  y = "max(OR, 1/OR)") )
+  }
+}
+print(p27)
+print(p31)
+print(p35)
 ```
@@
 
-<!-- === -->
-```{r, eval = F, echo = F}
-vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", "TOUT_AGE", "&refine.semaine_injection=2021-", "35", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.factor(commune_residence)) %>%
-  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
-
-vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", "35", "&refine.classe_age=", "TOUT_AGE", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.factor(epci)) %>%
-  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
-  plyr::rbind.fill(vacc_com)
-
-test = vacc %>% inner_join(LOG_fact %>%
-                             select(codgeo, Overcrowding_rate) %>%
-                             mutate(codgeo = as.factor(codgeo))) %>%
-  mutate(taux_cumu_1_inj = binarisation(as.numeric(taux_cumu_1_inj), 0.25))
-
-summary(test$Overcrowding_rate[test$taux_cumu_1_inj == 1])
-summary(test$Overcrowding_rate[test$taux_cumu_1_inj == 0])
-
-table(test$Overcrowding_rate, test$taux_cumu_1_inj)
-
-questionr::odds.ratio(test$Overcrowding_rate, test$taux_cumu_1_inj)
-```
-
-<!-- ## Données à la semaine non cumulées -->
-
-```{r, echo = F, message = F, warning = F, eval = F}
+# Par classe d'âge - données cumulées
+
+## 0 - 19 ans
+
+```{r, echo = F, message = F, warning = F}
 data = NULL
-for (i in 2:last_week){
+for (i in c(27, 31, 35)){
   data = bind_rows(
     data,
-    make_data_covid(i, variable = "taux_1_inj") %>%
+    make_data_covid(i, classe_age = "00-19") %>%
       arrange(theme, id) %>%
@@
 
-```{r, echo = F, message = F, warning = F, eval = F}
+```{r, echo = F, message = F, warning = F}
 ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
@@
 fig = data %>%
-  mutate(shape = if_else(OR > 1, 0, 1)) %>%
-  # filter(week == 33) %>%
-  # arrange(OR) %>%
-  # mutate(pos2 = row_number()) %>%
-  # select(Variable, pos) %>%
-  # inner_join(data) %>%
+  mutate(shape = if_else(OR > 1, 219, 220)) %>%
+  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
+         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
+         value = (sup-inf))
+
 plot_ly(
+  fig,
   x = ~pos,
@@
     xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
-fig
-```
-
-```{r, echo = F, message = F, warning = F, eval = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 220, 219)) %>%
-  # filter(week == 33) %>%
-  # arrange(OR) %>%
-  # mutate(pos2 = row_number()) %>%
-  # select(Variable, pos) %>%
-  # inner_join(data) %>%
-  plot_ly(
-    x = ~pos,
-    y = ~`max_OR-inv_OR`,
-    size = ~-log10(p),
-    color = ~theme,
-    frame = ~week,
-    text = ~Variable,
-    symbol = ~shape,
-    symbols = c(219, 220),
-    hooverinfo = "text",
-    type = "scatter",
-    mode = "markers"
-  ) %>%
-  layout(scene = list(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim))))
-fig
-```
-
-# Par classe d'âge - données cumulées
-
-## 0 - 19 ans
-
-<!-- ### Données à la semaine -->
-
-```{r, echo = F, message = F, warning = F, eval = F}
-data = NULL
-for (i in 22:last_week){
-  data = bind_rows(
-    data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "00-19") %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
+    yaxis = list(title = "max(OR, 1/OR)"))
+
+for (wk in c(27, 31, 35)){
+  print(
+    fig %>%
+      filter(week == wk) %>%
+      ggplot() +
+      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
+      geom_pointrange() +
+      theme_minimal() +
+      labs(title = paste("OR for the whole population, week", wk),
+           x = "",
+           y = "max(OR, 1/OR)")
   )
 }
-
-# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
-#   filter(classe_age != "00-19") %>%
-#   group_by(epci) %>%
-#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
-#   ungroup()
-```
-
-```{r, echo = F, message = F, warning = F, eval = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 0, 1)) %>%
-  # filter(week == 33) %>%
-  # arrange(OR) %>%
-  # mutate(pos2 = row_number()) %>%
-  # select(Variable, pos) %>%
-  # inner_join(data) %>%
-  plot_ly(
-    x = ~pos,
-    y = ~`max_OR-inv_OR`,
-    size = ~-log10(p),
-    color = ~theme,
-    frame = ~week,
-    text = ~Variable,
-    alpha = 0.75,
-    symbol = ~shape,
-    symbols = c(220, 219),
-    hooverinfo = "text",
-    type = "scatter",
-    mode = "markers"
-  ) %>%
-  layout(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
-fig
-```
-
-<!-- === -->
-```{r, eval = F, echo = F}
-vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", "TOUT_AGE", "&refine.semaine_injection=2021-", "27", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.numeric(commune_residence)) %>%
-  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
-
-vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", "27", "&refine.classe_age=", "TOUT_AGE", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.numeric(epci)) %>%
-  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
-  plyr::rbind.fill(vacc_com)
-
-test = vacc %>% inner_join(LOG_fact %>%
-                             select(codgeo, Overcrowding_rate)) %>%
-  mutate(taux_cumu_1_inj = binarisation(as.numeric(taux_cumu_1_inj), 0.25))
-
-summary(factor(test$Overcrowding_rate, levels = c(0,1), labels = c(0,1)))
-summary(test$taux_cumu_1_inj)
-
-(t=table(test$Overcrowding_rate, test$taux_cumu_1_inj))
-
-questionr::odds.ratio(factor(test$Overcrowding_rate, levels = c(0,1), labels = c(0,1)), test$taux_cumu_1_inj)
-epitools::oddsratio(x = t, method = "fisher")
-```
-
-<!-- === -->
-
-<!-- ### Données cumulées -->
+```
+
+### Distributions des Odds ratios
+
+```{r, message = F, echo = F, warning = F}
+data %>%
+  filter(week %in% c(27, 31, 35)) %>%
+  mutate(week = factor(week)) %>%
+  ggplot() +
+  aes(x = `max_OR-inv_OR`, y = ..density.., color = week) +
+  geom_density(kernel = "gaussian") +
+  theme_bw() +
+  labs(title = "Distribution of max(OR, 1/OR) over every variable",
+       x = "max(OR, 1/OR)")
+```
+
+### Test de Wilcoxon
+
+```{r, message = F, echo = F, warning = F}
+w1 = data %>%
+  filter(week %in% c(27, 31)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w2 = data %>%
+  filter(week %in% c(31, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w3 = data %>%
+  filter(week %in% c(27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+data.frame(Comparison = c("wk27_wk31", "wk31_wk35", "wk27_wk35"),
+           method = c(w1$method, w2$method, w3$method), p.value = c(w1$p.value, w2$p.value, w3$p.value)) %>%
+  pander()
+```
+
+## 20 - 39 ans
 
@@
 
-## 20 - 39 ans
-
-<!-- ### Données à la semaine -->
-
-```{r, echo = F, message = F, warning = F, eval = F}
-data = NULL
-for (i in 22:last_week){
-  data = bind_rows(
-    data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "20-39") %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
-  )
-}
-
-# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
-#   filter(classe_age != "00-19") %>%
-#   group_by(epci) %>%
-#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
-#   ungroup()
-```
-
-```{r, echo = F, message = F, warning = F, eval = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 0, 1)) %>%
-  # filter(week == 33) %>%
-  # arrange(OR) %>%
-  # mutate(pos2 = row_number()) %>%
-  # select(Variable, pos) %>%
-  # inner_join(data) %>%
-  plot_ly(
-    x = ~pos,
-    y = ~`max_OR-inv_OR`,
-    size = ~-log10(p),
-    color = ~theme,
-    frame = ~week,
-    text = ~Variable,
-    alpha = 0.75,
-    symbol = ~shape,
-    symbols = c(220, 219),
-    hooverinfo = "text",
-    type = "scatter",
-    mode = "markers"
-  ) %>%
-  layout(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
-fig
-```
-
-<!-- ### Données cumulées -->
+## 40 - 54 ans
 
@@
     data,
-    make_data_covid(i, classe_age = "20-39") %>%
+    make_data_covid(i, classe_age = "40-54") %>%
       arrange(theme, id) %>%
@@
 
-```{r, eval = F, echo = F}
-vacc_com = read_csv2(
-  url(
-    paste0(
-      "https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=",
-      "75+et+%2B",
-      "&refine.semaine_injection=2021-",
-      "27",
-      "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.numeric(commune_residence)) %>%
-  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
-
-vacc = read_csv2(
-  url(
-    paste0(
-      "https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-",
-      "27",
-      "&refine.classe_age=",
-      "75+et+%2B",
-      "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.numeric(epci)) %>%
-  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
-  plyr::rbind.fill(vacc_com)
-
-test = vacc %>% inner_join(LOG_fact %>%
-                             select(codgeo, Overcrowding_rate)) %>%
-  mutate(taux_cumu_1_inj = binarisation(as.numeric(taux_cumu_1_inj), 0.25),
-         Overcrowding_rate = as.factor(Overcrowding_rate))
-
-summary(as.factor(test$Overcrowding_rate))
-summary(test$taux_cumu_1_inj)
-
-table(test$Overcrowding_rate, test$taux_cumu_1_inj)
-
-questionr::odds.ratio(test$Overcrowding_rate, test$taux_cumu_1_inj)
-```
-
-## 40 - 54 ans
-
-<!-- ### Données à la semaine -->
-
-```{r, echo = F, message = F, warning = F, eval = F}
-data = NULL
-for (i in 22:last_week){
-  data = bind_rows(
-    data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "40-54") %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
-  )
-}
-
-# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
-#   filter(classe_age != "00-19") %>%
-#   group_by(epci) %>%
-#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
-#   ungroup()
-```
-
-```{r, echo = F, message = F, warning = F, eval = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 24, 25)) %>%
-  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
-         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
-         value = (sup-inf))
-# filter(week == 33) %>%
-# arrange(OR) %>%
-# mutate(pos2 = row_number()) %>%
-# select(Variable, pos) %>%
-# inner_join(data) %>%
-
-plot_ly(
-  fig,
-  x = ~pos,
-  y = ~`max_OR-inv_OR`,
-  size = ~-log10(p),
-  color = ~theme,
-  frame = ~week,
-  text = ~Variable,
-  alpha = 0.75,
-  symbol = ~shape,
-  symbols = c(219, 219),
-  hooverinfo = "text",
-  type = "scatter",
-  mode = "markers"
-  # error_y = list(array = ~inf,
-  #                arrayminus = ~sup,
-  #                symmetric = FALSE,
-  #                type = "data")
-) %>%
-  layout(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)"))
-
-for (wk in c(27, 31, 35)){
-  print(
-    fig %>%
-      filter(week == wk) %>%
-      ggplot() +
-      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
-      geom_pointrange() +
-      theme_minimal() +
-      labs(title = paste("OR for the whole population, week", wk),
-           x = "",
-           y = "max(OR, 1/OR)")
-  )
-}
-```
-
-<!-- ### Données cumulées -->
+## 55 - 64 ans
 
@@
 
-## 55 - 64 ans
-
-<!-- ### Données à la semaine -->
-
-```{r, echo = F, message = F, warning = F, eval = F}
-data = NULL
-for (i in 22:last_week){
-  data = bind_rows(
-    data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "55-64") %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
-  )
-}
-
-# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
-#   filter(classe_age != "00-19") %>%
-#   group_by(epci) %>%
-#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
-#   ungroup()
-```
-
-```{r, echo = F, message = F, warning = F, eval = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 24, 25)) %>%
-  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
-         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
-         value = (sup-inf))
-# filter(week == 33) %>%
-# arrange(OR) %>%
-# mutate(pos2 = row_number()) %>%
-# select(Variable, pos) %>%
-# inner_join(data) %>%
-
-plot_ly(
-  fig,
-  x = ~pos,
-  y = ~`max_OR-inv_OR`,
-  size = ~-log10(p),
-  color = ~theme,
-  frame = ~week,
-  text = ~Variable,
-  alpha = 0.75,
-  symbol = ~shape,
-  symbols = c(219, 219),
-  hooverinfo = "text",
-  type = "scatter",
-  mode = "markers"
-  # error_y = list(array = ~inf,
-  #                arrayminus = ~sup,
-  #                symmetric = FALSE,
-  #                type = "data")
-) %>%
-  layout(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)"))
-
-for (wk in c(27, 31, 35)){
-  print(
-    fig %>%
-      filter(week == wk) %>%
-      ggplot() +
-      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
-      geom_pointrange() +
-      theme_minimal() +
-      labs(title = paste("OR for the whole population, week", wk),
-           x = "",
-           y = "max(OR, 1/OR)")
-  )
-}
-```
-
-<!-- ### Données cumulées -->
+## 65 - 74 ans
 
@@
     data,
-    make_data_covid(i, classe_age = "55-64") %>%
+    make_data_covid(i, classe_age = "65-74") %>%
       arrange(theme, id) %>%
@@
 
-## 65 - 74 ans
-
-<!-- ### Données à la semaine -->
-
-```{r, echo = F, message = F, warning = F, eval = F}
-data = NULL
-for (i in 22:last_week){
-  data = bind_rows(
-    data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "65-74") %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
-  )
-}
-
-# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
-#   filter(classe_age != "00-19") %>%
-#   group_by(epci) %>%
-#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
-#   ungroup()
-```
-
-```{r, echo = F, message = F, warning = F, eval = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 24, 25)) %>%
-  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
-         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
-         value = (sup-inf))
-# filter(week == 33) %>%
-# arrange(OR) %>%
-# mutate(pos2 = row_number()) %>%
-# select(Variable, pos) %>%
-# inner_join(data) %>%
-
-plot_ly(
-  fig,
-  x = ~pos,
-  y = ~`max_OR-inv_OR`,
-  size = ~-log10(p),
-  color = ~theme,
-  frame = ~week,
-  text = ~Variable,
-  alpha = 0.75,
-  symbol = ~shape,
-  symbols = c(219, 219),
-  hooverinfo = "text",
-  type = "scatter",
-  mode = "markers"
-  # error_y = list(array = ~inf,
-  #                arrayminus = ~sup,
-  #                symmetric = FALSE,
-  #                type = "data")
-) %>%
-  layout(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)"))
-
-for (wk in c(27, 31, 35)){
-  print(
-    fig %>%
-      filter(week == wk) %>%
-      ggplot() +
-      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
-      geom_pointrange() +
-      theme_minimal() +
-      labs(title = paste("OR for the whole population, week", wk),
-           x = "",
-           y = "max(OR, 1/OR)")
-  )
-}
-```
-
-<!-- ### Données cumulées -->
+## 75 ans et plus
 
@@
     data,
-    make_data_covid(i, classe_age = "65-74") %>%
+    make_data_covid(i, classe_age = "75+et+%2B") %>%
       arrange(theme, id) %>%
@@
 # data %>%
-#   filter(week %in% c(27, 31, 35)) %>%
-#   mutate(week = factor(week)) %>%
-#   ggplot() +
-#   aes(x = log(`max_OR-inv_OR`), y = ..density.., color = week) +
-#   geom_density(kernel = "gaussian") +
-#   theme_bw() +
-#   labs(title = "Distribution of log(max(OR, 1/OR)) over every variable",
-#        x = "log(max(OR, 1/OR))")
-```
-
-### Test de Wilcoxon
-
-```{r, message = F, echo = F, warning = F}
-w1 = data %>%
-  filter(week %in% c(27, 31)) %>%
-  mutate(week = factor(week)) %>%
-  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
-
-w2 = data %>%
-  filter(week %in% c(31, 35)) %>%
-  mutate(week = factor(week)) %>%
-  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
-
-w3 = data %>%
-  filter(week %in% c(27, 35)) %>%
-  mutate(week = factor(week)) %>%
-  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
-
-data.frame(Comparison = c("wk27_wk31", "wk31_wk35", "wk27_wk35"),
-           method = c(w1$method, w2$method, w3$method), p.value = c(w1$p.value, w2$p.value, w3$p.value)) %>%
-  pander()
-```
-
-## 75 ans et plus
-
-<!-- ### Données à la semaine -->
-
-```{r, echo = F, message = F, warning = F, eval = F}
-data = NULL
-for (i in 22:last_week){
-  data = bind_rows(
-    data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "75+et+%2B") %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
-  )
-}
-
-# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
-#   filter(classe_age != "00-19") %>%
-#   group_by(epci) %>%
-#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
-#   ungroup()
-```
-
-```{r, echo = F, message = F, warning = F, eval = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 24, 25)) %>%
-  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
-         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
-         value = (sup-inf))
-# filter(week == 33) %>%
-# arrange(OR) %>%
-# mutate(pos2 = row_number()) %>%
-# select(Variable, pos) %>%
-# inner_join(data) %>%
-
-plot_ly(
-  fig,
-  x = ~pos,
-  y = ~`max_OR-inv_OR`,
-  size = ~-log10(p),
-  color = ~theme,
-  frame = ~week,
-  text = ~Variable,
-  alpha = 0.75,
-  symbol = ~shape,
-  symbols = c(219, 219),
-  hooverinfo = "text",
-  type = "scatter",
-  mode = "markers"
-  # error_y = list(array = ~inf,
-  #                arrayminus = ~sup,
-  #                symmetric = FALSE,
-  #                type = "data")
-) %>%
-  layout(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)"))
-
-for (wk in c(27, 31, 35)){
-  print(
-    fig %>%
-      filter(week == wk) %>%
-      ggplot() +
-      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
-      geom_pointrange() +
-      theme_minimal() +
-      labs(title = paste("OR for the whole population, week", wk),
-           x = "",
-           y = "max(OR, 1/OR)")
-  )
-}
-```
-
-<!-- ### Données cumulées -->
-
-```{r, echo = F, message = F, warning = F}
-data = NULL
-for (i in c(27, 31, 35)){
-  data = bind_rows(
-    data,
-    make_data_covid(i, classe_age = "75+et+%2B") %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
-  )
-}
-```
-
-```{r, echo = F, message = F, warning = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 219, 220)) %>%
-  mutate(inf = if_else(OR > 1, `2.5 %`, `inv_2.5 %`),
-         sup = if_else(OR > 1, `97.5 %`, `inv_97.5 %`),
-         value = (sup-inf))
-# filter(week == 33) %>%
-# arrange(OR) %>%
-# mutate(pos2 = row_number()) %>%
-# select(Variable, pos) %>%
-# inner_join(data) %>%
-
-plot_ly(
-  fig,
-  x = ~pos,
-  y = ~`max_OR-inv_OR`,
-  size = ~-log10(p),
-  color = ~theme,
-  frame = ~week,
-  text = ~Variable,
-  alpha = 0.75,
-  symbol = ~shape,
-  symbols = c(219, 220),
-  hooverinfo = "text",
-  type = "scatter",
-  mode = "markers"
-  # error_y = list(array = ~inf,
-  #                arrayminus = ~sup,
-  #                symmetric = FALSE,
-  #                type = "data")
-) %>%
-  layout(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)"))
-
-for (wk in c(27, 31, 35)){
-  print(
-    fig %>%
-      filter(week == wk) %>%
-      ggplot() +
-      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
-      geom_pointrange() +
-      theme_minimal() +
-      labs(title = paste("OR for the whole population, week", wk),
-           x = "",
-           y = "max(OR, 1/OR)")
-  )
-}
-```
-
-### Distributions des Odds ratios
-
-```{r, message = F, echo = F, warning = F}
-data %>%
-  mutate(week = factor(week)) %>%
-  ggplot() +
-  aes(x = `max_OR-inv_OR`, y = ..density.., color = week) +
-  geom_density(kernel = "gaussian") +
-  theme_bw() +
-  labs(title = "Distribution of max(OR, 1/OR) over every variable",
-       x = "max(OR, 1/OR)")
-
-# data %>%
 #   filter(week %in% c(22, 27, 35)) %>%
@@
 
-<!-- # Données cumulées restreintes de la semaine 22 à 27 -->
-
-```{r, message = F, echo = F, warning = F, eval = F}
-data = make_data_covid_cumul(22:27)
-
-axis_df = data %>%
-  arrange(theme, id) %>%
-  mutate (pos = row_number()) %>%
-  group_by(theme) %>%
-  summarise(center = (max(pos) + min(pos)) /2)
-
-p = data %>%
-  arrange(theme, id) %>%
-  mutate (pos = row_number()) %>%
-  ggplot() +
-  aes(x = pos, y = -log10(p), variable = Variable, OR = OR) +
-  geom_point(aes(color = theme), alpha = 0.8, size = 1.3) +
-  # scale_color_manual(values = rep(c("grey", "skyblue"), 5)[1:9]) +
-  scale_x_continuous(label = axis_df$theme,
-                     breaks = axis_df$center, guide = guide_axis(angle = 45)) +
-  # ggrepel::geom_label_repel(data = subset(DF_OR_32%>%
-  #                                           arrange(theme, id) %>%
-  #                                           mutate (pos = row_number(),
-  #                                                   theme = as.factor(theme)),
-  #                                         -log10(p) > 61),
-  #                           aes(label = Variable), size = 3) +
-  theme_bw() +
-  # geom_point(data = subset(DF_OR %>%
-  #                            arrange(theme, id) %>%
-  #                            mutate (pos = row_number(),
-  #                                    theme = as.factor(theme)) %>% filter(p < 0.0001/dim(DF_OR)[1])), color = "orange", size = 2) +
-  theme(legend.position = "none",
-        panel.border = element_blank(),
-        panel.grid.major.x = element_blank(),
-        panel.grid.minor.x = element_blank()) +
-  labs(title = paste("Manhattan plot on the P-value, weeks 28 to 34"),
-       x = "")
-
-plotly::ggplotly(p) %>%
-  layout(showlegend = FALSE, xaxis = list(tickangle=45))
-```
-
-<!-- # Données cumulées restreintes de la semaine 28 à 34 -->
-
-```{r, message = F, echo = F, warning = F, eval = F}
-data = make_data_covid_cumul(28:34)
-
-axis_df = data %>%
-  arrange(theme, id) %>%
-  mutate (pos = row_number()) %>%
-  group_by(theme) %>%
-  summarise(center = (max(pos) + min(pos)) /2)
-
-pl = data %>%
-  arrange(theme, id) %>%
-  mutate (pos = row_number(),
-          max = if_else(OR > 1, "OR", "inv(OR)")) %>%
-  ggplot() +
-  aes(x = pos, y = `max_OR-inv_OR`, size = -log10(p), variable = Variable, Max = max) +
-  geom_point(aes(color = theme), alpha = 0.5) +
-  # scale_color_manual(values = rep(c("grey", "skyblue"), 5)[1:9]) +
-  scale_x_continuous(label = axis_df$theme,
-                     breaks = axis_df$center, guide = guide_axis(angle = 45)) +
-  # ggrepel::geom_label_repel(data = subset(DF_OR_32%>%
-  #                                           arrange(theme, id) %>%
-  #                                           mutate (pos = row_number(),
-  #                                                   theme = as.factor(theme)),
-  #                                         -log10(p) > 61),
-  #                           aes(label = Variable), size = 3) +
-  theme_bw() +
-  # geom_point(data = subset(DF_OR %>%
-  #                            arrange(theme, id) %>%
-  #                            mutate (pos = row_number(),
-  #                                    theme = as.factor(theme)) %>% filter(p < 0.0001/dim(DF_OR)[1])), color = "orange", size = 2) +
-  theme(legend.position = "none",
-        panel.border = element_blank(),
-        panel.grid.major.x = element_blank(),
-        panel.grid.minor.x = element_blank()) +
-  labs(title = paste("Manhattan plot on the P-value, weeks 28 to 34"),
-       x = "")
-
-plotly::ggplotly(pl) %>%
-  layout(showlegend = FALSE, xaxis = list(tickangle=45), yaxis = list(title = "max(OR, 1/OR)"))
-```
-
 # Taux de vaccinations selon les modalités des 3 variables les plus discriminantes
@@
     mutate(week = wk) %>%
-    select(codgeo, classe_age, population_carto, effectif_cumu_1_inj, week)
+    select(codgeo, classe_age, taux_cumu_1_inj, week)
 
@@
     mutate(week = wk) %>%
-    select(codgeo, classe_age, population_carto, effectif_cumu_1_inj, week) %>%
+    select(codgeo, classe_age, taux_cumu_1_inj, week) %>%
     plyr::rbind.fill(vacc_com)
@@
 
-dfocus = read_csv("data/LOG_fact.csv") %>%
+dfocus = read_csv("data/LOG_brut.csv") %>%
   select(codgeo, Overcrowding_rate) %>%
+  mutate(Overcrowding_rate = factor(ntile(Overcrowding_rate, 4))) %>%
   inner_join(read_csv("data/REV_fact.csv") %>%
-               select(codgeo, Unemployment_Benef, Interdecile_91_Ratio)) %>%
+               select(codgeo, Unemployment_Benef, Interdecile_91_Ratio) %>%
+               mutate(Unemployment_Benef = factor(ntile(Unemployment_Benef, 4)),
+                      Interdecile_91_Ratio = factor(ntile(Interdecile_91_Ratio, 4)))) %>%
   inner_join(vacct) %>%
-  pivot_longer(cols = c(Overcrowding_rate, Unemployment_Benef, Interdecile_91_Ratio),
+  filter(classe_age == "TOUT_AGE")
+# pivot_longer(cols = c(Overcrowding_rate, Unemployment_Benef, Interdecile_91_Ratio),
+#              names_to = "Variable",
+#              values_to = "half")
+```
+
+```{r, echo=F, message=FALSE, warning=FALSE}
+min = min(as.numeric(dfocus$taux_cumu_1_inj))
+max = max(as.numeric(dfocus$taux_cumu_1_inj))
+
+df_patch = dfocus %>%
+  # filter(week == wk) %>%
+  mutate(vaccination_rate = as.numeric(taux_cumu_1_inj)) %>%
+  pivot_longer(cols = c(Unemployment_Benef, Overcrowding_rate),
                names_to = "Variable",
-               values_to = "half")
-```
-
-```{r, echo = F, message = F, warning = F}
-
-dfocus %>%
-  filter(!is.na(half)) %>%
-  group_by(classe_age, week, Variable, half) %>%
-  summarise(population_carto = sum(population_carto, na.rm = T),
-            effectif_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T)) %>%
+               values_to = "quartile") %>%
+  filter(!is.na(quartile)) %>%
+  mutate(Week = factor(week),
+         Variable = if_else(Variable == "Unemployment_Benef", "Unemployment", "Overcrowding"))
+
+df_patch %>%
+  ggplot() +
+  aes(x=quartile, y=vaccination_rate, fill = Week) +
+  facet_grid(cols = vars(Variable)) +
+  scale_y_continuous(limits = c(min, max)) +
+  scale_fill_manual(values = c("#edf8b1", "#7fcdbb", "#2c7fb8")) +
+  geom_boxplot() +
+  theme_minimal() +
+  labs(y = "Vaccination rate",
+       x = "Quartile") +
+  theme(axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(size = 10),
+        strip.text.x = element_text(size = 11),
+        legend.position = "top")
+
+# dfocus %>%
+#   filter(!is.na(half)) %>%
+#   group_by(classe_age, week, Variable, half) %>%
+#   summarise(population_carto = sum(population_carto, na.rm = T),
+#             effectif_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T)) %>%
+#   ungroup() %>%
+#   mutate(taux_cumu_1_inj = effectif_cumu_1_inj/population_carto,
+#          Variable = paste(Variable, half)) %>%
+#   plot_ly(
+#     x = ~week,
+#     y = ~taux_cumu_1_inj,
+#     color = ~Variable,
+#     symbol = ~half,
+#     mode = "lines+markers",
+#     frame = ~classe_age 
+#   )
+
+ggsave(filename = "boxplots.pdf",
+       device = "pdf",
+       path = "plots",
+       width = 5*1.5,
+       height = 3*1.5)
+```
+
+```{r, echo=F, message=FALSE, warning=FALSE}
+df_patch %>% # DF qui m'a permis de tracer les boxplots de différentes couleurs
+  # colnames = c(codgeo, week, vaccination_rate, Variable, quartile)
+  filter(quartile %in% c(1, 4)) %>% # on ne garde que les quartiles 1 et 4
+  # pivot_wider( # + de colonnes
+  #   # Reshape : codgeo, variable, quartile, s27, s31, s35 -> taux de vaccination pour chaque semaine
+  #   id_cols = c(codgeo, Variable, week),
+  #   names_from = quartile,
+  #   values_from = vaccination_rate,
+  #   names_prefix = "q") %>%
+  # mutate(
+  #   # Calcul de la différence des taux de vaccination entre chaque semaine
+  #   s27_35 = s35-s27,
+  #   s27_31 = s31-s27,
+  #   s31_35 = s35-s31) %>%
+  # pivot_longer( # + de lignes
+  #   # Reshape : codgeo, Variable, quartile, comp (nom des variables calculées juste avant), diff (valeur calculée juste avant)
+  #   cols = c(s27_35, s27_31, s31_35),
+  #   names_to = "comp",
+  #   values_to = "diff") %>%
+  group_by(
+    # le calcul suivant se fera par variable, par quartile et par comparaison de semaine
+    Variable, quartile, week) %>% 
+  summarise(
+    # nombre de territoires
+    sample_size = n(),
+    # moyenne de la différence
+    Mean = mean(vaccination_rate),
+    # écart-type de la différence
+    sd = sd(vaccination_rate)) %>%
+  ungroup() %>% # étape technique qui ne change rien
+  mutate(
+    # Calcul des intervalles de confiance
+    Margin_Error = abs(qnorm(0.025))* sd/sqrt(sample_size),
+    Lower = Mean - Margin_Error,
+    Upper = Mean + Margin_Error,
+    week = as.factor(week),
+    Mean = Mean,
+    .keep = "unused") %>%
+  pivot_wider( # + de colonnes
+    # Reshape : Variable, comp, Mean_1, Mean_4, Lower_1, Lower_4, Upper_1, Upper_4 (moyennes, bornes inf, bornes sup des intervalles de confiances pour les quartiles 1 et 4)
+    id_cols = c(Variable, week),
+    names_from = quartile,
+    values_from = c(Mean, Lower, Upper)) %>%
+  mutate(
+    # Calcul des différences entre les moyennes, entre les bornes inf et entre les bornes sup
+    diff_mean = Mean_1 - Mean_4,
+    diff_lower = Lower_1 - Upper_4,
+    diff_upper = Upper_1 - Lower_4,
+    .keep = "unused") %>%
+
+ggplot() +
+  aes(x = week, y = diff_mean, ymin = diff_lower, ymax = diff_upper) + # sélection des différentes parties esthétiques
+  facet_grid(cols = vars(Variable)) + # séparation du graphe suivant des modalités
+  geom_point() + # nuage de points
+  geom_errorbar() + # intervalle de confiance
+  theme_minimal() + # couleur de fond
+  labs(title = "Confidence intervals of the difference of vaccination rate between Q1 and Q4",
+       y = "") # titres
+```
+
+```{r, echo=F, message=FALSE, warning=FALSE}
+# EPCI d'outremer
+siren_exclude = c(999999999, 249720061, 249720053, 200041788, 249710062,
+                  200044691, 249710070, 200018653, 200041507, 249710047,
+                  249730045, 249730052, 249730037, 200027548, 249740077,
+                  249740119, 249740093, 249740085, 249740101)
+wk = 35
+
+  vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+    mutate(codgeo = as.numeric(epci)) %>%
+    mutate(week = wk)
+
+vacc %>%
+  filter(!(codgeo %in% siren_exclude)) %>%
+  inner_join(pop %>% select(codgeo)) %>%
+  group_by(classe_age) %>%
+  summarise(population = sum(population_carto),
+            eff_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T)) %>%
   ungroup() %>%
-  mutate(taux_cumu_1_inj = effectif_cumu_1_inj/population_carto,
-         Variable = paste(Variable, half)) %>%
-  plot_ly(
-    x = ~week,
-    y = ~taux_cumu_1_inj,
-    color = ~Variable,
-    symbol = ~half,
-    mode = "lines+markers",
-    frame = ~classe_age 
-  )
-
+  mutate(tx_vax = eff_cumu_1_inj / population) %>% pander()
+```
+
+```{r}
+wk = 42
+
+  vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+    mutate(codgeo = as.numeric(epci)) %>%
+    mutate(week = wk)
+
+vacc %>%
+  filter(!(codgeo %in% siren_exclude)) %>%
+  inner_join(pop %>% select(codgeo)) %>%
+  group_by(classe_age) %>%
+  summarise(population = sum(population_carto),
+            eff_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T)) %>%
+  ungroup() %>%
+  mutate(tx_vax = eff_cumu_1_inj / population) %>% pander()
+```
+
+```{r, echo = F, warning = F, message = F}
+# mise en forme des différents graphiques
+
+library(patchwork)
+(p27 | p31 | p35) /
+  (q27 | q31 | q35 )
+
+(p27 / q27) + (p31 / q31) + (p35 / q35)
 ```
@@
 
-```{r, eval = F, echo = F}
+*Points d'attention sur les données de vaccination présentées*
+
+Il est possible qu’un patient ne reçoive qu’une injection et que sa vaccination soit ainsi terminée : cas des vaccins à une injection ou des patients ayant déjà été atteints par la Covid-19, par exemple ;
+
+La population de référence pour le calcul des effectifs de patients vaccinés et pour le calcul des taux est la population de la cartographie des pathologies et des dépenses de l’Assurance Maladie, et non la population recensée par l’Insee dont le découpage par tranche d’âge et par commune date de 2017 ;
+
+Seuls les patients vaccinés faisant partie de la population de la cartographie des pathologies et des dépenses de l’Assurance Maladie sont pris en compte dans les effectifs (> 95% des vaccinés) ;
+
+La répartition par EPCI n’est pas possible pour certains patients dont le département de résidence ou la commune est inconnu(e).
+Ces patients sont rattachés à l’EPCI « 999999999 » dans le jeu de données.
+
+A contrario : les données de Sante Publique France
+
+```{r, message = F, warning = F, echo = F}
 data = NULL
-for (i in 2:last_week){
+
+for (i in 1:40){
+  if (i < 10){
+    i = paste0("0", i)
+  }
   data = bind_rows(
     data,
-    make_data_covid(i) %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
+    read.csv(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", i, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")), sep = ";")
   )
 }
-```
-
-```{r, eval = F, echo = F}
-data1 = data
-```
-
-```{r, eval = F, echo = F}
-data = data1 %>%
-  # filter(Variable %in% c("NO-SE",
-  #                        "Overcrowding_rate",
-  #                        "Interdecile_91_Ratio",
-  #                        "Unemployment_Benef",
-  #                        "Immigrant",
-  #                        "Pop_NoChildFamily_HH")) %>%
-  filter(week >= 22) %>%
-  mutate(ban = as.factor(if_else(week <27, 0, 1)))
-p = data %>%
-  # filter(ban == 0) %>%
-  ggplot() +
-  aes(x = week, y = log(`max_OR-inv_OR`), color = Variable, alpha = 0.5) +
-  geom_point(size = 0.5) +
-  # geom_vline(aes(xintercept = 26.5)) +
-  geom_smooth(aes(fill = ban), size = 0.5, method = "lm", se = F)+
-  theme_bw() +
-  theme(legend.position = "none") 
-# ggplotly(p)
-
-# plot(data$`max_OR-inv_OR`,
-#      type="n",
-#      ylim=c(00,12),
-#      xlab="Week",
-#      ylab="log(Interdecile_91_Ratio)",
-#      bty="l",
-#      xaxt="n")
-# rect(26.5,0,34,12,col=grey(0.9),border=F)
-# points(log(data$`max_OR-inv_OR`[data$ban==0]),cex=0.7)
-```
-
-<!-- # Données de vaccination nationales -->
-
-```{r, echo = F, warning = F, message = F, eval = F}
-wk = 37
-
-vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.numeric(commune_residence)) %>%
-  mutate(week = wk) %>%
-  select(codgeo, classe_age, population_carto, effectif_cumu_1_inj, week)
-
-vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.numeric(epci)) %>%
-  mutate(week = wk) %>%
-  select(codgeo, classe_age, population_carto, effectif_cumu_1_inj, week) %>%
-  plyr::rbind.fill(vacc_com)
-
-vacc %>%
-  filter(!is.na(effectif_cumu_1_inj)) %>%
-  group_by(classe_age) %>%
-  summarise(pop = sum(population_carto, na.rm = T),
-            tot_vacc = sum(effectif_cumu_1_inj, na.rm = T)) %>%
+
+data %>%
+  filter(population_carto != "NS" & classe_age == "TOUT_AGE") %>%
+  select(effectif_cumu_1_inj, population_carto, date, epci, classe_age) %>%
+  group_by(date) %>%
+  summarise(effectif_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T),
+            population_carto = sum(as.numeric(population_carto))) %>%
   ungroup() %>%
-  mutate(tx_vacc = tot_vacc/pop)
-```
+  mutate(couv_dose1 = effectif_cumu_1_inj / population_carto,
+         source = "ameli",
+         jour = lubridate::ymd(date)) %>%
+  select(jour, couv_dose1, source)
+
+ggplotly(
+  read.csv(url("https://www.data.gouv.fr/fr/datasets/r/b273cf3b-e9de-437c-af55-eda5979e92fc"), sep = ";") %>%
+    group_by(jour) %>%
+    summarise(n_cum_dose1 = sum(n_cum_dose1, na.rm = T)) %>%
+    ungroup() %>%
+    mutate(couv_dose1 = n_cum_dose1 / 97114995,
+           jour = lubridate::ymd(jour),
+           source = "SPF") %>%
+    select(jour, couv_dose1, source) %>%
+    plyr::rbind.fill(data %>%
+                       filter(population_carto != "NS" & classe_age == "TOUT_AGE") %>%
+                       select(effectif_cumu_1_inj, population_carto, date, epci, classe_age) %>%
+                       group_by(date) %>%
+                       summarise(effectif_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T),
+                                 population_carto = sum(as.numeric(population_carto))) %>%
+                       ungroup() %>%
+                       mutate(couv_dose1 = effectif_cumu_1_inj / population_carto,
+                              source = "ameli",
+                              jour = lubridate::ymd(date)) %>%
+                       select(jour, couv_dose1, source)) %>%
+    ggplot() +
+    aes(x=jour, y=couv_dose1, color = source) +
+    geom_line() +
+    theme_minimal() +
+    labs(title = "Différence dans les données publiques",
+         y = "Couverture vaccinale 1ère dose") +
+    scale_y_continuous(labels = scales::percent)
+)
+```
+
+Quand je retire les moins de 12 ans qui n'ont pas accès à la vaccination, j'arrive à 83,4% de la population qui est vaccinée.
+Je pense que SPF publie un pourcentage de personnes vaccinées parmi les personnes qui ont accès au vaccin...
+
+On se demande d'où vient la différence, les données de vaccination ou les données de population générale ?
+
+```{r, message = F, warning = F, echo = F}
+ggplotly(
+  read.csv(url("https://www.data.gouv.fr/fr/datasets/r/fa4ad329-14ec-4394-85a4-c5df33769dff"), sep = ";") %>%
+    mutate(jour = lubridate::ymd(jour),
+           source = "SPF") %>%
+    select(jour, n_cum_dose1, source) %>%
+    plyr::rbind.fill(data %>%
+                       filter(population_carto != "NS" & classe_age == "TOUT_AGE") %>%
+                       group_by(date) %>%
+                       summarise(effectif_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T)) %>%
+                       ungroup() %>%
+                       mutate(n_cum_dose1 = effectif_cumu_1_inj,
+                              source = "ameli",
+                              jour = lubridate::ymd(date)) %>%
+                       select(jour, n_cum_dose1, source))%>%
+    ggplot() +
+    aes(x=jour, y=n_cum_dose1, color = source) +
+    geom_line() +
+    theme_minimal() +
+    labs(title = "Différence dans les données publiques",
+         y = "Nb vaccinations cumulées 1ère dose")
+)
+```
+
+```{r, message = F, warning = F, echo = F}
+ggplotly(
+  read.csv(url("https://www.data.gouv.fr/fr/datasets/r/fa4ad329-14ec-4394-85a4-c5df33769dff"), sep = ";") %>%
+    filter(couv_dose1 != 0) %>%
+    mutate(jour = lubridate::ymd(jour),
+           source = "SPF",
+           population_carto = n_cum_dose1*100/couv_dose1) %>%
+    select(jour, population_carto, source) %>%
+    plyr::rbind.fill(data %>%
+                       filter(population_carto != "NS" & classe_age == "TOUT_AGE") %>%
+                       select(population_carto, date, epci, classe_age) %>%
+                       group_by(date) %>%
+                       summarise(population_carto = sum(as.numeric(population_carto))) %>%
+                       ungroup() %>%
+                       mutate(source = "ameli",
+                              jour = lubridate::ymd(date)) %>%
+                       select(jour, population_carto, source)) %>%
+    ggplot() +
+    aes(x=jour, y=population_carto, color = source) +
+    geom_line() +
+    theme_minimal() +
+    labs(title = "Différence dans les données publiques",
+         y = "Estimation de la population française")
+)
+```

### 2022-02-01 code/manhattan_animated.Rmd
update manhattan animated
add election variables and homogeneisation population structure by age class

@@
 library(rAmCharts)
-```
-
-```{r, echo = F, message = F, warning = F}
+library(readxl)
+```
+
+## données électorales
+
+données électorales 2017 : https://www.data.gouv.fr/fr/datasets/election-presidentielle-des-23-avril-et-7-mai-2017-resultats-definitifs-du-1er-tour-par-communes/#resource-d282e53a-d273-425d-95bb-8a0d7632c79a-header
+
+données électorales de paris 2017 : https://opendata.paris.fr/explore/dataset/elections-presidentielles-2017-1ertour/export/?disjunctive.id_bvote&disjunctive.num_circ&disjunctive.num_quartier&disjunctive.num_arrond&sort=-num_arrond
+données électorales de marseille 2017 :
+https://trouver.datasud.fr/dataset/82a6d91c-c81d-423c-9a4a-3f76d121c8ce/resource/03e2ef07-c2d0-41dd-b503-26910ecb15c3/download/marseille_presidentielles2017_tour1.csv
+Lyon : https://www.interieur.gouv.fr/Elections/Les-resultats/Presidentielles/elecresult__presidentielle-2017/(path)/presidentielle-2017/084/069/069L.html
+
+composition communale des EPCI : https://www.insee.fr/fr/information/2510634
+
+Composition communale des communes nouvelles : https://www.insee.fr/fr/information/2549968
+
+```{r, eval = F, echo = F, message = F, warning = F}
+pres = "data/Presidentielle_2017_Resultats_Communes_T1_clean_def.csv"
+
+pres_paris = read_csv2(url("https://opendata.paris.fr/explore/dataset/elections-presidentielles-2017-1ertour/download/?format=csv&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
+  group_by(NUM_ARROND) %>%
+  summarise(Inscrits = sum(NB_INSCR),
+            Abstentions = Inscrits - sum(NB_VOTANT),
+            Abstention = Abstentions / Inscrits,
+            Blancs = sum(NB_BL),
+            Nuls = sum(NB_NUL),
+            Exprime = Inscrits - Abstentions - Blancs - Nuls,
+            LePen = sum(`LE PEN Marine`) / Exprime,
+            Melenchon = sum(`MÉLENCHON Jean-Luc`) / Exprime,
+            Macron = sum(`MACRON Emmanuel`) / Exprime,
+            Fillon = sum(`FILLON François`) / Exprime,
+            DupontAignan = sum(`DUPONT-AIGNAN Nicolas`) / Exprime,
+            Lassalle = sum(`LASSALLE Jean`) / Exprime,
+            Hamon = sum(`HAMON Benoît`) / Exprime,
+            Asselineau = sum(`ASSELINEAU François`) / Exprime,
+            Poutou = sum(`POUTOU Philippe`) / Exprime,
+            Arthaud = sum(`ARTHAUD Nathalie`) / Exprime,
+            Cheminade = sum(`CHEMINADE Jacques`) / Exprime) %>%
+  ungroup() %>%
+  mutate(codgeo = as.character(75100 + NUM_ARROND), .after = NUM_ARROND) %>%
+  select(-c(Inscrits, Abstentions, Blancs, Nuls, Exprime, NUM_ARROND))
+
+pres_marseille = read_csv(url("https://trouver.datasud.fr/dataset/82a6d91c-c81d-423c-9a4a-3f76d121c8ce/resource/03e2ef07-c2d0-41dd-b503-26910ecb15c3/download/marseille_presidentielles2017_tour1.csv")) %>%
+  group_by(ARRONDISSEMENT) %>%
+  summarise(Inscrits = sum(NB_INSCRITS_THEORIQUES),
+            Abstentions = Inscrits - sum(NB_VOTANTS),
+            Abstention = Abstentions / Inscrits,
+            Blancs = sum(NB_BLANCS),
+            Nuls = sum(NB_NULS),
+            Exprime = Inscrits - Abstentions - Blancs - Nuls,
+            LePen = sum(NB_VOIX_CANDIDAT_02) / Exprime,
+            Melenchon = sum(NB_VOIX_CANDIDAT_09) / Exprime,
+            Macron = sum(NB_VOIX_CANDIDAT_03) / Exprime,
+            Fillon = sum(NB_VOIX_CANDIDAT_11) / Exprime,
+            DupontAignan = sum(NB_VOIX_CANDIDAT_01) / Exprime,
+            Lassalle = sum(NB_VOIX_CANDIDAT_08) / Exprime,
+            Hamon = sum(NB_VOIX_CANDIDAT_04) / Exprime,
+            Asselineau = sum(NB_VOIX_CANDIDAT_10) / Exprime,
+            Poutou = sum(NB_VOIX_CANDIDAT_06) / Exprime,
+            Arthaud = sum(NB_VOIX_CANDIDAT_05) / Exprime,
+            Cheminade = sum(NB_VOIX_CANDIDAT_07) / Exprime) %>%
+  ungroup() %>%
+  mutate(codgeo = as.character(13200 + ARRONDISSEMENT), .after= ARRONDISSEMENT) %>%
+  select(-c(Inscrits, Abstentions, Blancs, Nuls, Exprime, ARRONDISSEMENT))
+
+pres_lyon = read.csv2("data/pres_lyon.csv") %>%
+  mutate(codgeo = as.character(codgeo),
+         Abstention = Abstentions / Inscrits,
+         LePen = LePen / Exprime,
+         Melenchon = Melenchon / Exprime,
+         Macron = Macron / Exprime,
+         Fillon = Fillon / Exprime,
+         DupontAignan = DupontAignan / Exprime,
+         Lassalle = Lassalle / Exprime,
+         Hamon = Hamon / Exprime,
+         Asselineau = Asselineau / Exprime,
+         Poutou = Poutou / Exprime,
+         Arthaud = Arthaud / Exprime,
+         Cheminade = Cheminade / Exprime) %>%
+  select(-c(Inscrits, Abstentions, Exprime))
+
+Presidentielle_2017 = read_csv(pres)
+
+Intercom <- read_excel("~/nas_backup_scripts_elr/INSEE_API/data/Intercommunalite-Metropole_au_01-01-2021.xlsx", 
+                       sheet = "Composition_communale", skip = 5)
+
+EPCI_PLM = c(200054781, 200046977, 200054807)
+EPCI_domtom = c(249710062, 200044691, 249710070, 200018653, 200041507, 249710047, #Guadeloupe
+                249720061, 249720053, 200041788, #Martinique
+                249730045, 249730052, 249730037, 200027548, #Guyane
+                249740077, 249740119, 249740093, 249740085, 249740101, #LaReunion
+                200060457, 200060465, 200050532, 200059871, 200060473) #Mayotte
+
+CN17 = read_excel("data/communes_nouvelles_2017.xls")
+CN18 = read_excel("data/communes_nouvelles_2018.xls")
+CN19 = read_excel("data/communes_nouvelles_2019.xls")
+CN20 = read_excel("data/communes_nouvelles_2020.xlsx")
+CN21 = read_excel("data/communes_nouvelles_2021.xlsx")
+
+CN = CN18 %>% select(DepComN, DepComA) %>%
+  bind_rows(CN17 %>% select(DepComN, DepComA)) %>%
+  bind_rows(CN19 %>% select(DepComN, DepComA)) %>%
+  bind_rows(CN20 %>%
+              mutate(DepComN = as.character(DepComN),
+                     DepComA = as.character(DepComA)) %>%
+              select(DepComN, DepComA)) %>%
+  bind_rows(CN21 %>% select(DepComN, DepComA))
+
+base_codes = EMP_brut %>%
+  select(codgeo)
+
+PRE_brut = Presidentielle_2017 %>%
+  select(CodeInsee, Inscrits, Abstentions, Votants, Blancs, Nuls, `LE PEN`,
+         MÉLENCHON, MACRON, FILLON, `DUPONT-AIGNAN`, LASSALLE, HAMON,
+         ASSELINEAU, POUTOU, ARTHAUD, CHEMINADE) %>%
+  mutate(CodeInsee = if_else(CodeInsee == "27676", "27058", CodeInsee)) %>%
+  left_join(CN, by = c("CodeInsee" = "DepComA")) %>%
+  mutate(DepComN = if_else(is.na(DepComN), CodeInsee, DepComN)) %>%
+  group_by(DepComN) %>%
+  summarise(Inscrits = sum(Inscrits),
+            Abstentions = sum(Abstentions),
+            Blancs = sum(Blancs),
+            Nuls = sum(Nuls),
+            LePen = sum(`LE PEN`),
+            Melenchon = sum(MÉLENCHON),
+            Macron = sum(MACRON),
+            Fillon = sum(FILLON),
+            DupontAignan = sum(`DUPONT-AIGNAN`),
+            Lassalle = sum(LASSALLE),
+            Hamon = sum(HAMON),
+            Asselineau = sum(ASSELINEAU),
+            Poutou = sum(POUTOU),
+            Arthaud = sum(ARTHAUD),
+            Cheminade = sum(CHEMINADE)) %>%
+  ungroup() %>%
+  anti_join(Intercom %>%
+              filter(EPCI %in% EPCI_domtom), by = c("DepComN" = "CODGEO")) %>%
+  left_join(Intercom %>%
+              filter(!(EPCI %in% EPCI_PLM)), by = c("DepComN" = "CODGEO")) %>%
+  mutate(EPCI = if_else(is.na(EPCI), DepComN, EPCI)) %>%
+  group_by(EPCI) %>%
+  summarise(Inscrits = sum(Inscrits),
+            Abstentions = sum(Abstentions),
+            Abstention = Abstentions / Inscrits,
+            Blancs = sum(Blancs),
+            Nuls = sum(Nuls),
+            Exprime = (Inscrits - Abstentions - Blancs - Nuls),
+            LePen = sum(LePen) / Exprime,
+            Melenchon = sum(Melenchon) / Exprime,
+            Macron = sum(Macron) / Exprime,
+            Fillon = sum(Fillon) / Exprime,
+            DupontAignan = sum(DupontAignan) / Exprime,
+            Lassalle = sum(Lassalle) / Exprime,
+            Hamon = sum(Hamon) / Exprime,
+            Asselineau = sum(Asselineau) / Exprime,
+            Poutou = sum(Poutou) / Exprime,
+            Arthaud = sum(Arthaud) / Exprime,
+            Cheminade = sum(Cheminade) / Exprime) %>%
+  ungroup() %>%
+  select(-c(Inscrits, Abstentions, Blancs, Nuls, Exprime)) %>%
+  rename(codgeo = EPCI) %>%
+  plyr::rbind.fill(pres_lyon, pres_marseille, pres_paris) %>%
+  filter(!is.na(codgeo)) %>%
+  inner_join(base_codes %>% mutate(codgeo = as.character(codgeo)))
+
+write_csv(PRE_brut, "data/PRE_brut.csv")
+
+PRE_fact = PRE_brut %>%
+  mutate(across(.cols = -codgeo, .fns = binarisation))
+
+write_csv(PRE_fact, "data/PRE_fact.csv")
+```
+
+```{r, insee-data, echo = F, message = F, warning = F}
 last_week = 35
@@
 FAM_fact = read_csv("data/FAM_fact.csv")
+PRE_fact = read.csv("data/PRE_fact.csv")
 
@@
 
-# LOG_brut = 
-# EMP_brut = read_csv2("data/EMP_brut.csv")
-# ACT_brut = read_csv2("data/ACT_brut.csv")
-# REV_brut = read_csv2("data/REV_brut.csv")
-# POP_brut = read_csv2("data/POP_brut.csv")
-# FOR_brut = read_csv2("data/FOR_brut.csv")
-# IMM_brut = read_csv2("data/IMM_brut.csv")
-# GEO_brut = read_csv("data/GEO_brut.csv")
-# FAM_brut = read_csv2("data/FAM_brut.csv")
-```
-
-```{r, echo = F, message = F, warning = F}
+base_codes = PRE_fact$codgeo
+```
+
+```{r, functions, echo = F, message = F, warning = F}
+# useful functions for correlation matrix
 get_upper_tri <- function(cormat){
@@
   if (classe_age == "tous"){
-    vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+    vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+      filter(classe_age != "TOUT_AGE") %>%
       mutate(codgeo = as.numeric(commune_residence)) %>%
@@
 
-    vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&refine.classe_age=TOUT_AGE&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+    vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+      filter(classe_age != "TOUT_AGE") %>%
       mutate(codgeo = as.numeric(epci)) %>%
@@
 
+  # homogénéisation de la population de l'EPCI par classe d'age
+  # la référence est la structure de la population francaise à la date
+  if (classe_age == "tous"){
+    vacc = unique(vacc) %>%
+      # Uniquement les codes géographiques des territoires de métropole sans les codes des métropole de Paris Lyon et marseille pour évides les comptes doubles
+      filter(codgeo %in% base_codes) %>% 
+      # Transformation de la population en numérique
+      mutate(population_carto = as.numeric(population_carto)) 
+    # Calcul de la population francaise totale
+    totPop = sum(vacc$population_carto)
+    # Calcul des proportions de chaque classe d'age dans la population francaise
+    props = vacc %>%
+      group_by(classe_age) %>%
+      summarise(proportionPop = sum(population_carto) / totPop) %>%
+      ungroup()
+    # Calcul des taux de vaccination homogénéisés par structure de population
+    vacc = vacc %>%
+      # Jointure des taux de vaccination au tableau de vaccination.
+      # La clé de jointure est la classe d'age
+      inner_join(props) %>%
+      # Multiplication du taux de vaccination par le taux de chaque classe d'age dans la population francaise
+      mutate(taux_cumu_1_inj = taux_cumu_1_inj * proportionPop) %>%
+      # Sommation des nouveaux taux de vaccination au sein de chaque ECPI
+      group_by(codgeo) %>%
+      summarise(taux_cumu_1_inj = sum(taux_cumu_1_inj)) %>%
+      ungroup()
+  }
+
   vacc = unique(vacc)
 
-  if (variable == "taux_cumu_1_inj"){
+  if (variable == "taux_cumu_1_inj"){ # dans la pratique on sera toujours dans ce cas
     LOG_1107 = LOG_fact %>%
-      select(-taux_cumu_1_inj) %>%
-      inner_join(vacc) %>%
-      mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)),
+      select(-taux_cumu_1_inj) %>% # suppression d'une variable
+      inner_join(vacc) %>% # jointure naturelle
+      mutate(
+        # Application de la fonction binarisation avec le seuil de 0.25 et mise en facteurs des variables
+        taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)), 
         across(-c(codgeo, taux_cumu_1_inj), function(x){
@@
                return(factor(x, levels = c(0,1), labels = c(0,1)))}))
+
+    PRE_1107 = PRE_fact %>%
+      inner_join(vacc) %>%
+      mutate(taux_cumu_1_inj = as.factor(binarisation(taux_cumu_1_inj, 0.25)),
+             across(-c(codgeo, taux_cumu_1_inj), function(x){
+               return(factor(x, levels = c(0,1), labels = c(0,1)))}))
+
   }else if (variable == "taux_1_inj"){
@@
     GEO_1107 = GEO_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
-  }
+    PRE_1107 = PRE_fact %>% select(-taux_cumu_1_inj) %>% inner_join(vacc) %>% mutate(taux_cumu_1_inj = as.factor(binarisation(as.numeric(taux_1_inj, 0.25))))
+  }
+
+  # calcul des OR - j'aurais très probablement pu faire tout ca en beaucoup moins de lignes mais j'avoue que je ne me suis pas vraiment penché sur la question.
 
@@
 
+  PRE_OR_1107 = questionr::odds.ratio(PRE_1107$Abstention, PRE_1107$taux_cumu_1_inj) %>%
+    rbind(questionr::odds.ratio(PRE_1107$LePen, PRE_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(PRE_1107$Melenchon, PRE_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(PRE_1107$Macron, PRE_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(PRE_1107$Fillon, GEO_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(PRE_1107$DupontAignan, GEO_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(PRE_1107$Lassalle, GEO_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(PRE_1107$Hamon, GEO_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(PRE_1107$Asselineau, GEO_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(PRE_1107$Poutou, GEO_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(PRE_1107$Arthaud, GEO_1107$taux_cumu_1_inj)) %>%
+    rbind(questionr::odds.ratio(PRE_1107$Cheminade, GEO_1107$taux_cumu_1_inj)) %>%
+    as.data.frame() %>%
+    bind_cols(Variable = colnames(PRE_1107)[2:13]) %>%
+    select(Variable, OR, `2.5 %`, `97.5 %`, p)
+  rownames(GEO_OR_1107) = NULL
+
+  # combinaison des tables
+
   DF_OR_1107 = LOG_OR_1107 %>% mutate(theme = "Housing", .after = Variable) %>%
@@
     bind_rows(FAM_OR_1107 %>% mutate(theme = "Family", .after = Variable)) %>%
-    bind_rows(REV_OR_1107 %>% mutate(theme = "Revenue", .after = Variable)) %>%
+    bind_rows(REV_OR_1107 %>% mutate(theme = "Income", .after = Variable)) %>%
     bind_rows(ACT_OR_1107 %>% mutate(theme = "Activity", .after = Variable)) %>%
-    bind_rows(FOR_OR_1107 %>% mutate(theme = "School", .after = Variable)) %>%
+    bind_rows(FOR_OR_1107 %>% mutate(theme = "Education", .after = Variable)) %>%
     bind_rows(POP_OR_1107 %>% mutate(theme = "Population", .after = Variable)) %>%
@@
     bind_rows(GEO_OR_1107 %>% mutate(theme = "Geography", .after = Variable)) %>%
+    bind_rows(PRE_OR_1107 %>% mutate(theme = "Elections", .after = Variable)) %>%
     group_by(theme) %>%
@@
          taux_cumu_1_inj = if_else(is.na(taux_cumu_1_inj), 0, taux_cumu_1_inj)) %>%
-  # test$taux_cumu_1_inj[is.na(test$taux_cumu_1_inj)] <- 0
-  # test %>%
-  pivot_wider(id_cols = codgeo,
+  filter(!(codgeo %in% c(999999999, 200054807, 200054781, 200046977))) %>%
+  select(codgeo, classe_age, taux_cumu_1_inj) %>%
+  pivot_wider(# reshape
+    id_cols = codgeo,
     names_from = classe_age,
@@
 
-### **Semaine 35** : le plus récent
-
-```{r, warning = F, echo = F, message = F}
+### **Semaine 35** : Après la mise en place du pass sanitaire
+
+```{r, s35, warning = F, echo = F, message = F}
 read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-35&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"),
@@
 
+### **Semaine 52** : Après l'annonce du pass vaccinal
+
+```{r, s52, warning = F, echo = F, message = F}
+read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-52&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"),
+          col_type = list(
+            date_reference = col_date(format = ""),
+            semaine_injection = col_character(),
+            epci = col_double(),
+            libelle_epci = col_character(),
+            population_carto = col_double(),
+            classe_age = col_character(),
+            libelle_classe_age = col_character(),
+            effectif_1_inj = col_double(),
+            effectif_termine = col_double(),
+            effectif_cumu_1_inj = col_double(),
+            effectif_cumu_termine = col_double(),
+            taux_1_inj = col_character(),
+            taux_termine = col_character(),
+            taux_cumu_1_inj = col_character(),
+            taux_cumu_termine = col_character(),
+            date = col_date(format = ""),
+            reg_code = col_double()
+          )) %>%
+  mutate(codgeo = epci) %>%
+  plyr::rbind.fill(read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-35&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"),
+                             col_type = list(
+                               date_reference = col_date(format = ""),
+                               semaine_injection = col_character(),
+                               commune_residence = col_double(),
+                               libelle_commune = col_character(),
+                               population_carto = col_double(),
+                               classe_age = col_character(),
+                               libelle_classe_age = col_character(),
+                               effectif_1_inj = col_double(),
+                               effectif_termine = col_double(),
+                               effectif_cumu_1_inj = col_double(),
+                               effectif_cumu_termine = col_double(),
+                               taux_1_inj = col_character(),
+                               taux_termine = col_character(),
+                               taux_cumu_1_inj = col_character(),
+                               taux_cumu_termine = col_character(),
+                               date = col_date(format = ""),
+                               reg_code = col_double()
+                             )) %>%
+                     mutate(codgeo = commune_residence)) %>%
+  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj),
+         taux_cumu_1_inj = if_else(is.na(taux_cumu_1_inj), 0, taux_cumu_1_inj)) %>%
+  filter(!(codgeo %in% c(999999999, 200054807, 200054781, 200046977))) %>%
+  select(codgeo, classe_age, taux_cumu_1_inj) %>%
+  pivot_wider(id_cols = codgeo,
+              names_from = classe_age,
+              values_from = taux_cumu_1_inj) %>%
+  inner_join(pop %>% select(codgeo)) %>%
+  select(4,6,5,2,3,7,8) %>%
+  desctable() %>%
+  pander()
+```
+
 # Les variables utilisées pour l'étude
@@
 ```
+
+## thématique vote politique 2017
+
+```{r, echo = F, message = F, warning = F}
+read.csv("data/PRE_brut.csv") %>%
+  desctable(stats = list("N" = length, "Med" = median, "IQR" = IQR)) %>%
+  pander()
+```
+
+```{r, echo = F, message = F, warning = F}
+data_b = read_csv("data/PRE_brut.csv")
+
+data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  ggplot() +
+  aes(x = Var1, y = Var2, fill = value) +
+  geom_tile(color = "white") +
+  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0, limit = c(-1,1), space = "Lab", name="Pearson\nCorrelation") +
+  theme_minimal() +
+  theme(axis.text.x = element_text(vjust = 1, size = 12, hjust = 1, angle = 45),
+        axis.text.y = element_text(vjust = 1, size = 12, hjust = 1)) +
+  coord_fixed()
+```
+
+```{r, echo = F, message = F, warning = F}
+database = data_b %>%
+  select(-codgeo) %>%
+  drop_na() %>%
+  cor() %>%
+  reorder_cormat() %>%
+  get_upper_tri() %>%
+  round(., 2) %>%
+  reshape2::melt(, na.rm = T) %>%
+  filter(Var1 != Var2 & (value > seuil | value < -seuil)) %>%
+  data.frame()
+
+nodes = data.frame(label = database$Var1) %>%
+  bind_rows(data.frame(label = database$Var2)) %>%
+  unique() %>%
+  mutate(id = row_number())
+
+edges = database %>%
+  inner_join(nodes, by = c("Var1" = "label")) %>%
+  rename(from = id) %>%
+  inner_join(nodes, by = c("Var2" = "label")) %>%
+  rename(to = id) %>%
+  select(from, to)
+
+visNetwork(nodes, edges) %>%
+  visOptions(highlightNearest = TRUE)
+```
+
+Les variables ne sont pas corrélées.
 
@@
 data = NULL
-for (i in c(27, 31, 35)){
+for (i in c(27, 31, 35, 52)){
   data = plyr::rbind.fill(
@@
 ```{r, echo = F, message = F, warning = F}
+colour = c("#13124e", "#ffb0af", "#2a3080", "#f57969", "#6d5aa1", "#d11d11", "#9c9bdb", "#f49600", "#bb749a", "#ffb92d")
+
 ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
@@
 
-for (wk in c(27, 31, 35)){
-  print(
+for (wk in c(27, 31, 35, 52)){
+  if (wk == 52){
+    assign(paste0("p", wk),
            fig %>%
@@
              theme_minimal() +
-      labs(title = paste("OR for the whole population, week", wk),
+             labs(title = paste("OR for the whole population - week", wk),
                   x = "",
-           y = "max(OR, 1/OR)")
-  )
-}
-```
-
-```{r, eval = F, warning = F, message = F, echo = F}
-plot_ly(data.frame(x=c(1,2,3,4),
-                   y=c(2,1,3,4),
-                   array = c(0.1, 0.2, 0.1, 0.1),
-                   arrayminus = c(0.2, 0.4, 1, 0.2)),
-        x = ~x,
-        y = ~y,
-        type = "scatter",
-        mode = "markers",
-        error_y = list(type = "data",
-                       symmetric = F,
-                       array = ~array,
-                       arrayminus = ~arrayminus))
+                  y = "max(OR, 1/OR)") +
+             scale_color_manual(values = colour) +
+             ylim(0, 22))
+
+  }else{
+    assign(paste0("p", wk),
+           fig %>%
+             filter(week == wk) %>%
+             ggplot() +
+             aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
+             geom_pointrange() +
+             theme_minimal() +
+             theme(legend.position = "none") +
+             labs(title = paste("OR for the whole population - week", wk),
+                  x = "",
+                  y = "max(OR, 1/OR)") +
+             scale_color_manual(values = colour) +
+             ylim(0, 22))
+  }
+}
+print(p27)
+print(p31)
+print(p35)
+print(p52)
+```
+
+```{r, evzl = F, echo = F}
+data %>%
+  group_by(theme) %>%
+  summarise(Indicators = n()/4) %>%
+  ungroup() %>%
+  View()
+```
+
+```{r}
+l_indicator = c("noTransport_toWk", "1564_Retired_amg_NW", "SingleParent_HH", "80+_amg_Single")
+```
+
+```{r, eval = F, echo = F}
+inds = c("Wk_Res_County-Municipality", "Wk_Res_Country-Region",
+         "15+_MenOnWomen_NoDiploma", "15+_VocationalGraduate_amg_WF",
+         "Macron", "Melenchon",
+         "1564_OtherInactive_amg_NW", "2554_women_Workforce_rate",
+         "OtherNoFamily_HH", "SingleParent_HH",
+         "latitude",
+         "1ry_res_FreeAcc",
+         "Immigrant",
+         "Unemployment_Benef", "Interdecile_91_Ratio",
+         "15+_CraftsBusinessShopkeeper_amg_POP", "15+_women_OtherNoActivity_amg_wPOP")
+
+data %>%
+  filter(theme == "Population" & week == 52) %>%
+  filter(`max_OR-inv_OR` == max(`max_OR-inv_OR`))
+
+data %>%
+  filter(Variable %in% inds) %>%
+  mutate(influence = if_else(OR >1, "OR", "1/OR"),
+         OR = round(if_else(influence == "OR", OR, inv_OR), 1),
+         `2.5 %` = round(if_else(influence == "OR", `2.5 %`, `inv_2.5 %`), 1),
+         `97.5 %` = round(if_else(influence == "OR", `97.5 %`, `inv_97.5 %`), 1),
+         `OR [IC]` = paste0(OR, " [", `2.5 %`, "; ", `97.5 %`, "]")) %>%
+  select(Variable, theme, influence, `OR [IC]`, week) %>%
+  pivot_wider(id_cols = c(Variable, theme, influence), names_from = week, values_from = `OR [IC]`, names_prefix = "w") %>%
+  View()
 ```
@@
 
-<!-- === -->
-```{r, eval = F, echo = F}
-vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", "TOUT_AGE", "&refine.semaine_injection=2021-", "35", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.factor(commune_residence)) %>%
-  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
-
-vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", "35", "&refine.classe_age=", "TOUT_AGE", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.factor(epci)) %>%
-  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
-  plyr::rbind.fill(vacc_com)
-
-test = vacc %>% inner_join(LOG_fact %>%
-                             select(codgeo, Overcrowding_rate) %>%
-                             mutate(codgeo = as.factor(codgeo))) %>%
-  mutate(taux_cumu_1_inj = binarisation(as.numeric(taux_cumu_1_inj), 0.25))
-
-summary(test$Overcrowding_rate[test$taux_cumu_1_inj == 1])
-summary(test$Overcrowding_rate[test$taux_cumu_1_inj == 0])
-
-table(test$Overcrowding_rate, test$taux_cumu_1_inj)
-
-questionr::odds.ratio(test$Overcrowding_rate, test$taux_cumu_1_inj)
-```
-
-<!-- ## Données à la semaine non cumulées -->
-
-```{r, echo = F, message = F, warning = F, eval = F}
+# Par classe d'âge - données cumulées
+
+## 0 - 19 ans
+
+```{r, echo = F, message = F, warning = F}
 data = NULL
-for (i in 2:last_week){
+for (i in c(27, 31, 35, 52)){
   data = bind_rows(
     data,
-    make_data_covid(i, variable = "taux_1_inj") %>%
+    make_data_covid(i, classe_age = "00-19") %>%
       arrange(theme, id) %>%
@@
     xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
-fig
-```
-
-```{r, echo = F, message = F, warning = F, eval = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 220, 219)) %>%
-  # filter(week == 33) %>%
-  # arrange(OR) %>%
-  # mutate(pos2 = row_number()) %>%
-  # select(Variable, pos) %>%
-  # inner_join(data) %>%
-  plot_ly(
-    x = ~pos,
-    y = ~`max_OR-inv_OR`,
-    size = ~-log10(p),
-    color = ~theme,
-    frame = ~week,
-    text = ~Variable,
-    symbol = ~shape,
-    symbols = c(219, 220),
-    hooverinfo = "text",
-    type = "scatter",
-    mode = "markers"
-  ) %>%
-  layout(scene = list(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim))))
-fig
-```
-
-# Par classe d'âge - données cumulées
-
-## 0 - 19 ans
-
-<!-- ### Données à la semaine -->
-
-```{r, echo = F, message = F, warning = F, eval = F}
+    yaxis = list(title = "max(OR, 1/OR)"))
+
+for (wk in c(27, 31, 35, 52)){
+  print(
+    fig %>%
+      filter(week == wk) %>%
+      ggplot() +
+      aes(x = pos, y = `max_OR-inv_OR`, color = theme, ymin = inf, ymax = sup) +
+      geom_pointrange() +
+      theme_minimal() +
+      labs(title = paste("OR for the whole population, week", wk),
+           x = "",
+           y = "max(OR, 1/OR)")
+  )
+}
+```
+
+### Distributions des Odds ratios
+
+```{r, message = F, echo = F, warning = F}
+data %>%
+  filter(week %in% c(27, 31, 35, 52)) %>%
+  mutate(week = factor(week)) %>%
+  ggplot() +
+  aes(x = `max_OR-inv_OR`, y = ..density.., color = week) +
+  geom_density(kernel = "gaussian") +
+  theme_bw() +
+  labs(title = "Distribution of max(OR, 1/OR) over every variable",
+       x = "max(OR, 1/OR)")
+```
+
+### Test de Wilcoxon
+
+```{r, message = F, echo = F, warning = F}
+w1 = data %>%
+  filter(week %in% c(27, 31)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w2 = data %>%
+  filter(week %in% c(31, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+w3 = data %>%
+  filter(week %in% c(27, 35)) %>%
+  mutate(week = factor(week)) %>%
+  wilcox.test(`max_OR-inv_OR` ~ week, data = .)
+
+data.frame(Comparison = c("wk27_wk31", "wk31_wk35", "wk27_wk35"),
+           method = c(w1$method, w2$method, w3$method), p.value = c(w1$p.value, w2$p.value, w3$p.value)) %>%
+  pander()
+```
+
+## 20 - 39 ans
+
+```{r, echo = F, message = F, warning = F}
 data = NULL
-for (i in 22:last_week){
+for (i in c(27, 31, 35, 52)){
   data = bind_rows(
     data,
-    make_data_covid(i, variable = "taux_1_inj", classe_age = "00-19") %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
-  )
-}
-
-# test = read_csv2(url("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-22&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")) %>%
-#   filter(classe_age != "00-19") %>%
-#   group_by(epci) %>%
-#   summarise(cumu_periode = sum(as.numeric(taux_1_inj))) %>%
-#   ungroup()
-```
-
-```{r, echo = F, message = F, warning = F, eval = F}
-ylim = max(data$`max_OR-inv_OR`[is.finite(data$`max_OR-inv_OR`)], na.rm = T)
-
-fig = data %>%
-  mutate(shape = if_else(OR > 1, 0, 1)) %>%
-  # filter(week == 33) %>%
-  # arrange(OR) %>%
-  # mutate(pos2 = row_number()) %>%
-  # select(Variable, pos) %>%
-  # inner_join(data) %>%
-  plot_ly(
-    x = ~pos,
-    y = ~`max_OR-inv_OR`,
-    size = ~-log10(p),
-    color = ~theme,
-    frame = ~week,
-    text = ~Variable,
-    alpha = 0.75,
-    symbol = ~shape,
-    symbols = c(220, 219),
-    hooverinfo = "text",
-    type = "scatter",
-    mode = "markers"
-  ) %>%
-  layout(
-    xaxis = list(title = "Variable"),
-    yaxis = list(title = "max(OR, 1/OR)", range = list(1, ylim)))
-fig
-```
-
-<!-- === -->
-```{r, eval = F, echo = F}
-vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.classe_age=", "TOUT_AGE", "&refine.semaine_injection=2021-", "27", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.numeric(commune_residence)) %>%
-  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj))
-
-vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", "27", "&refine.classe_age=", "TOUT_AGE", "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-  mutate(codgeo = as.numeric(epci)) %>%
-  mutate(taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) %>%
-  plyr::rbind.fill(vacc_com)
-
-test = vacc %>% inner_join(LOG_fact %>%
-                             select(codgeo, Overcrowding_rate)) %>%
-  mutate(taux_cumu_1_inj = binarisation(as.numeric(taux_cumu_1_inj), 0.25))
-
-summary(factor(test$Overcrowding_rate, levels = c(0,1), labels = c(0,1)))
-summary(test$taux_cumu_1_inj)
-
-(t=table(test$Overcrowding_rate, test$taux_cumu_1_inj))
-
-questionr::odds.ratio(factor(test$Overcrowding_rate, levels = c(0,1), labels = c(0,1)), test$taux_cumu_1_inj)
-epitools::oddsratio(x = t, method = "fisher")
-```
-
-<!-- === -->
-
-<!-- ### Données cumulées -->
-
-```{r, echo = F, message = F, warning = F}
-data = NULL
-for (i in c(27, 31, 35)){
-  data = bind_rows(
-    data,
-    make_data_covid(i, classe_age = "00-19") %>%
+    make_data_covid(i, classe_age = "20-39") %>%
       arrange(theme, id) %>%
@@
 
-for (wk in c(27, 31, 35)){
+for (wk in c(27, 31, 35, 52)){
   print(
@@
 
-<!-- # Données cumulées restreintes de la semaine 22 à 27 -->
-
-```{r, message = F, echo = F, warning = F, eval = F}
-data = make_data_covid_cumul(22:27)
-
-axis_df = data %>%
-  arrange(theme, id) %>%
-  mutate (pos = row_number()) %>%
-  group_by(theme) %>%
-  summarise(center = (max(pos) + min(pos)) /2)
-
-p = data %>%
-  arrange(theme, id) %>%
-  mutate (pos = row_number()) %>%
+# Taux de vaccinations selon les modalités des 3 variables les plus discriminantes
+
+```{r, echo = F, message = F, warning = F}
+vacct = NULL
+
+for (wk in c(27, 31, 35, 52)){
+  vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+    mutate(codgeo = as.numeric(commune_residence))
+
+  vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+    mutate(codgeo = as.numeric(epci))
+  plyr::rbind.fill(vacc_com)
+
+  vacc = unique(vacc) %>%
+    filter(codgeo %in% base_codes) %>% 
+    mutate(population_carto = as.numeric(population_carto),
+           taux_cumu_1_inj = as.numeric(taux_cumu_1_inj)) 
+  totPop = sum(vacc$population_carto)
+  props = vacc %>%
+    group_by(classe_age) %>%
+    summarise(proportionPop = sum(population_carto) / totPop) %>%
+    ungroup()
+  vacc = vacc %>%
+    inner_join(props) %>%
+    mutate(taux_cumu_1_inj = taux_cumu_1_inj * proportionPop) %>%
+    group_by(codgeo) %>%
+    summarise(taux_cumu_1_inj = sum(taux_cumu_1_inj)) %>%
+    ungroup() %>%
+    mutate(week = wk)
+
+  vacct = vacct %>% plyr::rbind.fill(vacc)
+}
+
+dfocus = read_csv("data/REV_brut.csv") %>%
+  select(codgeo, Unemployment_Benef, Interdecile_91_Ratio) %>%
+  mutate(Unemployment_Benef = factor(ntile(Unemployment_Benef, 4)),
+         Interdecile_91_Ratio = factor(ntile(Interdecile_91_Ratio, 4))) %>%
+  inner_join(vacct)
+# pivot_longer(cols = c(Overcrowding_rate, Unemployment_Benef, Interdecile_91_Ratio),
+#              names_to = "Variable",
+#              values_to = "half")
+```
+
+```{r, echo=F, message=FALSE, warning=FALSE}
+min = min(as.numeric(dfocus$taux_cumu_1_inj))
+max = max(as.numeric(dfocus$taux_cumu_1_inj))
+
+df_patch = dfocus %>%
+  # filter(week == wk) %>%
+  mutate(vaccination_rate = as.numeric(taux_cumu_1_inj)) %>%
+  pivot_longer(cols = c(Unemployment_Benef, Interdecile_91_Ratio),
+               names_to = "Variable",
+               values_to = "quartile") %>%
+  filter(!is.na(quartile)) %>%
+  mutate(Week = factor(week),
+         Variable = if_else(Variable == "Unemployment_Benef", "Unemployment", "Income inequality"))
+
+df_patch %>%
   ggplot() +
-  aes(x = pos, y = -log10(p), variable = Variable, OR = OR) +
-  geom_point(aes(color = theme), alpha = 0.8, size = 1.3) +
-  # scale_color_manual(values = rep(c("grey", "skyblue"), 5)[1:9]) +
-  scale_x_continuous(label = axis_df$theme,
-                     breaks = axis_df$center, guide = guide_axis(angle = 45)) +
-  # ggrepel::geom_label_repel(data = subset(DF_OR_32%>%
-  #                                           arrange(theme, id) %>%
-  #                                           mutate (pos = row_number(),
-  #                                                   theme = as.factor(theme)),
-  #                                         -log10(p) > 61),
-  #                           aes(label = Variable), size = 3) +
-  theme_bw() +
-  # geom_point(data = subset(DF_OR %>%
-  #                            arrange(theme, id) %>%
-  #                            mutate (pos = row_number(),
-  #                                    theme = as.factor(theme)) %>% filter(p < 0.0001/dim(DF_OR)[1])), color = "orange", size = 2) +
-  theme(legend.position = "none",
-        panel.border = element_blank(),
-        panel.grid.major.x = element_blank(),
-        panel.grid.minor.x = element_blank()) +
-  labs(title = paste("Manhattan plot on the P-value, weeks 28 to 34"),
-       x = "")
-
-plotly::ggplotly(p) %>%
-  layout(showlegend = FALSE, xaxis = list(tickangle=45))
-```
-
-<!-- # Données cumulées restreintes de la semaine 28 à 34 -->
-
-```{r, message = F, echo = F, warning = F, eval = F}
-data = make_data_covid_cumul(28:34)
-
-axis_df = data %>%
-  arrange(theme, id) %>%
-  mutate (pos = row_number()) %>%
-  group_by(theme) %>%
-  summarise(center = (max(pos) + min(pos)) /2)
-
-pl = data %>%
-  arrange(theme, id) %>%
-  mutate (pos = row_number(),
-          max = if_else(OR > 1, "OR", "inv(OR)")) %>%
+  aes(x=quartile, y=vaccination_rate, fill = Week) +
+  facet_grid(cols = vars(Variable)) +
+  scale_y_continuous(limits = c(min, max)) +
+  scale_fill_manual(values = c("#edf8b1", "#7fcdbb", "#1d91c0", "#225ea8")) +
+  geom_boxplot() +
+  theme_minimal() +
+  labs(y = "Vaccination rate",
+       x = "Quartile") +
+  theme(axis.text.x = element_text(size = 10),
+        axis.text.y = element_text(size = 10),
+        strip.text.x = element_text(size = 11),
+        legend.position = "top")
+
+# dfocus %>%
+#   filter(!is.na(half)) %>%
+#   group_by(classe_age, week, Variable, half) %>%
+#   summarise(population_carto = sum(population_carto, na.rm = T),
+#             effectif_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T)) %>%
+#   ungroup() %>%
+#   mutate(taux_cumu_1_inj = effectif_cumu_1_inj/population_carto,
+#          Variable = paste(Variable, half)) %>%
+#   plot_ly(
+#     x = ~week,
+#     y = ~taux_cumu_1_inj,
+#     color = ~Variable,
+#     symbol = ~half,
+#     mode = "lines+markers",
+#     frame = ~classe_age 
+#   )
+
+ggsave(filename = "boxplots.pdf",
+       device = "pdf",
+       path = "plots",
+       width = 5*1.5,
+       height = 3*1.5)
+```
+
+```{r, echo=F, message=FALSE, warning=FALSE}
+df_patch %>% # DF qui m'a permis de tracer les boxplots de différentes couleurs
+  # colnames = c(codgeo, week, vaccination_rate, Variable, quartile)
+  filter(quartile %in% c(1, 4)) %>% # on ne garde que les quartiles 1 et 4
+  # pivot_wider( # + de colonnes
+  #   # Reshape : codgeo, variable, quartile, s27, s31, s35 -> taux de vaccination pour chaque semaine
+  #   id_cols = c(codgeo, Variable, week),
+  #   names_from = quartile,
+  #   values_from = vaccination_rate,
+  #   names_prefix = "q") %>%
+  # mutate(
+  #   # Calcul de la différence des taux de vaccination entre chaque semaine
+  #   s27_35 = s35-s27,
+  #   s27_31 = s31-s27,
+  #   s31_35 = s35-s31) %>%
+# pivot_longer( # + de lignes
+#   # Reshape : codgeo, Variable, quartile, comp (nom des variables calculées juste avant), diff (valeur calculée juste avant)
+#   cols = c(s27_35, s27_31, s31_35),
+#   names_to = "comp",
+#   values_to = "diff") %>%
+group_by(
+  # le calcul suivant se fera par variable, par quartile et par comparaison de semaine
+  Variable, quartile, week) %>% 
+  summarise(
+    # nombre de territoires
+    sample_size = n(),
+    # moyenne de la différence
+    Mean = mean(vaccination_rate),
+    # écart-type de la différence
+    sd = sd(vaccination_rate)) %>%
+  ungroup() %>% # étape technique qui ne change rien
+  mutate(
+    # Calcul des intervalles de confiance
+    Margin_Error = abs(qnorm(0.025))* sd/sqrt(sample_size),
+    Lower = Mean - Margin_Error,
+    Upper = Mean + Margin_Error,
+    week = as.factor(week),
+    Mean = Mean,
+    .keep = "unused") %>%
+  pivot_wider( # + de colonnes
+    # Reshape : Variable, comp, Mean_1, Mean_4, Lower_1, Lower_4, Upper_1, Upper_4 (moyennes, bornes inf, bornes sup des intervalles de confiances pour les quartiles 1 et 4)
+    id_cols = c(Variable, week),
+    names_from = quartile,
+    values_from = c(Mean, Lower, Upper)) %>%
+  mutate(
+    # Calcul des différences entre les moyennes, entre les bornes inf et entre les bornes sup
+    diff_mean = Mean_1 - Mean_4,
+    diff_lower = Lower_1 - Upper_4,
+    diff_upper = Upper_1 - Lower_4,
+    .keep = "unused") %>%
+
   ggplot() +
-  aes(x = pos, y = `max_OR-inv_OR`, size = -log10(p), variable = Variable, Max = max) +
-  geom_point(aes(color = theme), alpha = 0.5) +
-  # scale_color_manual(values = rep(c("grey", "skyblue"), 5)[1:9]) +
-  scale_x_continuous(label = axis_df$theme,
-                     breaks = axis_df$center, guide = guide_axis(angle = 45)) +
-  # ggrepel::geom_label_repel(data = subset(DF_OR_32%>%
-  #                                           arrange(theme, id) %>%
-  #                                           mutate (pos = row_number(),
-  #                                                   theme = as.factor(theme)),
-  #                                         -log10(p) > 61),
-  #                           aes(label = Variable), size = 3) +
-  theme_bw() +
-  # geom_point(data = subset(DF_OR %>%
-  #                            arrange(theme, id) %>%
-  #                            mutate (pos = row_number(),
-  #                                    theme = as.factor(theme)) %>% filter(p < 0.0001/dim(DF_OR)[1])), color = "orange", size = 2) +
-  theme(legend.position = "none",
-        panel.border = element_blank(),
-        panel.grid.major.x = element_blank(),
-        panel.grid.minor.x = element_blank()) +
-  labs(title = paste("Manhattan plot on the P-value, weeks 28 to 34"),
-       x = "")
-
-plotly::ggplotly(pl) %>%
-  layout(showlegend = FALSE, xaxis = list(tickangle=45), yaxis = list(title = "max(OR, 1/OR)"))
-```
-
-# Taux de vaccinations selon les modalités des 3 variables les plus discriminantes
-
-```{r, echo = F, message = F, warning = F}
-vacct = NULL
-
-for (wk in c(27, 31, 35)){
-  vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
-    mutate(codgeo = as.numeric(commune_residence)) %>%
-    mutate(week = wk) %>%
-    select(codgeo, classe_age, population_carto, effectif_cumu_1_inj, week)
+  aes(x = week, y = diff_mean, ymin = diff_lower, ymax = diff_upper) + # sélection des différentes parties esthétiques
+  facet_grid(cols = vars(Variable)) + # séparation du graphe suivant des modalités
+  geom_point() + # nuage de points
+  geom_errorbar() + # intervalle de confiance
+  theme_minimal() + # couleur de fond
+  labs(title = "Confidence intervals of the difference of vaccination rate between Q1 and Q4",
+       y = "") # titres
+```
+
+```{r, echo=F, message=FALSE, warning=FALSE}
+# EPCI d'outremer
+siren_exclude = c(999999999, 249720061, 249720053, 200041788, 249710062,
+                  200044691, 249710070, 200018653, 200041507, 249710047,
+                  249730045, 249730052, 249730037, 200027548, 249740077,
+                  249740119, 249740093, 249740085, 249740101)
+wk = 35
 
@@
   mutate(codgeo = as.numeric(epci)) %>%
-    mutate(week = wk) %>%
-    select(codgeo, classe_age, population_carto, effectif_cumu_1_inj, week) %>%
-    plyr::rbind.fill(vacc_com)
-
-  vacct = vacct %>% plyr::rbind.fill(vacc)
-}
-
-dfocus = read_csv("data/LOG_fact.csv") %>%
-  select(codgeo, Overcrowding_rate) %>%
-  inner_join(read_csv("data/REV_fact.csv") %>%
-               select(codgeo, Unemployment_Benef, Interdecile_91_Ratio)) %>%
-  inner_join(vacct) %>%
-  pivot_longer(cols = c(Overcrowding_rate, Unemployment_Benef, Interdecile_91_Ratio),
-               names_to = "Variable",
-               values_to = "half")
-```
-
-```{r, echo = F, message = F, warning = F}
-
-dfocus %>%
-  filter(!is.na(half)) %>%
-  group_by(classe_age, week, Variable, half) %>%
-  summarise(population_carto = sum(population_carto, na.rm = T),
-            effectif_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T)) %>%
+  mutate(week = wk)
+
+vacc %>%
+  filter(!(codgeo %in% siren_exclude)) %>%
+  inner_join(pop %>% select(codgeo)) %>%
+  group_by(classe_age) %>%
+  summarise(population = sum(population_carto),
+            eff_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T)) %>%
   ungroup() %>%
-  mutate(taux_cumu_1_inj = effectif_cumu_1_inj/population_carto,
-         Variable = paste(Variable, half)) %>%
-  plot_ly(
-    x = ~week,
-    y = ~taux_cumu_1_inj,
-    color = ~Variable,
-    symbol = ~half,
-    mode = "lines+markers",
-    frame = ~classe_age 
-  )
-
+  mutate(tx_vax = eff_cumu_1_inj / population) %>% pander()
+```
+
+```{r}
+wk = 42
+
+vacc = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
+  mutate(codgeo = as.numeric(epci)) %>%
+  mutate(week = wk)
+
+vacc %>%
+  filter(!(codgeo %in% siren_exclude)) %>%
+  inner_join(pop %>% select(codgeo)) %>%
+  group_by(classe_age) %>%
+  summarise(population = sum(population_carto),
+            eff_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T)) %>%
+  ungroup() %>%
+  mutate(tx_vax = eff_cumu_1_inj / population) %>% pander()
+```
+
+```{r, echo = F, warning = F, message = F}
+# mise en forme des différents graphiques
+
+library(patchwork)
+(p27 | p31 | p35) /
+  (q27 | q31 | q35 )
+
+(p27 / q27) + (p31 / q31) + (p35 / q35)
+```
+
+```{r}
+p27 | p31 | p35 | p52
 ```
@@
 
-```{r, eval = F, echo = F}
+*Points d'attention sur les données de vaccination présentées*
+
+Il est possible qu’un patient ne reçoive qu’une injection et que sa vaccination soit ainsi terminée : cas des vaccins à une injection ou des patients ayant déjà été atteints par la Covid-19, par exemple ;
+
+La population de référence pour le calcul des effectifs de patients vaccinés et pour le calcul des taux est la population de la cartographie des pathologies et des dépenses de l’Assurance Maladie, et non la population recensée par l’Insee dont le découpage par tranche d’âge et par commune date de 2017 ;
+
+Seuls les patients vaccinés faisant partie de la population de la cartographie des pathologies et des dépenses de l’Assurance Maladie sont pris en compte dans les effectifs (> 95% des vaccinés) ;
+
+La répartition par EPCI n’est pas possible pour certains patients dont le département de résidence ou la commune est inconnu(e).
+Ces patients sont rattachés à l’EPCI « 999999999 » dans le jeu de données.
+
+A contrario : les données de Sante Publique France
+
+```{r, message = F, warning = F, echo = F}
 data = NULL
-for (i in 2:last_week){
+
+for (i in 1:40){
+  if (i < 10){
+    i = paste0("0", i)
+  }
   data = bind_rows(
     data,
-    make_data_covid(i) %>%
-      arrange(theme, id) %>%
-      mutate (pos = row_number(),
-              week = i)
+    read.csv(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2021-", i, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B")), sep = ";")
   )
 }
-```
-
-```{r, eval = F, echo = F}
-data1 = data
-```
-
-```{r, eval = F, echo = F}
-data = data1 %>%
-  # filter(Variable %in% c("NO-SE",
-  #                        "Overcrowding_rate",
-  #                        "Interdecile_91_Ratio",
-  #                        "Unemployment_Benef",
-  #                        "Immigrant",
-  #                        "Pop_NoChildFamily_HH")) %>%
-  filter(week >= 22) %>%
-  mutate(ban = as.factor(if_else(week <27, 0, 1)))
-p = data %>%
-  # filter(ban == 0) %>%
+
+data %>%
+  filter(population_carto != "NS" & classe_age == "TOUT_AGE") %>%
+  select(effectif_cumu_1_inj, population_carto, date, epci, classe_age) %>%
+  group_by(date) %>%
+  summarise(effectif_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T),
+            population_carto = sum(as.numeric(population_carto))) %>%
+  ungroup() %>%
+  mutate(couv_dose1 = effectif_cumu_1_inj / population_carto,
+         source = "ameli",
+         jour = lubridate::ymd(date)) %>%
+  select(jour, couv_dose1, source)
+
+ggplotly(
+  read.csv(url("https://www.data.gouv.fr/fr/datasets/r/b273cf3b-e9de-437c-af55-eda5979e92fc"), sep = ";") %>%
+    group_by(jour) %>%
+    summarise(n_cum_dose1 = sum(n_cum_dose1, na.rm = T)) %>%
+    ungroup() %>%
+    mutate(couv_dose1 = n_cum_dose1 / 97114995,
+           jour = lubridate::ymd(jour),
+           source = "SPF") %>%
+    select(jour, couv_dose1, source) %>%
+    plyr::rbind.fill(data %>%
+                       filter(population_carto != "NS" & classe_age == "TOUT_AGE") %>%
+                       select(effectif_cumu_1_inj, population_carto, date, epci, classe_age) %>%
+                       group_by(date) %>%
+                       summarise(effectif_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T),
+                                 population_carto = sum(as.numeric(population_carto))) %>%
+                       ungroup() %>%
+                       mutate(couv_dose1 = effectif_cumu_1_inj / population_carto,
+                              source = "ameli",
+                              jour = lubridate::ymd(date)) %>%
+                       select(jour, couv_dose1, source)) %>%
     ggplot() +
-  aes(x = week, y = log(`max_OR-inv_OR`), color = Variable, alpha = 0.5) +
-  geom_point(size = 0.5) +
-  # geom_vline(aes(xintercept = 26.5)) +
-  geom_smooth(aes(fill = ban), size = 0.5, method = "lm", se = F)+
-  theme_bw() +
-  theme(legend.position = "none") 
-# ggplotly(p)
-
-# plot(data$`max_OR-inv_OR`,
-#      type="n",
-#      ylim=c(00,12),
-#      xlab="Week",
-#      ylab="log(Interdecile_91_Ratio)",
-#      bty="l",
-#      xaxt="n")
-# rect(26.5,0,34,12,col=grey(0.9),border=F)
-# points(log(data$`max_OR-inv_OR`[data$ban==0]),cex=0.7)
-```
-
-<!-- # Données de vaccination nationales -->
-
-```{r, echo = F, warning = F, message = F, eval = F}
-wk = 37
-
+    aes(x=jour, y=couv_dose1, color = source) +
+    geom_line() +
+    theme_minimal() +
+    labs(title = "Différence dans les données publiques",
+         y = "Couverture vaccinale 1ère dose") +
+    scale_y_continuous(labels = scales::percent)
+)
+```
+
+Quand je retire les moins de 12 ans qui n'ont pas accès à la vaccination, j'arrive à 83,4% de la population qui est vaccinée.
+Je pense que SPF publie un pourcentage de personnes vaccinées parmi les personnes qui ont accès au vaccin...
+
+On se demande d'où vient la différence, les données de vaccination ou les données de population générale ?
+
+```{r, message = F, warning = F, echo = F}
+ggplotly(
+  read.csv(url("https://www.data.gouv.fr/fr/datasets/r/fa4ad329-14ec-4394-85a4-c5df33769dff"), sep = ";") %>%
+    mutate(jour = lubridate::ymd(jour),
+           source = "SPF") %>%
+    select(jour, n_cum_dose1, source) %>%
+    plyr::rbind.fill(data %>%
+                       filter(population_carto != "NS" & classe_age == "TOUT_AGE") %>%
+                       group_by(date) %>%
+                       summarise(effectif_cumu_1_inj = sum(effectif_cumu_1_inj, na.rm = T)) %>%
+                       ungroup() %>%
+                       mutate(n_cum_dose1 = effectif_cumu_1_inj,
+                              source = "ameli",
+                              jour = lubridate::ymd(date)) %>%
+                       select(jour, n_cum_dose1, source))%>%
+    ggplot() +
+    aes(x=jour, y=n_cum_dose1, color = source) +
+    geom_line() +
+    theme_minimal() +
+    labs(title = "Différence dans les données publiques",
+         y = "Nb vaccinations cumulées 1ère dose")
+)
+```
+
+```{r, message = F, warning = F, echo = F}
+ggplotly(
+  read.csv(url("https://www.data.gouv.fr/fr/datasets/r/fa4ad329-14ec-4394-85a4-c5df33769dff"), sep = ";") %>%
+    filter(couv_dose1 != 0) %>%
+    mutate(jour = lubridate::ymd(jour),
+           source = "SPF",
+           population_carto = n_cum_dose1*100/couv_dose1) %>%
+    select(jour, population_carto, source) %>%
+    plyr::rbind.fill(data %>%
+                       filter(population_carto != "NS" & classe_age == "TOUT_AGE") %>%
+                       select(population_carto, date, epci, classe_age) %>%
+                       group_by(date) %>%
+                       summarise(population_carto = sum(as.numeric(population_carto))) %>%
+                       ungroup() %>%
+                       mutate(source = "ameli",
+                              jour = lubridate::ymd(date)) %>%
+                       select(jour, population_carto, source)) %>%
+    ggplot() +
+    aes(x=jour, y=population_carto, color = source) +
+    geom_line() +
+    theme_minimal() +
+    labs(title = "Différence dans les données publiques",
+         y = "Estimation de la population française")
+)
+```
+
+# Odds ratios à l'échelle de l'individu
+
+```{r, table}
+vacct = NULL
+
+for (wk in c(27, 31, 35)){
   vacc_com = read_csv2(url(paste0("https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&refine.semaine_injection=2021-", wk, "&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"))) %>%
     mutate(codgeo = as.numeric(commune_residence)) %>%
-  mutate(week = wk) %>%
-  select(codgeo, classe_age, population_carto, effectif_cumu_1_inj, week)
+    mutate(week = wk)
 
@@
     mutate(week = wk) %>%
-  select(codgeo, classe_age, population_carto, effectif_cumu_1_inj, week) %>%
     plyr::rbind.fill(vacc_com)
 
-vacc %>%
-  filter(!is.na(effectif_cumu_1_inj)) %>%
+  vacct = vacct %>% plyr::rbind.fill(vacc)
+}
+
+pop_matrix = vacct %>%
+  filter(!(codgeo %in% c(siren_exclude, 200054781, 200046977, 200054807)) &
+           classe_age == "TOUT_AGE" &
+           week == 27) %>%
+  select(codgeo, population_carto, effectif_cumu_1_inj) %>%
+  inner_join(LOG_fact %>% select(codgeo, Overcrowding_rate)) %>%
+  inner_join(REV_fact %>% select(codgeo, Unemployment_Benef))
+
+vacc = NULL
+over = NULL
+unem = NULL
+for (i in 1:length(pop_matrix$codgeo)){
+  vacc = c(vacc, rep(1, pop_matrix$effectif_cumu_1_inj[i]),
+           rep(0, pop_matrix$population_carto[i] - pop_matrix$effectif_cumu_1_inj[i]))
+  over = c(over, rep(pop_matrix$Overcrowding_rate[i], pop_matrix$population_carto[i]))
+  unem = c(unem, rep(pop_matrix$Unemployment_Benef[i], pop_matrix$population_carto[i]))
+}
+
+over_d = as.factor(over)
+unem_d = as.factor(unem)
+vacc_d = as.factor(vacc)
+questionr::odds.ratio(over_d, vacc_d)
+questionr::odds.ratio(unem_d, vacc_d)
+```
+
+```{r}
+pop_matrix = vacct %>%
+  filter(!(codgeo %in% c(siren_exclude, 200054781, 200046977, 200054807)) &
+           classe_age == "TOUT_AGE" &
+           week == 31) %>%
+  select(codgeo, population_carto, effectif_cumu_1_inj) %>%
+  inner_join(LOG_fact %>% select(codgeo, Overcrowding_rate)) %>%
+  inner_join(REV_fact %>% select(codgeo, Unemployment_Benef))
+
+vacc = NULL
+over = NULL
+unem = NULL
+for (i in 1:length(pop_matrix$codgeo)){
+  vacc = c(vacc, rep(1, pop_matrix$effectif_cumu_1_inj[i]),
+           rep(0, pop_matrix$population_carto[i] - pop_matrix$effectif_cumu_1_inj[i]))
+  over = c(over, rep(pop_matrix$Overcrowding_rate[i], pop_matrix$population_carto[i]))
+  unem = c(unem, rep(pop_matrix$Unemployment_Benef[i], pop_matrix$population_carto[i]))
+}
+
+over_d = as.factor(over)
+unem_d = as.factor(unem)
+vacc_d = as.factor(vacc)
+questionr::odds.ratio(over_d, vacc_d)
+questionr::odds.ratio(unem_d, vacc_d)
+```
+
+```{r}
+pop_matrix = vacct %>%
+  filter(!(codgeo %in% c(siren_exclude, 200054781, 200046977, 200054807)) &
+           classe_age == "TOUT_AGE" &
+           week == 35) %>%
+  select(codgeo, population_carto, effectif_cumu_1_inj) %>%
+  inner_join(LOG_fact %>% select(codgeo, Overcrowding_rate)) %>%
+  inner_join(REV_fact %>% select(codgeo, Unemployment_Benef))
+
+vacc = NULL
+over = NULL
+unem = NULL
+for (i in 1:length(pop_matrix$codgeo)){
+  vacc = c(vacc, rep(1, pop_matrix$effectif_cumu_1_inj[i]),
+           rep(0, pop_matrix$population_carto[i] - pop_matrix$effectif_cumu_1_inj[i]))
+  over = c(over, rep(pop_matrix$Overcrowding_rate[i], pop_matrix$population_carto[i]))
+  unem = c(unem, rep(pop_matrix$Unemployment_Benef[i], pop_matrix$population_carto[i]))
+}
+
+over_d = as.factor(over)
+unem_d = as.factor(unem)
+vacc_d = as.factor(vacc)
+questionr::odds.ratio(over_d, vacc_d)
+questionr::odds.ratio(unem_d, vacc_d)
+```
+
+```{r}
+median(over)
+```
+
+```{r}
+median(pop_matrix$Overcrowding_rate)
+```
+
+```{r}
+adresse = "https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&refine.semaine_injection=2022-01&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"
+data = read_csv2(url(adresse))
+data %>%
   group_by(classe_age) %>%
-  summarise(pop = sum(population_carto, na.rm = T),
-            tot_vacc = sum(effectif_cumu_1_inj, na.rm = T)) %>%
+  summarise(vacc1 = sum(effectif_cumu_1_inj, na.rm = T),
+            pop = sum(population_carto, na.rm = T)) %>%
   ungroup() %>%
-  mutate(tx_vacc = tot_vacc/pop)
-```
+  mutate(taux = 100*vacc1/pop)
+```

### 2022-02-17 plots/carto_indee_covid.Rmd
Add cartography

---
title: "Carto"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
```

```{r cars}
library(sf)
library(tidyverse)
library(plotly)
library(viridis)
library(leaflet)
library(ggspatial)
library(gridExtra)
library(htmltools)
```

```{r}
poly = st_read("georef-france-epci-millesime.shp")
poly_com = st_read("georef-france-commune-arrondissement-municipal-millesime.shp")

REV_brut = read_csv("REV_brut.csv")
LOG_brut = read.csv("LOG_brut.csv")

```

```{r}
poly$epci_code <- as.numeric(levels(poly$epci_code))[poly$epci_code]
poly_com$com_arm_cur <- as.numeric(levels(poly_com$com_arm_cur))[poly_com$com_arm_cur]

plot_REV = poly %>%
  inner_join(REV_brut, by = c("epci_code" = "codgeo")) %>%
  rename(codgeo = epci_code) %>%
  plyr::rbind.fill(poly_com %>%
                     inner_join(REV_brut, by = c("com_arm_cur" = "codgeo")) %>%
                     rename(codgeo = com_arm_cur))

plot_LOG = poly %>%
  inner_join(LOG_brut, by = c("epci_code" = "codgeo")) %>%
  rename(codgeo = epci_code) %>%
  plyr::rbind.fill(poly_com %>%
                     inner_join(LOG_brut, by = c("com_arm_cur" = "codgeo")) %>%
                     rename(codgeo = com_arm_cur))
```

# Represent vaccination rate

```{r}
vacct = read_csv("vacc_rates4.csv")
```

```{r}
plot_vacc = poly %>%
  rename(codgeo = epci_code) %>%
  plyr::rbind.fill(poly_com %>%
                     rename(codgeo = com_arm_cur)) %>%
  inner_join(vacct)
```

```{r}
carto_vacc = function(wk){
  vacc_sem = plot_vacc %>% filter(week == wk)

  min_r = min(vacc_sem$taux_cumu_1_inj, na.rm = T)
  max_r = max(vacc_sem$taux_cumu_1_inj, na.rm = T)

  set_scale = function(x, min_r, max_r){
    return((x-min_r)/(max_r-min_r))
  }

  min_p = set_scale(min(vacc_sem[vacc_sem$epci_name == "Métropole du Grand Paris",]$taux_cumu_1_inj, na.rm = T), min_r, max_r)
  max_p = set_scale(max(vacc_sem[vacc_sem$epci_name == "Métropole du Grand Paris",]$taux_cumu_1_inj, na.rm = T), min_r, max_r)

  min_l = set_scale(min(vacc_sem[vacc_sem$epci_name == "Métropole de Lyon",]$taux_cumu_1_inj, na.rm = T), min_r, max_r)
  max_l = set_scale(max(vacc_sem[vacc_sem$epci_name == "Métropole de Lyon",]$taux_cumu_1_inj, na.rm = T), min_r, max_r)

  min_m = set_scale(min(vacc_sem[vacc_sem$epci_name == "Métropole d'Aix-Marseille-Provence",]$taux_cumu_1_inj, na.rm = T), min_r, max_r)
  max_m = set_scale(max(vacc_sem[vacc_sem$epci_name == "Métropole d'Aix-Marseille-Provence",]$taux_cumu_1_inj, na.rm = T), min_r, max_r)

  p1 = vacc_sem %>%
    ggplot() +
    aes(fill = taux_cumu_1_inj) +
    scale_fill_viridis(name = paste("Vaccination Rate\nWeek", wk),option = "cividis") +
    geom_sf(size = 0)  +
    theme_void() +
    theme(legend.position = "top") +
    coord_sf(crs = st_crs(4326)) +
    labs(title = "France")

  p2 = vacc_sem %>%
    filter(epci_name == "Métropole du Grand Paris") %>%
    ggplot() +
    aes(fill = taux_cumu_1_inj) +
    scale_fill_viridis(option = "cividis", begin = min_p, end = max_p) +
    geom_sf(size = 0)  +
    theme_void() +
    theme(legend.position = "None") +
    coord_sf(crs = st_crs(4326)) +
    labs(title = "Paris")

  p3 = vacc_sem %>%
    filter(epci_name == "Métropole de Lyon") %>%
    ggplot() +
    aes(fill = taux_cumu_1_inj) +
    scale_fill_viridis(option = "cividis", begin = min_l, end = max_l) +
    geom_sf(size = 0)  +
    theme_void() +
    theme(legend.position = "None") +
    coord_sf(crs = st_crs(4326)) +
    labs(title = "Lyon")

  p4 = vacc_sem %>%
    filter(epci_name == "Métropole d'Aix-Marseille-Provence") %>%
    ggplot() +
    aes(fill = taux_cumu_1_inj) +
    scale_fill_viridis(option = "cividis", begin = min_m, end = max_m) +
    geom_sf(size = 0)  +
    theme_void() +
    theme(legend.position = "None") +
    coord_sf(crs = st_crs(4326)) +
    labs(title = "Marseille-Aix")

  return(grid.arrange(p1, p2, p3, p4,
                      widths = c(4,1,1,1),
                      layout_matrix = rbind(c(1, 2),
                                            c(1, 3),
                                            c(1, 4))))
}
```

```{r}
carto_vacc(27)
carto_vacc(31)
carto_vacc(35)
carto_vacc(52)
```

# Represent Unemployment

```{r}
min_r = min(plot_REV$Unemployment_Benef, na.rm = T)
max_r = max(plot_REV$Unemployment_Benef, na.rm = T)

set_scale = function(x, min_r, max_r){
  return((x-min_r)/(max_r-min_r))
}

min_p = set_scale(min(plot_REV[plot_REV$epci_name == "Métropole du Grand Paris",]$Unemployment_Benef, na.rm = T), min_r, max_r)
max_p = set_scale(max(plot_REV[plot_REV$epci_name == "Métropole du Grand Paris",]$Unemployment_Benef, na.rm = T), min_r, max_r)

min_l = set_scale(min(plot_REV[plot_REV$epci_name == "Métropole de Lyon",]$Unemployment_Benef, na.rm = T), min_r, max_r)
max_l = set_scale(max(plot_REV[plot_REV$epci_name == "Métropole de Lyon",]$Unemployment_Benef, na.rm = T), min_r, max_r)

min_m = set_scale(min(plot_REV[plot_REV$epci_name == "Métropole d'Aix-Marseille-Provence",]$Unemployment_Benef, na.rm = T), min_r, max_r)
max_m = set_scale(max(plot_REV[plot_REV$epci_name == "Métropole d'Aix-Marseille-Provence",]$Unemployment_Benef, na.rm = T), min_r, max_r)

p1 = plot_REV %>%
  ggplot() +
  aes(fill = Unemployment_Benef) +
  scale_fill_viridis(name = "Unemployment\nBenefits",option = "magma") +
  geom_sf(size = 0)  +
  theme_void() +
  theme(legend.position = "top") +
  coord_sf(crs = st_crs(4326)) +
  labs(title = "France")

p2 = plot_REV %>%
  filter(epci_name == "Métropole du Grand Paris") %>%
  ggplot() +
  aes(fill = Unemployment_Benef) +
  scale_fill_viridis(option = "magma", begin = min_p, end = max_p) +
  geom_sf(size = 0)  +
  theme_void() +
  theme(legend.position = "None") +
  coord_sf(crs = st_crs(4326)) +
  labs(title = "Paris")

p3 = plot_REV %>%
  filter(epci_name == "Métropole de Lyon") %>%
  ggplot() +
  aes(fill = Unemployment_Benef) +
  scale_fill_viridis(option = "magma", begin = min_l, end = max_l) +
  geom_sf(size = 0)  +
  theme_void() +
  theme(legend.position = "None") +
  coord_sf(crs = st_crs(4326)) +
  labs(title = "Lyon")

p4 = plot_REV %>%
  filter(epci_name == "Métropole d'Aix-Marseille-Provence") %>%
  ggplot() +
  aes(fill = Unemployment_Benef) +
  scale_fill_viridis(option = "magma", begin = min_m, end = max_m) +
  geom_sf(size = 0)  +
  theme_void() +
  theme(legend.position = "None") +
  coord_sf(crs = st_crs(4326)) +
  labs(title = "Marseille-Aix")

grid.arrange(p1, p2, p3, p4,
             widths = c(4,1,1,1),
             layout_matrix = rbind(c(1, 2),
                                   c(1, 3),
                                   c(1, 4)))
```

# Reprensent Overcrowding Rate

```{r}
min_r = min(plot_LOG$Overcrowding_rate, na.rm = T)
max_r = max(plot_LOG$Overcrowding_rate, na.rm = T)

set_scale = function(x, min_r, max_r){
  return((x-min_r)/(max_r-min_r))
}

min_p = set_scale(min(plot_LOG[plot_LOG$epci_name == "Métropole du Grand Paris",]$Overcrowding_rate, na.rm = T), min_r, max_r)
max_p = set_scale(max(plot_LOG[plot_LOG$epci_name == "Métropole du Grand Paris",]$Overcrowding_rate, na.rm = T), min_r, max_r)

min_l = set_scale(min(plot_LOG[plot_LOG$epci_name == "Métropole de Lyon",]$Overcrowding_rate, na.rm = T), min_r, max_r)
max_l = set_scale(max(plot_LOG[plot_LOG$epci_name == "Métropole de Lyon",]$Overcrowding_rate, na.rm = T), min_r, max_r)

min_m = set_scale(min(plot_LOG[plot_LOG$epci_name == "Métropole d'Aix-Marseille-Provence",]$Overcrowding_rate, na.rm = T), min_r, max_r)
max_m = set_scale(max(plot_LOG[plot_LOG$epci_name == "Métropole d'Aix-Marseille-Provence",]$Overcrowding_rate, na.rm = T), min_r, max_r)

p1 = plot_LOG %>%
  ggplot() +
  aes(fill = Overcrowding_rate) +
  scale_fill_viridis(name = "Overcrowding\nRate",option = "plasma") +
  geom_sf(size = 0)  +
  theme_void() +
  theme(legend.position = "top") +
  coord_sf(crs = st_crs(4326)) +
  labs(title = "France")

p2 = plot_LOG %>%
  filter(epci_name == "Métropole du Grand Paris") %>%
  ggplot() +
  aes(fill = Overcrowding_rate) +
  scale_fill_viridis(option = "plasma", begin = min_p, end = max_p) +
  geom_sf(size = 0)  +
  theme_void() +
  theme(legend.position = "None") +
  coord_sf(crs = st_crs(4326)) +
  labs(title = "Paris")

p3 = plot_LOG %>%
  filter(epci_name == "Métropole de Lyon") %>%
  ggplot() +
  aes(fill = Overcrowding_rate) +
  scale_fill_viridis(option = "plasma", begin = min_l, end = max_l) +
  geom_sf(size = 0)  +
  theme_void() +
  theme(legend.position = "None") +
  coord_sf(crs = st_crs(4326)) +
  labs(title = "Lyon")

p4 = plot_LOG %>%
  filter(epci_name == "Métropole d'Aix-Marseille-Provence") %>%
  ggplot() +
  aes(fill = Overcrowding_rate) +
  scale_fill_viridis(option = "plasma", begin = min_m, end = max_m) +
  geom_sf(size = 0)  +
  theme_void() +
  theme(legend.position = "None") +
  coord_sf(crs = st_crs(4326)) +
  labs(title = "Marseille-Aix")

grid.arrange(p1, p2, p3, p4,
             widths = c(4,1,1,1),
             layout_matrix = rbind(c(1, 2),
                                   c(1, 3),
                                   c(1, 4)))
```

# Interactive maps

## Unemployment Benefits

```{r}
# Remove missing data
plot_REV = plot_REV %>% filter(!is.na(Unemployment_Benef))

# set colours
pal = scales::gradient_n_pal(colours = c("lightblue", "black", "orange"),
                             values = c(min(plot_REV$Unemployment_Benef),
                                        median(plot_REV$Unemployment_Benef, na.rm = T),
                                        max(plot_REV$Unemployment_Benef)))

# we are representing the two layers (EPCI & Municipalities) separately
plot_REV_epci = poly %>%
  inner_join(REV_brut, by = c("epci_code" = "codgeo")) %>%
  rename(codgeo = epci_code)
plot_REV_com = poly_com %>%
  inner_join(REV_brut, by = c("com_arm_cur" = "codgeo")) %>%
  rename(codgeo = com_arm_cur)

# apply colours
plot_REV_epci$hex = pal(plot_REV_epci$Unemployment_Benef)
plot_REV_com$hex = pal(plot_REV_com$Unemployment_Benef)

# Build label
plot_REV_epci = plot_REV_epci %>%
  group_by(codgeo) %>%
  mutate(lab = paste0("<p>", epci_name, "</p><p>Unemployment Benefits: ", round(Unemployment_Benef, 2), "%</p>")) %>%
  ungroup()
plot_REV_com = plot_REV_com %>%
  group_by(codgeo) %>%
  mutate(lab = paste0("<p>", com_arm_nam, "</p><p>Unemployment Benefits: ", round(Unemployment_Benef, 2), "%</p>")) %>%
  ungroup()

leaflet() %>%
  addTiles() %>%
  addPolygons(data = plot_REV_epci,
              color = ~hex,
              weight = 1,
              opacity = 0.4,
              fillOpacity = 0.5,
              stroke = T,
              highlight = highlightOptions(opacity = 0.8,
                                           fillOpacity = 0.9,
                                           bringToFront = T),
              # label = lapply(plot_REV_epci$lab, HTML)
              label = ~paste0("Unemployment Benefits: ", round(Unemployment_Benef, 2), "%")
              ) %>%
  addPolygons(data = plot_REV_com,
              color = ~hex,
              weight = 1,
              opacity = 0.4,
              fillOpacity = 0.5,
              stroke = T,
              highlight = highlightOptions(opacity = 0.8,
                                           fillOpacity = 0.9,
                                           bringToFront = T),
              # label = lapply(plot_REV_com$lab, HTML)
              label = ~paste0("Unemployment Benefits: ", round(Unemployment_Benef, 2), "%")
              ) %>%
  addProviderTiles("Stamen.TonerLite")
```

## Overcrowding rate

```{r}
plot_LOG = plot_LOG %>% filter(!is.na(Overcrowding_rate))
pal = scales::gradient_n_pal(colours = c("green", "black", "red"),
                             values = c(min(plot_LOG$Overcrowding_rate),
                                        median(plot_LOG$Overcrowding_rate, na.rm = T),
                                        max(plot_LOG$Overcrowding_rate)))

plot_LOG_epci = poly %>%
  inner_join(LOG_brut, by = c("epci_code" = "codgeo")) %>%
  rename(codgeo = epci_code)
plot_LOG_com = poly_com %>%
  inner_join(LOG_brut, by = c("com_arm_cur" = "codgeo")) %>%
  rename(codgeo = com_arm_cur)

plot_LOG_epci$hex = pal(plot_LOG_epci$Overcrowding_rate)
plot_LOG_epci = plot_LOG_epci %>%
  group_by(codgeo) %>%
  mutate(lab = paste0("<p>", epci_name, "</p><p>Overcrowding rate: ", round(Overcrowding_rate, 2), "%</p>")) %>%
  ungroup()
plot_LOG_com$hex = pal(plot_LOG_com$Overcrowding_rate)
plot_LOG_com = plot_LOG_com %>%
  group_by(codgeo) %>%
  mutate(lab = paste0("<p>", com_arm_nam, "</p><p>Overcrowding rate: ", round(Overcrowding_rate, 2), "%</p>")) %>%
  ungroup()

leaflet() %>%
  addTiles() %>%
  addPolygons(data = plot_LOG_epci,
              color = ~hex,
              weight = 1,
              opacity = 0.4,
              fillOpacity = 0.5,
              stroke = T,
              highlight = highlightOptions(opacity = 0.8,
                                           fillOpacity = 0.9,
                                           bringToFront = T),
              # label = lapply(plot_LOG_epci$lab, HTML)
              label = ~paste0("Overcrowding rate: ", round(Overcrowding_rate, 2), "%")
              ) %>%
  addPolygons(data = plot_LOG_com,
              color = ~hex,
              weight = 1,
              opacity = 0.4,
              fillOpacity = 0.5,
              stroke = T,
              highlight = highlightOptions(opacity = 0.8,
                                           fillOpacity = 0.9,
                                           bringToFront = T),
              # label = lapply(plot_LOG_com$lab, HTML)
              label = ~paste0("Overcrowding rate: ", round(Overcrowding_rate, 2), "%")
              ) %>%
  addProviderTiles("Stamen.TonerLite")
```

## Vaccination rate

```{r}
plot52 = plot_vacc %>%
  filter(!is.na(taux_cumu_1_inj) & week == 52)

pal = scales::gradient_n_pal(colours = c("purple", "black", "yellow"),
                             values = c(min(plot52$taux_cumu_1_inj),
                                        median(plot52$taux_cumu_1_inj, na.rm = T),
                                        max(plot52$taux_cumu_1_inj)))

plot_vacc_epci = poly %>%
  inner_join(vacct %>% filter(week == 52), by = c("epci_code" = "codgeo")) %>%
  rename(codgeo = epci_code)
plot_vacc_com = poly_com %>%
  inner_join(vacct %>% filter(week == 52), by = c("com_arm_cur" = "codgeo")) %>%
  rename(codgeo = com_arm_cur)

plot_vacc_epci$hex = pal(plot_vacc_epci$taux_cumu_1_inj)
plot_vacc_com$hex = pal(plot_vacc_com$taux_cumu_1_inj)

plot_vacc_epci = plot_vacc_epci %>%
  group_by(codgeo) %>%
  mutate(lab = paste0("<p>", epci_name, "</p><p>Vaccination rate week 52: ", round(taux_cumu_1_inj*100, 2), "%</p>")) %>%
  ungroup()
plot_vacc_com = plot_vacc_com %>%
  group_by(codgeo) %>%
  mutate(lab = paste0("<p>", com_arm_nam, "</p><p>Vaccination rate week 52: ", round(taux_cumu_1_inj*100, 2), "%</p>")) %>%
  ungroup()

leaflet() %>%
  addTiles() %>%
  addPolygons(data = plot_vacc_epci,
              color = ~hex,
              weight = 1,
              opacity = 0.4,
              fillOpacity = 0.5,
              stroke = T,
              highlight = highlightOptions(opacity = 0.8,
                                           fillOpacity = 0.9,
                                           bringToFront = T),
              # label = lapply(plot_vacc_epci$lab, HTML)
              label = ~paste0("Vaccination rate week 52: ", round(taux_cumu_1_inj*100, 2), "%")
              ) %>%
  addPolygons(data = plot_vacc_com,
              color = ~hex,
              weight = 1,
              opacity = 0.4,
              fillOpacity = 0.5,
              stroke = T,
              highlight = highlightOptions(opacity = 0.8,
                                           fillOpacity = 0.9,
                                           bringToFront = T),
              # label = lapply(plot_vacc_com$lab, HTML)
              label = ~paste0("Vaccination rate week 52: ", round(taux_cumu_1_inj*100, 2), "%")
              ) %>%
  addProviderTiles("Stamen.TonerLite")
```

### 2022-02-22 code/florence.Rmd
first commit

---
title: "VaccinationIndicators"
author: "FD"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Initializations

```{r}
rm(list = ls())

# Package for odds ratios
library("epitools")
# Package for colors
library("RColorBrewer")
# Package for dynamical plots
library("plotly")

#library("igraph")
```

# Load data

## Indicators

```{r}
# The data have been dealt with in "0_INSEE_predictors.R" and saved as RData
load("../data/predictors.RData")

# Load region information for the different EPCI
regions <- read.csv("../data/geographic/EPCI_composition-communale.csv")
head(regions)
# Create dictionary 
dic.reg <- regions$REG
names(dic.reg) <- regions$EPCI
```

```{r}

```

## Vaccination data

Note: The files can be downloaded again (for updates) by running "0_loadAmeliData.R"

### EPCI

```{r}
vaccEPCI <- read.csv("../data/ameli_vaccination/vaccEPCI.csv", sep = ";")
head(vaccEPCI)

# Add region information
vaccEPCI$region <- dic.reg[as.character(vaccEPCI$epci)]
table(vaccEPCI$region, useNA = "ifany")

# Note: NAs correspond to unattributed locations
unique(vaccEPCI[is.na(vaccEPCI$region), "epci"])

# Exclude DROM using regional code
vaccEPCI <- vaccEPCI[vaccEPCI$region > 9, ]

# Exclude Metropoles for which we have Communes detail
epci.PLM <- c(200054781, # Paris
              200046977, # Lyon
              200054807  # Marseille
              )
vaccEPCI <- vaccEPCI[which(!is.element(vaccEPCI$epci, epci.PLM)), ]

# Rename some fields for future merging
names(vaccEPCI)[c(3, 4)] <- c("codgeo", "libelle_geo")
```

### Communes

```{r}
vaccCom <- read.csv("../data/ameli_vaccination/vaccCom.csv", sep = ";")
head(vaccCom)
# Rename some fields for future merging
names(vaccCom)[c(3, 4)] <- c("codgeo", "libelle_geo")

# Merge vaccination data into a single dataset
vacc <- rbind(vaccEPCI[, 1:16], vaccCom)

# Clean memory
rm(vaccCom, vaccEPCI)

# Make sure that population sizes are numeric
vacc$population_carto <- as.numeric(vacc$population_carto)

```

## Dates

```{r}
# Get all dates in the vaccination dataset
vaccDates <- sort(unique(vacc$date))

# Define specific dates
date1 <- "2021-07-11" # Just before pass sanitaire announcement
date2 <- "2021-08-08" # Just before pass sanitaire comes into force
date3 <- "2021-08-29" # Before back to school
date4 <- "2022-01-02" # Last date of the year
```

# Analysis

## Some definitions of common functions

### Quantiles

Conversion to binary values depending on a quantile

```{r}
# Convert to binary values depending on a chosen threshold
quantileConvert <- function(v, q){
  # v vector to be converted
  # q chosen quantile (between 0 and 1)

  # Compute the threshold value
  # Rem: need to remove NAs
  qval <- quantile(x = v, probs = q, na.rm = TRUE)

  # Return TRUE/FALSE depending on the position wrt the value, and change into 1/0
  out <- ifelse(v < qval, 0, 1)

  out
}

# Convert to binary values, with respect to 2 threshold values
quantilesConvert <- function(v, qmin = 0.1, qmax = 0.9){
  # v vector to be converted
  # qmin lower threshold value, data below it are coded 0
  # qmax higher threshold value, data above it are coded 1
  # and data between qmin and qmax are coded NA

  # Compute the threshold value
  # Rem: need to remove NAs
  qval <- quantile(x = v, probs = c(qmin, qmax), na.rm = TRUE)

  out <- rep(NA, length(v)) # Initialize output vector
  out[v < qval[1]] <- 0 
  out[v > qval[2]] <- 1

  out
}
```

### Treatment of the indicators

-  Discretization of the data with respect to quantiles

```{r}
# Function to discretize wrt to quantiles
discretizeQ <- function(v, prbs = seq(0, 1, by = 0.05)){
  # v     vector to discretize
  # prbs  positions of the boundaries

  # Define quantiles
  qq <- c(quantile(v, probs = prbs, na.rm = TRUE))

  # Extend the extreme values to make sure that they are included later
  qq[1] <- 0.5 * qq[1] # 0%
  qq[length(qq)] <- 1.5 * qq[length(qq)] # 100%

  # Add noise to avoid issues when data are too close
  noise <- c(0, runif(length(prbs)-2, max = 10^(-6)), 0)
  qq <- sort(qq + noise)

  # Put the values of v in the different classes
  out <- cut(v, breaks = qq, right = FALSE, labels = FALSE)
# table(out, useNA = "ifany")
  out
}
```

```{r, eval = FALSE}
# Test
for(pred in unique(names(dat.all)[-1])){
  vv <- dat.all[, pred]
  plot(discretizeQ(vv, prbs = seq(0, 1, by = 0.1)), vv, main = pred)
}
```

### Treatment of the vaccination data

-  Adjust the data

```{r}
adjustVacc <- function(r1, varVacc){
  # r1  vaccination dataset for a given date, with all ages, but not "TOUT_AGE"
  # varVacc  the vaccination variable that we want to investigate ("1_inj" or "termine")

  # Compute distribution of the population by age class
  #   Population size of each age classs
  distPop <- aggregate(r1$population_carto, by = list(classe_age = r1$classe_age), FUN = sum, na.rm = TRUE)
  #   Proportions
  distPop$propAgeClass <- distPop$x / sum(distPop$x)

  # Merge with vaccination data
  rr1 <- merge(r1, distPop, by = "classe_age")

  # Compute adjusted rates, by weighting each by each by the proportion in the overall population
  s1 <- aggregate(data.frame(taux_cumu = rr1[, paste0("taux_cumu_", varVacc)] * rr1$propAgeClass, population_carto = rr1$population_carto), by = list(codgeo = rr1$codgeo), FUN = sum, na.rm = TRUE)
  # Compute adjusted numbers of vaccinated people
  s1$n_cumu <- round(s1$taux_cumu * s1$population_carto)

  # Return the dataframe
  s1
}
```

-  Remove children

```{r}
adultVacc <- function(r1, varVacc){
  # r1  vaccination dataset for a given date, with all ages, but not "TOUT_AGE"
  # varVacc  the vaccination variable that we want to investigate ("1_inj" or "termine")

  # Remove children age class
  rr1 <- r1[which(r1$classe_age != "00-19"), ]

  # Compute sums of effectifs by codgeo
  s1 <- aggregate(data.frame(n_cumu = rr1[, paste0("effectif_cumu_", varVacc)], population_carto = rr1$population_carto), by = list(codgeo = rr1$codgeo), FUN = sum, na.rm = TRUE)

  # Compute taux
  s1$taux_cumu <- s1$n_cumu / s1$population_carto

  # Return the dataframe
  s1
}
```

## Other functions

```{r}
invlogit <- function(x) exp(x)/(1 + exp(x))

```

## Parameters

```{r}
parms <- expand.grid(clAge = sort(unique(vacc$classe_age)), 
                     varVacc = c("1_inj", "termine"), 
                     varPred = names(dat.all[, -1]), 
                     thedate = c(date1, date2, date3, date4), stringsAsFactors = FALSE)
```

## Odds ratios

### Function definitions

```{r computeOR}
# Function to compute odds ratio and p value
computeOR <- function(pred, result, method = "fisher"){
  # pred   vector of the predictor, dichotomized
  # result vector of the result, dichotomized
  # method one of c("midp", "fisher", "wald", "small"), see ?oddsratio

  # Compute contingency table
  contTable <- table(pred, result)

  # Compute OR and pval
  or <- oddsratio(x = contTable, method = method)
  # Format the output
  out <- c(N = or$data[3, 3], or$measure[2, ], or$p.value[2, ])

  #print(or) # For debugging and double-checking
  out
}
```

```{r}
getOR <- function(clAge, varVacc, varPred, thedate, thrVacc = 0.25, thrPred = 0.5){
  # clAge age class
  # varVacc variable for the vaccination data
  # varPred variable for the predictor
  # thedate date of the vaccination data
  # thrVacc threshold value for dichotomizing vaccination data
  # thrPred threshold value for dichotomizing predictor data

  # Subset vaccination data
  r1 <- vacc[vacc$classe_age == clAge & vacc$date == thedate, ]

  # Merge with predictor data
  m1 <- merge(r1, dat.all[, c("codgeo", varPred)], by = "codgeo")

  # Dichotomize the vectors
  result <- quantileConvert(m1[, paste0("taux_cumu_", varVacc)], thrVacc)
  pred <- quantileConvert(m1[, varPred], thrPred)

  # Compute OR
  computeOR(pred, result)
#  output <- c(date = thedate, varVacc = varVacc, clAge = clAge, varPred = varPred, computeOR(pred, result))
#  output
}
```

```{r computeORCheck}
# For debugging
# clAge <- "TOUT_AGE"
# varVacc <- "taux_cumu_1_inj"
# varPred <- "Overcrowding_rate"
# thedate <- date1
# dataTransform <- "discretize"
```

### Computation

```{r}
# Compute for all combinations that we want
# (Takes a few minutes)
nrow(parms)
output <- matrix(0, ncol = 7, nrow = nrow(parms))
for(i in 1:nrow(parms)){
  cat(i, "")
  output[i, ] <- do.call(getOR, parms[i, ])
}

# For debugging
getOR("TOUT_AGE", "1_inj", "Overcrowding_rate", date1, thrVacc = 0.25, thrPred = 0.5)

# Add the parameter information
mm <- cbind(parms, output)

names(mm) <- c("clAge", "varVacc", "varPred", "thedate", "N", "estimate", "lower", "upper", "midp.exact", "fisher.exact", "chi.square")

# Save the output
save(mm, file = "output_OR.RData")
```

## Anova

### Function definitions

```{r}
anovaVacc <- function(clAge, varVacc, varPred, thedate, thrPred = c(0.1, 0.9)){
  # clAge age class
  # varVacc variable for the vaccination data
  # varPred variable for the predictor
  # thedate date of the vaccination data
  # thrPred threshold value(s) for dichotomizing predictor data
  #         if one value, all data are binarized as 0: v<q, 1: v>=q
  #         if two values, 0: v<q1, NA: q1<= v <=q2, 1: v>q2

  # Subset vaccination data
  r1 <- vacc[vacc$classe_age == clAge & vacc$date == thedate, ]

  # Merge with predictor data
  m1 <- merge(r1, dat.all[, c("codgeo", varPred)], by = "codgeo")

  # Dichotomize the vector
  if(length(thrPred) == 1){
    m1$pred <- quantileConvert(m1[, varPred], thrPred)
  }else{
    m1$pred <- quantilesConvert(m1[, varPred], thrPred[1], thrPred[2])
  }
  m1$res <- m1[, paste0("taux_cumu_", varVacc)]

  aov(res ~ pred, data = m1)
}
```

### Computation

```{r}
mdl <- anovaVacc("TOUT_AGE", "1_inj", "Overcrowding_rate", date3)
(mdl$coefficients)[["pred"]]
summary(mdl)

effect3 <- rep(0, ncol(dat.all)-1)
for(i in 2:ncol(dat.all)){
  mdl <- anovaVacc("TOUT_AGE", "1_inj", names(dat.all)[i], date3)
  effect3[i-1] <- (mdl$coefficients)[["pred"]]
}

summary(mdl)
```

## Logistic regression

### Function definitions
```{r}
# Function to do a logistic regression on one of the variables
getLogReg <- function(varVacc, varPred, thedate, predTransform, vaccAge, by.prbs = 0.1, permutation = FALSE){
  # 
  # varVacc  takes values "1_inj" or "termine"
  # varPred  is the predictor value to be used
  # thedate  date at which the calculations are done
  # predTransform: how to deal with the predictor values 
  #                "standardize_msd", "standardize_max" or "discretize"
  # vaccAge: "raw_rates" if raw vaccination rates, without taking age into account
  #          "by_age" if model takes age into account
  #          "adjusted_rates" if adjusted vaccination rates
  #          "adults" all ages except 00-19
  # by.prbs  if "discretize", distance between breaks of the discretization

  # Check data entry
  stopifnot(is.element(predTransform, c("standardize_msd", "standardize_max", "discretize")))
  stopifnot(is.element(varVacc, c("1_inj", "termine")))
  stopifnot(is.element(vaccAge, c("raw_rates", "by_age", "adjusted_rates", "adults")))

  if(vaccAge == "raw_rates"){
    # Subset vaccination data; keep only ALL_AGE
    r1 <- vacc[vacc$classe_age == "TOUT_AGE" & vacc$date == thedate, ]
    # Rename columns
    r1$taux_cumu <- r1[, paste0("taux_cumu_", varVacc)]
    r1$n_cumu <- r1[, paste0("effectif_cumu_", varVacc)]
  }
  if(vaccAge == "by_age"){
    # Subset vaccination data; keep all age classes except ALL_AGE
    r1 <- vacc[vacc$classe_age != "TOUT_AGE" & vacc$date == thedate, ]
    # Rename columns
    r1$taux_cumu <- r1[, paste0("taux_cumu_", varVacc)]
    r1$n_cumu <- r1[, paste0("effectif_cumu_", varVacc)]
  }
  if(vaccAge == "adjusted_rates"){
    # Subset vaccination data; keep all age classes except ALL_AGE
    tmp <- vacc[vacc$classe_age != "TOUT_AGE" & vacc$date == thedate, ]
    r1 <- adjustVacc(tmp, varVacc)
  }
  if(vaccAge == "adults"){
    # Subset vaccination data; keep all age classes except ALL_AGE
    tmp <- vacc[vacc$classe_age != "TOUT_AGE" & vacc$date == thedate, ]
    r1 <- adultVacc(tmp, varVacc)
  }

  # Merge with predictor data
  m1 <- merge(r1, dat.all[, c("codgeo", varPred)], by = "codgeo")

  # Treat the predictor
  pp <- m1[, varPred]
  if(predTransform == "standardize_msd"){
    m1$pred.std <- (pp - mean(pp, na.rm = TRUE)) / sd(pp, na.rm = TRUE)
  }
  if(predTransform == "standardize_max"){
    pMax <- max(pp, na.rm = TRUE)
    pMin <- min(pp, na.rm = TRUE)
    m1$pred.std <- (pp - pMin) / (pMax - pMin)
  }
  if(predTransform == "discretize"){
    m1$pred.std <- discretizeQ(v = pp, prbs = seq(0, 1, by = by.prbs))
  }

  # Permutation if we want to (to test signif)
  if(permutation){
    permi <- sample(seq_len(nrow(m1)))
    m1$pred.std <- m1[permi, "pred.std"]
  }

  # Logistic model
  if(vaccAge == "by_age"){
    # Logistic model, with age effect
    mdl <- glm(cbind(n_cumu, population_carto - n_cumu) ~ pred.std + as.factor(classe_age) + pred.std * as.factor(classe_age), family = binomial(link = "logit"), data = m1)
  }
  if(is.element(vaccAge, c("raw_rates", "adjusted_rates", "adults"))){
    # Logistic model, no age effect (but potentially adjusted)
    mdl <- glm(cbind(n_cumu, population_carto - n_cumu) ~ pred.std, family = binomial(link = "logit"), data = m1)
  }

  # Extract values for pred.std
#  out <- summary(mdl)$coefficients["pred.std", ]
  # Return model
  mdl
}
```

### Computation, brouillon

```{r, eval = FALSE}
tmp <- getLogReg("1_inj", "Overcrowding_rate", thedate = date1, predTransform = "discretize", vaccAge = "raw_rates")
summary(tmp)
summary(getLogReg("1_inj", "Overcrowding_rate", thedate = date1, predTransform = "discretize", vaccAge = "raw_rates", permutation = TRUE))

tmp <- getLogReg("1_inj", "Overcrowding_rate", thedate = date1, predTransform = "standardize_msd", vaccAge = "raw_rates")
summary(tmp)

parmsLR <- expand.grid(varVacc = c("1_inj"), 
                     varPred = names(dat.nocorr[, -1]), 
                     thedate = c(date1, date2, date3, date4), 
#                     predTransform = c("standardize_msd", "standardize_max", "discretize"),
                     predTransform = c("discretize"),
                     vaccAge = c("raw_rates", "adjusted_rates", "adults"), 
                     permutation = c(FALSE, TRUE), 
                     stringsAsFactors = FALSE)
sort(names(dat.nocorr[, -1]))
nrow(parmsLR)
library("parallel")

outLR <- mclapply(seq_len(nrow(parmsLR)), function(i) do.call(getLogReg, parmsLR[i, ]))#,  mc.cores = 3)

# It takes a while with a list, but then we can check how fast it goes
outLR <- list()
for (i in seq_len(nrow(parmsLR))){
    cat(i, " ")
  outLR[[i]] <- do.call(getLogReg, parmsLR[i, ])
}

# Add line number in parms dataframe
parmsLR$i <- seq_len(nrow(parmsLR))

# Extract slope values
slopes <- unlist(lapply(seq_len(nrow(parmsLR)), function(i) summary(outLR[[i]])$coefficients["pred.std", "Estimate"]))

# Extract p values associated to the slopes
pvals <- unlist(lapply(seq_len(nrow(parmsLR)), function(i) summary(outLR[[i]])$coefficients["pred.std", "Pr(>|z|)"]))

# Compute decile values
tx01 <- unlist(lapply(seq_len(nrow(parmsLR)), function(i){cf <- outLR[[i]]$coefficients
invlogit(cf[1] + 1 * cf[2])}))

tx10 <- unlist(lapply(seq_len(nrow(parmsLR)), function(i){cf <- outLR[[i]]$coefficients
invlogit(cf[1] + 10 * cf[2])}))

# Put these values in a data frame
outputLR <- parmsLR
outputLR$slopes <- slopes
outputLR$pvals <- pvals
outputLR$tx01 <- tx01
outputLR$tx10 <- tx10

head(outputLR)

hist(-log(outputLR$pvals))

hist(outputLR$slopes)

hist(abs(outputLR$slopes))

head(outputLR[order(abs(outputLR$slopes), decreasing = TRUE), ])

for(predTransform in unique(outputLR$predTransform)){
  print("-----------------------------------------------------------------------------------")
  for(varVacc in unique(outputLR$varVacc)){
    for(thedate in unique(outputLR$thedate)){
      for(vaccAge in unique(outputLR$vaccAge)){
        for(permutation in c(TRUE, FALSE)){
          sub <- outputLR[outputLR$vaccAge == vaccAge & outputLR$thedate == thedate & outputLR$predTransform == predTransform & outputLR$varVacc == varVacc & outputLR$permutation == permutation, ]
          print(head(sub[order(abs(sub$slopes), decreasing = TRUE), ], n = 10))
          cat("\n")
          #        print(head(sub[order(abs(sub$tx10 - sub$tx01), decreasing = TRUE), ], n = 10))
          #        cat("\n")
          plot(abs(sub$slopes), ylim = c(0, max(c(0.07, max(abs(sub$slopes))))), 
               main = paste(predTransform, thedate, vaccAge, permutation))
        }
      }
    }
  }
}

vv <- dat.all$Unemployment_Benef
plot(discretizeQ(vv, seq(0, 1, by = 0.1)), vv)

invlogit <- function(x) exp(x)/(1 + exp(x))

outputLRD <- outputLR[which(outputLR$predTransform == "discretize"), ]

max(outputLRD$slopes)

save(outputLR, file = "outputLR_2022-02-19.RData")

```

Rationale for choosing how to treat the predictors:   
-  `standardize_msd` keeps extreme values, so still hard to compare distributions,
-  `standardize_max` also keeps extreme values, and if there are outliers, the rest of the distribution is completely condensed,  
so we will keep `discretize`.

```{r}
extractValuesOut <- function(outList, parmsMat){
  # Check dimensions
  stopifnot(length(outList) == nrow(parmsMat))

  # Initialize output
  m <- parmsMat

  # Add line number in parms dataframe
  m$i <- seq_len(nrow(parmsMat))

  # Extract slope values
  slopes <- unlist(lapply(seq_len(nrow(parmsMat)), function(i) summary(outList[[i]])$coefficients["pred.std", "Estimate"]))

# Extract p values associated to the slopes
  pvals <- unlist(lapply(seq_len(nrow(parmsMat)), function(i) summary(outList[[i]])$coefficients["pred.std", "Pr(>|z|)"]))

# Compute decile values
  tx01 <- unlist(lapply(seq_len(nrow(parmsMat)), function(i){cf <- outList[[i]]$coefficients
invlogit(cf[1] + 1 * cf[2])}))

  tx10 <- unlist(lapply(seq_len(nrow(parmsMat)), function(i){cf <- outList[[i]]$coefficients
invlogit(cf[1] + 10 * cf[2])}))

  # Compute SE
  preds <- predict(outList[[i]], newdata = data.frame(pred.std = 1:10), type = "response", se.fit = TRUE)
  se01 <- preds$se.fit[1]
  se10 <- preds$se.fit[10]

  # Put these values in a data frame
  m$slopes <- slopes
  m$pvals <- pvals
  m$tx01 <- tx01
  m$tx10 <- tx10
  m$se01 <- se01
  m$se10 <- se10
  m$difftx101 <- tx10 - tx01
  m
}
```

### Permutations

```{r permutationsSlopes, eval = FALSE}
# Combinations of parameters to test
parmsPerm <- expand.grid(varVacc = c("1_inj"), 
                     varPred = "French_nlty", 
                     thedate = c(date1, date2, date3, date4), 
                     predTransform = c("discretize"),
                     vaccAge = c("raw_rates", "adults"), 
                     permutation = c(TRUE), 
                     stringsAsFactors = FALSE)

# Number of replicates of each combination
nrep <- 1000

# Rewrite as table with replicates
#   List of the parameters, one element for one replicate
listParmsPerm <- list()
for(rep in 1:nrep) listParmsPerm[[rep]] <- parmsPerm
#   rbind them
parmsPermRep <- do.call(rbind, listParmsPerm)
#   clean memory
rm(listParmsPerm)
#   Check dimension
dim(parmsPermRep)

nperm <- nrow(parmsPerm) * nrep

# Compute model for all combinations and replicates
# It takes a while with a list, but then we can check how fast it goes
outPerm <- list()
for(rep in seq_len(nrep)){ # Replicates
  for (i in seq_len(nrow(parmsPerm))){ # Parameter values
    j <- (rep - 1) * nrow(parmsPerm) + i
    cat(j, " ")
    outPerm[[j]] <- do.call(getLogReg, parmsPerm[i, ])
  }
}

# Extract the key values
pPerm <- extractValuesOut(outList = outPerm, parmsMat = parmsPermRep)

save(pPerm, file = "randomPermutations_2022-02-21.RData")

# Clean memory 
rm(outPerm)
```

```{r}
length(outPerm)
dim(pPerm)  
head(pPerm)

hist(pPerm$slopes)
hist(abs(pPerm$slopes))

# Key values
quantile(abs(pPerm$slopes), 0.95)
quantile(abs(pPerm$slopes), 0.99)
quantile(abs(pPerm$slopes), 0.999)
max(abs(pPerm$slopes))

```

### Computation

```{r}
# Values to be tested
parmsLR <- expand.grid(varVacc = c("1_inj"), 
                     varPred = names(dat.nocorr[, -1]), 
                     thedate = c(date1, date2, date3, date4), 
                     predTransform = c("discretize"),
                     vaccAge = c("raw_rates", "adults"), 
                     permutation = c(FALSE), 
                     stringsAsFactors = FALSE)
```

```{r, eval = FALSE}
#outLR <- mclapply(seq_len(nrow(parmsLR)), function(i) do.call(getLogReg, parmsLR[i, ]))#,  mc.cores = 3)

nrow(parmsLR)

# It takes a while with a list, but then we can check how fast it goes
outLR <- list()
for (i in seq_len(nrow(parmsLR))){
    cat(i, " ")
  outLR[[i]] <- do.call(getLogReg, parmsLR[i, ])
}

# Extract the key values
pLR <- extractValuesOut(outList = outLR, parmsMat = parmsLR)

save(pLR, file = "LR_2022-02-21.RData")
```

```{r}
brks <- seq(0, 0.1, by = 0.0025)
h1 <- hist(abs(pLR$slopes), breaks = brks, freq = FALSE)
h0 <- hist(abs(pPerm$slopes), breaks = brks, freq = FALSE)
par(las = 1)
col1 <- rgb(0.8, 0, 0.8, 0.5)
col0 <- gray(0, 0.5)
plot(h1, col = col1, ylim = c(0, max(c(h0$density, h1$density))), freq = FALSE, main = "Slope values", xlab = "abs(slopes)")
plot(h0, add = TRUE, col = col0, freq = FALSE)
legend(horiz = FALSE, x ="right", pch = 15, pt.cex = 2, col = c(col0, col1), legend = c("Permutation", "Data"), box.lwd = 0)
```

```{r}
# Distribution of p values

-log(0.05/300)

cts <- c(-0.1, 0.0001, 0.001, 0.01, 0.05, 1)
hist(cut(pLR$pvals, cts, labels = FALSE), breaks = seq_along(cts) - 0.5, col = col1, ylim = c(0, 1), freq = FALSE)
hist(cut(pPerm$pvals, cts, labels = FALSE), breaks = seq_along(cts) - 0.5, add = TRUE, col = col0, freq = FALSE)

```

```{r}
# Distribution of interdecile differences
brks <- seq(0, 0.15, by = 0.005)
brks[1] <- brks[1] - 0.0001
par(las = 1)
hist(abs(pLR$tx10 - pLR$tx01), col = col1, breaks = brks, freq = FALSE, ylim = c(0, 100), main = "Interdecile difference")
hist(abs(pPerm$tx10 - pPerm$tx01), add = TRUE, col = col0, breaks = brks, freq = FALSE)
```

```{r, eval = FALSE}
for(predTransform in unique(pLR$predTransform)){
  print("-----------------------------------------------------------------------------------")
  for(varVacc in unique(pLR$varVacc)){
    for(thedate in unique(pLR$thedate)){
      for(vaccAge in unique(pLR$vaccAge)){
        for(permutation in unique(pLR$permutation)){
          sub <- pLR[pLR$vaccAge == vaccAge & pLR$thedate == thedate & pLR$predTransform == predTransform & pLR$varVacc == varVacc & pLR$permutation == permutation, ]
          print(head(sub[order(abs(sub$slopes), decreasing = TRUE), ], n = 10))
          cat("\n")
          #        print(head(sub[order(abs(sub$tx10 - sub$tx01), decreasing = TRUE), ], n = 10))
          #        cat("\n")
          plot(abs(sub$slopes), ylim = c(0, max(c(0.075, max(abs(sub$slopes))))), 
               main = paste(predTransform, thedate, vaccAge, permutation))
        }
      }
    }
  }
}

pLR$diff10.1 <- pLR$tx10 - pLR$tx01
pLR$diff10.1.se <- pLR$se10 - pLR$se01

for(predTransform in unique(pLR$predTransform)){
  print("-----------------------------------------------------------------------------------")
  for(varVacc in unique(pLR$varVacc)){
    for(thedate in unique(pLR$thedate)){
      for(vaccAge in unique(pLR$vaccAge)){
        for(permutation in unique(pLR$permutation)){
          sub <- pLR[pLR$vaccAge == vaccAge & pLR$thedate == thedate & pLR$predTransform == predTransform & pLR$varVacc == varVacc & pLR$permutation == permutation, ]
          print(head(sub[order(abs(sub$diff10.1), decreasing = TRUE), ], n = 10))
          cat("\n")
          #        print(head(sub[order(abs(sub$tx10 - sub$tx01), decreasing = TRUE), ], n = 10))
          #        cat("\n")
          yy <- abs(sub$diff10.1)
          plot(yy, ylim = c(0, 0.2), 
               main = paste(predTransform, thedate, vaccAge, permutation))
        }
      }
    }
  }
}

```

Decisions:  
-  Work with 20+ only to avoid issues with proportions of children

### Figures

```{r}
pPerm.adults <- pPerm[pPerm$vaccAge == "adults", ]
dim(pPerm.adults)

hP <- list()
brks <- seq(0, 0.2, by = 0.001)
column <- "difftx101"
for(i in 1:4){
  dt <- get(paste0("date", i))
  subP <- pPerm[pPerm$vaccAge == "adults" & pPerm$thedate == dt, ]
  hP[[i]] <- hist(abs(subP[, column]), breaks = brks)
  hP[[i]]$props <- hP[[i]]$counts / sum(hP[[i]]$counts)
  hP[[i]]$scaledcounts <- hP[[i]]$counts / max(hP[[i]]$counts)
}

i <- 1
subLR <- pLR[pLR$vaccAge == "adults" & pLR$thedate == get(paste0("date", i)), ]
plot(0, xlim = c(1, nrow(subLR)), ylim = c(0, 0.2), xaxs = "i", yaxs = "i", 
     frame.plot = FALSE, type = "n")
j <- 1:(length(brks)-1)
cols <- gray(1 - hP[[i]]$scaledcounts)
rect(xleft = rep(1, length(j)), xright = rep(nrow(subLR), length(j)), 
     ybottom = brks[j], ytop = brks[j+1], 
     border = cols, lwd = 0, col = cols)
par(xpd = TRUE)
points(abs(subLR[, column]), col = colClass[dicPred[subLR$varPred]], pch = 16)

classes <- dicPred[subLR$varPred]
aggregate(classes, FUN = length, by = list(classes))

unique(classes)

plot(0)
hP[[1]]
hP[[1]]
hist(pPerm.adults$tx10 - pPerm.adults$tx01)

```

### 2022-02-24 code/recomputeGeographic.R
add script to correct geographic data

@@ -1,0 +1,27 @@
+dat.GEO <- read.csv("../data/GEO_brut_OLD.csv")
+
+# Some values were erroneously entered, this script corrects them
+ierrors <- which(as.numeric(substr(dat.GEO$latitude, 1, 2)) < 35)
+
+# Correct the errors for Marseille
+dat.GEO[ierrors, "latitude"] <- dat.GEO[ierrors, "latitude"] + 30
+
+dat.GEO$lat01 <- (dat.GEO$latitude - min(dat.GEO$latitude)) / (max(dat.GEO$latitude) - min(dat.GEO$latitude))
+hist(dat.GEO$lat01)
+hist(dat.GEO$lon01)
+
+# Recompute distance to Paris
+# Paris = Paris 04
+iParis <- which(dat.GEO$codgeo == "75104")
+lat.Paris <- dat.GEO[iParis, "latitude"]
+lon.Paris <- dat.GEO[iParis, "longitude"]
+
+dat.GEO$distanceParis <- sqrt((dat.GEO$latitude - lat.Paris)^2 + (dat.GEO$longitude - lon.Paris)^2)
+hist(dat.GEO$distanceParis)
+
+# Remove the erroneous verions
+dat.GEO <- dat.GEO[, which(names(dat.GEO) != "distParis")]
+
+# Export the corrected dataset
+write.csv(x = dat.GEO, file = "../data/GEO_brut.csv", row.names = FALSE)
+

### 2022-02-24 code/geographic.R
script for geographic dataset

@@ -1,0 +1,94 @@
+#### INITIALIZATIONS ####
+# Global data: vacc
+stopifnot(exists("vacc"))
+stopifnot(exists("vaccCom"))
+stopifnot(exists("vaccEPCI"))
+# They are loaded in florence.Rmd
+
+#### LOAD AND CLEAN GEOGRAPHIC DATA ####
+# Source of the two datasets: https://datavaccin-covid.ameli.fr/explore/?sort=modified
+geoCom <- read.csv("../data/geographic/fromAmeli/georef-france-commune-arrondissement-municipal.csv",row.names = NULL, sep = ";")
+geoCom <- geoCom[, -which(colnames(geoCom) == "Geo.Shape")]
+
+geoEPCI <- read.csv("../data/geographic/fromAmeli/georef-france-epci.csv",row.names = NULL, sep = ";")
+geoEPCI <- geoEPCI[, -which(colnames(geoEPCI) == "Geo.Shape")]
+geoEPCI <- geoEPCI[, -which(colnames(geoEPCI) == "viewport")]
+
+# Extract latitude and longitude from the Geo.Point column
+tmpCom <- matrix(unlist(strsplit(geoCom$Geo.Point, ",")), byrow = TRUE, ncol = 2)
+geoCom$latitude <- as.numeric(tmpCom[, 1])
+geoCom$longitude <- as.numeric(tmpCom[, 2])
+
+tmpEPCI <- matrix(unlist(strsplit(geoEPCI$Geo.Point, ",")), byrow = TRUE, ncol = 2)
+geoEPCI$latitude <- as.numeric(tmpEPCI[, 1])
+geoEPCI$longitude <- as.numeric(tmpEPCI[, 2])
+
+#### MERGE WITH CODGEO ####
+
+# Check whether codgeo is found in the data
+
+## Communes
+mean(is.element(unique(vaccCom$codgeo), as.numeric(geoCom$Code.Officiel.Commune...Arrondissement.Municipal)))
+mean(is.element(unique(vaccCom$codgeo), as.numeric(geoCom$Code.Officiel.Commune)))
+mean(is.element(unique(vaccCom$codgeo), as.numeric(geoCom$Code.Officiel.Courant.Commune...Arrondissement.Municipal)))
+
+iii <- which(!is.element(unique(vaccCom$codgeo), as.numeric(geoCom$Code.Officiel.Courant.Commune...Arrondissement.Municipal)))
[…]

### 2022-02-24 code/geographic.R
add file sources URL

@@ -7,9 +7,12 @@ stopifnot(exists("vaccEPCI"))
 
 #### LOAD AND CLEAN GEOGRAPHIC DATA ####
 # Source of the two datasets: https://datavaccin-covid.ameli.fr/explore/?sort=modified
+
+#   Source: https://datavaccin-covid.ameli.fr/explore/dataset/georef-france-commune-arrondissement-municipal/download/?format=csv&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B
 geoCom <- read.csv("../data/geographic/fromAmeli/georef-france-commune-arrondissement-municipal.csv",row.names = NULL, sep = ";")
 geoCom <- geoCom[, -which(colnames(geoCom) == "Geo.Shape")]
 
+#  Source: https://datavaccin-covid.ameli.fr/explore/dataset/georef-france-epci/download/?format=csv&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B
 geoEPCI <- read.csv("../data/geographic/fromAmeli/georef-france-epci.csv",row.names = NULL, sep = ";")
 geoEPCI <- geoEPCI[, -which(colnames(geoEPCI) == "Geo.Shape")]
 geoEPCI <- geoEPCI[, -which(colnames(geoEPCI) == "viewport")]

### 2022-02-25 code/geographic.R
add density information

@@ -91,6 +91,12 @@ dat.GEO$NO.SE <- dat.GEO$lon01 - dat.GEO$lat01
 plot(dat.GEO$SO.NE, dat.GEO$lat01)
 plot(dat.GEO$NO.SE, dat.GEO$lat01)
 
+##### Densites #####
+# Load the old file
+tmp <- read.csv("../data/GEO_brut_OLD.csv")
+# Merge density information with what we have
+dat.GEO <- merge(dat.GEO, tmp[, c("codgeo", "densite")], by = "codgeo")
+
 #### EXPORT OUTPUT ####
 write.csv(dat.GEO, "../data/GEO_brut.csv", row.names = FALSE)
 system("git add ../data/GEO_brut.csv")

### 2022-03-07 code/vaccination-indicators.Rmd
first commit

---
title: "Vaccination"
author: "FD"
output: 
  html_document:
      self_contained: no

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Initializations

```{r, eval = FALSE, include = FALSE}
rm(list = ls())

for(i in dev.list()) dev.off()
```

```{r}
runComputations <- FALSE
```

# Load and clean data

-  Indicators

```{r loadPredictors}
# The data have been dealt with in "0_INSEE_predictors.R" and saved as RData
load("../data/predictors.RData")
```

-  Vaccination

```{r loadVaccinationData}
# Source vaccination data
source("load-clean_vaccination.R")
```

-  Dates

```{r}
# Get all dates in the vaccination dataset
vaccDates <- sort(unique(vacc$date))
range(vaccDates)

# Define specific dates
date1 <- "2021-07-11" # Just before pass sanitaire announcement
date2 <- "2021-08-08" # Just before pass sanitaire comes into force
date3 <- "2021-08-29" # Before back to school
date4 <- "2022-01-02" # Last date of the year
```

# Define analysis functions

```{r results = 'hide'}
# Functions to discretize the data
source("1_functions-quantiles.R")
# `discretizeQ`

# Functions to recompute vaccination rates
source("1_functions-adjustAges.R")

# Other
invlogit <- function(x){exp(x)/(1 + exp(x))}

uniqueNoNA <- function(x){
  out <- unique(x)
  out <- out[!is.na(out)]
  out
}

# Logistic model
source("1_functions-logisticRegression.R")

# Odds ratios
source("1_functions-oddsRatios.R")

# Functions for plotting
source("2_plot-manhattan.R")
source("2_plot-overTime.R")
```

# Computation

## Across median comparison

```{r}
if(runComputations){
  # Define the combinations of parameters to be tested
  parmsLR <- expand.grid(varPred = names(dat.nocorr)[-1], 
                         thedate = c(date1, date2, date3, date4), 
                         predTransform = "discretize_factor", 
                         vaccAge = "adults", 
                         by.prbs = 0.5, 
                         permutation = FALSE,
                         stringsAsFactors = FALSE)
  # Permutation 
  # Number of repetitions
  nrep <- 1000
  # Base combination of parameters
  tmpparmsPerm <- expand.grid(varPred = "French_nlty", 
                              thedate = c(date1, date2, date3, date4), 
                              predTransform = "discretize_factor", 
                              vaccAge = "adults", 
                              by.prbs = 0.5, 
                              permutation = TRUE,
                              stringsAsFactors = FALSE)
  # Add repeated parameters
  for(i in 1:nrep){
    parmsLR <- rbind(parmsLR, tmpparmsPerm)
  }
  rm(tmpparmsPerm)

  # Initialize output
  out <- as.data.frame(matrix(NA, ncol = 8, nrow = nrow(parmsLR)))
  cat(nrow(parmsLR), " combinations to be tested\n")
  # Compute OR for each combination of parameters
  for(i in 1:nrow(parmsLR)){
    if(i %% 10 == 0) cat(i, "") # Print counter
    # Compute the logistic regression on this combination of parameters
    mdl <- do.call(getLogReg, parmsLR[i, ])
    # Extract the odds ratios
    out[i, ] <- extractOR(mdl)
  }
  names(out) <- names(extractOR(mdl))

  # Add the parameters
  outLR <- cbind(parmsLR, out)

  # Add type of predictor information
  outLR$typePred <- dicPred[outLR$varPred]
  # Full names
  outLR$typePredFull <- dic.fullpred[outLR$typePred]

  save(outLR, file = "outLR.RData")

}
```

```{r manhattan_median}
load("outLR.RData")

# PLOT
plotManhattan(outLR, ntop = 5)
```

## By deciles, quantitatively, adjusting ages

```{r}
if(runComputations){
  # Define the combinations of parameters to be tested
  parmsDec <- expand.grid(varPred = names(dat.nocorr)[-1], 
                          thedate = c(date1, date2, date3, date4), 
                          predTransform = "discretize", 
                          vaccAge = "by_age", 
                          by.prbs = 0.1, 
                          permutation = FALSE,
                          stringsAsFactors = FALSE)

  # Permutation
  # Base combination of parameters
  tmpparmsPerm <- expand.grid(varPred = "French_nlty", 
                              thedate = c(date1, date2, date3, date4), 
                              predTransform = "discretize", 
                              vaccAge = "by_age", 
                              by.prbs = 0.1, 
                              permutation = TRUE,
                              stringsAsFactors = FALSE)
  # Add repeated parameters
  for(i in 1:nrep){
    parmsDec <- rbind(parmsDec, tmpparmsPerm)
  }
  rm(tmpparmsPerm)

  newd <- expand.grid(age.f = as.factor(ages), pred.std = 1:10)

  cat(nrow(parmsDec), " combinations to be tested\n")

  out <- as.data.frame(matrix(NA, ncol = 4, nrow = nrow(parmsDec)))

  # Compute OR for each combination of parameters
  for(i in 1:nrow(parmsDec)){
    if(i %% 10 == 0) cat(i, "") # Print counter
    # Compute the logistic regression on this combination of parameters
    mdl <- do.call(getLogReg, parmsDec[i, ])
    # Predicted values
    predsC <- adjustedPredict(mdl, newd, includeChildren = TRUE)
    predsA <- adjustedPredict(mdl, newd, includeChildren = FALSE)

    # Compute odds ratios
    ORC <- getORfromPredict(c(predsC[predsC$pred.std == 10, "adjustedRate"], predsC[predsC$pred.std == 1, "adjustedRate"]))
    ORA <- getORfromPredict(c(predsA[predsA$pred.std == 10, "adjustedRate"], predsA[predsA$pred.std == 1, "adjustedRate"]))

    out[i, ] <- c(ORC, ORA, max(ORC, 1/ORC), max(ORA, 1/ORA))
  }
  names(out) <- c("OR.withChildren", "OR.adults", "OR.abs.withChildren", "OR.abs.adults")
  dim(out)
  # Add the parameters
  outDec <- cbind(parmsDec, out)
  # Add type of predictor information
  outDec$typePred <- dicPred[outDec$varPred]
  # Full names
  outDec$typePredFull <- dic.fullpred[outDec$typePred]

  save(outDec, file = "outDec.RData")

}
```

```{r manhattan_decilesQ_withChildren}
load("outDec.RData")

suffix <- ".withChildren"

xx <- outDec
xx$OR <- outDec[, paste0("OR", suffix)]
xx$OR.abs <- outDec[, paste0("OR.abs", suffix)]
xx$OR.abs.CI.max <- outDec[, paste0("OR.abs", suffix)]

plotManhattan(xx, ntop = 5)
```

```{r manhattan_decilesQ_adultsOnly}
suffix <- ".adults"

xx <- outDec
xx$OR <- outDec[, paste0("OR", suffix)]
xx$OR.abs <- outDec[, paste0("OR.abs", suffix)]
xx$OR.abs.CI.max <- outDec[, paste0("OR.abs", suffix)]

plotManhattan(xx, ntop = 5)

```

## Over time

```{r}
if(runComputations){
  dates <- sort(unique(vacc$date))
  minDate <- "2021-05-01"
  dates <- dates[dates >= minDate]

  # Define the combinations of parameters to be tested
  parmsTime <- expand.grid(varPred = c("Unemployment_Benef", "French_nlty", "Asselineau"), 
                           thedate = dates, 
                           predTransform = "discretize_factor", 
                           vaccAge = "by_age", 
                           by.prbs = 0.1, 
                           permutation = FALSE,
                           stringsAsFactors = FALSE)

  dim(parmsTime)

  newd <- expand.grid(age.f = as.factor(ages), pred.std = as.factor(1:10))

  # Initialize output
  outC <- outA <- as.data.frame(matrix(NA, ncol = 10, nrow = nrow(parmsTime)))

  # Compute OR for each combination of parameters
  for(i in 1:nrow(parmsTime)){
    if(i %% 10 == 0) cat(i, "") # Print counter
    # Compute the logistic regression on this combination of parameters
    mdl <- do.call(getLogReg, parmsTime[i, ])
    # Predicted values
    predsC <- adjustedPredict(mdl, newd, includeChildren = TRUE)
    predsA <- adjustedPredict(mdl, newd, includeChildren = FALSE)

    # Save
    outC[i, ] <- predsC$adjustedRate
    outA[i, ] <- predsA$adjustedRate

  }

  outC <- cbind(parmsTime, outC)
  outA <- cbind(parmsTime, outA)

  save(outC, outA, dates, file = "outTime.RData")

}
```

```{r overtime_withChildren}
load("outTime.RData")

plotPropTime(outC)

```

```{r overtime_adultsOnly}
plotPropTime(outA)

```

# Geographic

```{r}
library(mapsf)
# Geographic information for maps
load("../data/mapFiles_withDepReg.RData")
load("../data/chefslieux.RData")
```

```{r}
#varPred <- "X1564_OtherInactive_amg_NW"

source("2_plot-map.R")
plotMapVar("Unemployment_Benef", byp = 0.1)

```

```{r}
plotMapVar("Unemployment_Benef", byp = 0.5)
plotMapVar("Unemployment_Benef", byp = 0.1)

vv <- dat.all[, "Unemployment_Benef"]
plot(discretizeQ(vv, seq(0, 1, 0.1)), 
     discretizeQ(vv, seq(0, 1, 0.5)))

plotMapVar("Asselineau", byp = 0.1)
plotMapVar("Abstention", byp = 0.1)
plotMapVar("French_nlty", byp = 0.1)

plotMapVar("X1564_OtherInactive_amg_NW", byp = 0.1)

plotMapVar("Stranger", byp = 0.1)

varPred <- "French_nlty"
```

# Essais

```{r, eval = FALSE}

v <- dat.all[, c("codgeo", "French_nlty")]
vx <- v[which(is.na(v$French_nlty)), ]
vx
v[1, ]
head(v)
tail(v)

library(inseeLocalData)
?inseeLocalData

#install.packages("insee")
library(insee)

get_dataset_list()

https://api.insee.fr/donnees-locales/V0.1/donnees/geo-POP@GEO2021RP2018/EPCI-247100647.INATC

```

```{r, eval = FALSE}
?prcomp

# Predictors
# New dataset with the predictors
dat2 <- dat.nocorr[, -1]

# For each predictor
for(col in colnames(dat2)){
  # Get the subset of the data
  v <- dat2[, col]
  # Compute the mean value, excluding NAs
  mv <- mean(v, na.rm = TRUE)
  # Fill in NAs with the mean
  v[is.na(v)] <- mv
  # Put back in the table
  dat2[, col] <- v
}

pca <- prcomp(dat2, center = TRUE, scale = TRUE)
ggbiplot(pca)

head(pca)

library(devtools)
install_github("vqv/ggbiplot")
library(ggbiplot)

plot(pca$x[, c("PC1", "PC2")])

pcax <- as.data.frame(pca$x)
pcax$codgeo <- dat.nocorr$codgeo

thedate <- date3
sub <- vacc[which(vacc$date == thedate & vacc$classe_age != "TOUT_AGE"), ]
subb <- adultVacc(sub)

sub3 <- merge(subb, pcax, all = TRUE, by = "codgeo")
sub3$typeTaux <- discretizeQ(sub3$taux_cumu, prbs = seq(0, 1, by = 0.1))
palCat <- rev(met.brewer("Hiroshige", n = 10, type = "continuous"))
names(palCat) <- 1:10

plot(sub3$PC1, sub3$PC2, col = palCat[sub3$typeTaux], pch = 16)

str(pca)
head(sub3)
dim(subb)
dim(pcax)

sort(pca$rotation[, "PC1"], decreasing = TRUE)[1:30]
sort(pca$rotation[, "PC2"], decreasing = TRUE)[1:30]

head(pca)
summary(pca)

pca$sdev / sum(pca$sdev)
str(pca)

length(pca$rotation[, "PC2"])
length(subb$taux_cumu)

plot(sub3$PC2, sub3$taux_cumu)

out <- matrix(NA, nrow = (ncol(pcax) - 1), ncol = 4)
for(i in 1:(ncol(pcax) - 1)){
  mdl <- cor.test(sub3[, paste0("PC", i)], sub3$taux_cumu)
  out[i, ] <- c(mdl$estimate, mdl$conf.int, mdl$p.value)
}
out <- as.data.frame(out)
names(out) <- c("estimate", "ci1", "ci2", "pval")
out$PC <- seq_len(nrow(out))

out[order(abs(out$estimate), decreasing = TRUE), ][1:5, ]
ii <- out[order(abs(out$estimate), decreasing = TRUE), ][1:5, "PC"]

# Composition of the PCs
for(i in ii){
  print(i)
  print(t(sort(pca$rotation[, paste0("PC", i)], decreasing = TRUE)[1:20])) 
}
sort(pca$rotation[, "PC2"], decreasing = TRUE)[1:30]

plot(sort(abs(out$estimate)))

range(out$estimate)

head(out)
mdl2 <- cor.test(sub3$PC2, sub3$taux_cumu)
mdl2

mdl1 <- cor.test(sub3$PC1, sub3$taux_cumu)
mdl1
str(mdl1)
summary(mdl1)
mdl3 <- cor.test(sub3$PC3, sub3$taux_cumu)
mdl3

summary(mdl)

library(nlme)
?gls
         gls(divspe ~ loggrad_urb+grad_agrimean, method = "ML", 
corr=corExp(c(300000,0.7), form=~x_lambert93+y_lambert93, nugget=T), 
na.action = na.omit, data = df)

```

### 2022-03-07 code/0_INSEE_predictors.R
update

@@ -14,6 +14,10 @@ sortData <- FALSE
 # Variables with absolute correlation above this threshold are removed from the analysis
 thrCor <- 0.95
 
+# Threshold for missing values
+# We will not consider variables with more than this threshold of missing values
+thrMissingVals <- 0.05
+
 ## FUNCTIONS
 
 # Function to check correlations
@@ -153,12 +157,26 @@ if(sortData){
 }
 
 
+#### CHECK MISSING VALUES ####
+
+# Count missing values
+missingvals <- apply(dat.all, 2, function(x) sum(is.na(x)))
+propMissingVals <- missingvals / nrow(dat.all)
+  
+# Show them
+sort(round(propMissingVals, 4), decreasing = TRUE)
+
+dat.removeMissing <- dat.all[, which(propMissingVals <= thrMissingVals)]
+
+dim(dat.all)
+dim(dat.removeMissing)
+
 #### CHECK CORRELATIONS ####
 
 ## Check correlations
 # Get all pairwise correlations
 # and take absolute value
-cormat <- abs(cor(dat.all[, -1], use = "pairwise.complete.obs"))
+cormat <- abs(cor(dat.removeMissing[, -1], use = "pairwise.complete.obs"))
 diag(cormat) <- NA # Remove diagonal
 
 # Sanity check
@@ -184,23 +202,25 @@ stopifnot(nrow(indOverThr)/2 == nrow(triangle))
 #   Get the names of the correlated columns
 correlated <- unique(colnames(cormat)[triangle[, 2]])
 #   Get their indices (col positions)
-i.corr <-   which(is.element(names(dat.all), correlated))
+i.corr <-   which(is.element(names(dat.removeMissing), correlated))
 #   Remove them
-dat.nocorr <- dat.all[, -i.corr]
+dat.nocorr <- dat.removeMissing[, -i.corr]
 
 dim(dat.nocorr)
 
 # Print names of the removed columns
-names(dat.all)[i.corr]
+names(dat.removeMissing)[i.corr]
 
 # Sanity check
-all(sort(names(dat.all)[i.corr]) == sort(correlated))
+all(sort(names(dat.removeMissing)[i.corr]) == sort(correlated))
 
 # Print names of the columns we keep
 sort(names(dat.nocorr))
 
+dim(dat.nocorr)
+
 # Get names of all the predictors
-predNames <- names(dat.all)
+predNames <- names(dat.removeMissing)
 predNames <- predNames[-1] # Remove codgeo
 
 #............................................................................

### 2022-03-07 code/1_functions-quantiles.R

@@ -43,8 +43,8 @@ discretizeQ <- function(v, prbs = seq(0, 1, by = 0.05)){
   qq <- c(quantile(v, probs = prbs, na.rm = TRUE))
   
   # Extend the extreme values to make sure that they are included later
-  qq[1] <- 0.5 * qq[1] # 0%
-  qq[length(qq)] <- 1.5 * qq[length(qq)] # 100%
+  qq[1] <- qq[1] - abs(0.5 * qq[1]) # 0%
+  qq[length(qq)] <- qq[length(qq)] + abs(0.5 * qq[length(qq)]) # 100%
   
   # Add noise to avoid issues with the `cut` function when data are too close
   noise <- c(0, runif(length(prbs)-2, max = 10^(-6)), 0)

### 2022-03-07 code/2_plot-overTime.R

@@ -13,9 +13,9 @@ plotPropTime <- function(out){
   # For each variable
   for(varPred in unique(out$varPred)){
     # Initialize plot
-    par(mar = c(3, 4, 2, 2), mgp = c(2.5, 0.5, 0), las = 1, tck = - 0.01)
+    par(mar = c(3, 4, 2, 2), mgp = c(1.75, 0.25, 0), las = 1, tck = - 0.01)
     plot(0, xlim = range(as.Date(dates)), ylim = c(0, 1), axes = FALSE, 
-         xlab = "date", ylab = "Adjusted vaccination rate", yaxs = "i", 
+         xlab = "date", ylab = "Adjusted vaccination rate", yaxs = "i", xaxs = "i", 
          main = varPred)
     axis(1, at = mnths, labels = format(mnths, "%b"))
     axis(2)

### 2022-03-07 code/geographic.R

@@ -26,6 +26,9 @@ tmpEPCI <- matrix(unlist(strsplit(geoEPCI$Geo.Point, ",")), byrow = TRUE, ncol =
 geoEPCI$latitude <- as.numeric(tmpEPCI[, 1])
 geoEPCI$longitude <- as.numeric(tmpEPCI[, 2])
 
+dim(geoEPCI)
+dim(geoCom)
+
 #### MERGE WITH CODGEO ####
 
 # Check whether codgeo is found in the data
@@ -101,3 +104,4 @@ dat.GEO <- merge(dat.GEO, tmp[, c("codgeo", "densite")], by = "codgeo")
 write.csv(dat.GEO, "../data/GEO_brut.csv", row.names = FALSE)
 system("git add ../data/GEO_brut.csv")
 system("git commit -m 'update GEO dataset'")
+

### 2022-03-07 code/vaccination-indicators.Rmd
update

@@
   # Define the combinations of parameters to be tested
-  parmsTime <- expand.grid(varPred = c("Unemployment_Benef", "French_nlty", "Asselineau"), 
+  parmsTime <- expand.grid(varPred = c("Unemployment_Benef", "Immigrant", "Asselineau"), 
                            thedate = dates, 
@@
 plotMapVar("Abstention", byp = 0.1)
-plotMapVar("French_nlty", byp = 0.1)
+plotMapVar("Immigrant", byp = 0.1)
 
 plotMapVar("X1564_OtherInactive_amg_NW", byp = 0.1)
-
-plotMapVar("Stranger", byp = 0.1)
-
-varPred <- "French_nlty"
 ```

### 2022-03-07 code/vaccination-indicators.tex
update for git

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\title{Vaccination}
\author{FD}
\date{}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Vaccination},
  pdfauthor={FD},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\begin{document}
\maketitle

\hypertarget{initializations}{%
\section{Initializations}\label{initializations}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{runComputations }\OtherTok{\textless{}{-}} \ConstantTok{FALSE}
\end{Highlighting}
\end{Shaded}

\hypertarget{load-and-clean-data}{%
\section{Load and clean data}\label{load-and-clean-data}}

\begin{itemize}
\tightlist
\item
  Indicators
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# The data have been dealt with in "0\_INSEE\_predictors.R" and saved as RData}
\FunctionTok{load}\NormalTok{(}\StringTok{"../data/predictors.RData"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{itemize}
\tightlist
\item
  Vaccination
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Source vaccination data}
\FunctionTok{source}\NormalTok{(}\StringTok{"load{-}clean\_vaccination.R"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{itemize}
\tightlist
\item
  Dates
\end{itemize}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Get all dates in the vaccination dataset}
\NormalTok{vaccDates }\OtherTok{\textless{}{-}} \FunctionTok{sort}\NormalTok{(}\FunctionTok{unique}\NormalTok{(vacc}\SpecialCharTok{$}\NormalTok{date))}
\FunctionTok{range}\NormalTok{(vaccDates)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] "2021-01-03" "2022-02-20"
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Define specific dates}
\NormalTok{date1 }\OtherTok{\textless{}{-}} \StringTok{"2021{-}07{-}11"} \CommentTok{\# Just before pass sanitaire announcement}
\NormalTok{date2 }\OtherTok{\textless{}{-}} \StringTok{"2021{-}08{-}08"} \CommentTok{\# Just before pass sanitaire comes into force}
\NormalTok{date3 }\OtherTok{\textless{}{-}} \StringTok{"2021{-}08{-}29"} \CommentTok{\# Before back to school}
\NormalTok{date4 }\OtherTok{\textless{}{-}} \StringTok{"2022{-}01{-}02"} \CommentTok{\# Last date of the year}
\end{Highlighting}
\end{Shaded}

\hypertarget{define-analysis-functions}{%
\section{Define analysis functions}\label{define-analysis-functions}}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Functions to discretize the data}
\FunctionTok{source}\NormalTok{(}\StringTok{"1\_functions{-}quantiles.R"}\NormalTok{)}
\CommentTok{\# \textasciigrave{}discretizeQ\textasciigrave{}}

\CommentTok{\# Functions to recompute vaccination rates}
\FunctionTok{source}\NormalTok{(}\StringTok{"1\_functions{-}adjustAges.R"}\NormalTok{)}

\CommentTok{\# Other}
\NormalTok{invlogit }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x)\{}\FunctionTok{exp}\NormalTok{(x)}\SpecialCharTok{/}\NormalTok{(}\DecValTok{1} \SpecialCharTok{+} \FunctionTok{exp}\NormalTok{(x))\}}

\NormalTok{uniqueNoNA }\OtherTok{\textless{}{-}} \ControlFlowTok{function}\NormalTok{(x)\{}
\NormalTok{  out }\OtherTok{\textless{}{-}} \FunctionTok{unique}\NormalTok{(x)}
\NormalTok{  out }\OtherTok{\textless{}{-}}\NormalTok{ out[}\SpecialCharTok{!}\FunctionTok{is.na}\NormalTok{(out)]}
\NormalTok{  out}
\NormalTok{\}}

\CommentTok{\# Logistic model}
\FunctionTok{source}\NormalTok{(}\StringTok{"1\_functions{-}logisticRegression.R"}\NormalTok{)}

\CommentTok{\# Odds ratios}
\FunctionTok{source}\NormalTok{(}\StringTok{"1\_functions{-}oddsRatios.R"}\NormalTok{)}

\CommentTok{\# Functions for plotting}
\FunctionTok{source}\NormalTok{(}\StringTok{"2\_plot{-}manhattan.R"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{vaccination-indicators_files/figure-latex/unnamed-chunk-4-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{source}\NormalTok{(}\StringTok{"2\_plot{-}overTime.R"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\hypertarget{computation}{%
\section{Computation}\label{computation}}

\hypertarget{across-median-comparison}{%
\subsection{Across median comparison}\label{across-median-comparison}}

\begin{Shaded}
\begin{Highlighting}[]
\ControlFlowTok{if}\NormalTok{(runComputations)\{}
  \CommentTok{\# Define the combinations of parameters to be tested}
\NormalTok{  parmsLR }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(}\AttributeTok{varPred =} \FunctionTok{names}\NormalTok{(dat.nocorr)[}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{], }
                         \AttributeTok{thedate =} \FunctionTok{c}\NormalTok{(date1, date2, date3, date4), }
                         \AttributeTok{predTransform =} \StringTok{"discretize\_factor"}\NormalTok{, }
                         \AttributeTok{vaccAge =} \StringTok{"adults"}\NormalTok{, }
                         \AttributeTok{by.prbs =} \FloatTok{0.5}\NormalTok{, }
                         \AttributeTok{permutation =} \ConstantTok{FALSE}\NormalTok{,}
                         \AttributeTok{stringsAsFactors =} \ConstantTok{FALSE}\NormalTok{)}
  \CommentTok{\# Permutation }
  \CommentTok{\# Number of repetitions}
\NormalTok{  nrep }\OtherTok{\textless{}{-}} \DecValTok{1000}
  \CommentTok{\# Base combination of parameters}
\NormalTok{  tmpparmsPerm }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(}\AttributeTok{varPred =} \StringTok{"French\_nlty"}\NormalTok{, }
                              \AttributeTok{thedate =} \FunctionTok{c}\NormalTok{(date1, date2, date3, date4), }
                              \AttributeTok{predTransform =} \StringTok{"discretize\_factor"}\NormalTok{, }
                              \AttributeTok{vaccAge =} \StringTok{"adults"}\NormalTok{, }
                              \AttributeTok{by.prbs =} \FloatTok{0.5}\NormalTok{, }
                              \AttributeTok{permutation =} \ConstantTok{TRUE}\NormalTok{,}
                              \AttributeTok{stringsAsFactors =} \ConstantTok{FALSE}\NormalTok{)}
  \CommentTok{\# Add repeated parameters}
  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{nrep)\{}
\NormalTok{    parmsLR }\OtherTok{\textless{}{-}} \FunctionTok{rbind}\NormalTok{(parmsLR, tmpparmsPerm)}
\NormalTok{  \}}
  \FunctionTok{rm}\NormalTok{(tmpparmsPerm)}

  \CommentTok{\# Initialize output}
\NormalTok{  out }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(}\FunctionTok{matrix}\NormalTok{(}\ConstantTok{NA}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{8}\NormalTok{, }\AttributeTok{nrow =} \FunctionTok{nrow}\NormalTok{(parmsLR)))}
  \FunctionTok{cat}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(parmsLR), }\StringTok{" combinations to be tested}\SpecialCharTok{\textbackslash{}n}\StringTok{"}\NormalTok{)}
  \CommentTok{\# Compute OR for each combination of parameters}
  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\FunctionTok{nrow}\NormalTok{(parmsLR))\{}
    \ControlFlowTok{if}\NormalTok{(i }\SpecialCharTok{\%\%} \DecValTok{10} \SpecialCharTok{==} \DecValTok{0}\NormalTok{) }\FunctionTok{cat}\NormalTok{(i, }\StringTok{""}\NormalTok{) }\CommentTok{\# Print counter}
    \CommentTok{\# Compute the logistic regression on this combination of parameters}
\NormalTok{    mdl }\OtherTok{\textless{}{-}} \FunctionTok{do.call}\NormalTok{(getLogReg, parmsLR[i, ])}
    \CommentTok{\# Extract the odds ratios}
\NormalTok{    out[i, ] }\OtherTok{\textless{}{-}} \FunctionTok{extractOR}\NormalTok{(mdl)}
\NormalTok{  \}}
  \FunctionTok{names}\NormalTok{(out) }\OtherTok{\textless{}{-}} \FunctionTok{names}\NormalTok{(}\FunctionTok{extractOR}\NormalTok{(mdl))}

  \CommentTok{\# Add the parameters}
\NormalTok{  outLR }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(parmsLR, out)}

  \CommentTok{\# Add type of predictor information}
\NormalTok{  outLR}\SpecialCharTok{$}\NormalTok{typePred }\OtherTok{\textless{}{-}}\NormalTok{ dicPred[outLR}\SpecialCharTok{$}\NormalTok{varPred]}
  \CommentTok{\# Full names}
\NormalTok{  outLR}\SpecialCharTok{$}\NormalTok{typePredFull }\OtherTok{\textless{}{-}}\NormalTok{ dic.fullpred[outLR}\SpecialCharTok{$}\NormalTok{typePred]}

  \FunctionTok{save}\NormalTok{(outLR, }\AttributeTok{file =} \StringTok{"outLR.RData"}\NormalTok{)}

\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{load}\NormalTok{(}\StringTok{"outLR.RData"}\NormalTok{)}

\CommentTok{\# PLOT}
\FunctionTok{plotManhattan}\NormalTok{(outLR, }\AttributeTok{ntop =} \DecValTok{5}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <b2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Abstention ▼' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Abstention ▼' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Abstention ▼' in 'mbcsToSbcs': dot
## substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' D1_st_Living ▲' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' D1_st_Living ▲' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' D1_st_Living ▲' in 'mbcsToSbcs': dot
## substituted for <b2>
\end{verbatim}

\includegraphics{vaccination-indicators_files/figure-latex/manhattan_median-1.pdf}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <b2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Abstention ▼' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Abstention ▼' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Abstention ▼' in 'mbcsToSbcs': dot
## substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' D1_st_Living ▲' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' D1_st_Living ▲' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' D1_st_Living ▲' in 'mbcsToSbcs': dot
## substituted for <b2>
\end{verbatim}

\includegraphics{vaccination-indicators_files/figure-latex/manhattan_median-2.pdf}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Immigrant ▼' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Immigrant ▼' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Immigrant ▼' in 'mbcsToSbcs': dot
## substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Overcrowding_rate ▼' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Overcrowding_rate ▼' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Overcrowding_rate ▼' in 'mbcsToSbcs': dot
## substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <b2>
\end{verbatim}

\includegraphics{vaccination-indicators_files/figure-latex/manhattan_median-3.pdf}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Immigrant ▼' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Immigrant ▼' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Immigrant ▼' in 'mbcsToSbcs': dot
## substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Overcrowding_rate ▼' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Overcrowding_rate ▼' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Overcrowding_rate ▼' in 'mbcsToSbcs': dot
## substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' NO.SE ▼' in 'mbcsToSbcs': dot substituted
## for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' NO.SE ▼' in 'mbcsToSbcs': dot substituted
## for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' NO.SE ▼' in 'mbcsToSbcs': dot substituted
## for <bc>
\end{verbatim}

\includegraphics{vaccination-indicators_files/figure-latex/manhattan_median-4.pdf}

\hypertarget{by-deciles-quantitatively-adjusting-ages}{%
\subsection{By deciles, quantitatively, adjusting
ages}\label{by-deciles-quantitatively-adjusting-ages}}

\begin{Shaded}
\begin{Highlighting}[]
\ControlFlowTok{if}\NormalTok{(runComputations)\{}
  \CommentTok{\# Define the combinations of parameters to be tested}
\NormalTok{  parmsDec }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(}\AttributeTok{varPred =} \FunctionTok{names}\NormalTok{(dat.nocorr)[}\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{], }
                          \AttributeTok{thedate =} \FunctionTok{c}\NormalTok{(date1, date2, date3, date4), }
                          \AttributeTok{predTransform =} \StringTok{"discretize"}\NormalTok{, }
                          \AttributeTok{vaccAge =} \StringTok{"by\_age"}\NormalTok{, }
                          \AttributeTok{by.prbs =} \FloatTok{0.1}\NormalTok{, }
                          \AttributeTok{permutation =} \ConstantTok{FALSE}\NormalTok{,}
                          \AttributeTok{stringsAsFactors =} \ConstantTok{FALSE}\NormalTok{)}

  \CommentTok{\# Permutation}
  \CommentTok{\# Base combination of parameters}
\NormalTok{  tmpparmsPerm }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(}\AttributeTok{varPred =} \StringTok{"French\_nlty"}\NormalTok{, }
                              \AttributeTok{thedate =} \FunctionTok{c}\NormalTok{(date1, date2, date3, date4), }
                              \AttributeTok{predTransform =} \StringTok{"discretize"}\NormalTok{, }
                              \AttributeTok{vaccAge =} \StringTok{"by\_age"}\NormalTok{, }
                              \AttributeTok{by.prbs =} \FloatTok{0.1}\NormalTok{, }
                              \AttributeTok{permutation =} \ConstantTok{TRUE}\NormalTok{,}
                              \AttributeTok{stringsAsFactors =} \ConstantTok{FALSE}\NormalTok{)}
  \CommentTok{\# Add repeated parameters}
  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{nrep)\{}
\NormalTok{    parmsDec }\OtherTok{\textless{}{-}} \FunctionTok{rbind}\NormalTok{(parmsDec, tmpparmsPerm)}
\NormalTok{  \}}
  \FunctionTok{rm}\NormalTok{(tmpparmsPerm)}

\NormalTok{  newd }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(}\AttributeTok{age.f =} \FunctionTok{as.factor}\NormalTok{(ages), }\AttributeTok{pred.std =} \DecValTok{1}\SpecialCharTok{:}\DecValTok{10}\NormalTok{)}

  \FunctionTok{cat}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(parmsDec), }\StringTok{" combinations to be tested}\SpecialCharTok{\textbackslash{}n}\StringTok{"}\NormalTok{)}

\NormalTok{  out }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(}\FunctionTok{matrix}\NormalTok{(}\ConstantTok{NA}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{4}\NormalTok{, }\AttributeTok{nrow =} \FunctionTok{nrow}\NormalTok{(parmsDec)))}

  \CommentTok{\# Compute OR for each combination of parameters}
  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\FunctionTok{nrow}\NormalTok{(parmsDec))\{}
    \ControlFlowTok{if}\NormalTok{(i }\SpecialCharTok{\%\%} \DecValTok{10} \SpecialCharTok{==} \DecValTok{0}\NormalTok{) }\FunctionTok{cat}\NormalTok{(i, }\StringTok{""}\NormalTok{) }\CommentTok{\# Print counter}
    \CommentTok{\# Compute the logistic regression on this combination of parameters}
\NormalTok{    mdl }\OtherTok{\textless{}{-}} \FunctionTok{do.call}\NormalTok{(getLogReg, parmsDec[i, ])}
    \CommentTok{\# Predicted values}
\NormalTok{    predsC }\OtherTok{\textless{}{-}} \FunctionTok{adjustedPredict}\NormalTok{(mdl, newd, }\AttributeTok{includeChildren =} \ConstantTok{TRUE}\NormalTok{)}
\NormalTok{    predsA }\OtherTok{\textless{}{-}} \FunctionTok{adjustedPredict}\NormalTok{(mdl, newd, }\AttributeTok{includeChildren =} \ConstantTok{FALSE}\NormalTok{)}

    \CommentTok{\# Compute odds ratios}
\NormalTok{    ORC }\OtherTok{\textless{}{-}} \FunctionTok{getORfromPredict}\NormalTok{(}\FunctionTok{c}\NormalTok{(predsC[predsC}\SpecialCharTok{$}\NormalTok{pred.std }\SpecialCharTok{==} \DecValTok{10}\NormalTok{, }\StringTok{"adjustedRate"}\NormalTok{], predsC[predsC}\SpecialCharTok{$}\NormalTok{pred.std }\SpecialCharTok{==} \DecValTok{1}\NormalTok{, }\StringTok{"adjustedRate"}\NormalTok{]))}
\NormalTok{    ORA }\OtherTok{\textless{}{-}} \FunctionTok{getORfromPredict}\NormalTok{(}\FunctionTok{c}\NormalTok{(predsA[predsA}\SpecialCharTok{$}\NormalTok{pred.std }\SpecialCharTok{==} \DecValTok{10}\NormalTok{, }\StringTok{"adjustedRate"}\NormalTok{], predsA[predsA}\SpecialCharTok{$}\NormalTok{pred.std }\SpecialCharTok{==} \DecValTok{1}\NormalTok{, }\StringTok{"adjustedRate"}\NormalTok{]))}

\NormalTok{    out[i, ] }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(ORC, ORA, }\FunctionTok{max}\NormalTok{(ORC, }\DecValTok{1}\SpecialCharTok{/}\NormalTok{ORC), }\FunctionTok{max}\NormalTok{(ORA, }\DecValTok{1}\SpecialCharTok{/}\NormalTok{ORA))}
\NormalTok{  \}}
  \FunctionTok{names}\NormalTok{(out) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"OR.withChildren"}\NormalTok{, }\StringTok{"OR.adults"}\NormalTok{, }\StringTok{"OR.abs.withChildren"}\NormalTok{, }\StringTok{"OR.abs.adults"}\NormalTok{)}
  \FunctionTok{dim}\NormalTok{(out)}
  \CommentTok{\# Add the parameters}
\NormalTok{  outDec }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(parmsDec, out)}
  \CommentTok{\# Add type of predictor information}
\NormalTok{  outDec}\SpecialCharTok{$}\NormalTok{typePred }\OtherTok{\textless{}{-}}\NormalTok{ dicPred[outDec}\SpecialCharTok{$}\NormalTok{varPred]}
  \CommentTok{\# Full names}
\NormalTok{  outDec}\SpecialCharTok{$}\NormalTok{typePredFull }\OtherTok{\textless{}{-}}\NormalTok{ dic.fullpred[outDec}\SpecialCharTok{$}\NormalTok{typePred]}

  \FunctionTok{save}\NormalTok{(outDec, }\AttributeTok{file =} \StringTok{"outDec.RData"}\NormalTok{)}

\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{load}\NormalTok{(}\StringTok{"outDec.RData"}\NormalTok{)}

\NormalTok{suffix }\OtherTok{\textless{}{-}} \StringTok{".withChildren"}

\NormalTok{xx }\OtherTok{\textless{}{-}}\NormalTok{ outDec}
\NormalTok{xx}\SpecialCharTok{$}\NormalTok{OR }\OtherTok{\textless{}{-}}\NormalTok{ outDec[, }\FunctionTok{paste0}\NormalTok{(}\StringTok{"OR"}\NormalTok{, suffix)]}
\NormalTok{xx}\SpecialCharTok{$}\NormalTok{OR.abs }\OtherTok{\textless{}{-}}\NormalTok{ outDec[, }\FunctionTok{paste0}\NormalTok{(}\StringTok{"OR.abs"}\NormalTok{, suffix)]}
\NormalTok{xx}\SpecialCharTok{$}\NormalTok{OR.abs.CI.max }\OtherTok{\textless{}{-}}\NormalTok{ outDec[, }\FunctionTok{paste0}\NormalTok{(}\StringTok{"OR.abs"}\NormalTok{, suffix)]}

\FunctionTok{plotManhattan}\NormalTok{(xx, }\AttributeTok{ntop =} \DecValTok{5}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 15._men_NoDiploma_amg_mWF ▼' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 15._men_NoDiploma_amg_mWF ▼' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 15._men_NoDiploma_amg_mWF ▼' in
## 'mbcsToSbcs': dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Median_st_Living ▲' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Median_st_Living ▲' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Median_st_Living ▲' in 'mbcsToSbcs': dot
## substituted for <b2>
\end{verbatim}

\includegraphics{vaccination-indicators_files/figure-latex/manhattan_decilesQ_withChildren-1.pdf}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <b2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <bc>
\end{verbatim}

\includegraphics{vaccination-indicators_files/figure-latex/manhattan_decilesQ_withChildren-2.pdf}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <b2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' NO.SE ▼' in 'mbcsToSbcs': dot substituted
## for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' NO.SE ▼' in 'mbcsToSbcs': dot substituted
## for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' NO.SE ▼' in 'mbcsToSbcs': dot substituted
## for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <bc>
\end{verbatim}

\includegraphics{vaccination-indicators_files/figure-latex/manhattan_decilesQ_withChildren-3.pdf}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Immigrant ▼' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Immigrant ▼' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Immigrant ▼' in 'mbcsToSbcs': dot
## substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <b2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Overcrowding_rate ▼' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Overcrowding_rate ▼' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Overcrowding_rate ▼' in 'mbcsToSbcs': dot
## substituted for <bc>
\end{verbatim}

\includegraphics{vaccination-indicators_files/figure-latex/manhattan_decilesQ_withChildren-4.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{suffix }\OtherTok{\textless{}{-}} \StringTok{".adults"}

\NormalTok{xx }\OtherTok{\textless{}{-}}\NormalTok{ outDec}
\NormalTok{xx}\SpecialCharTok{$}\NormalTok{OR }\OtherTok{\textless{}{-}}\NormalTok{ outDec[, }\FunctionTok{paste0}\NormalTok{(}\StringTok{"OR"}\NormalTok{, suffix)]}
\NormalTok{xx}\SpecialCharTok{$}\NormalTok{OR.abs }\OtherTok{\textless{}{-}}\NormalTok{ outDec[, }\FunctionTok{paste0}\NormalTok{(}\StringTok{"OR.abs"}\NormalTok{, suffix)]}
\NormalTok{xx}\SpecialCharTok{$}\NormalTok{OR.abs.CI.max }\OtherTok{\textless{}{-}}\NormalTok{ outDec[, }\FunctionTok{paste0}\NormalTok{(}\StringTok{"OR.abs"}\NormalTok{, suffix)]}

\FunctionTok{plotManhattan}\NormalTok{(xx, }\AttributeTok{ntop =} \DecValTok{5}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 15._men_NoDiploma_amg_mWF ▼' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 15._men_NoDiploma_amg_mWF ▼' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 15._men_NoDiploma_amg_mWF ▼' in
## 'mbcsToSbcs': dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Median_st_Living ▲' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Median_st_Living ▲' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Median_st_Living ▲' in 'mbcsToSbcs': dot
## substituted for <b2>
\end{verbatim}

\includegraphics{vaccination-indicators_files/figure-latex/manhattan_decilesQ_adultsOnly-1.pdf}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 2554_women_Workforce_rate ▲' in
## 'mbcsToSbcs': dot substituted for <b2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' NO.SE ▼' in 'mbcsToSbcs': dot substituted
## for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' NO.SE ▼' in 'mbcsToSbcs': dot substituted
## for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' NO.SE ▼' in 'mbcsToSbcs': dot substituted
## for <bc>
\end{verbatim}

\includegraphics{vaccination-indicators_files/figure-latex/manhattan_decilesQ_adultsOnly-2.pdf}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' NO.SE ▼' in 'mbcsToSbcs': dot substituted
## for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' NO.SE ▼' in 'mbcsToSbcs': dot substituted
## for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' NO.SE ▼' in 'mbcsToSbcs': dot substituted
## for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <bc>
\end{verbatim}

\includegraphics{vaccination-indicators_files/figure-latex/manhattan_decilesQ_adultsOnly-3.pdf}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' Unemployment_Benef ▼' in 'mbcsToSbcs':
## dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' NO.SE ▼' in 'mbcsToSbcs': dot substituted
## for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' NO.SE ▼' in 'mbcsToSbcs': dot substituted
## for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels =
## paste0(" ", : conversion failure on ' NO.SE ▼' in 'mbcsToSbcs': dot substituted
## for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' Asselineau ▼' in 'mbcsToSbcs': dot
## substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_NW ▼' in
## 'mbcsToSbcs': dot substituted for <bc>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <e2>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <96>
\end{verbatim}

\begin{verbatim}
## Warning in text.default(y = tmp$i, x = tmp$OR.abs, adj = c(0, 0.5), labels
## = paste0(" ", : conversion failure on ' 1564_OtherInactive_amg_WF ▼' in
## 'mbcsToSbcs': dot substituted for <bc>
\end{verbatim}

\includegraphics{vaccination-indicators_files/figure-latex/manhattan_decilesQ_adultsOnly-4.pdf}

\hypertarget{over-time}{%
\subsection{Over time}\label{over-time}}

\begin{Shaded}
\begin{Highlighting}[]
\ControlFlowTok{if}\NormalTok{(runComputations)\{}
\NormalTok{  dates }\OtherTok{\textless{}{-}} \FunctionTok{sort}\NormalTok{(}\FunctionTok{unique}\NormalTok{(vacc}\SpecialCharTok{$}\NormalTok{date))}
\NormalTok{  minDate }\OtherTok{\textless{}{-}} \StringTok{"2021{-}05{-}01"}
\NormalTok{  dates }\OtherTok{\textless{}{-}}\NormalTok{ dates[dates }\SpecialCharTok{\textgreater{}=}\NormalTok{ minDate]}

  \CommentTok{\# Define the combinations of parameters to be tested}
\NormalTok{  parmsTime }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(}\AttributeTok{varPred =} \FunctionTok{c}\NormalTok{(}\StringTok{"Unemployment\_Benef"}\NormalTok{, }\StringTok{"Immigrant"}\NormalTok{, }\StringTok{"Asselineau"}\NormalTok{), }
                           \AttributeTok{thedate =}\NormalTok{ dates, }
                           \AttributeTok{predTransform =} \StringTok{"discretize\_factor"}\NormalTok{, }
                           \AttributeTok{vaccAge =} \StringTok{"by\_age"}\NormalTok{, }
                           \AttributeTok{by.prbs =} \FloatTok{0.1}\NormalTok{, }
                           \AttributeTok{permutation =} \ConstantTok{FALSE}\NormalTok{,}
                           \AttributeTok{stringsAsFactors =} \ConstantTok{FALSE}\NormalTok{)}

  \FunctionTok{dim}\NormalTok{(parmsTime)}

\NormalTok{  newd }\OtherTok{\textless{}{-}} \FunctionTok{expand.grid}\NormalTok{(}\AttributeTok{age.f =} \FunctionTok{as.factor}\NormalTok{(ages), }\AttributeTok{pred.std =} \FunctionTok{as.factor}\NormalTok{(}\DecValTok{1}\SpecialCharTok{:}\DecValTok{10}\NormalTok{))}

  \CommentTok{\# Initialize output}
\NormalTok{  outC }\OtherTok{\textless{}{-}}\NormalTok{ outA }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(}\FunctionTok{matrix}\NormalTok{(}\ConstantTok{NA}\NormalTok{, }\AttributeTok{ncol =} \DecValTok{10}\NormalTok{, }\AttributeTok{nrow =} \FunctionTok{nrow}\NormalTok{(parmsTime)))}

  \CommentTok{\# Compute OR for each combination of parameters}
  \ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\FunctionTok{nrow}\NormalTok{(parmsTime))\{}
    \ControlFlowTok{if}\NormalTok{(i }\SpecialCharTok{\%\%} \DecValTok{10} \SpecialCharTok{==} \DecValTok{0}\NormalTok{) }\FunctionTok{cat}\NormalTok{(i, }\StringTok{""}\NormalTok{) }\CommentTok{\# Print counter}
    \CommentTok{\# Compute the logistic regression on this combination of parameters}
\NormalTok{    mdl }\OtherTok{\textless{}{-}} \FunctionTok{do.call}\NormalTok{(getLogReg, parmsTime[i, ])}
    \CommentTok{\# Predicted values}
\NormalTok{    predsC }\OtherTok{\textless{}{-}} \FunctionTok{adjustedPredict}\NormalTok{(mdl, newd, }\AttributeTok{includeChildren =} \ConstantTok{TRUE}\NormalTok{)}
\NormalTok{    predsA }\OtherTok{\textless{}{-}} \FunctionTok{adjustedPredict}\NormalTok{(mdl, newd, }\AttributeTok{includeChildren =} \ConstantTok{FALSE}\NormalTok{)}

    \CommentTok{\# Save}
\NormalTok{    outC[i, ] }\OtherTok{\textless{}{-}}\NormalTok{ predsC}\SpecialCharTok{$}\NormalTok{adjustedRate}
\NormalTok{    outA[i, ] }\OtherTok{\textless{}{-}}\NormalTok{ predsA}\SpecialCharTok{$}\NormalTok{adjustedRate}

\NormalTok{  \}}

\NormalTok{  outC }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(parmsTime, outC)}
\NormalTok{  outA }\OtherTok{\textless{}{-}} \FunctionTok{cbind}\NormalTok{(parmsTime, outA)}

  \FunctionTok{save}\NormalTok{(outC, outA, dates, }\AttributeTok{file =} \StringTok{"outTime.RData"}\NormalTok{)}

\NormalTok{\}}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{load}\NormalTok{(}\StringTok{"outTime.RData"}\NormalTok{)}

\FunctionTok{plotPropTime}\NormalTok{(outC)}
\end{Highlighting}
\end{Shaded}

\includegraphics{vaccination-indicators_files/figure-latex/overtime_withChildren-1.pdf}
\includegraphics{vaccination-indicators_files/figure-latex/overtime_withChildren-2.pdf}
\includegraphics{vaccination-indicators_files/figure-latex/overtime_withChildren-3.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plotPropTime}\NormalTok{(outA)}
\end{Highlighting}
\end{Shaded}

\includegraphics{vaccination-indicators_files/figure-latex/overtime_adultsOnly-1.pdf}
\includegraphics{vaccination-indicators_files/figure-latex/overtime_adultsOnly-2.pdf}
\includegraphics{vaccination-indicators_files/figure-latex/overtime_adultsOnly-3.pdf}

\hypertarget{geographic}{%
\section{Geographic}\label{geographic}}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{library}\NormalTok{(mapsf)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Loading required package: sf
\end{verbatim}

\begin{verbatim}
## Linking to GEOS 3.9.1, GDAL 3.3.1, PROJ 8.1.0
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\# Geographic information for maps}
\FunctionTok{load}\NormalTok{(}\StringTok{"../data/mapFiles\_withDepReg.RData"}\NormalTok{)}
\FunctionTok{load}\NormalTok{(}\StringTok{"../data/chefslieux.RData"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{\#varPred \textless{}{-} "X1564\_OtherInactive\_amg\_NW"}

\FunctionTok{source}\NormalTok{(}\StringTok{"2\_plot{-}map.R"}\NormalTok{)}
\FunctionTok{plotMapVar}\NormalTok{(}\StringTok{"Unemployment\_Benef"}\NormalTok{, }\AttributeTok{byp =} \FloatTok{0.1}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{vaccination-indicators_files/figure-latex/unnamed-chunk-9-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plotMapVar}\NormalTok{(}\StringTok{"Unemployment\_Benef"}\NormalTok{, }\AttributeTok{byp =} \FloatTok{0.5}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{vaccination-indicators_files/figure-latex/unnamed-chunk-10-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plotMapVar}\NormalTok{(}\StringTok{"Unemployment\_Benef"}\NormalTok{, }\AttributeTok{byp =} \FloatTok{0.1}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{vaccination-indicators_files/figure-latex/unnamed-chunk-10-2.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{vv }\OtherTok{\textless{}{-}}\NormalTok{ dat.all[, }\StringTok{"Unemployment\_Benef"}\NormalTok{]}
\FunctionTok{plot}\NormalTok{(}\FunctionTok{discretizeQ}\NormalTok{(vv, }\FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\FloatTok{0.1}\NormalTok{)), }
     \FunctionTok{discretizeQ}\NormalTok{(vv, }\FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\FloatTok{0.5}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

\includegraphics{vaccination-indicators_files/figure-latex/unnamed-chunk-10-3.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plotMapVar}\NormalTok{(}\StringTok{"Asselineau"}\NormalTok{, }\AttributeTok{byp =} \FloatTok{0.1}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{vaccination-indicators_files/figure-latex/unnamed-chunk-10-4.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plotMapVar}\NormalTok{(}\StringTok{"Abstention"}\NormalTok{, }\AttributeTok{byp =} \FloatTok{0.1}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{vaccination-indicators_files/figure-latex/unnamed-chunk-10-5.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plotMapVar}\NormalTok{(}\StringTok{"Immigrant"}\NormalTok{, }\AttributeTok{byp =} \FloatTok{0.1}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{vaccination-indicators_files/figure-latex/unnamed-chunk-10-6.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{plotMapVar}\NormalTok{(}\StringTok{"X1564\_OtherInactive\_amg\_NW"}\NormalTok{, }\AttributeTok{byp =} \FloatTok{0.1}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{vaccination-indicators_files/figure-latex/unnamed-chunk-10-7.pdf}

\hypertarget{essais}{%
\section{Essais}\label{essais}}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{v }\OtherTok{\textless{}{-}}\NormalTok{ dat.all[, }\FunctionTok{c}\NormalTok{(}\StringTok{"codgeo"}\NormalTok{, }\StringTok{"French\_nlty"}\NormalTok{)]}
\NormalTok{vx }\OtherTok{\textless{}{-}}\NormalTok{ v[}\FunctionTok{which}\NormalTok{(}\FunctionTok{is.na}\NormalTok{(v}\SpecialCharTok{$}\NormalTok{French\_nlty)), ]}
\NormalTok{vx}
\NormalTok{v[}\DecValTok{1}\NormalTok{, ]}
\FunctionTok{head}\NormalTok{(v)}
\FunctionTok{tail}\NormalTok{(v)}

\FunctionTok{library}\NormalTok{(inseeLocalData)}
\NormalTok{?inseeLocalData}

\CommentTok{\#install.packages("insee")}
\FunctionTok{library}\NormalTok{(insee)}

\FunctionTok{get\_dataset\_list}\NormalTok{()}

\NormalTok{https}\SpecialCharTok{:}\ErrorTok{//}\NormalTok{api.insee.fr}\SpecialCharTok{/}\NormalTok{donnees}\SpecialCharTok{{-}}\NormalTok{locales}\SpecialCharTok{/}\NormalTok{V0}\FloatTok{.1}\SpecialCharTok{/}\NormalTok{donnees}\SpecialCharTok{/}\NormalTok{geo}\SpecialCharTok{{-}}\NormalTok{POP}\SpecialCharTok{@}\NormalTok{GEO2021RP2018}\SpecialCharTok{/}\NormalTok{EPCI}\FloatTok{{-}247100647.}\NormalTok{INATC}
\end{Highlighting}
\end{Shaded}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{?prcomp}

\CommentTok{\# Predictors}
\CommentTok{\# New dataset with the predictors}
\NormalTok{dat2 }\OtherTok{\textless{}{-}}\NormalTok{ dat.nocorr[, }\SpecialCharTok{{-}}\DecValTok{1}\NormalTok{]}

\CommentTok{\# For each predictor}
\ControlFlowTok{for}\NormalTok{(col }\ControlFlowTok{in} \FunctionTok{colnames}\NormalTok{(dat2))\{}
  \CommentTok{\# Get the subset of the data}
\NormalTok{  v }\OtherTok{\textless{}{-}}\NormalTok{ dat2[, col]}
  \CommentTok{\# Compute the mean value, excluding NAs}
\NormalTok{  mv }\OtherTok{\textless{}{-}} \FunctionTok{mean}\NormalTok{(v, }\AttributeTok{na.rm =} \ConstantTok{TRUE}\NormalTok{)}
  \CommentTok{\# Fill in NAs with the mean}
\NormalTok{  v[}\FunctionTok{is.na}\NormalTok{(v)] }\OtherTok{\textless{}{-}}\NormalTok{ mv}
  \CommentTok{\# Put back in the table}
\NormalTok{  dat2[, col] }\OtherTok{\textless{}{-}}\NormalTok{ v}
\NormalTok{\}}

\NormalTok{pca }\OtherTok{\textless{}{-}} \FunctionTok{prcomp}\NormalTok{(dat2, }\AttributeTok{center =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{scale =} \ConstantTok{TRUE}\NormalTok{)}
\FunctionTok{ggbiplot}\NormalTok{(pca)}

\FunctionTok{head}\NormalTok{(pca)}

\FunctionTok{library}\NormalTok{(devtools)}
\FunctionTok{install\_github}\NormalTok{(}\StringTok{"vqv/ggbiplot"}\NormalTok{)}
\FunctionTok{library}\NormalTok{(ggbiplot)}

\FunctionTok{plot}\NormalTok{(pca}\SpecialCharTok{$}\NormalTok{x[, }\FunctionTok{c}\NormalTok{(}\StringTok{"PC1"}\NormalTok{, }\StringTok{"PC2"}\NormalTok{)])}

\NormalTok{pcax }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(pca}\SpecialCharTok{$}\NormalTok{x)}
\NormalTok{pcax}\SpecialCharTok{$}\NormalTok{codgeo }\OtherTok{\textless{}{-}}\NormalTok{ dat.nocorr}\SpecialCharTok{$}\NormalTok{codgeo}

\NormalTok{thedate }\OtherTok{\textless{}{-}}\NormalTok{ date3}
\NormalTok{sub }\OtherTok{\textless{}{-}}\NormalTok{ vacc[}\FunctionTok{which}\NormalTok{(vacc}\SpecialCharTok{$}\NormalTok{date }\SpecialCharTok{==}\NormalTok{ thedate }\SpecialCharTok{\&}\NormalTok{ vacc}\SpecialCharTok{$}\NormalTok{classe\_age }\SpecialCharTok{!=} \StringTok{"TOUT\_AGE"}\NormalTok{), ]}
\NormalTok{subb }\OtherTok{\textless{}{-}} \FunctionTok{adultVacc}\NormalTok{(sub)}

\NormalTok{sub3 }\OtherTok{\textless{}{-}} \FunctionTok{merge}\NormalTok{(subb, pcax, }\AttributeTok{all =} \ConstantTok{TRUE}\NormalTok{, }\AttributeTok{by =} \StringTok{"codgeo"}\NormalTok{)}
\NormalTok{sub3}\SpecialCharTok{$}\NormalTok{typeTaux }\OtherTok{\textless{}{-}} \FunctionTok{discretizeQ}\NormalTok{(sub3}\SpecialCharTok{$}\NormalTok{taux\_cumu, }\AttributeTok{prbs =} \FunctionTok{seq}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{1}\NormalTok{, }\AttributeTok{by =} \FloatTok{0.1}\NormalTok{))}
\NormalTok{palCat }\OtherTok{\textless{}{-}} \FunctionTok{rev}\NormalTok{(}\FunctionTok{met.brewer}\NormalTok{(}\StringTok{"Hiroshige"}\NormalTok{, }\AttributeTok{n =} \DecValTok{10}\NormalTok{, }\AttributeTok{type =} \StringTok{"continuous"}\NormalTok{))}
\FunctionTok{names}\NormalTok{(palCat) }\OtherTok{\textless{}{-}} \DecValTok{1}\SpecialCharTok{:}\DecValTok{10}

\FunctionTok{plot}\NormalTok{(sub3}\SpecialCharTok{$}\NormalTok{PC1, sub3}\SpecialCharTok{$}\NormalTok{PC2, }\AttributeTok{col =}\NormalTok{ palCat[sub3}\SpecialCharTok{$}\NormalTok{typeTaux], }\AttributeTok{pch =} \DecValTok{16}\NormalTok{)}

\FunctionTok{str}\NormalTok{(pca)}
\FunctionTok{head}\NormalTok{(sub3)}
\FunctionTok{dim}\NormalTok{(subb)}
\FunctionTok{dim}\NormalTok{(pcax)  }

\FunctionTok{sort}\NormalTok{(pca}\SpecialCharTok{$}\NormalTok{rotation[, }\StringTok{"PC1"}\NormalTok{], }\AttributeTok{decreasing =} \ConstantTok{TRUE}\NormalTok{)[}\DecValTok{1}\SpecialCharTok{:}\DecValTok{30}\NormalTok{]}
\FunctionTok{sort}\NormalTok{(pca}\SpecialCharTok{$}\NormalTok{rotation[, }\StringTok{"PC2"}\NormalTok{], }\AttributeTok{decreasing =} \ConstantTok{TRUE}\NormalTok{)[}\DecValTok{1}\SpecialCharTok{:}\DecValTok{30}\NormalTok{]}

\FunctionTok{head}\NormalTok{(pca)}
\FunctionTok{summary}\NormalTok{(pca)}

\NormalTok{pca}\SpecialCharTok{$}\NormalTok{sdev }\SpecialCharTok{/} \FunctionTok{sum}\NormalTok{(pca}\SpecialCharTok{$}\NormalTok{sdev)}
\FunctionTok{str}\NormalTok{(pca)}

\FunctionTok{length}\NormalTok{(pca}\SpecialCharTok{$}\NormalTok{rotation[, }\StringTok{"PC2"}\NormalTok{])}
\FunctionTok{length}\NormalTok{(subb}\SpecialCharTok{$}\NormalTok{taux\_cumu)}

\FunctionTok{plot}\NormalTok{(sub3}\SpecialCharTok{$}\NormalTok{PC2, sub3}\SpecialCharTok{$}\NormalTok{taux\_cumu)}

\NormalTok{out }\OtherTok{\textless{}{-}} \FunctionTok{matrix}\NormalTok{(}\ConstantTok{NA}\NormalTok{, }\AttributeTok{nrow =}\NormalTok{ (}\FunctionTok{ncol}\NormalTok{(pcax) }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{), }\AttributeTok{ncol =} \DecValTok{4}\NormalTok{)}
\ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in} \DecValTok{1}\SpecialCharTok{:}\NormalTok{(}\FunctionTok{ncol}\NormalTok{(pcax) }\SpecialCharTok{{-}} \DecValTok{1}\NormalTok{))\{}
\NormalTok{  mdl }\OtherTok{\textless{}{-}} \FunctionTok{cor.test}\NormalTok{(sub3[, }\FunctionTok{paste0}\NormalTok{(}\StringTok{"PC"}\NormalTok{, i)], sub3}\SpecialCharTok{$}\NormalTok{taux\_cumu)}
\NormalTok{  out[i, ] }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(mdl}\SpecialCharTok{$}\NormalTok{estimate, mdl}\SpecialCharTok{$}\NormalTok{conf.int, mdl}\SpecialCharTok{$}\NormalTok{p.value)}
\NormalTok{\}}
\NormalTok{out }\OtherTok{\textless{}{-}} \FunctionTok{as.data.frame}\NormalTok{(out)}
\FunctionTok{names}\NormalTok{(out) }\OtherTok{\textless{}{-}} \FunctionTok{c}\NormalTok{(}\StringTok{"estimate"}\NormalTok{, }\StringTok{"ci1"}\NormalTok{, }\StringTok{"ci2"}\NormalTok{, }\StringTok{"pval"}\NormalTok{)}
\NormalTok{out}\SpecialCharTok{$}\NormalTok{PC }\OtherTok{\textless{}{-}} \FunctionTok{seq\_len}\NormalTok{(}\FunctionTok{nrow}\NormalTok{(out))}

\NormalTok{out[}\FunctionTok{order}\NormalTok{(}\FunctionTok{abs}\NormalTok{(out}\SpecialCharTok{$}\NormalTok{estimate), }\AttributeTok{decreasing =} \ConstantTok{TRUE}\NormalTok{), ][}\DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{, ]}
\NormalTok{ii }\OtherTok{\textless{}{-}}\NormalTok{ out[}\FunctionTok{order}\NormalTok{(}\FunctionTok{abs}\NormalTok{(out}\SpecialCharTok{$}\NormalTok{estimate), }\AttributeTok{decreasing =} \ConstantTok{TRUE}\NormalTok{), ][}\DecValTok{1}\SpecialCharTok{:}\DecValTok{5}\NormalTok{, }\StringTok{"PC"}\NormalTok{]}

\CommentTok{\# Composition of the PCs}
\ControlFlowTok{for}\NormalTok{(i }\ControlFlowTok{in}\NormalTok{ ii)\{}
  \FunctionTok{print}\NormalTok{(i)}
  \FunctionTok{print}\NormalTok{(}\FunctionTok{t}\NormalTok{(}\FunctionTok{sort}\NormalTok{(pca}\SpecialCharTok{$}\NormalTok{rotation[, }\FunctionTok{paste0}\NormalTok{(}\StringTok{"PC"}\NormalTok{, i)], }\AttributeTok{decreasing =} \ConstantTok{TRUE}\NormalTok{)[}\DecValTok{1}\SpecialCharTok{:}\DecValTok{20}\NormalTok{])) }
\NormalTok{\}}
\FunctionTok{sort}\NormalTok{(pca}\SpecialCharTok{$}\NormalTok{rotation[, }\StringTok{"PC2"}\NormalTok{], }\AttributeTok{decreasing =} \ConstantTok{TRUE}\NormalTok{)[}\DecValTok{1}\SpecialCharTok{:}\DecValTok{30}\NormalTok{]}

\FunctionTok{plot}\NormalTok{(}\FunctionTok{sort}\NormalTok{(}\FunctionTok{abs}\NormalTok{(out}\SpecialCharTok{$}\NormalTok{estimate)))}

\FunctionTok{range}\NormalTok{(out}\SpecialCharTok{$}\NormalTok{estimate)}

\FunctionTok{head}\NormalTok{(out)}
\NormalTok{mdl2 }\OtherTok{\textless{}{-}} \FunctionTok{cor.test}\NormalTok{(sub3}\SpecialCharTok{$}\NormalTok{PC2, sub3}\SpecialCharTok{$}\NormalTok{taux\_cumu)}
\NormalTok{mdl2}

\NormalTok{mdl1 }\OtherTok{\textless{}{-}} \FunctionTok{cor.test}\NormalTok{(sub3}\SpecialCharTok{$}\NormalTok{PC1, sub3}\SpecialCharTok{$}\NormalTok{taux\_cumu)}
\NormalTok{mdl1}
\FunctionTok{str}\NormalTok{(mdl1)}
\FunctionTok{summary}\NormalTok{(mdl1)}
\NormalTok{mdl3 }\OtherTok{\textless{}{-}} \FunctionTok{cor.test}\NormalTok{(sub3}\SpecialCharTok{$}\NormalTok{PC3, sub3}\SpecialCharTok{$}\NormalTok{taux\_cumu)}
\NormalTok{mdl3}

\FunctionTok{summary}\NormalTok{(mdl)}

\FunctionTok{library}\NormalTok{(nlme)}
\NormalTok{?gls}
         \FunctionTok{gls}\NormalTok{(divspe }\SpecialCharTok{\textasciitilde{}}\NormalTok{ loggrad\_urb}\SpecialCharTok{+}\NormalTok{grad\_agrimean, }\AttributeTok{method =} \StringTok{"ML"}\NormalTok{, }
\AttributeTok{corr=}\FunctionTok{corExp}\NormalTok{(}\FunctionTok{c}\NormalTok{(}\DecValTok{300000}\NormalTok{,}\FloatTok{0.7}\NormalTok{), }\AttributeTok{form=}\SpecialCharTok{\textasciitilde{}}\NormalTok{x\_lambert93}\SpecialCharTok{+}\NormalTok{y\_lambert93, }\AttributeTok{nugget=}\NormalTok{T), }
\AttributeTok{na.action =}\NormalTok{ na.omit, }\AttributeTok{data =}\NormalTok{ df)}
\end{Highlighting}
\end{Shaded}

\end{document}

### 2022-03-07 code/vaccination-indicators.Rmd
update for git

@@
     self_contained: no
-
+    keep_md: true
+    toc: true
+    toc_float: true
+  pdf_document: default
 ---
@@
 
-```{r results = 'hide'}
+```{r results = 'hide', fig.show='hide'}
 # Functions to discretize the data
@@
 
-vv <- dat.all[, "Unemployment_Benef"]
-plot(discretizeQ(vv, seq(0, 1, 0.1)), 
-     discretizeQ(vv, seq(0, 1, 0.5)))
+#vv <- dat.all[, "Unemployment_Benef"]
+#plot(discretizeQ(vv, seq(0, 1, 0.1)), 
+#     discretizeQ(vv, seq(0, 1, 0.5)))
 

### 2022-03-09 ms/ms.Rmd
first commit

---
title: "PassSanitaire"
author: "FD"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

load("../code/savevalues.RData")
```

The French domestic Pass Sanitaire did not solve vaccination inequities: a nationwide longitudinal study on `r round(totPopSize / 10^6)` million individuals

# Abstract

Context: The French sanitary pass led to an increase in vaccination rates in France, but spatial heterogeneities in vaccination rates are still striking [LG1]. To identify potential determinants of these heterogeneities and evaluate the the French sanitary pass' efficacy in reducing them, we used a data-driven approach on exhaustive nationwide data, gathering `r nIndicatorsAfterRemovingCorrMiss` socio-economic, political and geographic indicators.

Methods: We considered the association between being a district above the median value of the first-dose vaccination rates and being above the median value of each indicator at four time points: week `r format(as.Date(date1), "%W")`, (just before the sanitary pass announcement), week `r format(as.Date(date2), "%W")` (when the sanitary pass came fully into force), week `r format(as.Date(date3), "%W")` (end of the summer) and week `r format(as.Date(date4), "%W")` (end of data collection). We then considered the change over time of vaccination rates according to the XX most associated indicators, by deciles.

Results: The XX indicators most associated with vaccination rates were XX, XX, XX.

Conclusion: Our analysis reveals that, both before and after the introduction of the French sanitary pass, factors with the largest impact are related to poverty XX, XXX, XXX.

# Introduction

The rapid development of effective COVID-19 vaccines brought the hope of a rapid return to normalcy, but heterogeneous vaccination rates, both among countries because of inequitable distributions of doses [Usher21] and within countries [Caspi21, Murthy21], jeopardize epidemic control.

Hesitancy and hostility toward vaccination have been comparatively high in France in recent decades. It is particularly the case since the 2009-2010 vaccination campaign against pandemic flu, whose contested management in France was a tipping point that led to higher vaccine hesitancy and hostility [Ward19; Guimier2021]. 
The trend was confirmed with the COVID-19 pandemic [Spire21]: just before Covid-19 vaccines became available, intentions to get vaccinated were comparatively very low in France (44% of the respondents in [Wouters2021] in the Fall 2020; about 40% of respondent in [SantePubliqueFrance21] in December 2020). Acceptance of the COVID-19 vaccine however gradually grew during 2021 [SantePubliqueFrance22].
<!-- Lazarus21 does not talk directly about France -->

Spatial heterogeneties in vaccination rates have already been documented in France for previous vaccines. Vaccination coverage for the Hepatitis B vaccine and for the Measles-Mumps-Rubella vaccine has been lower in the South of France, and especially in the South-East of the country [Guimier21]. Distance to the central political power in Paris, as well as a sense of belonging to a local community with a strong cultural identity, have been put forward as potential explanations for this geographic gradient in vaccination rates [Guimier21].

Attitudes toward vaccination are also known to be influenced by social and territorial inequalities. Surveys conducted in 2020 in France showed that respondents with lower education [Schwarzinger21, Spire21], lower income levels or less trust in authorities [Spire21] were more likely to be hostile to COVID-19 vaccines. Whether differential intentions translated into effective differences in vaccination, as described in other countries [Caspi21, Murthy21], remained to be shown in France. (XX New Bajos Paper?)

By mid-July 2021, XX% of the eligible population in France had received a first dose, and the France was facing an epidemic wave due to the Delta variant. To speed up vaccination, President Macron announced on 12 July 2021 the implementation of a domestic "sanitary pass" (le passe sanitaire), which came fully into force on 9 August 2021. The "sanitary pass" was required in most cultural venues, for both indoor and outdoor dining and in health structures. This announcement led to an unprecedented demand for vaccination, which was celebrated internationally [Ref NYT?]. Vaccination rates climbed from 54% of the whole population (XX change into eligible) by 12 July 2021 to 69% on 4 September 2021. Because it targeted pay-for social activities, however, the "sanitary pass" was feared to have a limited impact on vaccination inequities.

This study aims to obtain further insights into the association between social inequities, vaccination and sanitary pass implementation in France using nationwide data.

Methods

The French state health insurance service (Assurance Maladie) provides public datasets of exhaustive weekly first-dose vaccination data at the district scale nationally and at the suburban scale for the Paris, Lyon, and Marseille metropolitan areas. Our data included 1552 districts in mainland France (63,601,670 individuals; median district size 22,705 inhabitants; interquartile range 6,282--39,128). We associated these data with 176 socioeconomic [JA2] and 5 geographic indicators at the same geographic scales from public datasets. We allocated those indicators into categories (Activity: 12 indicators; Employment: 41 indicators; Family: 27 indicators; Geography: 5 indicators; Housing: 35 indicators; Immigration: 1 indicator; Population: 26 indicators; Revenue: 15 indicators; School: 19 indicators)

We considered the association between being a district in the lowest quartile (25th percentile) of the first-dose vaccination rate and being above the median value of each indicator. We computed odds ratios and their 95% confidence intervals at three time points: week 27 (just before the sanitary pass announcement), week 31 (when the sanitary pass came fully into force), and week 35 (end of data collection). For the two indicators achieving the highest odds ratios, we computed vaccination levels for each indicator quartile on the same dates. Analyses were done using R (v4.0.3). To enhance odds-ratio visualization, we computed Manhattan plots giving odds-ratios and their confidence intervals by socioeconomic indicators categories.
For each week, the significance threshold is calculated by performing 1000 random permutations on the vaccination rate. Then we take the maximum OR calculated over every indicator for each permutation. Finally the threshold is fixed at the 950th value of the maximum OR sorted in ascending order.

### 2022-03-09 ms/ms.Rmd
results done

@@
 author: "FD"
-output: html_document
+output:
+  bookdown::html_document2:
+    self_contained: no
+    keep_md: true
+    number_sections: no
 ---
@@
 load("../code/savevalues.RData")
+load("../code/data_indicators.RData") 
 ```
@@
 
-Context: The French sanitary pass led to an increase in vaccination rates in France, but spatial heterogeneities in vaccination rates are still striking [LG1].
-To identify potential determinants of these heterogeneities and evaluate the the French sanitary pass' efficacy in reducing them, we used a data-driven approach on exhaustive nationwide data, gathering `r nIndicatorsAfterRemovingCorrMiss` socio-economic, political and geographic indicators.
+Context: Implemented during the Summer 2021, the French "Sanitary Pass" led to an increase in vaccination rates in France, but spatial heterogeneities in vaccination rates are still striking [LG1].
+It morphed into a "Vaccine Pass" in early 2022.
+To identify potential determinants of these heterogeneities and evaluate the French Sanitary and Vaccine Pass' efficacies in reducing them, we used a data-driven approach on exhaustive nationwide data, gathering `r nIndicatorsAfterRemovingCorrMiss` socio-economic, political and geographic indicators.
 
-Methods: We considered the association between being a district above the median value of the first-dose vaccination rates and being above the median value of each indicator at four time points: week `r format(as.Date(date1), "%W")`, (just before the sanitary pass announcement), week `r format(as.Date(date2), "%W")` (when the sanitary pass came fully into force), week `r format(as.Date(date3), "%W")` (end of the summer) and week `r format(as.Date(date4), "%W")` (end of data collection).
+Methods: We considered the association between being a district above the median value of the first-dose vaccination rates and being above the median value of each indicator at different time points: just before the sanitary pass announcement (week `r format(as.Date(datesAnalysis[1]), "%Y-W%W")`), just before the sanitary pass came into force (week `r format(as.Date(datesAnalysis[2]), "%Y-W%W")`) and one month after (week `r format(as.Date(datesAnalysis[3]), "%Y-W%W")`), and the equivalent dates for the vaccine pass (weeks `r format(as.Date(datesAnalysis[4:6]), "%Y-W%W")`).
 We then considered the change over time of vaccination rates according to the XX most associated indicators, by deciles.
@@
 Surveys conducted in 2020 in France showed that respondents with lower education [Schwarzinger21, Spire21], lower income levels or less trust in authorities [Spire21] were more likely to be hostile to COVID-19 vaccines.
-Whether differential intentions translated into effective differences in vaccination, as described in other countries [Caspi21, Murthy21], remained to be shown in France.
-(XX New Bajos Paper?)
+A survey conducted in July 2021 in France [Bajos2022] on close to 81000 participants indicated that unvaccinated respondents were more likely to have lower income and more likely to belong to racialised minorities than vaccinated ones.
+The survey also confirmed that mistrust in the government was fueling refusal to be vaccinated [Bajos2022].
+
+<!-- XX MOVE INTERNATIONAL COMPARISONS IN THE DISCUSSION Whether differential intentions translated into effective differences in vaccination, as described in other countries [Caspi21, Murthy21], remained to be shown in France.
+(XX New Bajos Paper?) -->
 
@@
 
-This study aims to obtain further insights into the association between social inequities, vaccination and sanitary pass implementation in France using nationwide data.
+This study aims to obtain further insights on the socio-economic, political and geographic factor associated with vaccination rates, and to evaluate the effect of the French domestic sanitary pass, by using nation-wide, exhaustive datasets.
 
-Methods
+# Methods
 
-The French state health insurance service (Assurance Maladie) provides public datasets of exhaustive weekly first-dose vaccination data at the district scale nationally and at the suburban scale for the Paris, Lyon, and Marseille metropolitan areas.
-Our data included 1552 districts in mainland France (63,601,670 individuals; median district size 22,705 inhabitants; interquartile range 6,282--39,128).
-We associated these data with 176 socioeconomic [JA2] and 5 geographic indicators at the same geographic scales from public datasets.
-We allocated those indicators into categories (Activity: 12 indicators; Employment: 41 indicators; Family: 27 indicators; Geography: 5 indicators; Housing: 35 indicators; Immigration: 1 indicator; Population: 26 indicators; Revenue: 15 indicators; School: 19 indicators)
+## Data
 
-We considered the association between being a district in the lowest quartile (25th percentile) of the first-dose vaccination rate and being above the median value of each indicator.
-We computed odds ratios and their 95% confidence intervals at three time points: week 27 (just before the sanitary pass announcement), week 31 (when the sanitary pass came fully into force), and week 35 (end of data collection).
-For the two indicators achieving the highest odds ratios, we computed vaccination levels for each indicator quartile on the same dates.
-Analyses were done using R (v4.0.3).
-To enhance odds-ratio visualization, we computed Manhattan plots giving odds-ratios and their confidence intervals by socioeconomic indicators categories.
-For each week, the significance threshold is calculated by performing 1000 random permutations on the vaccination rate.
-Then we take the maximum OR calculated over every indicator for each permutation.
-Finally the threshold is fixed at the 950th value of the maximum OR sorted in ascending order.
+<!-- Vaccination -->
+The French state health insurance service (Assurance Maladie) provides public datasets of vaccination rates in France.
+These datasets are based on aggregated individual data on beneficiaries of the national health insurance service who received health care in the past year.
+These exhaustive datasets are updated weekly, and are provided at the district scale nationally (EPCI: *Établissement public de coopération intercommunale*, an administrative level gathering multiple towns or cities) and at the suburban scale for the Paris, Lyon, and Marseille metropolitan areas.
+For this study, we focused on Metropolitain France, because vaccination rates are much lower in oversea localities, and because determinants of vaccination rates are likely to differ in oversea localities compared to metropolitain ones.
+Our dataset included `r sum(nlocalities)` districts (`r nlocalities["EPCI"]` EPCI and `r nlocalities["PLM"]` districts at the suburban scale in Paris, Lyon, Marseille).
+
+The vaccination dataset for mainland France encompasses about XX individuals (median district size XX, itq range XX).
+The vaccination data are available by age class: 00--19, 20--39, 40--54, 55--64, 65--74, 75 and over.
+Population sizes for each locality and each age class are also provided.
+These population sizes are updated monthly to account for individuals aging, potential residential moves, and deaths.
+
+<!-- Other data -->
+
+```{r, echo = FALSE}
+insee.indicators.names <- names(typesDataAll)[!is.element(names(typesDataAll), c("Geography", "Elections"))]
+
+tb <- typesDataNoCorr[!is.element(names(typesDataNoCorr), c("Geography", "Elections"))]
+output.INSEE <- ""
+for(i in 1:length(tb)) output.INSEE <- paste0(output.INSEE, names(tb)[i], ": n = ", tb[i], "; ")
+output.INSEE <- substr(output.INSEE, 1, nchar(output.INSEE)-2)
+```
+
+We paired these vaccination data with three other datasets gathering socio-economic, political and geographic variables.
+
+Socio-economic data are provided by the French national statistics institute (INSEE), and are available at the same administrative levels as the vaccination data.
+The different predictors are classified into `r length(insee.indicators.names)` categories (`r insee.indicators.names`).
+Latitude, longitude and surface data were extracted from maps datasets [ref OpenMaps].
+We calculated from them four additional geographic indicators: distance to Paris, relative position along a South-East--North-West gradient, relative position along a South-West--North-East gradient, and local population density.
+Our political dataset consisted of the results of the two round of the 2017 Presidential election in France, which we aggregated to reconstitute the same administrative levels as the vaccination dataset.
+This political dataset contains the proportions of votes for each of the 11 candidates of the first round, 2 candidates of the second round (Macron and Le Pen), and proportion of abstention at each round.
+
+These three datasets comprised `r nIndicatorsTot` indicators.
+We then removed those indicators with over `r round(thrMissingVals * 100)`% missing data, or with over `r thrCor` correlation with other indicators of the dataset, which left us with `r nIndicatorsAfterRemovingCorrMiss` indicators: `r sum(tb)` socio-economic indicators (`r output.INSEE`); `r typesDataNoCorr[is.element(names(typesDataNoCorr), c("Geography"))]` geographic indicators; `r typesDataNoCorr[is.element(names(typesDataNoCorr), c("Elections"))]` political indicators.
+
+## Analysis
+
+Vaccination was accessible to all adults in France after 27 May 2021.
+It opened to teenagers (12-17 year olds) on 15 June 2021, and to children (5-11 year olds) on 22 December 2021.
+Because of this differential accessibility of vaccines, and because vaccine passport rules also differed for non-adults, we excluded the 00-19 age class from our analysis, and focused on vaccination rates among 20+ year-old individuals (hereafter "adults").
+
+For each indicator in our dataset, at each of the four chosen dates (weeks `r format(as.Date(datesAnalysis), "%Y-W%W")`), we considered the association between living in a district above the median of a that indicator and individual first-dose vaccination rates among adults.
+Odds ratios (OR) were computed from the output of a logistic regression.
+To be able to compare predictors irrespective of the direction of the effect, we considered the maximum of `OR, 1/OR` (hereafter $\overline{OR}$).
+Vaccination data are at the individual level, and indicator data at the district level.
+For each date, we determined a significance threshold by computing odds ratios on `r nrep` random permutations of a predictor, and identifying the value of the XX 99% percentile odd ratios ($\overline{OR}$) of these permuted data.
+
+For representative indicators with the strongest association to vaccination data, we estimated age-adjusted vaccination rates among adults over time, for each decile of each indicator (treated as a factor).
+These estimations were obtained from a logistic model taking age class into account, and adult vaccination rates were computed on a standardized age distribution matching that of metropolitain France.
+
+All analysis code is available at XXX; analyses were done in `r R.Version()$version.string`.
+
+<!--
+
+- **27 mai 2021 (S21)** : toutes les personnes majeures peuvent prendre rendez-vous pour se faire vacciner en centre de vaccination pour des injections avec les vaccins Pfizer-BioNTech ou Moderna à compter du 31 mai 2021.
+- **15 juin 2021 (S24)** : les 12 à 17 ans inclus ans peuvent se faire vacciner avec le vaccin Pfizer-BioNTech en centre de vaccination.
+Le 24 juillet 2021, l'Agence européenne du médicament (EMA) a délivré une autorisation du vaccin Moderna sur lequel la HAS a rendu un avis favorable le 28 juillet.
+- **12 juillet 2021 (S28)** : annonce du président le la république concernant la mise en place du pass sanitaire.
+- **9 août 2021 (S32)** : mise en place de l'obligation du passe sanitaire dans les lieux concernés.
+- **1er septembre 2021 (S35)** : une campagne de rappel est mise en place pour stimuler le système immunitaire des plus vulnérables : les résidents d'EHPAD et d'USLD, les personnes de 65 ans et plus vivant à domicile, les personnes souffrant de comorbidité(s), les personnes atteintes de pathologies à haut risque de forme grave, les personnes ayant été vaccinées avec le vaccin Janssen.
+- **15 septembre 2021 (S37)** : l'obligation vaccinale concernerait tous les personnels des établissements de santé, établissements d'hébergement pour personnes âgées dépendantes (Ehpad) et établissements pour personnes en situation de handicap et tous les professionnels ou les bénévoles en contact avec des personnes âgées ou vulnérables, y compris à domicile.
+Cette mesure a fait l'objet d'un projet de loi relatif à la gestion de la crise sanitaire examiné par le Parlement depuis le 20 juillet 2021.
+
+-->
+
+# Results
+
+We investigated the associations between each of the `r nIndicatorsAfterRemovingCorrMiss` indicators and first-dose vaccination rates.
+Two indicators were among the top five most associated one at all time points (see Figure \@ref(fig:figManhattan)): the share of local income coming from unemployment benefits (`Unemployment_Benef`) and vote for Mr Asselineau (`Asselineau`).
+The three other most associated indicators did not change in the later dates that we considered, and were the proportion of immigrants in the district (`Immigrant`), the district's relative position along a North-West--South-East gradient (`NO-SE`) and the proportion of overcrowded household (`Overcrowding_rate`).
+
+GIVE NAMES OF NOT ASSOCIATED INDICATORS?
+
+GIVE VALUES IN A TABLE?
+
+```{r figManhattan, echo=FALSE, fig.height=9, fig.width=9, fig.cap="Manhattan plots of the Odds ratios for each of the indicator of our dataset, by date.
+Left column: around the Sanitary Pass implementation; right column: around the Vaccine Pass implementation.
+The top five odds ratios are labelled at each time point; the arrow next to the name indicates the direction of the effect.
+The gray rectangle corresponds to the 99% percentile of odds ratios in the permuted data; points falling in the rectangle are considered as non-significant."}
+load("../data/predictors.RData")
+load("../code/outLR.RData")
+source("../code/2_plot-manhattan.R")
+layout(matrix(1:6, ncol = 2))
+# PLOT
+plotManhattan(outLR, ntop = 5)
+```
+
+Our odds ratio calculations were based on a crude version of each indicator, which were dichotomized into values above or below the median of each indicator.
+To better visualize the effects (or lack thereof) of the sanitary and vaccine passes on vaccination rates over time, we computed age-adjusted vaccination rates over time, by decile of three of the most associated indicators, treated as factors (see Figure \@ref(fig:figOverTime)).
+While the Sanitary Pass led to an overall increase in vaccination rates, the Vaccine Pass did not affect the trend of change in vaccination rates.
+Heterogeneities in vaccination rates persisted after both types of pass, neatly ordered by decile of each indicator.
+
+```{r figOverTime, fig.height=10, fig.width=4, fig.cap="Age-adjusted vaccination rates among adults, over time, by decile of each indicator. ", echo = FALSE}
+load("../code/outTime.RData")
+source("../code/2_plot-overTime.R")
+layout(matrix(1:3, ncol = 1))
+plotPropTime(outA, plotDates = TRUE, plotGraduations = TRUE)
+```
+
+Finally, historically under-vaccinated areas in France stand out as being less vaccinated against Covid-19, in particular the South-East region.
+
+FIGURE MAP
+
+# Discussion

### 2022-03-09 code/2_plot-map.R
first commit

@@ -1,0 +1,220 @@
+#### PLOT MAP PREDICTOR ####
+plotMapVar <- function(varPred, byp = 0.1){
+  # varPred: name of the predictor
+  # byp: interval for discretization
+  # Global variables: datasets, map shapes
+  
+  # Build minimum dataframe with information on the variable
+  tmp <- data.frame(codgeo = dat.all$codgeo, pred = dat.all[, varPred])
+  # Discretize the predictor
+  tmp$pred.std <- discretizeQ(tmp$pred, prbs = seq(0, 1, by = byp))
+  # Add to geographic data
+  mergedFrance <- merge(france, tmp, by.x = "SIREN", by.y = "codgeo", all.x = TRUE)
+  
+  # Main map
+  mf_theme("default", mar = c(0, 0, 0, 0), bg = NA)
+  
+  # Map Parameters
+  eBB <- c(.5, .2, 0, 0)
+  h2 <- c(0.01, 0.275) # (ymin, ymax) of the metropoles
+  
+  # Color palette
+  nn <- 1/byp # number of types
+  palCat <- rev(met.brewer("Hiroshige", nn, type = "continuous"))
+  names(palCat) <- 1:nn
+  
+  brks <- quantile(tmp$pred, probs = seq(0, 1, by = byp), na.rm = TRUE)
+  
+  # Initialize map
+  mf_init(france, expandBB = eBB)
+  
+  # Rename variable
+  tit <- varPred
+  if(substr(tit, 1, 1) == "X") tit <- substr(tit, 2, nchar(tit))
+  
+  # Plot map
+  mf_map(mergedFrance, type = "choro", var = "pred", 
+         pal = palCat, breaks = brks,
+         border = gray(0, 0), add = TRUE, 
+         leg_pos = "topleft", leg_title = paste0(tit, ", discretized"), leg_no_data = "no data", leg_val_cex = 0.5, leg_val_rnd = 3)
+  
+  # Fill in PLM
+  plm <- france[is.element(france$SIREN, epci.PLM), ]
+  mf_map(plm, add = TRUE, border = gray(0, 0), col = gray(0.7))
+  
+  
+  # Add departements
+  mf_map(mdeps, type = "base", add = TRUE, col = gray(0, 0), lwd = 0.5, border = "black")
+  # Add regions
[…]

### 2022-03-10 ms/ms.Rmd
discussion and map

@@
 title: "PassSanitaire"
-author: "FD"
+author: ""
 output:
@@
     number_sections: no
+  bookdown::word_document2: 
+    number_sections: no
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+
+library("mapsf")
 
@@
 To speed up vaccination, President Macron announced on 12 July 2021 the implementation of a domestic "sanitary pass" (le passe sanitaire), which came fully into force on 9 August 2021.
+Presenting as a QR code, a long-term sanitary pass was obtained after full vaccination (two doses, or one in the case of a document Covid-19 infection previously), and a short-term version could be obtained with a negative Covid-19 test.
 The "sanitary pass" was required in most cultural venues, for both indoor and outdoor dining and in health structures.
@@
 Because it targeted pay-for social activities, however, the "sanitary pass" was feared to have a limited impact on vaccination inequities.
+By mid-December 2021, at the height of the winter Delta wave, and while the Omicron wave was looming, the French Prime Minister announced that the Sanitary Pass would become a Vaccine Pass, i.e.
+that a negative Covid-19 test would not provide a temporary QR code any longer for adults.
+The Vaccine Pass came into force on 24 January 2022.
 
@@
 Socio-economic data are provided by the French national statistics institute (INSEE), and are available at the same administrative levels as the vaccination data.
+We selected the most recent dataset available (year 2018).
 The different predictors are classified into `r length(insee.indicators.names)` categories (`r insee.indicators.names`).
@@
 
+The share of local income coming from unemployment benefits (`Unemployment_Benef`) and the proportion of overcrowded household (`Overcrowding_rate`) are two indicators linked to poverty.
+In 2017, less than $1\%$ of cast votes were for Mr Asselineau (`Asselineau`) in France; this candidate for instance proposed that France exits the European Union, leave the Euro zone and reinstall the Franc currency, and was a proponent of hydroxychloroquin and ivermectin during the Covid-19 pandemic, and publicly expressed doubts about the available Covid-19 vaccines.
+
 GIVE NAMES OF NOT ASSOCIATED INDICATORS?
@@
 Left column: around the Sanitary Pass implementation; right column: around the Vaccine Pass implementation.
-The top five odds ratios are labelled at each time point; the arrow next to the name indicates the direction of the effect.
+The top odds ratios are labelled at each time point; the arrow next to the name indicates the direction of the effect.
 The gray rectangle corresponds to the 99% percentile of odds ratios in the permuted data; points falling in the rectangle are considered as non-significant."}
@@
 
-```{r figOverTime, fig.height=10, fig.width=4, fig.cap="Age-adjusted vaccination rates among adults, over time, by decile of each indicator. ", echo = FALSE}
+```{r figOverTime, fig.height=8, fig.width=4, fig.cap="Age-adjusted vaccination rates among adults, over time, by decile of each indicator. ", echo = FALSE}
 load("../code/outTime.RData")
@@
 
+```{r figMap, fig.height=5, fig.width=4, fig.cap="Adult vaccination rates by district", echo = FALSE}
+source("../code/2_plot-map.R")
+source("../code/1_functions-adjustAges.R")
+load("../data/mapFiles_withDepReg.RData")
+load("../data/chefslieux.RData")
+# Choose date
+thedate <- datesAnalysis[6]
+# Vaccination data by age at that date
+tmpVacc <- vacc[vacc$date == thedate & vacc$classe_age != "TOUT_AGE", ]
+#tmpVacc2 <- vacc[vacc$date == thedate & vacc$classe_age == "TOUT_AGE", ]
+#tmpVacc2$taux_cumu <- tmpVacc2$taux_cumu_1_inj
+
+# Compute adult vaccination rate
+adultVaccinationRate <- adultVacc(tmpVacc)
+
+#plotMapVacc(adultVaccinationRate, thetitle = paste0("Adult vaccination rates on ", thedate), palName = "Hiroshige", byp = 5)
+
+# Compute mean vaccination rate
+meanVacc <- sum(adultVaccinationRate$n_cumu) / sum(adultVaccinationRate$population_carto)
+# Compute difference to max to center the color scale
+maxDiff <- max(c(max(adultVaccinationRate$taux_cumu) - meanVacc, meanVacc - min(adultVaccinationRate$taux_cumu)))
+
+plotMapVacc(adultVaccinationRate, thetitle = paste0("Adult vaccination rates on ", thedate), palName = "Hiroshige", byp = 2, zmin = floor(100*(meanVacc - maxDiff)), zmax = ceiling(100*(meanVacc + maxDiff)))
+
+#plotMapVacc(tmpVacc2, thetitle = paste0("Adult vaccination rates on ", date6))
+
+```
+
 # Discussion
+
+Our results, based on exhaustive national datasets, indicate that the French sanitary pass, and the later vaccine pass, did not solve Covid-19 vaccination heterogeneities, but instead crystallized them.
+Indicators most associated with vaccination rates were associated to poverty, immigration, and anti-establishment vote (or abstention).
+For instance, the odds for an adult to still be unvaccinated by the end of February 2021 are about $1.4$ <!-- extract value --> times higher when living in the districts with higher than median value share of income coming from unemployment benefits, and when living in the districts with lower than median value.
+
+The indicators associated to vaccination rates can be interpreted in the light of the dimensions of vaccine hesitancy [Ward2022].  
+A first reason for vaccine hesitancy is complacency: not fully perceiving the benefit of vaccination or the risks of severe disease.
+While in this case a sanitary or vaccine pass may convince complacent individuals to get vaccinated, it is less efficient if the associated constrain is low.
+As the French domestic pass was associated to pay-for activities (restaurants, tourism), its persuading effect could be limited among poorer populations, which may explain the association of lower vaccination rate with poverty in the data that we analyzed.
+A second reason for vaccine hesitancy is confidence, i.e.
+trust in the vaccine, in the health care system, and more generally in the government [Ward2022].
+A survey conducted in July 2021 in France confirmed that trust in the government and trust in scientists were associated to higher odds to be vaccinated [Bajos2022].
+Votes for Mr Asselineau can be interpreted as mistrust in the government (or more generally, against the establishment), and the association with lower vaccination rates can be interpreted as a lack of confidence.
+Among political indicators, the second strongest association is with abstention rates (higher abstention rates being associated to lower vaccination rates), again signaling higher distrust for institutions [Ward2020].
+Likewise, the lower vaccinations rates in the South-East of France can be interpreted as mistrust of the central government in Paris.
+Finally, a third reason for vaccine hesitancy is convenience, that is availability and accessibility of the vaccines [Ward2022].
+During the first half of 2021, vaccination rate in France was mostly constrained by dose availability.
+Vaccination slots were to be booked online, and there was no general system for sending individual invitations to get vaccinated.
+These accessibility issues may explain the association we find between lower vaccination rates and living in a district with a high proportion of immigrants, which may for instance reveal language barriers.
+BAJOS AND RACIALISED INDIV?
+
+Although presented in our study independently, the different indicators are linked, and their combinations affect vaccination rates.
+For instance, the effect of mistrust in the government on vaccination refusal was shown to be even stronger in poorer individuals than in richer points in a survey conducted in July 2021 in France [Bajos2022].
+
+Relative position of the district of residency along a North-West--South-East gradient is also associated with vaccination probability, the South-East being less vaccinated.
+This geographic feature, already documented for other kinds of vaccination [Guimier2021], have been shown to be the consequence of multiple determinants with a common consequence: a local climate of mistrust for the central Parisian power.
+Politically, anti-system votes (from the right as well as from the left) are traditionally concentrated in the South-East of France.
+Medically, General Practitioners (GPs) based in the South-East, and to a lesser extent those in the South-West, have been shown to tend to have a more negative opinion of vaccination than their colleagues practicing in the northern part of France [Gautier et al.
+2013].
+This greater skepticism influences GP practices and attitudes, resulting in a lesser degree of compliance with vaccination schedules than GPs in the northern half of France [Collange et al., 2015].
+Physical distance to the central government and institutions, based in Paris, coupled with a sense of belonging to a local community with a strong cultural identity, as is the case for example in the Marseille metropolis or in the Cévennes, play a role in indifference or mistrust towards institutions perceived as distant authorities [Guimier, 2021].
+Finally, in and around the Marseille metropolis, the image of a rebellious territory was reinforced since the first months of the epidemic in France through the hypermediatized Pr Didier Raoult.
+Based in Marseille, he was a promoter of a controversial treatment against Covid-19 based on hydroxychloroquine and azithromycin, and later held ambiguous positions regarding Covid-19 vaccination.
+He has become a local icon, thanks to his anti-system positions, and against the hostility of most of the medical world towards his work.
+All in all, around the city of Marseille, and more broadly in South-Eastern France, the climate of suspicion against Parisian institutions, which had long been rooted in the area, hardened during the Covid-19 crisis, and was associated with distrust of Covid-19 vaccines.
+
+<!-- Limitations -->
+In this study, we used a data-driven approach, i.e.
+we did not focus on indicators that we *a priori* thought to be associated with vaccination rate.
+While our vaccination data are at the individual level, the socio-economic, political and geographic indicators are at the district level, and must therefore be interpreted as such (e.g., we cannot not show that receiving unemployment benefits is associated with lower vaccination probability, but we find an association with lower vaccination probability and the fact of living in a district where a large share of income comes from unemployment benefits).
+Our data cover Metropolitain France, XX million individuals, and are real-world data: we consider realized vaccination rates and not intentions to be vaccinated.
+In addition, since our data are based on record of the national health insurance service, vaccination rates do not come from self-reported, and there is in theory no reporting bias.
+
+Although we interpreted our results through the lens of a classification of reasons for vaccine hesitancy, our data only concern realized vaccination rates, and not the associated intentions.
+According to a survey conducted in the Fall 2021, the introduction of the sanitary pass led to an increase in the share of individuals reporting being "angry they had to be vaccinated" [Ward2022].
+Conversely, we cannot tell why individuals who are still not vaccinated in February 2022 are so -- e.g., whether it is hesitancy, refusal, or accessibility issues.
+Given the implementation of the vaccination campaign in France, namely the absence of individual invitations to get vaccinated, the reliance on private online booking systems, it is still possible that, in spite of some local outreach efforts, vaccine accessibility remains an issue, and may explain at least part of the association of lower vaccination rates with poverty.
+
+By emphasizing a differentiated use of COVID-19 vaccination according to a socio-economic gradient, our study confirms the strong impact of social inequalities on COVID-19.
+The most deprived areas have already been shown to have been disproportionately infected and hospitalized during the pandemic [Jannot21, Bajos21].
+We show that poorer districts are also the least vaccinated and, hence, the most still at risk, despite the widely celebrated domestic sanitary pass.
+There is an urgent need to define new vaccination policies that truly address social inequities.
++ DEPOLITICIZE (Bajos/Ward)
+
+AUTRES POINTS DE DISCUSSION: distrust with promises of return to normal life (Summer 2021); changing conditions (inclusion of booster dose)

### 2022-03-17 code/vaccination-indicators.Rmd
code update

@@
 date2 <- "2021-08-08" # Just before pass sanitaire comes into force
-date3 <- "2021-08-29" # Before back to school
-date4 <- "2022-01-02" # Last date of the year
+date3 <- "2021-09-05" # One month after pass sanitaire
+date4 <- "2021-12-12" # Before pass vaccinal announcement
+date5 <- "2022-01-23" # Just before pass vaccinal came into force
+date6 <- "2022-02-20" # One month after pass sanitaires
+
+datesAnalysis <- c(date1, date2, date3, date4, date5, date6)
+
+date.SP.announcement <- "2021-07-12"
+date.SP.implementation <- "2021-08-09"
+date.VP.announcement <- "2021-12-16"
+date.VP.implementation <- "2022-01-24"
+
 ```
@@
 
-```{r}
+```{r computationAcrossMedianComparisons}
 if(runComputations){
@@
   parmsLR <- expand.grid(varPred = names(dat.nocorr)[-1], 
-                         thedate = c(date1, date2, date3, date4), 
+                         thedate = datesAnalysis, 
                          predTransform = "discretize_factor", 
@@
   # Base combination of parameters
-  tmpparmsPerm <- expand.grid(varPred = "French_nlty", 
-                              thedate = c(date1, date2, date3, date4), 
+  tmpparmsPerm <- expand.grid(varPred = "Abstention", 
+                              thedate = datesAnalysis, 
                               predTransform = "discretize_factor", 
@@
 
+```{r eval = FALSE}
+# Elections
+tmpPRE <- outLR[is.element(outLR$typePred, "PRE") & outLR$permutation == FALSE, c("varPred", "thedate", "OR", "OR.abs")]
+tmpPRE[order(tmpPRE$OR.abs, decreasing = TRUE), ]
+```
+
 ## By deciles, quantitatively, adjusting ages
 
-```{r}
+```{r computationsByDeciles}
 if(runComputations){
@@
   parmsDec <- expand.grid(varPred = names(dat.nocorr)[-1], 
-                          thedate = c(date1, date2, date3, date4), 
+                          thedate = datesAnalysis, 
                           predTransform = "discretize", 
@@
   # Base combination of parameters
-  tmpparmsPerm <- expand.grid(varPred = "French_nlty", 
-                              thedate = c(date1, date2, date3, date4), 
+  tmpparmsPerm <- expand.grid(varPred = "Abstention", 
+                              thedate = datesAnalysis, 
                               predTransform = "discretize", 
@@
 
-```{r}
+```{r computationsOverTime}
 if(runComputations){
@@
 
+## Indicators
+
 ```{r}
@@
 
+## Vaccination
+
+```{r}
+# Choose date
+thedate <- date6
+# Vaccination data by age at that date
+tmpVacc <- vacc[vacc$date == thedate & vacc$classe_age != "TOUT_AGE", ]
+#tmpVacc2 <- vacc[vacc$date == thedate & vacc$classe_age == "TOUT_AGE", ]
+#tmpVacc2$taux_cumu <- tmpVacc2$taux_cumu_1_inj
+
+# Compute adult vaccination rate
+adultVaccinationRate <- adultVacc(tmpVacc)
+
+#plotMapVacc(adultVaccinationRate, thetitle = paste0("Adult vaccination rates on ", thedate), palName = "Hiroshige", byp = 5)
+
+# Compute mean vaccination rate
+meanVacc <- sum(adultVaccinationRate$n_cumu) / sum(adultVaccinationRate$population_carto)
+# Compute difference to max to center the color scale
+maxDiff <- max(c(max(adultVaccinationRate$taux_cumu) - meanVacc, meanVacc - min(adultVaccinationRate$taux_cumu)))
+
+plotMapVacc(adultVaccinationRate, thetitle = paste0("Adult vaccination rates on ", thedate), palName = "Hiroshige", byp = 2, zmin = floor(100*(meanVacc - maxDiff)), zmax = ceiling(100*(meanVacc + maxDiff)))
+
+#plotMapVacc(tmpVacc2, thetitle = paste0("Adult vaccination rates on ", date6))
+
+```
+
+# Compute values for the paper
+
+```{r}
+head(vacc)
+## Population size
+# Note: DROMs have already been excluded when loading the `vacc` dataset
+totPopSize <- sum(vacc[vacc$date == date2 & vacc$classe_age == "TOUT_AGE", "population_carto"])
+totPopSize.adults <- sum(vacc[vacc$date == date2 & vacc$classe_age != "TOUT_AGE" & vacc$classe_age != "00-19", "population_carto"])
+
+## Indicators
+nIndicatorsTot <- ncol(dat.all[, ])
+nIndicatorsAfterRemovingCorrMiss <- ncol(dat.nocorr[, -1])
+
+tmp <- vacc[vacc$date == date1 & vacc$classe_age == "TOUT_AGE", ]
+nlocalities <- table(nchar(tmp$codgeo))
+names(nlocalities) <- c("PLM", "EPCI")
+
+```
+
+```{r}
+# Population size
+computeTotPop <- function(thedate){
+  tmp <- vacc[vacc$date == thedate & vacc$classe_age == "TOUT_AGE", ]
+  # Make sure to have the localities we want
+  sub <- merge(tmp, data.frame(codgeo = dat.all$codgeo), by = "codgeo")
+  c(sum(sub$population_carto, na.rm = TRUE), sum(tmp$population_carto, na.rm = TRUE))
+}
+
+rm(thedate)
+dts <- sort(unique(vacc$date))
+pops <- as.data.frame(t(vapply(dts, computeTotPop, FUN.VALUE = c(1, 2))))
+names(pops) <- c("totPop.noNALoc", "totPop")
+pops
+data.frame(date = dts, population = pops)
+
+tmp <- vacc[vacc$codgeo == "75115" & vacc$classe_age == "TOUT_AGE", c("date", "population_carto")]
+tmp
+
+tmp <- vacc[vacc$codgeo == "75115" & vacc$classe_age == "20-39", c("date", "population_carto")]
+tmp
+
+# Problem: total population size is constant, seems like population size is not updated in the dataset? 
+```
+
+```{r}
+
+# Global vaccination rate
+computeGlobalVacc <- function(thedate, adults = TRUE){
+  if(adults){
+      tmp <- vacc[vacc$date == thedate & 
+                    vacc$classe_age != "TOUT_AGE" & 
+                    vacc$classe_age != "00-19", ]
+  }else{
+      tmp <- vacc[vacc$date == thedate & vacc$classe_age == "TOUT_AGE", ]
+  }
+  # Make sure to have the localities we want
+  sub <- merge(tmp, data.frame(codgeo = dat.all$codgeo), by = "codgeo")
+
+  # Compute total populations
+  totVacc <- sum(sub$effectif_cumu_1_inj, na.rm = TRUE)
+  totPop <- sum(sub$population_carto, na.rm = TRUE)
+  c(totVacc/totPop, totVacc, totPop)
+}
+
+txVaccAdults <- as.data.frame(t(vapply(dts, computeGlobalVacc, FUN.VALUE = c(1, 2, 3))))
+txVaccTot <- as.data.frame(t(vapply(dts, computeGlobalVacc, FUN.VALUE = c(1, 2, 3), adults = FALSE)))
+
+names(txVaccAdults) <- names(txVaccTot) <- c("txVacc", "nVacc", "nTot")
+txVaccAdults$date <- rownames(txVaccAdults)
+txVaccTot$date <- rownames(txVaccTot)
+
+plot(as.Date(txVaccAdults$date), txVaccAdults$txVacc, ylim = c(0, 1), xlim = c(as.Date("2021-05-01"), as.Date("2022-02-01")), type = "l")
+```
+
+Compute district size distribution
+
+```{r}
+tmp <- vacc[vacc$date == "2022-01-02" & vacc$classe_age == "TOUT_AGE", ]
+# Get the ones for which we have data
+tmpp <- merge(tmp, data.frame(codgeo = dat.all$codgeo), by = "codgeo")
+
+popSizeDistribMedian <- median(tmpp$population_carto)
+popSizeDistribMedian
+
+popSizeDistrib <- quantile(tmpp$population_carto, probs = c(0.25, 0.5, 0.75))
+popSizeDistrib["50%"]
+
+```
+
+```{r}
+# max ORs
+maxOR.Unemployment_Benef <- outLR[outLR$varPred == "Unemployment_Benef" & outLR$thedate == max(outLR$thedate), "OR.abs"]
+```
+
+Export
+
+```{r}
+save(totPopSize, totPopSize.adults, 
+     nIndicatorsTot, nIndicatorsAfterRemovingCorrMiss, 
+     datesAnalysis,
+     nlocalities, 
+     nrep,
+     date.SP.announcement, date.SP.implementation, date.VP.announcement, date.VP.implementation, 
+     dicPred, dic.fullpred,
+     vacc,
+     epci.PLM,
+     txVaccAdults, 
+     txVaccTot,
+     popSizeDistrib, 
+     pops, 
+     maxOR.Unemployment_Benef,
+     file = "savevalues.RData")
+
+```
+
 # Essais
@@
 
-v <- dat.all[, c("codgeo", "French_nlty")]
-vx <- v[which(is.na(v$French_nlty)), ]
+v <- dat.all[, c("codgeo", "Abstention")]
+vx <- v[which(is.na(v$Abstention)), ]
 vx

### 2022-03-17 code/0_INSEE_predictors.R

@@ -12,7 +12,7 @@ sortData <- FALSE
 
 # Threshold for correlation in the variables
 # Variables with absolute correlation above this threshold are removed from the analysis
-thrCor <- 0.95
+thrCor <- 0.9
 
 # Threshold for missing values
 # We will not consider variables with more than this threshold of missing values
@@ -290,4 +290,21 @@ if(sortData){
 
 # Export the result
 save(dat.all, dat.nocorr, dicPred, dic.fullpred, colClass, file = "../data/predictors.RData")
+
+typesDataAll <- table(dic.fullpred[dicPred[names(dat.all[, -1])]])
+typesDataNoCorr <- table(dic.fullpred[dicPred[names(dat.nocorr[, -1])]])
+
+sum(typesDataNoCorr[!is.element(names(typesDataNoCorr), c("Geography", "Elections"))])
+
+tb <- typesDataNoCorr[!is.element(names(typesDataNoCorr), c("Geography", "Elections"))]
+for(i in 1:length(tb)) cat(paste0(names(tb)[i], ": n = ", tb[i], "; "))
+
+
+names(dat.nocorr[, -1])[dic.fullpred[dicPred[names(dat.nocorr[, -1])]] == "Geography"]
+names(dat.all[, -1])[dic.fullpred[dicPred[names(dat.all[, -1])]] == "Geography"]
+
+names(dat.nocorr[, -1])[dic.fullpred[dicPred[names(dat.nocorr[, -1])]] == "Elections"]
+names(dat.all[, -1])[dic.fullpred[dicPred[names(dat.all[, -1])]] == "Elections"]
+
+save(thrCor, thrMissingVals, typesDataAll, typesDataNoCorr, file = "data_indicators.RData")
 

### 2022-03-17 code/2_plot-manhattan.R

@@ -7,7 +7,7 @@ pal <- pal[c(1, 6, 2, 7, 3, 8, 4, 9, 5, 10)]
 
 pal <- c("#a6cee3", "#e31a1c", "#1f78b4", "#fdbf6f", "#b2df8a", "#ff7f00", "#33a02c", "#cab2d6", "#fb9a99", "#6a3d9a")
 names(pal) <- unique(dicPred[names(dat.nocorr[-1])])
-plot(1:10, col = pal, cex = 2, pch = 15)
+# plot(1:10, col = pal, cex = 2, pch = 15)
 
 colPerm <- gray(0, 0.4)
 

### 2022-03-17 code/2_plot-map.R

@@ -112,6 +112,8 @@ plotMapVacc <- function(tabVacc, byp = 2.5, zmin = NA, zmax = NA, thetitle = "Ad
     # byp: interval for discretization
   # Global variables: datasets, map shapes
   
+  layout(matrix(c(1, 1, 1, 2, 3, 4), byrow = TRUE, ncol = 3), heights = c(3, 1))
+  
   tabVacc$pourcentVacc <- tabVacc$taux_cumu * 100
   
   # Add to geographic data
@@ -128,7 +130,8 @@ plotMapVacc <- function(tabVacc, byp = 2.5, zmin = NA, zmax = NA, thetitle = "Ad
   }
   
   # Map Parameters
-  eBB <- c(.5, .2, 0, 0)
+#  eBB <- c(.5, .2, 0, 0)
+  eBB <- c(0, 0.2, 0, 0)
   h2 <- c(0.01, 0.275) # (ymin, ymax) of the metropoles
   
   # Color palette
@@ -180,7 +183,7 @@ plotMapVacc <- function(tabVacc, byp = 2.5, zmin = NA, zmax = NA, thetitle = "Ad
   marMet <- c(0, 0, .8, 0) # margin
   
   # PARIS
-  mf_inset_on(fig = c(0, 0.33, h2))
+#  mf_inset_on(fig = c(0, 0.33, h2))
   mf_theme(mar = marMet)
   paris <- tca[is.element(substr(tca$insee, 1,2), c("75", "91", "92", "93", "94", "95")), ]
   paris <- merge(paris, tabVacc, by.x = "insee", by.y = "codgeo", all.x = TRUE)
@@ -190,10 +193,10 @@ plotMapVacc <- function(tabVacc, byp = 2.5, zmin = NA, zmax = NA, thetitle = "Ad
          leg_pos = "n")
   mf_title(txt = "Métropole du Grand Paris", pos = "center", tab = FALSE, bg = NA, 
            fg = "black", cex = .65, line = .8)
-  mf_inset_off()
+#  mf_inset_off()
   
   # LYON
-  mf_inset_on(fig = c(0.33, 0.66, h2))
+#  mf_inset_on(fig = c(0.33, 0.66, h2))
   mf_theme(mar = marMet)
   
   lyon <- tca[is.element(substr(tca$insee, 1,2), c("69")),]
[…]

### 2022-03-17 code/2_plot-overTime.R

@@ -1,6 +1,6 @@
 
 
-plotPropTime <- function(out){
+plotPropTime <- function(out, plotDates = FALSE, plotGraduations = FALSE){
   # out table of results, with parameter values
   
   # Define color palette
@@ -21,6 +21,13 @@ plotPropTime <- function(out){
     axis(2)
     axis(4)
     
+    if(plotGraduations){
+      for(i in seq(0, 1, by = 0.1)){
+        par(xpd = FALSE)
+        abline(h = i, col = gray(0.8))
+      }
+    }
+    
     # Subset of the data for this predictor
     sub <- out[out$varPred == varPred, ]
     
@@ -29,8 +36,28 @@ plotPropTime <- function(out){
       lines(as.Date(sub$thedate), sub[, paste0("V", i)], col = palCat[i], lwd = 2)
     }
     
+    # Show dates
+    if(plotDates){
+      par(xpd = FALSE)
+      abline(v = as.Date(date.SP.announcement), lty = 2)
+      abline(v = as.Date(date.SP.implementation))
+      
+      abline(v = as.Date(date.VP.announcement), lty = 2)
+      abline(v = as.Date(date.VP.implementation))
+      
+      par(xpd = TRUE)
+      yt <- 0.05
+      cext <- 0.75
+      text(x = c(as.Date(date.SP.announcement), as.Date(date.VP.announcement)), y = rep(yt, 2), adj = c(1, 0.5), labels = "announcement ", cex = cext)
+      text(x = c(as.Date(date.SP.implementation), as.Date(date.VP.implementation)), y = rep(yt, 2), adj = c(0, 0.5), labels = " implementation", cex = cext)
+      yt2 <- yt + 0.0
+      cext2 <- 0.9
+      text(x = mean(as.Date(c(date.SP.announcement, date.SP.implementation))), y = yt2, labels = "Sanitary\nPass", cex = cext2, adj = c(0.5, 0.5))
+      text(x = mean(as.Date(c(date.VP.announcement, date.VP.implementation))), y = yt2, labels = "Vaccine\nPass", cex = cext2, adj = c(0.5, 0.5))
+    }
+
     # Add legend
-    legend("bottomright", col = palCat, legend = paste(c("0-10%", 
+    legend("right", col = palCat, legend = paste(c("0-10%", 
                                                          "10-20%", 
                                                          "20-30%", 
                                                          "30-40%", 
@@ -40,7 +67,10 @@ plotPropTime <- function(out){
[…]

### 2022-03-17 ms/ms.Rmd
update ms

@@
     number_sections: no
+bibliography: VaccinationInequalities.bib
+
 ---
@@
 
-The French domestic Pass Sanitaire did not solve vaccination inequities: a nationwide longitudinal study on `r round(totPopSize / 10^6)` million individuals
+The French domestic Pass Sanitaire did not solve vaccination inequities: a nationwide longitudinal study on `r round(pops[nrow(pops), 1] / 10^6, 1)` million individuals
 
@@
 
-Results: The XX indicators most associated with vaccination rates were XX, XX, XX.
+Results: The indicators most associated with vaccination rates were the share of local income coming from unemployment benefits, the proportion of immigrants in the district, and vote for a fringe candidate at the 2017 Presidential election (XXX revoir description Asselineau).
+Vaccination rate also follow a marked North-West -- South East gradient, with lower vaccination coverage in the South-East of France.
 
-Conclusion: Our analysis reveals that, both before and after the introduction of the French sanitary pass, factors with the largest impact are related to poverty XX, XXX, XXX.
+Conclusion: Our analysis reveals that, both before and after the introduction of the French sanitary pass, factors with the largest impact are related to poverty, immigration, and trust in the government XXX Check if you agree.
 
@@
 
-The rapid development of effective COVID-19 vaccines brought the hope of a rapid return to normalcy, but heterogeneous vaccination rates, both among countries because of inequitable distributions of doses [Usher21] and within countries [Caspi21, Murthy21], jeopardize epidemic control.
+The rapid development of effective COVID-19 vaccines brought the hope of a rapid return to normalcy, but heterogeneous vaccination rates, both among countries because of inequitable distributions of doses [@usherBeautifulIdeaHow2021] and within countries [@caspiSocioeconomicDisparitiesCOVID192021; @murthyDisparitiesCOVID19Vaccination2021], jeopardize epidemic control.
 
-Hesitancy and hostility toward vaccination have been comparatively high in France in recent decades.
-It is particularly the case since the 2009-2010 vaccination campaign against pandemic flu, whose contested management in France was a tipping point that led to higher vaccine hesitancy and hostility [Ward19; Guimier2021].
-The trend was confirmed with the COVID-19 pandemic [Spire21]: just before Covid-19 vaccines became available, intentions to get vaccinated were comparatively very low in France (44% of the respondents in [Wouters2021] in the Fall 2020; about 40% of respondent in [SantePubliqueFrance21] in December 2020).
-Acceptance of the COVID-19 vaccine however gradually grew during 2021 [SantePubliqueFrance22].
+Hesitancy and hostility toward vaccination have been comparatively high in France in recent decades [@europeancommission.directorategeneralforhealthandfoodsafety.StateVaccineConfidence2018].
+It is particularly the case since the 2009-2010 vaccination campaign against pandemic flu, the contested management of which in France was a tipping point that led to higher vaccine hesitancy and hostility [@guimierResistancesFrancaisesAux2021; @wardVaccineHesitancyCoercion2019].
+The trend was confirmed with the COVID-19 pandemic [@lindholtPublicAcceptanceCOVID192021;  @spireSocialInequalitiesHostility2021]: just before Covid-19 vaccines became available, intentions to get vaccinated were comparatively very low in France (44% of the respondents in [@woutersChallengesEnsuringGlobal2021] in the Fall 2020; about 40% of respondent in XXX [@santepubliquefranceCoviPrevEnquetePour2021] (XXX TODO clean citation) in December 2020).
+Acceptance of the COVID-19 vaccine however gradually grew during 2021 XXX [@santepubliquefranceCoviPrevEnquetePour2021].
 <!-- Lazarus21 does not talk directly about France -->
@@
 Spatial heterogeneties in vaccination rates have already been documented in France for previous vaccines.
-Vaccination coverage for the Hepatitis B vaccine and for the Measles-Mumps-Rubella vaccine has been lower in the South of France, and especially in the South-East of the country [Guimier21].
-Distance to the central political power in Paris, as well as a sense of belonging to a local community with a strong cultural identity, have been put forward as potential explanations for this geographic gradient in vaccination rates [Guimier21].
+Vaccination coverage for the Hepatitis B vaccine and for the Measles-Mumps-Rubella vaccine has been lower in the South of France, and especially in the South-East of the country [@guimierResistancesFrancaisesAux2021].
+Distance to the central political power in Paris, as well as a sense of belonging to a local community with a strong cultural identity, have been put forward as potential explanations for this geographic gradient in vaccination rates [@guimierResistancesFrancaisesAux2021].
 
 Attitudes toward vaccination are also known to be influenced by social and territorial inequalities.
-Surveys conducted in 2020 in France showed that respondents with lower education [Schwarzinger21, Spire21], lower income levels or less trust in authorities [Spire21] were more likely to be hostile to COVID-19 vaccines.
-A survey conducted in July 2021 in France [Bajos2022] on close to 81000 participants indicated that unvaccinated respondents were more likely to have lower income and more likely to belong to racialised minorities than vaccinated ones.
-The survey also confirmed that mistrust in the government was fueling refusal to be vaccinated [Bajos2022].
+Surveys conducted in 2020 in France showed that respondents with lower education [@schwarzingerCOVID19VaccineHesitancy2021, @spireSocialInequalitiesHostility2021], lower income levels or less trust in authorities [@spireSocialInequalitiesHostility2021; @lindholtPublicAcceptanceCOVID192021] were more likely to be hostile to COVID-19 vaccines.
+A survey conducted in July 2021 in France [@bajosWhenMistrustGovernment2022] on close to 81000 participants indicated that unvaccinated respondents were more likely to have lower income and more likely to belong to racialised minorities than vaccinated ones.
+The survey also confirmed that mistrust in the government was fueling refusal to be vaccinated [@bajosWhenMistrustGovernment2022].
 
 <!-- XX MOVE INTERNATIONAL COMPARISONS IN THE DISCUSSION Whether differential intentions translated into effective differences in vaccination, as described in other countries [Caspi21, Murthy21], remained to be shown in France.
-(XX New Bajos Paper?) -->
+-->
 
-By mid-July 2021, XX% of the eligible population in France had received a first dose, and the France was facing an epidemic wave due to the Delta variant.
+By mid-July 2021, France was facing an epidemic wave due to the Delta variant.
 To speed up vaccination, President Macron announced on 12 July 2021 the implementation of a domestic "sanitary pass" (le passe sanitaire), which came fully into force on 9 August 2021.
-Presenting as a QR code, a long-term sanitary pass was obtained after full vaccination (two doses, or one in the case of a document Covid-19 infection previously), and a short-term version could be obtained with a negative Covid-19 test.
+Presenting as a QR code, a long-term sanitary pass was obtained after full vaccination (two doses, or only one dose in the case of a documented previous Covid-19 infection), and a short-term version could be obtained with a negative Covid-19 test.
 The "sanitary pass" was required in most cultural venues, for both indoor and outdoor dining and in health structures.
-This announcement led to an unprecedented demand for vaccination, which was celebrated internationally [Ref NYT?].
-Vaccination rates climbed from 54% of the whole population (XX change into eligible) by 12 July 2021 to 69% on 4 September 2021.
+This announcement led to an unprecedented demand for vaccination [@oliu-bartonEffectCOVIDCertificates2022], which was celebrated internationally XXX [Ref quel article?].
+Vaccination rates climbed from about `r round(100 * txVaccAdults[txVaccAdults$date == "2021-07-11", "txVacc"])`% of the population over 20 years old by 11 July 2021 (`r round(100 * txVaccTot[txVaccAdults$date == "2021-07-11", "txVacc"])`% of all ages) to `r round(100 * txVaccAdults[txVaccAdults$date == "2021-09-05", "txVacc"])` on 5 September 2021 (`r round(100 * txVaccTot[txVaccTot$date == "2021-09-05", "txVacc"])` of all ages).
 Because it targeted pay-for social activities, however, the "sanitary pass" was feared to have a limited impact on vaccination inequities.
 By mid-December 2021, at the height of the winter Delta wave, and while the Omicron wave was looming, the French Prime Minister announced that the Sanitary Pass would become a Vaccine Pass, i.e.
-that a negative Covid-19 test would not provide a temporary QR code any longer for adults.
+that a negative Covid-19 test would not provide a temporary QR code any longer for adults -- making vaccination implicitly mandatory in France.
 The Vaccine Pass came into force on 24 January 2022.
@@
 These exhaustive datasets are updated weekly, and are provided at the district scale nationally (EPCI: *Établissement public de coopération intercommunale*, an administrative level gathering multiple towns or cities) and at the suburban scale for the Paris, Lyon, and Marseille metropolitan areas.
-For this study, we focused on Metropolitain France, because vaccination rates are much lower in oversea localities, and because determinants of vaccination rates are likely to differ in oversea localities compared to metropolitain ones.
-Our dataset included `r sum(nlocalities)` districts (`r nlocalities["EPCI"]` EPCI and `r nlocalities["PLM"]` districts at the suburban scale in Paris, Lyon, Marseille).
+For this study, we focused on mainland France, because vaccination rates are much lower in oversea localities, and because determinants of vaccination rates are likely to differ in oversea localities compared to mainland ones.
+Our dataset included `r sum(nlocalities)` districts (`r nlocalities["EPCI"]` EPCIs and `r nlocalities["PLM"]` districts at the suburban scale in Paris, Lyon, Marseille).
 
-The vaccination dataset for mainland France encompasses about XX individuals (median district size XX, itq range XX).
+The vaccination dataset for mainland France encompasses about `r round(pops[nrow(pops), 1] / 10^6, 1)` million individuals (median district size `r round(popSizeDistrib["50%"])`, interquartile range `r round(popSizeDistrib["25%"])`--`r round(popSizeDistrib["75%"])`).
 The vaccination data are available by age class: 00--19, 20--39, 40--54, 55--64, 65--74, 75 and over.
@@
 These population sizes are updated monthly to account for individuals aging, potential residential moves, and deaths.
+XXX TODO: Demander pourquoi les tailles de pop sont constantes au cours du temps
 
@@
 The different predictors are classified into `r length(insee.indicators.names)` categories (`r insee.indicators.names`).
-Latitude, longitude and surface data were extracted from maps datasets [ref OpenMaps].
+Latitude, longitude and surface data were extracted from open geographic data.
 We calculated from them four additional geographic indicators: distance to Paris, relative position along a South-East--North-West gradient, relative position along a South-West--North-East gradient, and local population density.
@@
 To be able to compare predictors irrespective of the direction of the effect, we considered the maximum of `OR, 1/OR` (hereafter $\overline{OR}$).
-Vaccination data are at the individual level, and indicator data at the district level.
-For each date, we determined a significance threshold by computing odds ratios on `r nrep` random permutations of a predictor, and identifying the value of the XX 99% percentile odd ratios ($\overline{OR}$) of these permuted data.
+Note that vaccination data are at the individual level, and indicator data at the district level.
+For each date, we determined a significance threshold by computing odds ratios on `r nrep` random permutations of a predictor, and identifying the value of the 99% percentile odd ratios ($\overline{OR}$) of these permuted data.
 
 For representative indicators with the strongest association to vaccination data, we estimated age-adjusted vaccination rates among adults over time, for each decile of each indicator (treated as a factor).
-These estimations were obtained from a logistic model taking age class into account, and adult vaccination rates were computed on a standardized age distribution matching that of metropolitain France.
+These estimations were obtained from a logistic model taking age class into account, and adult vaccination rates were computed on a standardized age distribution matching that of mainland France.
 
@@
 Two indicators were among the top five most associated one at all time points (see Figure \@ref(fig:figManhattan)): the share of local income coming from unemployment benefits (`Unemployment_Benef`) and vote for Mr Asselineau (`Asselineau`).
-The three other most associated indicators did not change in the later dates that we considered, and were the proportion of immigrants in the district (`Immigrant`), the district's relative position along a North-West--South-East gradient (`NO-SE`) and the proportion of overcrowded household (`Overcrowding_rate`).
+The three other most associated indicators did not change in the later dates that we considered, and were the proportion of immigrants in the district (`Immigrant`), the district's relative position along a North-West--South-East gradient (`NO-SE`) and the proportion of overcrowded households (`Overcrowding_rate`).
 
-The share of local income coming from unemployment benefits (`Unemployment_Benef`) and the proportion of overcrowded household (`Overcrowding_rate`) are two indicators linked to poverty.
-In 2017, less than $1\%$ of cast votes were for Mr Asselineau (`Asselineau`) in France; this candidate for instance proposed that France exits the European Union, leave the Euro zone and reinstall the Franc currency, and was a proponent of hydroxychloroquin and ivermectin during the Covid-19 pandemic, and publicly expressed doubts about the available Covid-19 vaccines.
+The share of local income coming from unemployment benefits (`Unemployment_Benef`) and the proportion of overcrowded households (`Overcrowding_rate`) are two indicators linked to poverty.
+Votes for Mr Asselineau (`Asselineau`) represented a minority of cast votes in 2017 in France (less than $1\%$ overall).
+This candidate for instance proposed that France exits the European Union, leave the Euro zone and reinstall the Franc currency; he was a proponent of hydroxychloroquin and ivermectin during the Covid-19 pandemic, and publicly expressed doubts about the available Covid-19 vaccines.
 
-GIVE NAMES OF NOT ASSOCIATED INDICATORS?
+XXX GIVE NAMES OF NOT ASSOCIATED INDICATORS?
 
-GIVE VALUES IN A TABLE?
+XXX GIVE VALUES IN A TABLE?
 
@@
 While the Sanitary Pass led to an overall increase in vaccination rates, the Vaccine Pass did not affect the trend of change in vaccination rates.
-Heterogeneities in vaccination rates persisted after both types of pass, neatly ordered by decile of each indicator.
+Heterogeneities in vaccination rates persisted after both types of pass; vaccination rates appear neatly ordered by decile of each indicator.
 
-```{r figOverTime, fig.height=8, fig.width=4, fig.cap="Age-adjusted vaccination rates among adults, over time, by decile of each indicator. ", echo = FALSE}
+```{r figOverTime, fig.height=8, fig.width=4, fig.cap="Age-adjusted vaccination rates among adults, over time, by decile of each indicator (presented by a color gradient).
+The dates of announcements and implementations of the sanitary and vaccine pass are indicated near the horizontal axes.", echo = FALSE}
 load("../code/outTime.RData")
@@
 
-Finally, historically under-vaccinated areas in France stand out as being less vaccinated against Covid-19, in particular the South-East region.
-
-FIGURE MAP
+Finally, historically under-vaccinated areas in France stand out as being less vaccinated against Covid-19, in particular the South-East region (see Figure \@ref(fig:figMap)).
 
@@
 Indicators most associated with vaccination rates were associated to poverty, immigration, and anti-establishment vote (or abstention).
-For instance, the odds for an adult to still be unvaccinated by the end of February 2021 are about $1.4$ <!-- extract value --> times higher when living in the districts with higher than median value share of income coming from unemployment benefits, and when living in the districts with lower than median value.
+For instance, the odds for an adult to still be unvaccinated by the end of February 2021 are about `r round(maxOR.Unemployment_Benef, 1)` times higher when living in the districts with higher than median value share of income coming from unemployment benefits, and when living in the districts with lower than median value.
 
-The indicators associated to vaccination rates can be interpreted in the light of the dimensions of vaccine hesitancy [Ward2022].  
+The indicators associated to vaccination rates can be interpreted in the light of the dimensions of vaccine hesitancy [@wardFrenchHealthPass2022].  
 A first reason for vaccine hesitancy is complacency: not fully perceiving the benefit of vaccination or the risks of severe disease.
@@
 A second reason for vaccine hesitancy is confidence, i.e.
-trust in the vaccine, in the health care system, and more generally in the government [Ward2022].
-A survey conducted in July 2021 in France confirmed that trust in the government and trust in scientists were associated to higher odds to be vaccinated [Bajos2022].
+trust in the vaccine, in the health care system, and more generally in the government [@wardFrenchHealthPass2022; @lindholtPublicAcceptanceCOVID192021].
+A survey conducted in July 2021 in France confirmed that trust in the government and trust in scientists were associated to higher odds to be vaccinated [@bajosWhenMistrustGovernment2022].
 Votes for Mr Asselineau can be interpreted as mistrust in the government (or more generally, against the establishment), and the association with lower vaccination rates can be interpreted as a lack of confidence.
-Among political indicators, the second strongest association is with abstention rates (higher abstention rates being associated to lower vaccination rates), again signaling higher distrust for institutions [Ward2020].
+Among political indicators, the second strongest association is with abstention rates (higher abstention rates being associated to lower vaccination rates), again signaling higher distrust for institutions [@wardFrenchPublicAttitudes2020].
 Likewise, the lower vaccinations rates in the South-East of France can be interpreted as mistrust of the central government in Paris.
-Finally, a third reason for vaccine hesitancy is convenience, that is availability and accessibility of the vaccines [Ward2022].
+Finally, a third reason for vaccine hesitancy is convenience, that is availability and accessibility of the vaccines [@wardFrenchHealthPass2022].
 During the first half of 2021, vaccination rate in France was mostly constrained by dose availability.
@@
 These accessibility issues may explain the association we find between lower vaccination rates and living in a district with a high proportion of immigrants, which may for instance reveal language barriers.
-BAJOS AND RACIALISED INDIV?
 
 Although presented in our study independently, the different indicators are linked, and their combinations affect vaccination rates.
-For instance, the effect of mistrust in the government on vaccination refusal was shown to be even stronger in poorer individuals than in richer points in a survey conducted in July 2021 in France [Bajos2022].
+For instance, the effect of mistrust in the government on vaccination refusal was shown to be even stronger in poorer individuals than in richer points in a survey conducted in July 2021 in France [@bajosWhenMistrustGovernment2022].
 
 Relative position of the district of residency along a North-West--South-East gradient is also associated with vaccination probability, the South-East being less vaccinated.
-This geographic feature, already documented for other kinds of vaccination [Guimier2021], have been shown to be the consequence of multiple determinants with a common consequence: a local climate of mistrust for the central Parisian power.
+This geographic feature, already documented for other kinds of vaccination [@guimierResistancesFrancaisesAux2021], have been shown to be the consequence of multiple determinants with a common consequence: a local climate of mistrust for the central Parisian power.
 Politically, anti-system votes (from the right as well as from the left) are traditionally concentrated in the South-East of France.
-Medically, General Practitioners (GPs) based in the South-East, and to a lesser extent those in the South-West, have been shown to tend to have a more negative opinion of vaccination than their colleagues practicing in the northern part of France [Gautier et al.
-2013].
-This greater skepticism influences GP practices and attitudes, resulting in a lesser degree of compliance with vaccination schedules than GPs in the northern half of France [Collange et al., 2015].
-Physical distance to the central government and institutions, based in Paris, coupled with a sense of belonging to a local community with a strong cultural identity, as is the case for example in the Marseille metropolis or in the Cévennes, play a role in indifference or mistrust towards institutions perceived as distant authorities [Guimier, 2021].
+Medically, General Practitioners (GPs) based in the South-East, and to a lesser extent those in the South-West, have been shown to tend to have a more negative opinion of vaccination than their colleagues practicing in the northern part of France [@Gautier2013a].
+This greater skepticism influences GP practices and attitudes, resulting in a lesser degree of compliance with vaccination schedules than GPs in the northern half of France [@Collange2015].
+Physical distance to the central government and institutions, based in Paris, coupled with a sense of belonging to a local community with a strong cultural identity, as is the case for example in the Marseille metropolis or in the Cévennes, play a role in indifference or mistrust towards institutions perceived as distant authorities [@guimierResistancesFrancaisesAux2021].
 Finally, in and around the Marseille metropolis, the image of a rebellious territory was reinforced since the first months of the epidemic in France through the hypermediatized Pr Didier Raoult.
@@
 While our vaccination data are at the individual level, the socio-economic, political and geographic indicators are at the district level, and must therefore be interpreted as such (e.g., we cannot not show that receiving unemployment benefits is associated with lower vaccination probability, but we find an association with lower vaccination probability and the fact of living in a district where a large share of income comes from unemployment benefits).
-Our data cover Metropolitain France, XX million individuals, and are real-world data: we consider realized vaccination rates and not intentions to be vaccinated.
+Our data cover mainland France, `r round(pops[nrow(pops), 1] / 10^6, 1)` million individuals, and are real-world data: we consider realized vaccination rates and not intentions to be vaccinated.
 In addition, since our data are based on record of the national health insurance service, vaccination rates do not come from self-reported, and there is in theory no reporting bias.
@@
 Although we interpreted our results through the lens of a classification of reasons for vaccine hesitancy, our data only concern realized vaccination rates, and not the associated intentions.
-According to a survey conducted in the Fall 2021, the introduction of the sanitary pass led to an increase in the share of individuals reporting being "angry they had to be vaccinated" [Ward2022].
+According to a survey conducted in the Fall 2021, the introduction of the sanitary pass led to an increase in the share of individuals reporting being "angry they had to be vaccinated" [@wardFrenchHealthPass2022].
 Conversely, we cannot tell why individuals who are still not vaccinated in February 2022 are so -- e.g., whether it is hesitancy, refusal, or accessibility issues.
@@
 By emphasizing a differentiated use of COVID-19 vaccination according to a socio-economic gradient, our study confirms the strong impact of social inequalities on COVID-19.
-The most deprived areas have already been shown to have been disproportionately infected and hospitalized during the pandemic [Jannot21, Bajos21].
+The most deprived areas have already been shown to have been disproportionately infected and hospitalized during the pandemic [@jannotLowincomeNeighbourhoodWas2021; @bajosWhenLockdownPolicies2021].
 We show that poorer districts are also the least vaccinated and, hence, the most still at risk, despite the widely celebrated domestic sanitary pass.
 There is an urgent need to define new vaccination policies that truly address social inequities.
+
+AUTRES POINTS DE DISCUSSION POSSIBLES: distrust with promises of return to normal life (Summer 2021); changing conditions (inclusion of booster dose)
+
 + DEPOLITICIZE (Bajos/Ward)
-
-AUTRES POINTS DE DISCUSSION: distrust with promises of return to normal life (Summer 2021); changing conditions (inclusion of booster dose)

### 2022-04-11 ms/ms.Rmd
update ms

@@
 ---
-title: "PassSanitaire"
-author: ""
+title: "The French domestic Pass Sanitaire did not solve vaccination inequities: a nationwide longitudinal study on 64.5 million individuals"
+author: "F. Débarre, E. Lecoeur, L. Guimier, M. Jauffret-Roustide, A.-S. Jannot"
 output:
+  bookdown::word_document2: 
+    number_sections: no
   bookdown::html_document2:
@@
     number_sections: no
-  bookdown::word_document2: 
-    number_sections: no
+  pdf_document: 
+    keep_tex: yes
+    latex_engine: pdflatex
+    includes:
+      in_header: template.tex
 bibliography: VaccinationInequalities.bib
-
 ---
@@
 
-The French domestic Pass Sanitaire did not solve vaccination inequities: a nationwide longitudinal study on `r round(pops[nrow(pops), 1] / 10^6, 1)` million individuals
+<!-- The French domestic Pass Sanitaire did not solve vaccination inequities: a nationwide longitudinal study on `r round(pops[nrow(pops), 1] / 10^6, 1)` million individuals
+-->
+
+## Affiliations
+
+FD:  Institute of Ecology and Environmental Sciences of Paris (IEES-Paris, UMR 7618), CNRS, Sorbonne Université, UPEC, IRD, INRAE, 75252 Paris, France  
+EL:  Clinical research unit, Hôpital Européen Georges Pompidou, APHP, Paris, France  
+LG:  French Institute of Geopolitics, Paris, France  
+MJR:  Centre d’Étude des Mouvements Sociaux (Inserm U1276/CNRS UMR8044/EHESS), Paris, France.  
+      British Columbia Center For Substance Use (BCCSU), Vancouver, Canada  
+      Bady Center on Law and Social Policy, Buffalo, NY, USA  
+AJR:  Medical Informatics, biostatistics and public health unit, Hôpital Européen Georges Pompidou, APHP, Paris, France  
+      Université de Paris, Paris, France  
+      HeKA, Centre de Recherche des Cordeliers, Inserm, INRIA, Paris, France
+
+*Corresponding author:* Anne-Sophie Jannot, Hôpital Européen Georges Pompidou, 20 rue Leblanc, 75015 Paris. `annesophie.jannot@aphp.fr`
+
+### Keywords:
+vaccination, covid-19, data mining, socio-economic factors, health inequities.
+
+## Acknowledgements
+We thank the producers of public datasets, in particular David Levy at INSEE and Antoine Rachas at Assurance Maladie.
+
+## Funding
+EL received funding to match socio-economic data with medical data from AP-HP Centre Université de Paris.
+
+## Contributions 
+ASJ and FD designed the study with inputs from all authors.
+EL extracted socio-economic and political orientation data at district scale and computed indicators.
+ASJ, EL and FD had full access to aggregated data used for this study and take responsibility for the integrity of the data.
+EL and FD did the analyses and takes responsibility for the accuracy of the data analysis.
+FD drafted the paper with the help of ASJ, MR.
+All authors critically revised the manuscript for important intellectual content and gave final approval for the version to be published.
+
+## Conflict of interest statement
+No conflict of interest to disclose
+
+## Data sources
+-  Assurance Maladie: <https://datavaccin-covid.ameli.fr/explore/dataset/donnees-devaccination-par-epci/> <https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-parcommune/information/>
+-  INSEE: <https://www.insee.fr/fr/statistiques/5359146#consulter>
 
@@
 
-Context: Implemented during the Summer 2021, the French "Sanitary Pass" led to an increase in vaccination rates in France, but spatial heterogeneities in vaccination rates are still striking [LG1].
-It morphed into a "Vaccine Pass" in early 2022.
+Context: To encourage Covid-19 vaccination, France introduced during the Summer 2021 a "Sanitary Pass", which morphed into a "Vaccine Passe" in early 2022.
+While the Sanity Pass led to an increase in Covid-19 vaccination rates, spatial heterogeneities in vaccination rates remained.
 To identify potential determinants of these heterogeneities and evaluate the French Sanitary and Vaccine Pass' efficacies in reducing them, we used a data-driven approach on exhaustive nationwide data, gathering `r nIndicatorsAfterRemovingCorrMiss` socio-economic, political and geographic indicators.
@@
 Methods: We considered the association between being a district above the median value of the first-dose vaccination rates and being above the median value of each indicator at different time points: just before the sanitary pass announcement (week `r format(as.Date(datesAnalysis[1]), "%Y-W%W")`), just before the sanitary pass came into force (week `r format(as.Date(datesAnalysis[2]), "%Y-W%W")`) and one month after (week `r format(as.Date(datesAnalysis[3]), "%Y-W%W")`), and the equivalent dates for the vaccine pass (weeks `r format(as.Date(datesAnalysis[4:6]), "%Y-W%W")`).
-We then considered the change over time of vaccination rates according to the XX most associated indicators, by deciles.
+We then considered the change over time of vaccination rates according to deciles of the three of the most associated indicators.
 
-Results: The indicators most associated with vaccination rates were the share of local income coming from unemployment benefits, the proportion of immigrants in the district, and vote for a fringe candidate at the 2017 Presidential election (XXX revoir description Asselineau).
-Vaccination rate also follow a marked North-West -- South East gradient, with lower vaccination coverage in the South-East of France.
+Results: The indicators most associated with vaccination rates were the share of local income coming from unemployment benefits, the proportion of overcrowded households, the proportion of immigrants in the district, and vote for an "anti-establishment" candidate at the 2017 Presidential election.
+Vaccination rate also were also contrasted along a North-West -- South East axis, with lower vaccination coverage in the South-East of France.
 
-Conclusion: Our analysis reveals that, both before and after the introduction of the French sanitary pass, factors with the largest impact are related to poverty, immigration, and trust in the government XXX Check if you agree.
+Conclusion: Our analysis reveals that, both before and after the introduction of the French sanitary and vaccination passes, factors with the largest impact are related to poverty, immigration, and trust in the government.
 
@@
 Hesitancy and hostility toward vaccination have been comparatively high in France in recent decades [@europeancommission.directorategeneralforhealthandfoodsafety.StateVaccineConfidence2018].
-It is particularly the case since the 2009-2010 vaccination campaign against pandemic flu, the contested management of which in France was a tipping point that led to higher vaccine hesitancy and hostility [@guimierResistancesFrancaisesAux2021; @wardVaccineHesitancyCoercion2019].
-The trend was confirmed with the COVID-19 pandemic [@lindholtPublicAcceptanceCOVID192021;  @spireSocialInequalitiesHostility2021]: just before Covid-19 vaccines became available, intentions to get vaccinated were comparatively very low in France (44% of the respondents in [@woutersChallengesEnsuringGlobal2021] in the Fall 2020; about 40% of respondent in XXX [@santepubliquefranceCoviPrevEnquetePour2021] (XXX TODO clean citation) in December 2020).
-Acceptance of the COVID-19 vaccine however gradually grew during 2021 XXX [@santepubliquefranceCoviPrevEnquetePour2021].
-<!-- Lazarus21 does not talk directly about France -->
+Modern vaccine hesitancy in France started with claims of a link between the hepatitis B vaccine and multiple sclerosis [@wardVaccineHesitancyCoercion2019]; it strongly increased following the 2009-2010 vaccination campaign against pandemic flu, the contested management of which in France was a tipping point that led to higher vaccine hesitancy and hostility [@guimierResistancesFrancaisesAux2021; @wardVaccineHesitancyCoercion2019].
+The trend was confirmed with the COVID-19 pandemic [@lindholtPublicAcceptanceCOVID192021;  @spireSocialInequalitiesHostility2021]: just before Covid-19 vaccines became available, intentions to get vaccinated were comparatively very low in France compared to other countries (44% of the respondents in [@woutersChallengesEnsuringGlobal2021] in the Fall 2020; about 40% of respondent in [@santepubliquefranceCoviPrevEnquetePour2021] in December 2020).
+Acceptance of the COVID-19 vaccine however gradually grew during 2021 [@santepubliquefranceCoviPrevEnquetePour2021; @wardPremiersResultatsEnquete2021].
 
@@
 Attitudes toward vaccination are also known to be influenced by social and territorial inequalities.
-Surveys conducted in 2020 in France showed that respondents with lower education [@schwarzingerCOVID19VaccineHesitancy2021, @spireSocialInequalitiesHostility2021], lower income levels or less trust in authorities [@spireSocialInequalitiesHostility2021; @lindholtPublicAcceptanceCOVID192021] were more likely to be hostile to COVID-19 vaccines.
-A survey conducted in July 2021 in France [@bajosWhenMistrustGovernment2022] on close to 81000 participants indicated that unvaccinated respondents were more likely to have lower income and more likely to belong to racialised minorities than vaccinated ones.
+Surveys conducted in 2020 in France showed that respondents with lower education [@schwarzingerCOVID19VaccineHesitancy2021; @coulaudCOVID19VaccineIntention2022], lower income levels or less trust in authorities [@spireSocialInequalitiesHostility2021; @lindholtPublicAcceptanceCOVID192021] were more likely to be hostile to COVID-19 vaccines.
+<!-- A survey conducted in July 2021 in France [@bajosWhenMistrustGovernment2022] on close to 81000 participants indicated that unvaccinated respondents were more likely to have lower income and more likely to belong to racialised minorities than vaccinated ones.
 The survey also confirmed that mistrust in the government was fueling refusal to be vaccinated [@bajosWhenMistrustGovernment2022].
+-->
 
@@
 The "sanitary pass" was required in most cultural venues, for both indoor and outdoor dining and in health structures.
-This announcement led to an unprecedented demand for vaccination [@oliu-bartonEffectCOVIDCertificates2022], which was celebrated internationally XXX [Ref quel article?].
-Vaccination rates climbed from about `r round(100 * txVaccAdults[txVaccAdults$date == "2021-07-11", "txVacc"])`% of the population over 20 years old by 11 July 2021 (`r round(100 * txVaccTot[txVaccAdults$date == "2021-07-11", "txVacc"])`% of all ages) to `r round(100 * txVaccAdults[txVaccAdults$date == "2021-09-05", "txVacc"])` on 5 September 2021 (`r round(100 * txVaccTot[txVaccTot$date == "2021-09-05", "txVacc"])` of all ages).
+This announcement led to an unprecedented demand for vaccination [@oliu-bartonEffectCOVIDCertificates2022], which was considered internationally as a potential model to follow.
+Vaccination rates climbed from about `r round(100 * txVaccAdults[txVaccAdults$date == "2021-07-11", "txVacc"])`% of the population over 20 years old by 11 July 2021 (`r round(100 * txVaccTot[txVaccAdults$date == "2021-07-11", "txVacc"])`% of all ages) to `r round(100 * txVaccAdults[txVaccAdults$date == "2021-09-05", "txVacc"])` on 5 September 2021 (`r round(100 * txVaccTot[txVaccTot$date == "2021-09-05", "txVacc"])`% of all ages).
 Because it targeted pay-for social activities, however, the "sanitary pass" was feared to have a limited impact on vaccination inequities.
@@
 
-The vaccination dataset for mainland France encompasses about `r round(pops[nrow(pops), 1] / 10^6, 1)` million individuals (median district size `r round(popSizeDistrib["50%"])`, interquartile range `r round(popSizeDistrib["25%"])`--`r round(popSizeDistrib["75%"])`).
+The vaccination dataset for mainland France encompasses about `r round(pops[nrow(pops), 1] / 10^6, 1)` million individuals (median district size `r format(round(popSizeDistrib["50%"]), scientific = FALSE)` inhabitants, interquartile range `r format(round(popSizeDistrib["25%"]), scientific = FALSE)`--`r format(round(popSizeDistrib["75%"]), scientific = FALSE)`).
 The vaccination data are available by age class: 00--19, 20--39, 40--54, 55--64, 65--74, 75 and over.
 Population sizes for each locality and each age class are also provided.
-These population sizes are updated monthly to account for individuals aging, potential residential moves, and deaths.
-XXX TODO: Demander pourquoi les tailles de pop sont constantes au cours du temps
+<!-- These population sizes are updated monthly to account for individuals aging, potential residential moves, and deaths.
+XXX TODO: Demander pourquoi les tailles de pop sont constantes au cours du temps FD: Removed because was not specified -->
 
@@
 
-We paired these vaccination data with three other datasets gathering socio-economic, political and geographic variables.
+We paired these vaccination data with three other datasets gathering socio-economic, political orientation and geographic variables.
 
@@
 We selected the most recent dataset available (year 2018).
-The different predictors are classified into `r length(insee.indicators.names)` categories (`r insee.indicators.names`).
-Latitude, longitude and surface data were extracted from open geographic data.
+The different variables available in the dataset are classified by INSEE according to `r length(insee.indicators.names)` categories (`r insee.indicators.names`).
+Latitude, longitude and surface data were extracted from open geographic datasets.
 We calculated from them four additional geographic indicators: distance to Paris, relative position along a South-East--North-West gradient, relative position along a South-West--North-East gradient, and local population density.
-Our political dataset consisted of the results of the two round of the 2017 Presidential election in France, which we aggregated to reconstitute the same administrative levels as the vaccination dataset.
+Political orientation data consisted of the results of the 2017 Presidential election in France, which we aggregated to reconstitute the same administrative levels as the vaccination dataset.
 This political dataset contains the proportions of votes for each of the 11 candidates of the first round, 2 candidates of the second round (Macron and Le Pen), and proportion of abstention at each round.
@@
 Note that vaccination data are at the individual level, and indicator data at the district level.
+The analysis is done at the individual level, with indicators characterizing the geographic districts in which individuals live.
 For each date, we determined a significance threshold by computing odds ratios on `r nrep` random permutations of a predictor, and identifying the value of the 99% percentile odd ratios ($\overline{OR}$) of these permuted data.
 
-For representative indicators with the strongest association to vaccination data, we estimated age-adjusted vaccination rates among adults over time, for each decile of each indicator (treated as a factor).
-These estimations were obtained from a logistic model taking age class into account, and adult vaccination rates were computed on a standardized age distribution matching that of mainland France.
+For representative indicators among the most statistically significantly associated ones, we estimated standardized vaccination rates among adults over time, for each decile of each indicator (treated as a factor).
+These estimations were obtained from a logistic model taking age class into account; adult vaccination rates were standarsized using an age distribution matching that of mainland France.
 
@@
 
-We investigated the associations between each of the `r nIndicatorsAfterRemovingCorrMiss` indicators and first-dose vaccination rates.
-Two indicators were among the top five most associated one at all time points (see Figure \@ref(fig:figManhattan)): the share of local income coming from unemployment benefits (`Unemployment_Benef`) and vote for Mr Asselineau (`Asselineau`).
-The three other most associated indicators did not change in the later dates that we considered, and were the proportion of immigrants in the district (`Immigrant`), the district's relative position along a North-West--South-East gradient (`NO-SE`) and the proportion of overcrowded households (`Overcrowding_rate`).
+```{r loadData_outLR, echo = FALSE}
+load("../data/predictors.RData")
+load("../code/outLR.RData")
 
+# Extract OR values for the most associated variables
+tmp <- outLR[outLR$varPred == "Asselineau", ]
+maxAsselineau <- tmp[order(tmp$OR.abs, decreasing = TRUE), ][1, ]
+
+tmp <- outLR[outLR$varPred == "Unemployment_Benef", ]
+maxUnemployment_Benef <- tmp[order(tmp$OR.abs, decreasing = TRUE), ][1, ]
+
+tmp <- outLR[outLR$varPred == "Immigrant", ]
+maxImmigrant <- tmp[order(tmp$OR.abs, decreasing = TRUE), ][1, ]
+
+tmp <- outLR[outLR$varPred == "NO.SE", ]
+maxNOSE <- tmp[order(tmp$OR.abs, decreasing = TRUE), ][1, ]
+
+tmp <- outLR[outLR$varPred == "Overcrowding_rate", ]
+maxOvercrowding_rate <- tmp[order(tmp$OR.abs, decreasing = TRUE), ][1, ]
+
+roundOR <- 3 # Number of decimals for OR
+
+```
+
+We investigated the associations between each of the `r nIndicatorsAfterRemovingCorrMiss` indicators characterizing districts of residence, and the fact of having received at least one Covid-19 vaccine dose, on the whole population of mainland France.
+Two indicators were among the top five most associated one at all time points (see Figure \@ref(fig:figManhattan)): the share of local income coming from unemployment benefits (`Unemployment_Benef`; strongest association on `r maxUnemployment_Benef$thedate`, $OR = `r round(maxUnemployment_Benef$OR, roundOR)`$)
+and vote for the "anti-establishment" political party represented by the candidate Asselineau (`Asselineau`; $OR = `r round(maxAsselineau$OR, roundOR)`$ on `r maxAsselineau$thedate`). 
+The three other most associated indicators did not change in the later dates that we considered, and were the proportion of immigrants in the district (`Immigrant`; $OR = `r round(maxImmigrant$OR, roundOR)`$ on `r maxImmigrant$thedate`),
+the district's relative position along a North-West--South-East gradient (`NO-SE`; $OR = `r round(maxNOSE$OR, roundOR)`$ on `r maxNOSE$thedate`) 
+and the proportion of overcrowded households (`Overcrowding_rate`; $OR = `r round(maxOvercrowding_rate$OR, roundOR)`$ on `r maxOvercrowding_rate$thedate`).
+
+<!-- [moved to Discussion]
 The share of local income coming from unemployment benefits (`Unemployment_Benef`) and the proportion of overcrowded households (`Overcrowding_rate`) are two indicators linked to poverty.
 Votes for Mr Asselineau (`Asselineau`) represented a minority of cast votes in 2017 in France (less than $1\%$ overall).
-This candidate for instance proposed that France exits the European Union, leave the Euro zone and reinstall the Franc currency; he was a proponent of hydroxychloroquin and ivermectin during the Covid-19 pandemic, and publicly expressed doubts about the available Covid-19 vaccines.
-
-XXX GIVE NAMES OF NOT ASSOCIATED INDICATORS?
-
-XXX GIVE VALUES IN A TABLE?
+This candidate for instance proposed that France exits the European Union, leave the Euro zone and reinstall the Franc currency; he was a proponent of hydroxychloroquin and ivermectin during the Covid-19 pandemic, and publicly expressed doubts about the safety of available Covid-19 vaccines.
+-->
 
@@
 Left column: around the Sanitary Pass implementation; right column: around the Vaccine Pass implementation.
-The top odds ratios are labelled at each time point; the arrow next to the name indicates the direction of the effect.
+The top odds ratios are labelled at each time point; the symbol next to the name indicates the direction of the effect.
 The gray rectangle corresponds to the 99% percentile of odds ratios in the permuted data; points falling in the rectangle are considered as non-significant."}
-load("../data/predictors.RData")
-load("../code/outLR.RData")
 source("../code/2_plot-manhattan.R")
@@
 To better visualize the effects (or lack thereof) of the sanitary and vaccine passes on vaccination rates over time, we computed age-adjusted vaccination rates over time, by decile of three of the most associated indicators, treated as factors (see Figure \@ref(fig:figOverTime)).
-While the Sanitary Pass led to an overall increase in vaccination rates, the Vaccine Pass did not affect the trend of change in vaccination rates.
-Heterogeneities in vaccination rates persisted after both types of pass; vaccination rates appear neatly ordered by decile of each indicator.
+The Sanitary Pass, implemented in the Summer 2021, led to an overall increase in vaccination rates; on the other hand, the Vaccine Pass, implemented in the end of 2021, did not affect the evolution of vaccination rates.
+Heterogeneities in vaccination rates persisted after both types of pass; vaccination rates gradually decrease by decile of each indicator, confirming the association of these indicators with vaccination rates without threshold effect.
+Of note, for the Unemployment and Asselineau vote indicators, the difference between the 9th and 10th deciles appears to be much larger than between the other consecutive deciles.
 
 ```{r figOverTime, fig.height=8, fig.width=4, fig.cap="Age-adjusted vaccination rates among adults, over time, by decile of each indicator (presented by a color gradient).
-The dates of announcements and implementations of the sanitary and vaccine pass are indicated near the horizontal axes.", echo = FALSE}
+The vertical lines indicate the dates of announcements and implementations of the sanitary and vaccine passes.", echo = FALSE}
 load("../code/outTime.RData")
@@
 
-```{r figMap, fig.height=5, fig.width=4, fig.cap="Adult vaccination rates by district", echo = FALSE}
+```{r figMap, fig.height=5, fig.width=4, fig.cap="Adult vaccination rates by district of mainland France", echo = FALSE}
 source("../code/2_plot-map.R")
@@
 
-plotMapVacc(adultVaccinationRate, thetitle = paste0("Adult vaccination rates on ", thedate), palName = "Hiroshige", byp = 2, zmin = floor(100*(meanVacc - maxDiff)), zmax = ceiling(100*(meanVacc + maxDiff)))
+plotMapVacc(adultVaccinationRate, thetitle = paste0("Adult vaccination rates on ", thedate), palName = "Cassatt2", byp = 2, zmin = floor(100*(meanVacc - maxDiff)), zmax = ceiling(100*(meanVacc + maxDiff)))
 
@@
 Our results, based on exhaustive national datasets, indicate that the French sanitary pass, and the later vaccine pass, did not solve Covid-19 vaccination heterogeneities, but instead crystallized them.
-Indicators most associated with vaccination rates were associated to poverty, immigration, and anti-establishment vote (or abstention).
-For instance, the odds for an adult to still be unvaccinated by the end of February 2021 are about `r round(maxOR.Unemployment_Benef, 1)` times higher when living in the districts with higher than median value share of income coming from unemployment benefits, and when living in the districts with lower than median value.
+<!-- Indicators that were the most strongly associated to vaccination rates are linked to poverty (the share of local income coming from unemployment benefits (`Unemployment_Benef`), and the proportion of overcrowded households (`Overcrowding_rate`)), immigration (the proportion of immigrants in the population (`Immigrant`)), -->
+Indicators most associated with vaccination rates were associated to poverty, immigration, anti-establishment vote (or abstention), and a North-West -- South-East contrast.
+For instance, the odds for an adult to still be unvaccinated by the end of February 2021 are about `r round(maxOR.Unemployment_Benef, 1)` times higher when living in the districts with higher than median value share of income coming from unemployment benefits, than when living in the districts with lower than median value.
 
@@
 While in this case a sanitary or vaccine pass may convince complacent individuals to get vaccinated, it is less efficient if the associated constrain is low.
-As the French domestic pass was associated to pay-for activities (restaurants, tourism), its persuading effect could be limited among poorer populations, which may explain the association of lower vaccination rate with poverty in the data that we analyzed.
+As the French domestic pass was associated to pay-for activities (restaurants, tourism), its persuading effect could be limited among poorer populations.
+This may explain the association of lower vaccination rate with poverty in the data that we analyzed: vaccination rates decrease as the share of local income coming from unemployment benefits (`Unemployment_Benef`) or the proportion of overcrowded households (`Overcrowding_rate`)) increase.
+<!-- -->
 A second reason for vaccine hesitancy is confidence, i.e.
@@
 A survey conducted in July 2021 in France confirmed that trust in the government and trust in scientists were associated to higher odds to be vaccinated [@bajosWhenMistrustGovernment2022].
-Votes for Mr Asselineau can be interpreted as mistrust in the government (or more generally, against the establishment), and the association with lower vaccination rates can be interpreted as a lack of confidence.
-Among political indicators, the second strongest association is with abstention rates (higher abstention rates being associated to lower vaccination rates), again signaling higher distrust for institutions [@wardFrenchPublicAttitudes2020].
+Votes for Mr Asselineau -- which represented a minority of cast votes in 2017 in France (less than $1\%$ overall) -- can be interpreted as mistrust in the government (or more generally, against the establishment): This candidate for instance proposed that France exits the European Union, leave the Euro zone and reinstall the Franc currency; he was a proponent of hydroxychloroquin and ivermectin during the Covid-19 pandemic, and publicly expressed doubts about the safety of available Covid-19 vaccines.
+The association of higher proportion of votes for Mr Asselineau with lower vaccination rates can be interpreted as revealing a lack of confidence for the government.
+Noteworthily, among political indicators, the second strongest association is with abstention rates (higher abstention rates being associated to lower vaccination rates), again signaling higher distrust for institutions [@wardFrenchPublicAttitudes2020].
 Likewise, the lower vaccinations rates in the South-East of France can be interpreted as mistrust of the central government in Paris.
-Finally, a third reason for vaccine hesitancy is convenience, that is availability and accessibility of the vaccines [@wardFrenchHealthPass2022].
+<!-- -->
+Finally, a third reason for vaccine hesitancy is convenience, that is, the availability and accessibility of the vaccines [@wardFrenchHealthPass2022].
 During the first half of 2021, vaccination rate in France was mostly constrained by dose availability.
 Vaccination slots were to be booked online, and there was no general system for sending individual invitations to get vaccinated.
-These accessibility issues may explain the association we find between lower vaccination rates and living in a district with a high proportion of immigrants, which may for instance reveal language barriers.
-
-Although presented in our study independently, the different indicators are linked, and their combinations affect vaccination rates.
-For instance, the effect of mistrust in the government on vaccination refusal was shown to be even stronger in poorer individuals than in richer points in a survey conducted in July 2021 in France [@bajosWhenMistrustGovernment2022].
+It is therefore still possible that, in spite of some local outreach efforts, vaccine accessibility remained an issue, which may explain at least part of the association of lower vaccination rates with poverty.
+These accessibility issues may also explain the association we find between lower vaccination rates and living in a district with a high proportion of immigrants, which may for instance reveal language barriers.
+These associations of lower vaccination rates with more poverty and with higher proportions of immigrants in the district of residence are compatible with the results of a survey conducted in July 2021 in France [@bajosWhenMistrustGovernment2022] on close to 81000 participants, which indicated that unvaccinated respondents were more likely to have lower income and more likely to belong to racialised minorities than vaccinated respondents
 
@@
 Finally, in and around the Marseille metropolis, the image of a rebellious territory was reinforced since the first months of the epidemic in France through the hypermediatized Pr Didier Raoult.
-Based in Marseille, he was a promoter of a controversial treatment against Covid-19 based on hydroxychloroquine and azithromycin, and later held ambiguous positions regarding Covid-19 vaccination.
+Based in Marseille, he was a promoter of a controversial treatment against Covid-19 based on hydroxychloroquine and azithromycin [@schultzDoesPublicKnow2022], and later held ambiguous positions regarding Covid-19 vaccination.
 He has become a local icon, thanks to his anti-system positions, and against the hostility of most of the medical world towards his work.
@@
 
-<!-- Limitations -->
-In this study, we used a data-driven approach, i.e.
+<!-- Positive points -->
+The design of our study offers several advantages.
+First, we used a data-driven approach, i.e.
 we did not focus on indicators that we *a priori* thought to be associated with vaccination rate.
-While our vaccination data are at the individual level, the socio-economic, political and geographic indicators are at the district level, and must therefore be interpreted as such (e.g., we cannot not show that receiving unemployment benefits is associated with lower vaccination probability, but we find an association with lower vaccination probability and the fact of living in a district where a large share of income comes from unemployment benefits).
-Our data cover mainland France, `r round(pops[nrow(pops), 1] / 10^6, 1)` million individuals, and are real-world data: we consider realized vaccination rates and not intentions to be vaccinated.
-In addition, since our data are based on record of the national health insurance service, vaccination rates do not come from self-reported, and there is in theory no reporting bias.
+The indicators that we identified as the most associated with vaccination rates were not biased towards our previous knowledge or surveys about vaccine hesitancy.
+Secondly, the data that we used are real-world data on effective vaccination, and not vaccination intentions.
+Intentions to be vaccinated and realized vaccination may not always match, especially with the introduction of measures like the French Sanitary and Vaccine Passes.
+For instance, according to a survey conducted in the Fall 2021, the introduction of the sanitary pass led to an increase in the share of individuals reporting being "angry they had to be vaccinated" [@wardFrenchHealthPass2022].
+From an immediate public health perspective, such as the limitation of the number of severe cases, realized vaccination rates are a more useful metric.
+Finally,  the vaccination data we used are based on records of the national health insurance service: they cover `r round(pops[nrow(pops), 1] / 10^6, 1)` million individuals living in mainland France, and vaccination rates are not self-reported, which strongly limits reporting bias.
 
-Although we interpreted our results through the lens of a classification of reasons for vaccine hesitancy, our data only concern realized vaccination rates, and not the associated intentions.
-According to a survey conducted in the Fall 2021, the introduction of the sanitary pass led to an increase in the share of individuals reporting being "angry they had to be vaccinated" [@wardFrenchHealthPass2022].
-Conversely, we cannot tell why individuals who are still not vaccinated in February 2022 are so -- e.g., whether it is hesitancy, refusal, or accessibility issues.
-Given the implementation of the vaccination campaign in France, namely the absence of individual invitations to get vaccinated, the reliance on private online booking systems, it is still possible that, in spite of some local outreach efforts, vaccine accessibility remains an issue, and may explain at least part of the association of lower vaccination rates with poverty.
+<!-- Limitation 1 -->
+Still, the design of our study also presents limitations.
+While our vaccination data are at the individual level, the socio-economic, political and geographic indicators are at the district level, and must therefore be interpreted as such: for instance, we cannot not show that receiving unemployment benefits is associated with lower vaccination probability, but we find an association with lower vaccination probability and the fact of living in a district where a large share of income comes from unemployment benefits.
+<!-- Limitation 2 -->
+In addition, although the different indicators are analysed independently in our study, their combinations may affect vaccination rates.
+For instance, the effect of mistrust in the government on vaccination refusal was shown to be even stronger among individuals from lower social classes than from higher social classes [@bajosWhenMistrustGovernment2022].
+Finally, our data do not inform directly on the reasons for non-vaccination -- e.g., whether it is hesitancy, refusal, or accessibility issues, which is why our approach is complementary to qualitative surveys.
 
-By emphasizing a differentiated use of COVID-19 vaccination according to a socio-economic gradient, our study confirms the strong impact of social inequalities on COVID-19.
-The most deprived areas have already been shown to have been disproportionately infected and hospitalized during the pandemic [@jannotLowincomeNeighbourhoodWas2021; @bajosWhenLockdownPolicies2021].
-We show that poorer districts are also the least vaccinated and, hence, the most still at risk, despite the widely celebrated domestic sanitary pass.
+To conclude, by emphasizing a differentiated use of COVID-19 vaccination according to a socio-economic gradient, our study confirms the strong impact of social inequalities on COVID-19.
+Previous research found that the most deprived areas have been disproportionately infected and hospitalized during the pandemic [@jannotLowincomeNeighbourhoodWas2021; @bajosWhenLockdownPolicies2021].
+We further show that poorer districts are also the least vaccinated and, hence, the most still at risk, despite the widely celebrated domestic sanitary pass.
 There is an urgent need to define new vaccination policies that truly address social inequities.
 
-AUTRES POINTS DE DISCUSSION POSSIBLES: distrust with promises of return to normal life (Summer 2021); changing conditions (inclusion of booster dose)
-
-+ DEPOLITICIZE (Bajos/Ward)
+# References

### 2022-04-11 ms/ms.tex
update ms

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\title{The French domestic Pass Sanitaire did not solve vaccination
inequities: a nationwide longitudinal study on 64.5 million individuals}
\author{F. Débarre, E. Lecoeur, L. Guimier, M. Jauffret-Roustide, A.-S.
Jannot}
\date{}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The French domestic Pass Sanitaire did not solve vaccination inequities: a nationwide longitudinal study on 64.5 million individuals},
  pdfauthor={F. Débarre, E. Lecoeur, L. Guimier, M. Jauffret-Roustide, A.-S. Jannot},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{setspace}
\usepackage{lineno} % line numbering
\linenumbers

% Line spacing
\usepackage{setspace}
%\doublespacing

\usepackage{geometry}
\geometry{top=2.5cm, bottom=3cm, left=4cm, right=4cm}

% Fonts of the main text
\usepackage{fourier}
% Helvetica for sans serif fonts
\renewcommand{\sfdefault}{phv}

\usepackage[font={small,sf, doublespacing}, labelfont=bf]{caption}
\captionsetup{format=hang, font={it}, labelfont={bf}} % Format of captions
\captionsetup[table]{position=bottom}   %% or below
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\begin{document}
\maketitle

\hypertarget{affiliations}{%
\subsection{Affiliations}\label{affiliations}}

FD: Institute of Ecology and Environmental Sciences of Paris
(IEES-Paris, UMR 7618), CNRS, Sorbonne Université, UPEC, IRD, INRAE,
75252 Paris, France\\
EL: Clinical research unit, Hôpital Européen Georges Pompidou, APHP,
Paris, France\\
LG: French Institute of Geopolitics, Paris, France\\
MJR: Centre d'Étude des Mouvements Sociaux (Inserm U1276/CNRS
UMR8044/EHESS), Paris, France.\\
British Columbia Center For Substance Use (BCCSU), Vancouver, Canada\\
Bady Center on Law and Social Policy, Buffalo, NY, USA\\
AJR: Medical Informatics, biostatistics and public health unit, Hôpital
Européen Georges Pompidou, APHP, Paris, France\\
Université de Paris, Paris, France\\
HeKA, Centre de Recherche des Cordeliers, Inserm, INRIA, Paris, France

\emph{Corresponding author:} Anne-Sophie Jannot, Hôpital Européen
Georges Pompidou, 20 rue Leblanc, 75015 Paris.
\texttt{annesophie.jannot@aphp.fr}

\hypertarget{keywords}{%
\subsubsection{Keywords:}\label{keywords}}

vaccination, covid-19, data mining, socio-economic factors, health
inequities.

\hypertarget{acknowledgements}{%
\subsection{Acknowledgements}\label{acknowledgements}}

We thank the producers of public datasets, in particular David Levy at
INSEE and Antoine Rachas at Assurance Maladie.

\hypertarget{funding}{%
\subsection{Funding}\label{funding}}

EL received funding to match socio-economic data with medical data from
AP-HP Centre Université de Paris.

\hypertarget{contributions}{%
\subsection{Contributions}\label{contributions}}

ASJ and FD designed the study with inputs from all authors. EL extracted
socio-economic and political orientation data at district scale and
computed indicators. ASJ, EL and FD had full access to aggregated data
used for this study and take responsibility for the integrity of the
data. EL and FD did the analyses and takes responsibility for the
accuracy of the data analysis. FD drafted the paper with the help of
ASJ, MR. All authors critically revised the manuscript for important
intellectual content and gave final approval for the version to be
published.

\hypertarget{conflict-of-interest-statement}{%
\subsection{Conflict of interest
statement}\label{conflict-of-interest-statement}}

No conflict of interest to disclose

\hypertarget{data-sources}{%
\subsection{Data sources}\label{data-sources}}

\begin{itemize}
\tightlist
\item
  Assurance Maladie:
  \url{https://datavaccin-covid.ameli.fr/explore/dataset/donnees-devaccination-par-epci/}
  \url{https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-parcommune/information/}
\item
  INSEE: \url{https://www.insee.fr/fr/statistiques/5359146\#consulter}
\end{itemize}

\hypertarget{abstract}{%
\section{Abstract}\label{abstract}}

Context: To encourage Covid-19 vaccination, France introduced during the
Summer 2021 a ``Sanitary Pass,'' which morphed into a ``Vaccine Passe''
in early 2022. While the Sanity Pass led to an increase in Covid-19
vaccination rates, spatial heterogeneities in vaccination rates
remained. To identify potential determinants of these heterogeneities
and evaluate the French Sanitary and Vaccine Pass' efficacies in
reducing them, we used a data-driven approach on exhaustive nationwide
data, gathering 141 socio-economic, political and geographic indicators.

Methods: We considered the association between being a district above
the median value of the first-dose vaccination rates and being above the
median value of each indicator at different time points: just before the
sanitary pass announcement (week 2021-W27), just before the sanitary
pass came into force (week 2021-W31) and one month after (week
2021-W35), and the equivalent dates for the vaccine pass (weeks
2021-W49, 2022-W03, 2022-W07). We then considered the change over time
of vaccination rates according to deciles of the three of the most
associated indicators.

Results: The indicators most associated with vaccination rates were the
share of local income coming from unemployment benefits, the proportion
of overcrowded households, the proportion of immigrants in the district,
and vote for an ``anti-establishment'' candidate at the 2017
Presidential election. Vaccination rate also were also contrasted along
a North-West -- South East axis, with lower vaccination coverage in the
South-East of France.

Conclusion: Our analysis reveals that, both before and after the
introduction of the French sanitary and vaccination passes, factors with
the largest impact are related to poverty, immigration, and trust in the
government.

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

The rapid development of effective COVID-19 vaccines brought the hope of
a rapid return to normalcy, but heterogeneous vaccination rates, both
among countries because of inequitable distributions of doses (Usher
2021) and within countries (Caspi et al. 2021; Murthy et al. 2021),
jeopardize epidemic control.

Hesitancy and hostility toward vaccination have been comparatively high
in France in recent decades (European Commission. Directorate General
for Health and Food Safety. 2018). Modern vaccine hesitancy in France
started with claims of a link between the hepatitis B vaccine and
multiple sclerosis (J. K. Ward et al. 2019); it strongly increased
following the 2009-2010 vaccination campaign against pandemic flu, the
contested management of which in France was a tipping point that led to
higher vaccine hesitancy and hostility (Guimier 2021; J. K. Ward et al.
2019). The trend was confirmed with the COVID-19 pandemic (Lindholt et
al. 2021; Spire, Bajos, and Silberzan 2021): just before Covid-19
vaccines became available, intentions to get vaccinated were
comparatively very low in France compared to other countries (44\% of
the respondents in (Wouters et al. 2021) in the Fall 2020; about 40\% of
respondent in (Santé Publique France 2021) in December 2020). Acceptance
of the COVID-19 vaccine however gradually grew during 2021 (Santé
Publique France 2021; J. Ward 2021).

Spatial heterogeneties in vaccination rates have already been documented
in France for previous vaccines. Vaccination coverage for the Hepatitis
B vaccine and for the Measles-Mumps-Rubella vaccine has been lower in
the South of France, and especially in the South-East of the country
(Guimier 2021). Distance to the central political power in Paris, as
well as a sense of belonging to a local community with a strong cultural
identity, have been put forward as potential explanations for this
geographic gradient in vaccination rates (Guimier 2021).

Attitudes toward vaccination are also known to be influenced by social
and territorial inequalities. Surveys conducted in 2020 in France showed
that respondents with lower education (Schwarzinger et al. 2021; Coulaud
et al. 2022), lower income levels or less trust in authorities (Spire,
Bajos, and Silberzan 2021; Lindholt et al. 2021) were more likely to be
hostile to COVID-19 vaccines.

By mid-July 2021, France was facing an epidemic wave due to the Delta
variant. To speed up vaccination, President Macron announced on 12 July
2021 the implementation of a domestic ``sanitary pass'' (le passe
sanitaire), which came fully into force on 9 August 2021. Presenting as
a QR code, a long-term sanitary pass was obtained after full vaccination
(two doses, or only one dose in the case of a documented previous
Covid-19 infection), and a short-term version could be obtained with a
negative Covid-19 test. The ``sanitary pass'' was required in most
cultural venues, for both indoor and outdoor dining and in health
structures. This announcement led to an unprecedented demand for
vaccination (Oliu-Barton et al. 2022), which was considered
internationally as a potential model to follow. Vaccination rates
climbed from about 64\% of the population over 20 years old by 11 July
2021 (52\% of all ages) to 82 on 5 September 2021 (69\% of all ages).
Because it targeted pay-for social activities, however, the ``sanitary
pass'' was feared to have a limited impact on vaccination inequities. By
mid-December 2021, at the height of the winter Delta wave, and while the
Omicron wave was looming, the French Prime Minister announced that the
Sanitary Pass would become a Vaccine Pass, i.e.~that a negative Covid-19
test would not provide a temporary QR code any longer for adults --
making vaccination implicitly mandatory in France. The Vaccine Pass came
into force on 24 January 2022.

This study aims to obtain further insights on the socio-economic,
political and geographic factor associated with vaccination rates, and
to evaluate the effect of the French domestic sanitary pass, by using
nation-wide, exhaustive datasets.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{data}{%
\subsection{Data}\label{data}}

The French state health insurance service (Assurance Maladie) provides
public datasets of vaccination rates in France. These datasets are based
on aggregated individual data on beneficiaries of the national health
insurance service who received health care in the past year. These
exhaustive datasets are updated weekly, and are provided at the district
scale nationally (EPCI: \emph{Établissement public de coopération
intercommunale}, an administrative level gathering multiple towns or
cities) and at the suburban scale for the Paris, Lyon, and Marseille
metropolitan areas. For this study, we focused on mainland France,
because vaccination rates are much lower in oversea localities, and
because determinants of vaccination rates are likely to differ in
oversea localities compared to mainland ones. Our dataset included 1555
districts (1228 EPCIs and 327 districts at the suburban scale in Paris,
Lyon, Marseille).

The vaccination dataset for mainland France encompasses about 64.5
million individuals (median district size 22310 inhabitants,
interquartile range 11012--43038). The vaccination data are available by
age class: 00--19, 20--39, 40--54, 55--64, 65--74, 75 and over.
Population sizes for each locality and each age class are also provided.

We paired these vaccination data with three other datasets gathering
socio-economic, political orientation and geographic variables.

Socio-economic data are provided by the French national statistics
institute (INSEE), and are available at the same administrative levels
as the vaccination data. We selected the most recent dataset available
(year 2018). The different variables available in the dataset are
classified by INSEE according to 8 categories (Activity, Education,
Employment, Family, Housing, Immigration, Income, Population).\\
Latitude, longitude and surface data were extracted from open geographic
datasets. We calculated from them four additional geographic indicators:
distance to Paris, relative position along a South-East--North-West
gradient, relative position along a South-West--North-East gradient, and
local population density.\\
Political orientation data consisted of the results of the 2017
Presidential election in France, which we aggregated to reconstitute the
same administrative levels as the vaccination dataset. This political
dataset contains the proportions of votes for each of the 11 candidates
of the first round, 2 candidates of the second round (Macron and Le
Pen), and proportion of abstention at each round.

These three datasets comprised 312 indicators. We then removed those
indicators with over 5\% missing data, or with over 0.9 correlation with
other indicators of the dataset, which left us with 141 indicators: 123
socio-economic indicators (Activity: n = 10; Education: n = 16;
Employment: n = 25; Family: n = 20; Housing: n = 30; Immigration: n = 1;
Income: n = 13; Population: n = 8); 6 geographic indicators; 12
political indicators.

\hypertarget{analysis}{%
\subsection{Analysis}\label{analysis}}

Vaccination was accessible to all adults in France after 27 May 2021. It
opened to teenagers (12-17 year olds) on 15 June 2021, and to children
(5-11 year olds) on 22 December 2021. Because of this differential
accessibility of vaccines, and because vaccine passport rules also
differed for non-adults, we excluded the 00-19 age class from our
analysis, and focused on vaccination rates among 20+ year-old
individuals (hereafter ``adults'').

For each indicator in our dataset, at each of the four chosen dates
(weeks 2021-W27, 2021-W31, 2021-W35, 2021-W49, 2022-W03, 2022-W07), we
considered the association between living in a district above the median
of a that indicator and individual first-dose vaccination rates among
adults. Odds ratios (OR) were computed from the output of a logistic
regression. To be able to compare predictors irrespective of the
direction of the effect, we considered the maximum of \texttt{OR,\ 1/OR}
(hereafter \(\overline{OR}\)). Note that vaccination data are at the
individual level, and indicator data at the district level. The analysis
is done at the individual level, with indicators characterizing the
geographic districts in which individuals live.\\
For each date, we determined a significance threshold by computing odds
ratios on 1000 random permutations of a predictor, and identifying the
value of the 99\% percentile odd ratios (\(\overline{OR}\)) of these
permuted data.

For representative indicators among the most statistically significantly
associated ones, we estimated standardized vaccination rates among
adults over time, for each decile of each indicator (treated as a
factor). These estimations were obtained from a logistic model taking
age class into account; adult vaccination rates were standarsized using
an age distribution matching that of mainland France.

All analysis code is available at XXX; analyses were done in R version
4.0.4 (2021-02-15).

\hypertarget{results}{%
\section{Results}\label{results}}

We investigated the associations between each of the 141 indicators
characterizing districts of residence, and the fact of having received
at least one Covid-19 vaccine dose, on the whole population of mainland
France. Two indicators were among the top five most associated one at
all time points (see Figure @ref(fig:figManhattan)): the share of local
income coming from unemployment benefits (\texttt{Unemployment\_Benef};
strongest association on 2022-01-23, \(OR = 0.716\)) and vote for the
``anti-establishment'' political party represented by the candidate
Asselineau (\texttt{Asselineau}; \(OR = 0.712\) on 2022-02-20). The
three other most associated indicators did not change in the later dates
that we considered, and were the proportion of immigrants in the
district (\texttt{Immigrant}; \(OR = 0.713\) on 2022-02-20), the
district's relative position along a North-West--South-East gradient
(\texttt{NO-SE}; \(OR = 0.745\) on 2021-12-12) and the proportion of
overcrowded households (\texttt{Overcrowding\_rate}; \(OR = 0.738\) on
2022-01-23).

\begin{figure}
\centering
\includegraphics{ms_files/figure-latex/figManhattan-1.pdf}
\caption{Manhattan plots of the Odds ratios for each of the indicator of
our dataset, by date. Left column: around the Sanitary Pass
implementation; right column: around the Vaccine Pass implementation.
The top odds ratios are labelled at each time point; the symbol next to
the name indicates the direction of the effect. The gray rectangle
corresponds to the 99\% percentile of odds ratios in the permuted data;
points falling in the rectangle are considered as non-significant.}
\end{figure}

Our odds ratio calculations were based on a crude version of each
indicator, which were dichotomized into values above or below the median
of each indicator. To better visualize the effects (or lack thereof) of
the sanitary and vaccine passes on vaccination rates over time, we
computed age-adjusted vaccination rates over time, by decile of three of
the most associated indicators, treated as factors (see Figure
@ref(fig:figOverTime)). The Sanitary Pass, implemented in the Summer
2021, led to an overall increase in vaccination rates; on the other
hand, the Vaccine Pass, implemented in the end of 2021, did not affect
the evolution of vaccination rates. Heterogeneities in vaccination rates
persisted after both types of pass; vaccination rates gradually decrease
by decile of each indicator, confirming the association of these
indicators with vaccination rates without threshold effect. Of note, for
the Unemployment and Asselineau vote indicators, the difference between
the 9th and 10th deciles appears to be much larger than between the
other consecutive deciles.

\begin{figure}
\centering
\includegraphics{ms_files/figure-latex/figOverTime-1.pdf}
\caption{Age-adjusted vaccination rates among adults, over time, by
decile of each indicator (presented by a color gradient). The vertical
lines indicate the dates of announcements and implementations of the
sanitary and vaccine passes.}
\end{figure}

Finally, historically under-vaccinated areas in France stand out as
being less vaccinated against Covid-19, in particular the South-East
region (see Figure @ref(fig:figMap)).

\begin{figure}
\centering
\includegraphics{ms_files/figure-latex/figMap-1.pdf}
\caption{Adult vaccination rates by district of mainland France}
\end{figure}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

Our results, based on exhaustive national datasets, indicate that the
French sanitary pass, and the later vaccine pass, did not solve Covid-19
vaccination heterogeneities, but instead crystallized them. Indicators
most associated with vaccination rates were associated to poverty,
immigration, anti-establishment vote (or abstention), and a North-West
-- South-East contrast. For instance, the odds for an adult to still be
unvaccinated by the end of February 2021 are about 1.4 times higher when
living in the districts with higher than median value share of income
coming from unemployment benefits, than when living in the districts
with lower than median value.

The indicators associated to vaccination rates can be interpreted in the
light of the dimensions of vaccine hesitancy (J. K. Ward et al. 2022). A
first reason for vaccine hesitancy is complacency: not fully perceiving
the benefit of vaccination or the risks of severe disease. While in this
case a sanitary or vaccine pass may convince complacent individuals to
get vaccinated, it is less efficient if the associated constrain is low.
As the French domestic pass was associated to pay-for activities
(restaurants, tourism), its persuading effect could be limited among
poorer populations. This may explain the association of lower
vaccination rate with poverty in the data that we analyzed: vaccination
rates decrease as the share of local income coming from unemployment
benefits (\texttt{Unemployment\_Benef}) or the proportion of overcrowded
households (\texttt{Overcrowding\_rate})) increase.\\
A second reason for vaccine hesitancy is confidence, i.e.~trust in the
vaccine, in the health care system, and more generally in the government
(J. K. Ward et al. 2022; Lindholt et al. 2021). A survey conducted in
July 2021 in France confirmed that trust in the government and trust in
scientists were associated to higher odds to be vaccinated (Bajos et al.
2022). Votes for Mr Asselineau -- which represented a minority of cast
votes in 2017 in France (less than \(1\%\) overall) -- can be
interpreted as mistrust in the government (or more generally, against
the establishment): This candidate for instance proposed that France
exits the European Union, leave the Euro zone and reinstall the Franc
currency; he was a proponent of hydroxychloroquin and ivermectin during
the Covid-19 pandemic, and publicly expressed doubts about the safety of
available Covid-19 vaccines. The association of higher proportion of
votes for Mr Asselineau with lower vaccination rates can be interpreted
as revealing a lack of confidence for the government. Noteworthily,
among political indicators, the second strongest association is with
abstention rates (higher abstention rates being associated to lower
vaccination rates), again signaling higher distrust for institutions (J.
K. Ward et al. 2020). Likewise, the lower vaccinations rates in the
South-East of France can be interpreted as mistrust of the central
government in Paris.\\
Finally, a third reason for vaccine hesitancy is convenience, that is,
the availability and accessibility of the vaccines (J. K. Ward et al.
2022). During the first half of 2021, vaccination rate in France was
mostly constrained by dose availability. Vaccination slots were to be
booked online, and there was no general system for sending individual
invitations to get vaccinated. It is therefore still possible that, in
spite of some local outreach efforts, vaccine accessibility remained an
issue, which may explain at least part of the association of lower
vaccination rates with poverty. These accessibility issues may also
explain the association we find between lower vaccination rates and
living in a district with a high proportion of immigrants, which may for
instance reveal language barriers. These associations of lower
vaccination rates with more poverty and with higher proportions of
immigrants in the district of residence are compatible with the results
of a survey conducted in July 2021 in France (Bajos et al. 2022) on
close to 81000 participants, which indicated that unvaccinated
respondents were more likely to have lower income and more likely to
belong to racialised minorities than vaccinated respondents

Relative position of the district of residency along a
North-West--South-East gradient is also associated with vaccination
probability, the South-East being less vaccinated. This geographic
feature, already documented for other kinds of vaccination (Guimier
2021), have been shown to be the consequence of multiple determinants
with a common consequence: a local climate of mistrust for the central
Parisian power. Politically, anti-system votes (from the right as well
as from the left) are traditionally concentrated in the South-East of
France. Medically, General Practitioners (GPs) based in the South-East,
and to a lesser extent those in the South-West, have been shown to tend
to have a more negative opinion of vaccination than their colleagues
practicing in the northern part of France (Gautier, Jestin, and Beck
2013). This greater skepticism influences GP practices and attitudes,
resulting in a lesser degree of compliance with vaccination schedules
than GPs in the northern half of France (Collange et al. 2015). Physical
distance to the central government and institutions, based in Paris,
coupled with a sense of belonging to a local community with a strong
cultural identity, as is the case for example in the Marseille
metropolis or in the Cévennes, play a role in indifference or mistrust
towards institutions perceived as distant authorities (Guimier 2021).
Finally, in and around the Marseille metropolis, the image of a
rebellious territory was reinforced since the first months of the
epidemic in France through the hypermediatized Pr Didier Raoult. Based
in Marseille, he was a promoter of a controversial treatment against
Covid-19 based on hydroxychloroquine and azithromycin (Schultz et al.
2022), and later held ambiguous positions regarding Covid-19
vaccination. He has become a local icon, thanks to his anti-system
positions, and against the hostility of most of the medical world
towards his work. All in all, around the city of Marseille, and more
broadly in South-Eastern France, the climate of suspicion against
Parisian institutions, which had long been rooted in the area, hardened
during the Covid-19 crisis, and was associated with distrust of Covid-19
vaccines.

The design of our study offers several advantages. First, we used a
data-driven approach, i.e.~we did not focus on indicators that we
\emph{a priori} thought to be associated with vaccination rate. The
indicators that we identified as the most associated with vaccination
rates were not biased towards our previous knowledge or surveys about
vaccine hesitancy. Secondly, the data that we used are real-world data
on effective vaccination, and not vaccination intentions. Intentions to
be vaccinated and realized vaccination may not always match, especially
with the introduction of measures like the French Sanitary and Vaccine
Passes. For instance, according to a survey conducted in the Fall 2021,
the introduction of the sanitary pass led to an increase in the share of
individuals reporting being ``angry they had to be vaccinated'' (J. K.
Ward et al. 2022). From an immediate public health perspective, such as
the limitation of the number of severe cases, realized vaccination rates
are a more useful metric. Finally, the vaccination data we used are
based on records of the national health insurance service: they cover
64.5 million individuals living in mainland France, and vaccination
rates are not self-reported, which strongly limits reporting bias.

Still, the design of our study also presents limitations. While our
vaccination data are at the individual level, the socio-economic,
political and geographic indicators are at the district level, and must
therefore be interpreted as such: for instance, we cannot not show that
receiving unemployment benefits is associated with lower vaccination
probability, but we find an association with lower vaccination
probability and the fact of living in a district where a large share of
income comes from unemployment benefits. In addition, although the
different indicators are analysed independently in our study, their
combinations may affect vaccination rates. For instance, the effect of
mistrust in the government on vaccination refusal was shown to be even
stronger among individuals from lower social classes than from higher
social classes (Bajos et al. 2022). Finally, our data do not inform
directly on the reasons for non-vaccination -- e.g., whether it is
hesitancy, refusal, or accessibility issues, which is why our approach
is complementary to qualitative surveys.

To conclude, by emphasizing a differentiated use of COVID-19 vaccination
according to a socio-economic gradient, our study confirms the strong
impact of social inequalities on COVID-19. Previous research found that
the most deprived areas have been disproportionately infected and
hospitalized during the pandemic (Jannot et al. 2021; Bajos et al.
2021). We further show that poorer districts are also the least
vaccinated and, hence, the most still at risk, despite the widely
celebrated domestic sanitary pass. There is an urgent need to define new
vaccination policies that truly address social inequities.

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-bajosWhenLockdownPolicies2021}{}}%
Bajos, Nathalie, Florence Jusot, Ariane Pailhé, Alexis Spire, Claude
Martin, Laurence Meyer, Nathalie Lydié, et al. 2021. {``When Lockdown
Policies Amplify Social Inequalities in {COVID-19} Infections: Evidence
from a Cross-Sectional Population-Based Survey in {France}.''} \emph{BMC
Public Health} 21 (1): 705.
\url{https://doi.org/10.1186/s12889-021-10521-5}.

\leavevmode\vadjust pre{\hypertarget{ref-bajosWhenMistrustGovernment2022}{}}%
Bajos, Nathalie, Alexis Spire, Lena Silberzan, Antoine Sireyjol,
Florence Jusot, Laurence Meyer, Jeanna-Eve Franck, and Josiane
Warszawski. 2022. {``When Mistrust in the Government and Scientists
Reinforce Social Inequalities in Vaccination Against {Covid-19}.''}
Preprint. {Public and Global Health}.
\url{https://doi.org/10.1101/2022.02.23.22271397}.

\leavevmode\vadjust pre{\hypertarget{ref-caspiSocioeconomicDisparitiesCOVID192021}{}}%
Caspi, Gil, Avshalom Dayan, Yael Eshal, Sigal Liverant-Taub, Gilad Twig,
Uri Shalit, Yair Lewis, Avi Shina, and Oren Caspi. 2021.
{``Socioeconomic Disparities and {COVID-19} Vaccination Acceptance: A
Nationwide Ecologic Study.''} \emph{Clinical Microbiology and
Infection}, June, S1198743X21002779.
\url{https://doi.org/10.1016/j.cmi.2021.05.030}.

\leavevmode\vadjust pre{\hypertarget{ref-Collange2015}{}}%
Collange, Fanny, Lisa Fressard, Pierre Verger, Fanny Josancy, Rémy
Sebbah, Arnaud Gautier, Christine Jestin, et al. 2015. {``Vaccinations :
Attitudes Et Pratiques Des Médecins Généralistes.''} 910. {Direction de
la recherche, des études, de l'évaluation et des statistiques}.

\leavevmode\vadjust pre{\hypertarget{ref-coulaudCOVID19VaccineIntention2022}{}}%
Coulaud, Pierre-julien, Aidan Ablona, Naseeb Bolduc, Danya Fast, Karine
Bertrand, Jeremy K. Ward, Devon Greyson, Marie Jauffret-Roustide, and
Rod Knight. 2022. {``{COVID-19} Vaccine Intention Among Young Adults:
{Comparative} Results from a Cross-Sectional Study in {Canada} and
{France}.''} \emph{Vaccine} 40 (16): 2442--56.
\url{https://doi.org/10.1016/j.vaccine.2022.02.085}.

\leavevmode\vadjust pre{\hypertarget{ref-europeancommission.directorategeneralforhealthandfoodsafety.StateVaccineConfidence2018}{}}%
European Commission. Directorate General for Health and Food Safety.
2018. \emph{State of Vaccine Confidence in the {EU} 2018.} {LU}:
{Publications Office}.

\leavevmode\vadjust pre{\hypertarget{ref-Gautier2013a}{}}%
Gautier, Arnaud, Christine Jestin, and François Beck. 2013.
{``Vaccination : Baisse de l'adhésion de La Population Et Rôle Clé Des
Professionnels de Santé.''} \emph{La Santé En Action} 423 (2013-03):
50--53.

\leavevmode\vadjust pre{\hypertarget{ref-guimierResistancesFrancaisesAux2021}{}}%
Guimier, Lucie. 2021. {``Les Résistances Françaises Aux Vaccinations :
Continuité Et Ruptures à La Lumière de La Pandémie de {Covid-19}:''}
\emph{Hérodote} N\textdegree{} 183 (4): 227--50.
\url{https://doi.org/10.3917/her.183.0227}.

\leavevmode\vadjust pre{\hypertarget{ref-jannotLowincomeNeighbourhoodWas2021}{}}%
Jannot, Anne-Sophie, Hector Countouris, Alexis Van Straaten, Anita
Burgun, Sandrine Katsahian, and Bastien Rance. 2021. {``Low-Income
Neighbourhood Was a Key Determinant of Severe {COVID-19} Incidence
During the First Wave of the Epidemic in {Paris}.''} \emph{Journal of
Epidemiology and Community Health}, June, jech-2020-216068.
\url{https://doi.org/10.1136/jech-2020-216068}.

\leavevmode\vadjust pre{\hypertarget{ref-lindholtPublicAcceptanceCOVID192021}{}}%
Lindholt, Marie Fly, Frederik Jørgensen, Alexander Bor, and Michael Bang
Petersen. 2021. {``Public Acceptance of {COVID-19} Vaccines:
Cross-National Evidence on Levels and Individual-Level Predictors Using
Observational Data.''} \emph{BMJ Open} 11 (6): e048172.
\url{https://doi.org/10.1136/bmjopen-2020-048172}.

\leavevmode\vadjust pre{\hypertarget{ref-murthyDisparitiesCOVID19Vaccination2021}{}}%
Murthy, Bhavini Patel, Natalie Sterrett, Daniel Weller, Elizabeth Zell,
Laura Reynolds, Robin L. Toblin, Neil Murthy, et al. 2021.
{``Disparities in {COVID-19 Vaccination Coverage Between Urban} and
{Rural Counties} \textemdash{} {United States}, {December} 14,
2020\textendash{{April}} 10, 2021.''} \emph{MMWR. Morbidity and
Mortality Weekly Report} 70 (20): 759--64.
\url{https://doi.org/10.15585/mmwr.mm7020e3}.

\leavevmode\vadjust pre{\hypertarget{ref-oliu-bartonEffectCOVIDCertificates2022}{}}%
Oliu-Barton, Miquel, Bary SR Pradel, Nicolas Woloszko, Lionel
Guetta-Jeanrenaud, Philippe Aghion, Patrick Artus, Arnaud Fontanet,
Philippe Martin, and Guntram B Wolff. 2022. {``The Effect of {COVID}
Certificates on Vaccine Uptake, Health Outcomes, and the Economy.''}
Preprint. {In Review}.
\url{https://doi.org/10.21203/rs.3.rs-1242919/v2}.

\leavevmode\vadjust pre{\hypertarget{ref-santepubliquefranceCoviPrevEnquetePour2021}{}}%
Santé Publique France. 2021. {``{CoviPrev} : Une Enquête Pour Suivre
l'évolution Des Comportements Et de La Santé Mentale Pendant l'épidémie
de {COVID-19}.''}

\leavevmode\vadjust pre{\hypertarget{ref-schultzDoesPublicKnow2022}{}}%
Schultz, Émilien, Laëtitia Atlani-Duault, Patrick Peretti-Watel, and
Jeremy K. Ward. 2022. {``Does the Public Know When a Scientific
Controversy Is over? {Public} Perceptions of Hydroxychloroquine in
{France} Between {April} 2020 and {June} 2021.''} \emph{Therapies},
January, S0040595722000105.
\url{https://doi.org/10.1016/j.therap.2022.01.008}.

\leavevmode\vadjust pre{\hypertarget{ref-schwarzingerCOVID19VaccineHesitancy2021}{}}%
Schwarzinger, Michaël, Verity Watson, Pierre Arwidson, François Alla,
and Stéphane Luchini. 2021. {``{COVID-19} Vaccine Hesitancy in a
Representative Working-Age Population in {France}: A Survey Experiment
Based on Vaccine Characteristics.''} \emph{The Lancet Public Health} 6
(4): e210--21. \url{https://doi.org/10.1016/S2468-2667(21)00012-8}.

\leavevmode\vadjust pre{\hypertarget{ref-spireSocialInequalitiesHostility2021}{}}%
Spire, Alexis, Nathalie Bajos, and Léna Silberzan. 2021. {``Social
Inequalities in Hostility Toward Vaccination Against {Covid-19}.''}
Preprint. {Public and Global Health}.
\url{https://doi.org/10.1101/2021.06.07.21258461}.

\leavevmode\vadjust pre{\hypertarget{ref-usherBeautifulIdeaHow2021}{}}%
Usher, Ann Danaiya. 2021. {``A Beautiful Idea: How {COVAX} Has Fallen
Short.''} \emph{The Lancet} 397 (10292): 2322--25.
\url{https://doi.org/10.1016/S0140-6736(21)01367-2}.

\leavevmode\vadjust pre{\hypertarget{ref-wardPremiersResultatsEnquete2021}{}}%
Ward, Jeremy. 2021. {``{Premiers résultats de l'enquête SLAVACO Vague 1
et approfondissement de l'analyse de l'enquête COVIREIVAC - les français
et la vaccination}.''}

\leavevmode\vadjust pre{\hypertarget{ref-wardFrenchPublicAttitudes2020}{}}%
Ward, Jeremy K., Caroline Alleaume, Patrick Peretti-Watel, Patrick
Peretti-Watel, Valérie Seror, Sébastien Cortaredona, Odile Launay, et
al. 2020. {``The {French} Public's Attitudes to a Future {COVID-19}
Vaccine: {The} Politicization of a Public Health Issue.''} \emph{Social
Science \& Medicine} 265 (November): 113414.
\url{https://doi.org/10.1016/j.socscimed.2020.113414}.

\leavevmode\vadjust pre{\hypertarget{ref-wardFrenchHealthPass2022}{}}%
Ward, Jeremy K., Fatima Gauna, Amandine Gagneux-Brunon, Elisabeth
Botelho-Nevers, Jean-Luc Cracowski, Charles Khouri, Odile Launay, Pierre
Verger, and Patrick Peretti-Watel. 2022. {``The {French} Health Pass
Holds Lessons for Mandatory {COVID-19} Vaccination.''} \emph{Nature
Medicine}, January. \url{https://doi.org/10.1038/s41591-021-01661-7}.

\leavevmode\vadjust pre{\hypertarget{ref-wardVaccineHesitancyCoercion2019}{}}%
Ward, Jeremy K., Patrick Peretti-Watel, Aurélie Bocquier, Valérie Seror,
and Pierre Verger. 2019. {``Vaccine Hesitancy and Coercion: All Eyes on
{France}.''} \emph{Nature Immunology} 20 (10): 1257--59.
\url{https://doi.org/10.1038/s41590-019-0488-9}.

\leavevmode\vadjust pre{\hypertarget{ref-woutersChallengesEnsuringGlobal2021}{}}%
Wouters, Olivier J, Kenneth C Shadlen, Maximilian Salcher-Konrad, Andrew
J Pollard, Heidi J Larson, Yot Teerawattananon, and Mark Jit. 2021.
{``Challenges in Ensuring Global Access to {COVID-19} Vaccines:
Production, Affordability, Allocation, and Deployment.''} \emph{The
Lancet} 397 (10278): 1023--34.
\url{https://doi.org/10.1016/S0140-6736(21)00306-8}.

\end{CSLReferences}

\end{document}

### 2022-04-11 clean/code/vaccination-indicators.Rmd
clean up files

--- 2022-03-17 code/vaccination-indicators.Rmd
@@
 author: "FD"
-output:
-  html_document:
-    self_contained: no
+output: html_notebook:
   keep_md: true
-    toc: true
-    toc_float: true
-  pdf_document: default
+editor_options: 
+  chunk_output_type: console
 ---
@@
 # Source vaccination data
-source("load-clean_vaccination.R")
+source("1_load-clean_vaccination.R")
 ```
@@
      maxOR.Unemployment_Benef,
-     file = "savevalues.RData")
+     file = "outsavevalues.RData")
 
 ```
-
-# Essais
-
-```{r, eval = FALSE}
-
-v <- dat.all[, c("codgeo", "Abstention")]
-vx <- v[which(is.na(v$Abstention)), ]
-vx
-v[1, ]
-head(v)
-tail(v)
-
-library(inseeLocalData)
-?inseeLocalData
-
-#install.packages("insee")
-library(insee)
-
-get_dataset_list()
-
-https://api.insee.fr/donnees-locales/V0.1/donnees/geo-POP@GEO2021RP2018/EPCI-247100647.INATC
-
-```
-
-```{r, eval = FALSE}
-?prcomp
-
-# Predictors
-# New dataset with the predictors
-dat2 <- dat.nocorr[, -1]
-
-# For each predictor
-for(col in colnames(dat2)){
-  # Get the subset of the data
-  v <- dat2[, col]
-  # Compute the mean value, excluding NAs
-  mv <- mean(v, na.rm = TRUE)
-  # Fill in NAs with the mean
-  v[is.na(v)] <- mv
-  # Put back in the table
-  dat2[, col] <- v
-}
-
-pca <- prcomp(dat2, center = TRUE, scale = TRUE)
-ggbiplot(pca)
-
-head(pca)
-
-library(devtools)
-install_github("vqv/ggbiplot")
-library(ggbiplot)
-
-plot(pca$x[, c("PC1", "PC2")])
-
-pcax <- as.data.frame(pca$x)
-pcax$codgeo <- dat.nocorr$codgeo
-
-thedate <- date3
-sub <- vacc[which(vacc$date == thedate & vacc$classe_age != "TOUT_AGE"), ]
-subb <- adultVacc(sub)
-
-sub3 <- merge(subb, pcax, all = TRUE, by = "codgeo")
-sub3$typeTaux <- discretizeQ(sub3$taux_cumu, prbs = seq(0, 1, by = 0.1))
-palCat <- rev(met.brewer("Hiroshige", n = 10, type = "continuous"))
-names(palCat) <- 1:10
-
-plot(sub3$PC1, sub3$PC2, col = palCat[sub3$typeTaux], pch = 16)
-
-str(pca)
-head(sub3)
-dim(subb)
-dim(pcax)
-
-sort(pca$rotation[, "PC1"], decreasing = TRUE)[1:30]
-sort(pca$rotation[, "PC2"], decreasing = TRUE)[1:30]
-
-head(pca)
-summary(pca)
-
-pca$sdev / sum(pca$sdev)
-str(pca)
-
-length(pca$rotation[, "PC2"])
-length(subb$taux_cumu)
-
-plot(sub3$PC2, sub3$taux_cumu)
-
-out <- matrix(NA, nrow = (ncol(pcax) - 1), ncol = 4)
-for(i in 1:(ncol(pcax) - 1)){
-  mdl <- cor.test(sub3[, paste0("PC", i)], sub3$taux_cumu)
-  out[i, ] <- c(mdl$estimate, mdl$conf.int, mdl$p.value)
-}
-out <- as.data.frame(out)
-names(out) <- c("estimate", "ci1", "ci2", "pval")
-out$PC <- seq_len(nrow(out))
-
-out[order(abs(out$estimate), decreasing = TRUE), ][1:5, ]
-ii <- out[order(abs(out$estimate), decreasing = TRUE), ][1:5, "PC"]
-
-# Composition of the PCs
-for(i in ii){
-  print(i)
-  print(t(sort(pca$rotation[, paste0("PC", i)], decreasing = TRUE)[1:20])) 
-}
-sort(pca$rotation[, "PC2"], decreasing = TRUE)[1:30]
-
-plot(sort(abs(out$estimate)))
-
-range(out$estimate)
-
-head(out)
-mdl2 <- cor.test(sub3$PC2, sub3$taux_cumu)
-mdl2
-
-mdl1 <- cor.test(sub3$PC1, sub3$taux_cumu)
-mdl1
-str(mdl1)
-summary(mdl1)
-mdl3 <- cor.test(sub3$PC3, sub3$taux_cumu)
-mdl3
-
-summary(mdl)
-
-library(nlme)
-?gls
-         gls(divspe ~ loggrad_urb+grad_agrimean, method = "ML", 
-corr=corExp(c(300000,0.7), form=~x_lambert93+y_lambert93, nugget=T), 
-na.action = na.omit, data = df)
-
-```

### 2022-04-11 clean/ms/ms.Rmd
clean up files

--- 2022-04-11 ms/ms.Rmd
@@
 
-load("../code/savevalues.RData")
+load("../code/outsavevalues.RData")
 load("../code/data_indicators.RData") 
@@
 Surveys conducted in 2020 in France showed that respondents with lower education [@schwarzingerCOVID19VaccineHesitancy2021; @coulaudCOVID19VaccineIntention2022], lower income levels or less trust in authorities [@spireSocialInequalitiesHostility2021; @lindholtPublicAcceptanceCOVID192021] were more likely to be hostile to COVID-19 vaccines.
-<!-- A survey conducted in July 2021 in France [@bajosWhenMistrustGovernment2022] on close to 81000 participants indicated that unvaccinated respondents were more likely to have lower income and more likely to belong to racialised minorities than vaccinated ones.
-The survey also confirmed that mistrust in the government was fueling refusal to be vaccinated [@bajosWhenMistrustGovernment2022].
--->
-
-<!-- XX MOVE INTERNATIONAL COMPARISONS IN THE DISCUSSION Whether differential intentions translated into effective differences in vaccination, as described in other countries [Caspi21, Murthy21], remained to be shown in France.
--->
 
@@
 Population sizes for each locality and each age class are also provided.
-<!-- These population sizes are updated monthly to account for individuals aging, potential residential moves, and deaths.
-XXX TODO: Demander pourquoi les tailles de pop sont constantes au cours du temps FD: Removed because was not specified -->
 
@@
 <!-- 
+Key dates:
 
@@
 
-<!-- [moved to Discussion]
-The share of local income coming from unemployment benefits (`Unemployment_Benef`) and the proportion of overcrowded households (`Overcrowding_rate`) are two indicators linked to poverty.
-Votes for Mr Asselineau (`Asselineau`) represented a minority of cast votes in 2017 in France (less than $1\%$ overall).
-This candidate for instance proposed that France exits the European Union, leave the Euro zone and reinstall the Franc currency; he was a proponent of hydroxychloroquin and ivermectin during the Covid-19 pandemic, and publicly expressed doubts about the safety of available Covid-19 vaccines.
--->
-
 ```{r figManhattan, echo=FALSE, fig.height=9, fig.width=9, fig.cap="Manhattan plots of the Odds ratios for each of the indicator of our dataset, by date.
@@
 load("../data/mapFiles_withDepReg.RData")
-load("../data/chefslieux.RData")
+load("../data/mapchefslieux.RData")
 # Choose date
@@
 Our results, based on exhaustive national datasets, indicate that the French sanitary pass, and the later vaccine pass, did not solve Covid-19 vaccination heterogeneities, but instead crystallized them.
-<!-- Indicators that were the most strongly associated to vaccination rates are linked to poverty (the share of local income coming from unemployment benefits (`Unemployment_Benef`), and the proportion of overcrowded households (`Overcrowding_rate`)), immigration (the proportion of immigrants in the population (`Immigrant`)), -->
 Indicators most associated with vaccination rates were associated to poverty, immigration, anti-establishment vote (or abstention), and a North-West -- South-East contrast.

### 2022-04-11 clean/ms/template.tex
clean up files

--- 2022-04-11 ms/ms.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-]{article}
-\title{The French domestic Pass Sanitaire did not solve vaccination
-inequities: a nationwide longitudinal study on 64.5 million individuals}
-\author{F. Débarre, E. Lecoeur, L. Guimier, M. Jauffret-Roustide, A.-S.
-Jannot}
-\date{}
-
-\usepackage{amsmath,amssymb}
-\usepackage{lmodern}
-\usepackage{iftex}
-\ifPDFTeX
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={The French domestic Pass Sanitaire did not solve vaccination inequities: a nationwide longitudinal study on 64.5 million individuals},
-  pdfauthor={F. Débarre, E. Lecoeur, L. Guimier, M. Jauffret-Roustide, A.-S. Jannot},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage[margin=1in]{geometry}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newlength{\cslentryspacingunit} % times entry-spacing
-\setlength{\cslentryspacingunit}{\parskip}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1
-  \let\oldpar\par
-  \def\par{\hangindent=\cslhangindent\oldpar}
-  \fi
-  % set entry spacing
-  \setlength{\parskip}{#2\cslentryspacingunit}
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 \usepackage{setspace}
@@
 \captionsetup[table]{position=bottom}   %% or below
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-
-\begin{document}
-\maketitle
-
-\hypertarget{affiliations}{%
-\subsection{Affiliations}\label{affiliations}}
-
-FD: Institute of Ecology and Environmental Sciences of Paris
-(IEES-Paris, UMR 7618), CNRS, Sorbonne Université, UPEC, IRD, INRAE,
-75252 Paris, France\\
-EL: Clinical research unit, Hôpital Européen Georges Pompidou, APHP,
-Paris, France\\
-LG: French Institute of Geopolitics, Paris, France\\
-MJR: Centre d'Étude des Mouvements Sociaux (Inserm U1276/CNRS
-UMR8044/EHESS), Paris, France.\\
-British Columbia Center For Substance Use (BCCSU), Vancouver, Canada\\
-Bady Center on Law and Social Policy, Buffalo, NY, USA\\
-AJR: Medical Informatics, biostatistics and public health unit, Hôpital
-Européen Georges Pompidou, APHP, Paris, France\\
-Université de Paris, Paris, France\\
-HeKA, Centre de Recherche des Cordeliers, Inserm, INRIA, Paris, France
-
-\emph{Corresponding author:} Anne-Sophie Jannot, Hôpital Européen
-Georges Pompidou, 20 rue Leblanc, 75015 Paris.
-\texttt{annesophie.jannot@aphp.fr}
-
-\hypertarget{keywords}{%
-\subsubsection{Keywords:}\label{keywords}}
-
-vaccination, covid-19, data mining, socio-economic factors, health
-inequities.
-
-\hypertarget{acknowledgements}{%
-\subsection{Acknowledgements}\label{acknowledgements}}
-
-We thank the producers of public datasets, in particular David Levy at
-INSEE and Antoine Rachas at Assurance Maladie.
-
-\hypertarget{funding}{%
-\subsection{Funding}\label{funding}}
-
-EL received funding to match socio-economic data with medical data from
-AP-HP Centre Université de Paris.
-
-\hypertarget{contributions}{%
-\subsection{Contributions}\label{contributions}}
-
-ASJ and FD designed the study with inputs from all authors. EL extracted
-socio-economic and political orientation data at district scale and
-computed indicators. ASJ, EL and FD had full access to aggregated data
-used for this study and take responsibility for the integrity of the
-data. EL and FD did the analyses and takes responsibility for the
-accuracy of the data analysis. FD drafted the paper with the help of
-ASJ, MR. All authors critically revised the manuscript for important
-intellectual content and gave final approval for the version to be
-published.
-
-\hypertarget{conflict-of-interest-statement}{%
-\subsection{Conflict of interest
-statement}\label{conflict-of-interest-statement}}
-
-No conflict of interest to disclose
-
-\hypertarget{data-sources}{%
-\subsection{Data sources}\label{data-sources}}
-
-\begin{itemize}
-\tightlist
-\item
-  Assurance Maladie:
-  \url{https://datavaccin-covid.ameli.fr/explore/dataset/donnees-devaccination-par-epci/}
-  \url{https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-parcommune/information/}
-\item
-  INSEE: \url{https://www.insee.fr/fr/statistiques/5359146\#consulter}
-\end{itemize}
-
-\hypertarget{abstract}{%
-\section{Abstract}\label{abstract}}
-
-Context: To encourage Covid-19 vaccination, France introduced during the
-Summer 2021 a ``Sanitary Pass,'' which morphed into a ``Vaccine Passe''
-in early 2022. While the Sanity Pass led to an increase in Covid-19
-vaccination rates, spatial heterogeneities in vaccination rates
-remained. To identify potential determinants of these heterogeneities
-and evaluate the French Sanitary and Vaccine Pass' efficacies in
-reducing them, we used a data-driven approach on exhaustive nationwide
-data, gathering 141 socio-economic, political and geographic indicators.
-
-Methods: We considered the association between being a district above
-the median value of the first-dose vaccination rates and being above the
-median value of each indicator at different time points: just before the
-sanitary pass announcement (week 2021-W27), just before the sanitary
-pass came into force (week 2021-W31) and one month after (week
-2021-W35), and the equivalent dates for the vaccine pass (weeks
-2021-W49, 2022-W03, 2022-W07). We then considered the change over time
-of vaccination rates according to deciles of the three of the most
-associated indicators.
-
-Results: The indicators most associated with vaccination rates were the
-share of local income coming from unemployment benefits, the proportion
-of overcrowded households, the proportion of immigrants in the district,
-and vote for an ``anti-establishment'' candidate at the 2017
-Presidential election. Vaccination rate also were also contrasted along
-a North-West -- South East axis, with lower vaccination coverage in the
-South-East of France.
-
-Conclusion: Our analysis reveals that, both before and after the
-introduction of the French sanitary and vaccination passes, factors with
-the largest impact are related to poverty, immigration, and trust in the
-government.
-
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
-
-The rapid development of effective COVID-19 vaccines brought the hope of
-a rapid return to normalcy, but heterogeneous vaccination rates, both
-among countries because of inequitable distributions of doses (Usher
-2021) and within countries (Caspi et al. 2021; Murthy et al. 2021),
-jeopardize epidemic control.
-
-Hesitancy and hostility toward vaccination have been comparatively high
-in France in recent decades (European Commission. Directorate General
-for Health and Food Safety. 2018). Modern vaccine hesitancy in France
-started with claims of a link between the hepatitis B vaccine and
-multiple sclerosis (J. K. Ward et al. 2019); it strongly increased
-following the 2009-2010 vaccination campaign against pandemic flu, the
-contested management of which in France was a tipping point that led to
-higher vaccine hesitancy and hostility (Guimier 2021; J. K. Ward et al.
-2019). The trend was confirmed with the COVID-19 pandemic (Lindholt et
-al. 2021; Spire, Bajos, and Silberzan 2021): just before Covid-19
-vaccines became available, intentions to get vaccinated were
-comparatively very low in France compared to other countries (44\% of
-the respondents in (Wouters et al. 2021) in the Fall 2020; about 40\% of
-respondent in (Santé Publique France 2021) in December 2020). Acceptance
-of the COVID-19 vaccine however gradually grew during 2021 (Santé
-Publique France 2021; J. Ward 2021).
-
-Spatial heterogeneties in vaccination rates have already been documented
-in France for previous vaccines. Vaccination coverage for the Hepatitis
-B vaccine and for the Measles-Mumps-Rubella vaccine has been lower in
-the South of France, and especially in the South-East of the country
-(Guimier 2021). Distance to the central political power in Paris, as
-well as a sense of belonging to a local community with a strong cultural
-identity, have been put forward as potential explanations for this
-geographic gradient in vaccination rates (Guimier 2021).
-
-Attitudes toward vaccination are also known to be influenced by social
-and territorial inequalities. Surveys conducted in 2020 in France showed
-that respondents with lower education (Schwarzinger et al. 2021; Coulaud
-et al. 2022), lower income levels or less trust in authorities (Spire,
-Bajos, and Silberzan 2021; Lindholt et al. 2021) were more likely to be
-hostile to COVID-19 vaccines.
-
-By mid-July 2021, France was facing an epidemic wave due to the Delta
-variant. To speed up vaccination, President Macron announced on 12 July
-2021 the implementation of a domestic ``sanitary pass'' (le passe
-sanitaire), which came fully into force on 9 August 2021. Presenting as
-a QR code, a long-term sanitary pass was obtained after full vaccination
-(two doses, or only one dose in the case of a documented previous
-Covid-19 infection), and a short-term version could be obtained with a
-negative Covid-19 test. The ``sanitary pass'' was required in most
-cultural venues, for both indoor and outdoor dining and in health
-structures. This announcement led to an unprecedented demand for
-vaccination (Oliu-Barton et al. 2022), which was considered
-internationally as a potential model to follow. Vaccination rates
-climbed from about 64\% of the population over 20 years old by 11 July
-2021 (52\% of all ages) to 82 on 5 September 2021 (69\% of all ages).
-Because it targeted pay-for social activities, however, the ``sanitary
-pass'' was feared to have a limited impact on vaccination inequities. By
-mid-December 2021, at the height of the winter Delta wave, and while the
-Omicron wave was looming, the French Prime Minister announced that the
-Sanitary Pass would become a Vaccine Pass, i.e.~that a negative Covid-19
-test would not provide a temporary QR code any longer for adults --
-making vaccination implicitly mandatory in France. The Vaccine Pass came
-into force on 24 January 2022.
-
-This study aims to obtain further insights on the socio-economic,
-political and geographic factor associated with vaccination rates, and
-to evaluate the effect of the French domestic sanitary pass, by using
-nation-wide, exhaustive datasets.
-
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
-
-\hypertarget{data}{%
-\subsection{Data}\label{data}}
-
-The French state health insurance service (Assurance Maladie) provides
-public datasets of vaccination rates in France. These datasets are based
-on aggregated individual data on beneficiaries of the national health
-insurance service who received health care in the past year. These
-exhaustive datasets are updated weekly, and are provided at the district
-scale nationally (EPCI: \emph{Établissement public de coopération
-intercommunale}, an administrative level gathering multiple towns or
-cities) and at the suburban scale for the Paris, Lyon, and Marseille
-metropolitan areas. For this study, we focused on mainland France,
-because vaccination rates are much lower in oversea localities, and
-because determinants of vaccination rates are likely to differ in
-oversea localities compared to mainland ones. Our dataset included 1555
-districts (1228 EPCIs and 327 districts at the suburban scale in Paris,
-Lyon, Marseille).
-
-The vaccination dataset for mainland France encompasses about 64.5
-million individuals (median district size 22310 inhabitants,
-interquartile range 11012--43038). The vaccination data are available by
-age class: 00--19, 20--39, 40--54, 55--64, 65--74, 75 and over.
-Population sizes for each locality and each age class are also provided.
-
-We paired these vaccination data with three other datasets gathering
-socio-economic, political orientation and geographic variables.
-
-Socio-economic data are provided by the French national statistics
-institute (INSEE), and are available at the same administrative levels
-as the vaccination data. We selected the most recent dataset available
-(year 2018). The different variables available in the dataset are
-classified by INSEE according to 8 categories (Activity, Education,
-Employment, Family, Housing, Immigration, Income, Population).\\
-Latitude, longitude and surface data were extracted from open geographic
-datasets. We calculated from them four additional geographic indicators:
-distance to Paris, relative position along a South-East--North-West
-gradient, relative position along a South-West--North-East gradient, and
-local population density.\\
-Political orientation data consisted of the results of the 2017
-Presidential election in France, which we aggregated to reconstitute the
-same administrative levels as the vaccination dataset. This political
-dataset contains the proportions of votes for each of the 11 candidates
-of the first round, 2 candidates of the second round (Macron and Le
-Pen), and proportion of abstention at each round.
-
-These three datasets comprised 312 indicators. We then removed those
-indicators with over 5\% missing data, or with over 0.9 correlation with
-other indicators of the dataset, which left us with 141 indicators: 123
-socio-economic indicators (Activity: n = 10; Education: n = 16;
-Employment: n = 25; Family: n = 20; Housing: n = 30; Immigration: n = 1;
-Income: n = 13; Population: n = 8); 6 geographic indicators; 12
-political indicators.
-
-\hypertarget{analysis}{%
-\subsection{Analysis}\label{analysis}}
-
-Vaccination was accessible to all adults in France after 27 May 2021. It
-opened to teenagers (12-17 year olds) on 15 June 2021, and to children
-(5-11 year olds) on 22 December 2021. Because of this differential
-accessibility of vaccines, and because vaccine passport rules also
-differed for non-adults, we excluded the 00-19 age class from our
-analysis, and focused on vaccination rates among 20+ year-old
-individuals (hereafter ``adults'').
-
-For each indicator in our dataset, at each of the four chosen dates
-(weeks 2021-W27, 2021-W31, 2021-W35, 2021-W49, 2022-W03, 2022-W07), we
-considered the association between living in a district above the median
-of a that indicator and individual first-dose vaccination rates among
-adults. Odds ratios (OR) were computed from the output of a logistic
-regression. To be able to compare predictors irrespective of the
-direction of the effect, we considered the maximum of \texttt{OR,\ 1/OR}
-(hereafter \(\overline{OR}\)). Note that vaccination data are at the
-individual level, and indicator data at the district level. The analysis
-is done at the individual level, with indicators characterizing the
-geographic districts in which individuals live.\\
-For each date, we determined a significance threshold by computing odds
-ratios on 1000 random permutations of a predictor, and identifying the
-value of the 99\% percentile odd ratios (\(\overline{OR}\)) of these
-permuted data.
-
-For representative indicators among the most statistically significantly
-associated ones, we estimated standardized vaccination rates among
-adults over time, for each decile of each indicator (treated as a
-factor). These estimations were obtained from a logistic model taking
-age class into account; adult vaccination rates were standarsized using
-an age distribution matching that of mainland France.
-
-All analysis code is available at XXX; analyses were done in R version
-4.0.4 (2021-02-15).
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-We investigated the associations between each of the 141 indicators
-characterizing districts of residence, and the fact of having received
-at least one Covid-19 vaccine dose, on the whole population of mainland
-France. Two indicators were among the top five most associated one at
-all time points (see Figure @ref(fig:figManhattan)): the share of local
-income coming from unemployment benefits (\texttt{Unemployment\_Benef};
-strongest association on 2022-01-23, \(OR = 0.716\)) and vote for the
-``anti-establishment'' political party represented by the candidate
-Asselineau (\texttt{Asselineau}; \(OR = 0.712\) on 2022-02-20). The
-three other most associated indicators did not change in the later dates
-that we considered, and were the proportion of immigrants in the
-district (\texttt{Immigrant}; \(OR = 0.713\) on 2022-02-20), the
-district's relative position along a North-West--South-East gradient
-(\texttt{NO-SE}; \(OR = 0.745\) on 2021-12-12) and the proportion of
-overcrowded households (\texttt{Overcrowding\_rate}; \(OR = 0.738\) on
-2022-01-23).
-
-\begin{figure}
-\centering
-\includegraphics{ms_files/figure-latex/figManhattan-1.pdf}
-\caption{Manhattan plots of the Odds ratios for each of the indicator of
-our dataset, by date. Left column: around the Sanitary Pass
-implementation; right column: around the Vaccine Pass implementation.
-The top odds ratios are labelled at each time point; the symbol next to
-the name indicates the direction of the effect. The gray rectangle
-corresponds to the 99\% percentile of odds ratios in the permuted data;
-points falling in the rectangle are considered as non-significant.}
-\end{figure}
-
-Our odds ratio calculations were based on a crude version of each
-indicator, which were dichotomized into values above or below the median
-of each indicator. To better visualize the effects (or lack thereof) of
-the sanitary and vaccine passes on vaccination rates over time, we
-computed age-adjusted vaccination rates over time, by decile of three of
-the most associated indicators, treated as factors (see Figure
-@ref(fig:figOverTime)). The Sanitary Pass, implemented in the Summer
-2021, led to an overall increase in vaccination rates; on the other
-hand, the Vaccine Pass, implemented in the end of 2021, did not affect
-the evolution of vaccination rates. Heterogeneities in vaccination rates
-persisted after both types of pass; vaccination rates gradually decrease
-by decile of each indicator, confirming the association of these
-indicators with vaccination rates without threshold effect. Of note, for
-the Unemployment and Asselineau vote indicators, the difference between
-the 9th and 10th deciles appears to be much larger than between the
-other consecutive deciles.
-
-\begin{figure}
-\centering
-\includegraphics{ms_files/figure-latex/figOverTime-1.pdf}
-\caption{Age-adjusted vaccination rates among adults, over time, by
-decile of each indicator (presented by a color gradient). The vertical
-lines indicate the dates of announcements and implementations of the
-sanitary and vaccine passes.}
-\end{figure}
-
-Finally, historically under-vaccinated areas in France stand out as
-being less vaccinated against Covid-19, in particular the South-East
-region (see Figure @ref(fig:figMap)).
-
-\begin{figure}
-\centering
-\includegraphics{ms_files/figure-latex/figMap-1.pdf}
-\caption{Adult vaccination rates by district of mainland France}
-\end{figure}
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
-
-Our results, based on exhaustive national datasets, indicate that the
-French sanitary pass, and the later vaccine pass, did not solve Covid-19
-vaccination heterogeneities, but instead crystallized them. Indicators
-most associated with vaccination rates were associated to poverty,
-immigration, anti-establishment vote (or abstention), and a North-West
--- South-East contrast. For instance, the odds for an adult to still be
-unvaccinated by the end of February 2021 are about 1.4 times higher when
-living in the districts with higher than median value share of income
-coming from unemployment benefits, than when living in the districts
-with lower than median value.
-
-The indicators associated to vaccination rates can be interpreted in the
-light of the dimensions of vaccine hesitancy (J. K. Ward et al. 2022). A
-first reason for vaccine hesitancy is complacency: not fully perceiving
-the benefit of vaccination or the risks of severe disease. While in this
-case a sanitary or vaccine pass may convince complacent individuals to
-get vaccinated, it is less efficient if the associated constrain is low.
-As the French domestic pass was associated to pay-for activities
-(restaurants, tourism), its persuading effect could be limited among
-poorer populations. This may explain the association of lower
-vaccination rate with poverty in the data that we analyzed: vaccination
-rates decrease as the share of local income coming from unemployment
-benefits (\texttt{Unemployment\_Benef}) or the proportion of overcrowded
-households (\texttt{Overcrowding\_rate})) increase.\\
-A second reason for vaccine hesitancy is confidence, i.e.~trust in the
-vaccine, in the health care system, and more generally in the government
-(J. K. Ward et al. 2022; Lindholt et al. 2021). A survey conducted in
-July 2021 in France confirmed that trust in the government and trust in
-scientists were associated to higher odds to be vaccinated (Bajos et al.
-2022). Votes for Mr Asselineau -- which represented a minority of cast
-votes in 2017 in France (less than \(1\%\) overall) -- can be
-interpreted as mistrust in the government (or more generally, against
-the establishment): This candidate for instance proposed that France
-exits the European Union, leave the Euro zone and reinstall the Franc
-currency; he was a proponent of hydroxychloroquin and ivermectin during
-the Covid-19 pandemic, and publicly expressed doubts about the safety of
-available Covid-19 vaccines. The association of higher proportion of
-votes for Mr Asselineau with lower vaccination rates can be interpreted
-as revealing a lack of confidence for the government. Noteworthily,
-among political indicators, the second strongest association is with
-abstention rates (higher abstention rates being associated to lower
-vaccination rates), again signaling higher distrust for institutions (J.
-K. Ward et al. 2020). Likewise, the lower vaccinations rates in the
-South-East of France can be interpreted as mistrust of the central
-government in Paris.\\
-Finally, a third reason for vaccine hesitancy is convenience, that is,
-the availability and accessibility of the vaccines (J. K. Ward et al.
-2022). During the first half of 2021, vaccination rate in France was
-mostly constrained by dose availability. Vaccination slots were to be
-booked online, and there was no general system for sending individual
-invitations to get vaccinated. It is therefore still possible that, in
-spite of some local outreach efforts, vaccine accessibility remained an
-issue, which may explain at least part of the association of lower
-vaccination rates with poverty. These accessibility issues may also
-explain the association we find between lower vaccination rates and
-living in a district with a high proportion of immigrants, which may for
-instance reveal language barriers. These associations of lower
-vaccination rates with more poverty and with higher proportions of
-immigrants in the district of residence are compatible with the results
-of a survey conducted in July 2021 in France (Bajos et al. 2022) on
-close to 81000 participants, which indicated that unvaccinated
-respondents were more likely to have lower income and more likely to
-belong to racialised minorities than vaccinated respondents
-
-Relative position of the district of residency along a
-North-West--South-East gradient is also associated with vaccination
-probability, the South-East being less vaccinated. This geographic
-feature, already documented for other kinds of vaccination (Guimier
-2021), have been shown to be the consequence of multiple determinants
-with a common consequence: a local climate of mistrust for the central
-Parisian power. Politically, anti-system votes (from the right as well
-as from the left) are traditionally concentrated in the South-East of
-France. Medically, General Practitioners (GPs) based in the South-East,
-and to a lesser extent those in the South-West, have been shown to tend
-to have a more negative opinion of vaccination than their colleagues
-practicing in the northern part of France (Gautier, Jestin, and Beck
-2013). This greater skepticism influences GP practices and attitudes,
-resulting in a lesser degree of compliance with vaccination schedules
-than GPs in the northern half of France (Collange et al. 2015). Physical
-distance to the central government and institutions, based in Paris,
-coupled with a sense of belonging to a local community with a strong
-cultural identity, as is the case for example in the Marseille
-metropolis or in the Cévennes, play a role in indifference or mistrust
-towards institutions perceived as distant authorities (Guimier 2021).
-Finally, in and around the Marseille metropolis, the image of a
-rebellious territory was reinforced since the first months of the
-epidemic in France through the hypermediatized Pr Didier Raoult. Based
-in Marseille, he was a promoter of a controversial treatment against
-Covid-19 based on hydroxychloroquine and azithromycin (Schultz et al.
-2022), and later held ambiguous positions regarding Covid-19
-vaccination. He has become a local icon, thanks to his anti-system
-positions, and against the hostility of most of the medical world
-towards his work. All in all, around the city of Marseille, and more
-broadly in South-Eastern France, the climate of suspicion against
-Parisian institutions, which had long been rooted in the area, hardened
-during the Covid-19 crisis, and was associated with distrust of Covid-19
-vaccines.
-
-The design of our study offers several advantages. First, we used a
-data-driven approach, i.e.~we did not focus on indicators that we
-\emph{a priori} thought to be associated with vaccination rate. The
-indicators that we identified as the most associated with vaccination
-rates were not biased towards our previous knowledge or surveys about
-vaccine hesitancy. Secondly, the data that we used are real-world data
-on effective vaccination, and not vaccination intentions. Intentions to
-be vaccinated and realized vaccination may not always match, especially
-with the introduction of measures like the French Sanitary and Vaccine
-Passes. For instance, according to a survey conducted in the Fall 2021,
-the introduction of the sanitary pass led to an increase in the share of
-individuals reporting being ``angry they had to be vaccinated'' (J. K.
-Ward et al. 2022). From an immediate public health perspective, such as
-the limitation of the number of severe cases, realized vaccination rates
-are a more useful metric. Finally, the vaccination data we used are
-based on records of the national health insurance service: they cover
-64.5 million individuals living in mainland France, and vaccination
-rates are not self-reported, which strongly limits reporting bias.
-
-Still, the design of our study also presents limitations. While our
-vaccination data are at the individual level, the socio-economic,
-political and geographic indicators are at the district level, and must
-therefore be interpreted as such: for instance, we cannot not show that
-receiving unemployment benefits is associated with lower vaccination
-probability, but we find an association with lower vaccination
-probability and the fact of living in a district where a large share of
-income comes from unemployment benefits. In addition, although the
-different indicators are analysed independently in our study, their
-combinations may affect vaccination rates. For instance, the effect of
-mistrust in the government on vaccination refusal was shown to be even
-stronger among individuals from lower social classes than from higher
-social classes (Bajos et al. 2022). Finally, our data do not inform
-directly on the reasons for non-vaccination -- e.g., whether it is
-hesitancy, refusal, or accessibility issues, which is why our approach
-is complementary to qualitative surveys.
-
-To conclude, by emphasizing a differentiated use of COVID-19 vaccination
-according to a socio-economic gradient, our study confirms the strong
-impact of social inequalities on COVID-19. Previous research found that
-the most deprived areas have been disproportionately infected and
-hospitalized during the pandemic (Jannot et al. 2021; Bajos et al.
-2021). We further show that poorer districts are also the least
-vaccinated and, hence, the most still at risk, despite the widely
-celebrated domestic sanitary pass. There is an urgent need to define new
-vaccination policies that truly address social inequities.
-
-\hypertarget{references}{%
-\section*{References}\label{references}}
-\addcontentsline{toc}{section}{References}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-bajosWhenLockdownPolicies2021}{}}%
-Bajos, Nathalie, Florence Jusot, Ariane Pailhé, Alexis Spire, Claude
-Martin, Laurence Meyer, Nathalie Lydié, et al. 2021. {``When Lockdown
-Policies Amplify Social Inequalities in {COVID-19} Infections: Evidence
-from a Cross-Sectional Population-Based Survey in {France}.''} \emph{BMC
-Public Health} 21 (1): 705.
-\url{https://doi.org/10.1186/s12889-021-10521-5}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-bajosWhenMistrustGovernment2022}{}}%
-Bajos, Nathalie, Alexis Spire, Lena Silberzan, Antoine Sireyjol,
-Florence Jusot, Laurence Meyer, Jeanna-Eve Franck, and Josiane
-Warszawski. 2022. {``When Mistrust in the Government and Scientists
-Reinforce Social Inequalities in Vaccination Against {Covid-19}.''}
-Preprint. {Public and Global Health}.
-\url{https://doi.org/10.1101/2022.02.23.22271397}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-caspiSocioeconomicDisparitiesCOVID192021}{}}%
-Caspi, Gil, Avshalom Dayan, Yael Eshal, Sigal Liverant-Taub, Gilad Twig,
-Uri Shalit, Yair Lewis, Avi Shina, and Oren Caspi. 2021.
-{``Socioeconomic Disparities and {COVID-19} Vaccination Acceptance: A
-Nationwide Ecologic Study.''} \emph{Clinical Microbiology and
-Infection}, June, S1198743X21002779.
-\url{https://doi.org/10.1016/j.cmi.2021.05.030}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Collange2015}{}}%
-Collange, Fanny, Lisa Fressard, Pierre Verger, Fanny Josancy, Rémy
-Sebbah, Arnaud Gautier, Christine Jestin, et al. 2015. {``Vaccinations :
-Attitudes Et Pratiques Des Médecins Généralistes.''} 910. {Direction de
-la recherche, des études, de l'évaluation et des statistiques}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-coulaudCOVID19VaccineIntention2022}{}}%
-Coulaud, Pierre-julien, Aidan Ablona, Naseeb Bolduc, Danya Fast, Karine
-Bertrand, Jeremy K. Ward, Devon Greyson, Marie Jauffret-Roustide, and
-Rod Knight. 2022. {``{COVID-19} Vaccine Intention Among Young Adults:
-{Comparative} Results from a Cross-Sectional Study in {Canada} and
-{France}.''} \emph{Vaccine} 40 (16): 2442--56.
-\url{https://doi.org/10.1016/j.vaccine.2022.02.085}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-europeancommission.directorategeneralforhealthandfoodsafety.StateVaccineConfidence2018}{}}%
-European Commission. Directorate General for Health and Food Safety.
-2018. \emph{State of Vaccine Confidence in the {EU} 2018.} {LU}:
-{Publications Office}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Gautier2013a}{}}%
-Gautier, Arnaud, Christine Jestin, and François Beck. 2013.
-{``Vaccination : Baisse de l'adhésion de La Population Et Rôle Clé Des
-Professionnels de Santé.''} \emph{La Santé En Action} 423 (2013-03):
-50--53.
-
-\leavevmode\vadjust pre{\hypertarget{ref-guimierResistancesFrancaisesAux2021}{}}%
-Guimier, Lucie. 2021. {``Les Résistances Françaises Aux Vaccinations :
-Continuité Et Ruptures à La Lumière de La Pandémie de {Covid-19}:''}
-\emph{Hérodote} N\textdegree{} 183 (4): 227--50.
-\url{https://doi.org/10.3917/her.183.0227}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-jannotLowincomeNeighbourhoodWas2021}{}}%
-Jannot, Anne-Sophie, Hector Countouris, Alexis Van Straaten, Anita
-Burgun, Sandrine Katsahian, and Bastien Rance. 2021. {``Low-Income
-Neighbourhood Was a Key Determinant of Severe {COVID-19} Incidence
-During the First Wave of the Epidemic in {Paris}.''} \emph{Journal of
-Epidemiology and Community Health}, June, jech-2020-216068.
-\url{https://doi.org/10.1136/jech-2020-216068}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lindholtPublicAcceptanceCOVID192021}{}}%
-Lindholt, Marie Fly, Frederik Jørgensen, Alexander Bor, and Michael Bang
-Petersen. 2021. {``Public Acceptance of {COVID-19} Vaccines:
-Cross-National Evidence on Levels and Individual-Level Predictors Using
-Observational Data.''} \emph{BMJ Open} 11 (6): e048172.
-\url{https://doi.org/10.1136/bmjopen-2020-048172}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-murthyDisparitiesCOVID19Vaccination2021}{}}%
-Murthy, Bhavini Patel, Natalie Sterrett, Daniel Weller, Elizabeth Zell,
-Laura Reynolds, Robin L. Toblin, Neil Murthy, et al. 2021.
-{``Disparities in {COVID-19 Vaccination Coverage Between Urban} and
-{Rural Counties} \textemdash{} {United States}, {December} 14,
-2020\textendash{{April}} 10, 2021.''} \emph{MMWR. Morbidity and
-Mortality Weekly Report} 70 (20): 759--64.
-\url{https://doi.org/10.15585/mmwr.mm7020e3}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-oliu-bartonEffectCOVIDCertificates2022}{}}%
-Oliu-Barton, Miquel, Bary SR Pradel, Nicolas Woloszko, Lionel
-Guetta-Jeanrenaud, Philippe Aghion, Patrick Artus, Arnaud Fontanet,
-Philippe Martin, and Guntram B Wolff. 2022. {``The Effect of {COVID}
-Certificates on Vaccine Uptake, Health Outcomes, and the Economy.''}
-Preprint. {In Review}.
-\url{https://doi.org/10.21203/rs.3.rs-1242919/v2}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-santepubliquefranceCoviPrevEnquetePour2021}{}}%
-Santé Publique France. 2021. {``{CoviPrev} : Une Enquête Pour Suivre
-l'évolution Des Comportements Et de La Santé Mentale Pendant l'épidémie
-de {COVID-19}.''}
-
-\leavevmode\vadjust pre{\hypertarget{ref-schultzDoesPublicKnow2022}{}}%
-Schultz, Émilien, Laëtitia Atlani-Duault, Patrick Peretti-Watel, and
-Jeremy K. Ward. 2022. {``Does the Public Know When a Scientific
-Controversy Is over? {Public} Perceptions of Hydroxychloroquine in
-{France} Between {April} 2020 and {June} 2021.''} \emph{Therapies},
-January, S0040595722000105.
-\url{https://doi.org/10.1016/j.therap.2022.01.008}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-schwarzingerCOVID19VaccineHesitancy2021}{}}%
-Schwarzinger, Michaël, Verity Watson, Pierre Arwidson, François Alla,
-and Stéphane Luchini. 2021. {``{COVID-19} Vaccine Hesitancy in a
-Representative Working-Age Population in {France}: A Survey Experiment
-Based on Vaccine Characteristics.''} \emph{The Lancet Public Health} 6
-(4): e210--21. \url{https://doi.org/10.1016/S2468-2667(21)00012-8}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-spireSocialInequalitiesHostility2021}{}}%
-Spire, Alexis, Nathalie Bajos, and Léna Silberzan. 2021. {``Social
-Inequalities in Hostility Toward Vaccination Against {Covid-19}.''}
-Preprint. {Public and Global Health}.
-\url{https://doi.org/10.1101/2021.06.07.21258461}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-usherBeautifulIdeaHow2021}{}}%
-Usher, Ann Danaiya. 2021. {``A Beautiful Idea: How {COVAX} Has Fallen
-Short.''} \emph{The Lancet} 397 (10292): 2322--25.
-\url{https://doi.org/10.1016/S0140-6736(21)01367-2}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-wardPremiersResultatsEnquete2021}{}}%
-Ward, Jeremy. 2021. {``{Premiers résultats de l'enquête SLAVACO Vague 1
-et approfondissement de l'analyse de l'enquête COVIREIVAC - les français
-et la vaccination}.''}
-
-\leavevmode\vadjust pre{\hypertarget{ref-wardFrenchPublicAttitudes2020}{}}%
-Ward, Jeremy K., Caroline Alleaume, Patrick Peretti-Watel, Patrick
-Peretti-Watel, Valérie Seror, Sébastien Cortaredona, Odile Launay, et
-al. 2020. {``The {French} Public's Attitudes to a Future {COVID-19}
-Vaccine: {The} Politicization of a Public Health Issue.''} \emph{Social
-Science \& Medicine} 265 (November): 113414.
-\url{https://doi.org/10.1016/j.socscimed.2020.113414}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-wardFrenchHealthPass2022}{}}%
-Ward, Jeremy K., Fatima Gauna, Amandine Gagneux-Brunon, Elisabeth
-Botelho-Nevers, Jean-Luc Cracowski, Charles Khouri, Odile Launay, Pierre
-Verger, and Patrick Peretti-Watel. 2022. {``The {French} Health Pass
-Holds Lessons for Mandatory {COVID-19} Vaccination.''} \emph{Nature
-Medicine}, January. \url{https://doi.org/10.1038/s41591-021-01661-7}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-wardVaccineHesitancyCoercion2019}{}}%
-Ward, Jeremy K., Patrick Peretti-Watel, Aurélie Bocquier, Valérie Seror,
-and Pierre Verger. 2019. {``Vaccine Hesitancy and Coercion: All Eyes on
-{France}.''} \emph{Nature Immunology} 20 (10): 1257--59.
-\url{https://doi.org/10.1038/s41590-019-0488-9}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-woutersChallengesEnsuringGlobal2021}{}}%
-Wouters, Olivier J, Kenneth C Shadlen, Maximilian Salcher-Konrad, Andrew
-J Pollard, Heidi J Larson, Yot Teerawattananon, and Mark Jit. 2021.
-{``Challenges in Ensuring Global Access to {COVID-19} Vaccines:
-Production, Affordability, Allocation, and Deployment.''} \emph{The
-Lancet} 397 (10278): 1023--34.
-\url{https://doi.org/10.1016/S0140-6736(21)00306-8}.
-
-\end{CSLReferences}
-
-\end{document}

### 2022-04-11 clean/code/0_INSEE_predictors.R

@@ -1,0 +1,310 @@
+#### INITIALIZATIONS ####
+#library("RColorBrewer")
+
+# Project is at the root; change wd to code/ if not already in there
+if(!file.exists("0_INSEE_predictors.R")){
+  setwd("code/")
+}
+
+sortData <- FALSE
+
+## PARAMETERS 
+
+# Threshold for correlation in the variables
+# Variables with absolute correlation above this threshold are removed from the analysis
+thrCor <- 0.9
+
+# Threshold for missing values
+# We will not consider variables with more than this threshold of missing values
+thrMissingVals <- 0.05
+
+## FUNCTIONS
+
+# Function to check correlations
+checkCor <- function(dat){
+  # Compute correlations
+  cor.dat <- cor(dat, use = "pairwise.complete.obs")
+  # Set diagonal to NA (variance)
+  diag(cor.dat) <- NA
+  # Turn into binary depending on position wrt threshold
+  cor.dat2 <- 1*(abs(cor.dat) > thrCor)
+  # Remove diagonal
+  diag(cor.dat2) <- 0
+  print(sum(cor.dat2))
+  
+  # Trim table to only show lines with correlations
+  rs <- rowSums(cor.dat2)
+  keep <- (rs > 0)
+  cor.dat[keep, keep] # Output
+}
+
+#### LOAD INSEE AND GEO DATA ####
+
+# Initialize the dataType vector. It will contain information on the classes
+dataType <- data.frame(predName = c(), predType = c())
+
+# Activity data ---------------------------------------------------------------------------------------
+# Check if there are differences in the two versions of the data file
+system("diff ../data/INSEE_transformed/ACT_brut.csv ../data/ACT_brut.csv")
+# Loaf the data
+dat.ACT <- read.csv("../data/ACT_brut.csv")
+dim(dat.ACT)
+head(dat.ACT)
+# Remove vaccination data
+dat.ACT <- dat.ACT[, -which(is.element(names(dat.ACT), "taux_cumu_1_inj"))]
+# Check duplicates in names
+any(duplicated(names(dat.ACT)))
+# Add information to the dataType vector
+dataType <- rbind(dataType, data.frame(predName = names(dat.ACT)[-1], predType = "ACT"))
+
+
+# Structure is then the same as for ACT, so not commented in detail
+
[…]

### 2022-04-11 clean/code/0_loadAmeliData.R

@@ -1,0 +1,17 @@
+# Update datasets #
+
+
+# Load vaccination data
+
+# Source: https://datavaccin-covid.ameli.fr/explore/?exclude.theme=Datavisualisation&sort=modified
+
+URL.AmeliCom <- "https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-commune/download/?format=csv&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"
+
+system(paste0("wget -O ../data/ameli_vaccination/vaccCom.csv ", URL.AmeliCom))
+
+
+URL.AmeliEPCI <- "https://datavaccin-covid.ameli.fr/explore/dataset/donnees-de-vaccination-par-epci/download/?format=csv&timezone=Europe/Berlin&lang=fr&use_labels_for_header=true&csv_separator=%3B"
+
+system(paste0("wget -O ../data/ameli_vaccination/vaccEPCI.csv ", URL.AmeliEPCI))
+
+

### 2022-04-11 clean/code/1_functions-logisticRegression.R

@@ -1,0 +1,90 @@
+# Function to do a logistic regression on one of the variables
+getLogReg <- function(varVacc = "1_inj", varPred, thedate, predTransform, vaccAge, by.prbs = 0.1, permutation = FALSE, refAge = "40-54"){
+  # 
+  # varVacc  takes values "1_inj" or "termine"
+  # varPred  is the predictor value to be used
+  # thedate  date at which the calculations are done
+  # predTransform: how to deal with the predictor values 
+  #                "standardize_msd", "standardize_max" or "discretize" or "discretize_factor"
+  # vaccAge: "raw_rates" if raw vaccination rates, without taking age into account
+  #          "by_age" if model takes age into account
+  #          "adjusted_rates" if adjusted vaccination rates and model on global rates
+  #          "adults" all ages except 00-19
+  # by.prbs  if "discretize", distance between breaks of the discretization
+  # permutation Whether to permuate the predictors (for null hypothesis)
+  # refAge   if "by_age", which age is taken as reference
+  
+  # Check data entry
+  stopifnot(is.element(predTransform, c("standardize_msd", "standardize_max", "discretize", "discretize_factor")))
+  stopifnot(is.element(varVacc, c("1_inj", "termine")))
+  stopifnot(is.element(vaccAge, c("raw_rates", "by_age", "adjusted_rates", "adults")))
+  
+  stopifnot(is.element(varPred, names(dat.all)))
+  
+  # 1) How we treat the vaccination data
+  if(vaccAge == "raw_rates"){
+    # Subset vaccination data; keep only ALL_AGE
+    r1 <- vacc[vacc$classe_age == "TOUT_AGE" & vacc$date == thedate, ]
+    # Rename columns
+    r1$taux_cumu <- r1[, paste0("taux_cumu_", varVacc)]
+    r1$n_cumu <- r1[, paste0("effectif_cumu_", varVacc)]
+  }
+  if(vaccAge == "by_age"){
+    # Subset vaccination data; keep all age classes except ALL_AGE
+    r1 <- vacc[vacc$classe_age != "TOUT_AGE" & vacc$date == thedate, ]
+    # Rename columns
+    r1$taux_cumu <- r1[, paste0("taux_cumu_", varVacc)]
[…]

### 2022-04-11 clean/code/1_functions-oddsRatios.R

@@ -1,0 +1,83 @@
+# Extract OR from logistic model where the predictor is a factor
+extractOR <- function(mdl, nstd = NA){
+
+  # If not `nstd` is specified, take the last one
+  if(is.na(nstd)){
+    nstd <- length(mdl$coefficients)
+  }
+  
+  pred <- paste0("pred.std", nstd)
+  # mdl is the mdl obtained with a logistic regression, with a discretized and factorized predictor
+  # pred is the predictor value on which ORs are computed
+  
+  OR <- exp(summary(mdl)$coefficients[pred, "Estimate"])
+  OR.CI.min <- exp(summary(mdl)$coefficients[pred, 1] + 1.96 * summary(mdl)$coefficients[pred, 2])
+  OR.CI.max <- exp(summary(mdl)$coefficients[pred, 1] - 1.96 * summary(mdl)$coefficients[pred, 2])
+  
+  # Compute max(OR, 1/OR)
+  # (not taking it directly because CI may straddle the value 1)
+  inv <- (OR < 1)
+  if(inv){
+    OR.abs <- 1/OR
+    OR.abs.CI.min <- 1/OR.CI.min
+    OR.abs.CI.max <- 1/OR.CI.max
+  }else{
+    OR.abs <- OR
+    OR.abs.CI.min <- OR.CI.min
+    OR.abs.CI.max <- OR.CI.max
+  }
+  
+  # Predicted values of the extreme categories
+  predMin <- invlogit(summary(mdl)$coefficients["(Intercept)", "Estimate"])
+  predMax <- invlogit(summary(mdl)$coefficients["(Intercept)", "Estimate"] + summary(mdl)$coefficients[pred, "Estimate"])
+  
+  # Return output
+  c(OR = OR, 
+    OR.CI.min = OR.CI.min, 
+    OR.CI.max = OR.CI.max, 
+    OR.abs = OR.abs, 
+    OR.abs.CI.min = OR.abs.CI.min,
+    OR.abs.CI.max = OR.abs.CI.max, 
+    predMin = predMin, 
+    predMax = predMax)
+}
+
+#....................................................................................
+
+# Compute adjusted predicted values
+adjustedPredict <- function(mdl, newd, includeChildren = TRUE, distributionAges = distAge){
+  # mdl is model by age
+  # newd is new data for the predicted values
+  # includeChildren is a boolean indicating whether the 00-19 age class should be included in the adjusted rate
+  # distAge is the age distribution in France
+  
+  # Compute predicted values
[…]

### 2022-04-11 clean/code/1_functions-quantiles.R

@@ -1,0 +1,58 @@
+# Convert to binary values depending on a chosen threshold
+quantileConvert <- function(v, q){
+  # v vector to be converted
+  # q chosen quantile (between 0 and 1)
+  
+  # Compute the threshold value
+  # Rem: need to remove NAs
+  qval <- quantile(x = v, probs = q, na.rm = TRUE)
+  
+  # Return TRUE/FALSE depending on the position wrt the value, and change into 1/0
+  out <- ifelse(v < qval, 0, 1)
+  out
+}
+
+#.......................................................................
+
+# Convert to binary values, with respect to 2 threshold values
+quantilesConvert <- function(v, qmin = 0.1, qmax = 0.9){
+  # v vector to be converted
+  # qmin lower threshold value, data below it are coded 0
+  # qmax higher threshold value, data above it are coded 1
+  # and data between qmin and qmax are coded NA
+  
+  # Compute the threshold value
+  # Rem: need to remove NAs
+  qval <- quantile(x = v, probs = c(qmin, qmax), na.rm = TRUE)
+  
+  out <- rep(NA, length(v)) # Initialize output vector
+  out[v < qval[1]] <- 0 
+  out[v > qval[2]] <- 1
+  
+  out
+}
+
+#.......................................................................
+
+# Discretize wrt to quantiles 
+discretizeQ <- function(v, prbs = seq(0, 1, by = 0.05)){
+  # v     vector to discretize
+  # prbs  positions of the boundaries
+  
+  # Define quantiles
+  qq <- c(quantile(v, probs = prbs, na.rm = TRUE))
+  
+  # Extend the extreme values to make sure that they are included later
+  qq[1] <- qq[1] - abs(0.5 * qq[1]) # 0%
+  qq[length(qq)] <- qq[length(qq)] + abs(0.5 * qq[length(qq)]) # 100%
+  
+  # Add noise to avoid issues with the `cut` function when data are too close
+  noise <- c(0, runif(length(prbs)-2, max = 10^(-6)), 0)
+  qq <- sort(qq + noise)
+  
+  # Put the values of v in the different classes
+  out <- cut(v, breaks = qq, right = FALSE, labels = FALSE)
+  # table(out, useNA = "ifany")
+  out
+}
+

### 2022-04-11 clean/code/2_plot-manhattan.R

@@ -1,0 +1,84 @@
+# Define palette
+library("MetBrewer")
+
+pal <- met.brewer("Signac", 10, type= "discrete")
+# Reorder for better contrast
+pal <- pal[c(1, 6, 2, 7, 3, 8, 4, 9, 5, 10)]
+
+pal <- c("#a6cee3", "#e31a1c", "#1f78b4", "#fdbf6f", "#b2df8a", "#ff7f00", "#33a02c", "#cab2d6", "#fb9a99", "#6a3d9a")
+names(pal) <- unique(dicPred[names(dat.nocorr[-1])])
+# plot(1:10, col = pal, cex = 2, pch = 15)
+
+colPerm <- gray(0, 0.4)
+
+
+#...............................................................................
+# Manhattan plot
+plotManhattan <- function(out, qq = 0.99, ntop = 3){
+  # out is the output table, containing ORs and the parameters
+  # qq quantile for the permuted values
+  # ntop is number of labels to plot
+  
+  # Extract date values
+  thedates <- sort(unique(out$thedate))
+  
+  # xMax value
+  xMax <- 1.05 * max(out$OR.abs.CI.max)
+  
+  for(thedate in thedates){
+    # Subsets of the data at this date
+    subF <- out[out$thedate == thedate & out$permutation == FALSE, ]
+    subT <- out[out$thedate == thedate & out$permutation == TRUE, ]
+    
+    subF$i <- seq_len(nrow(subF)) # Add index
+    
+    # Initialize plot
+    par(mar = c(3, 5, 2, 2.3), mgp = c(1.25, 0.5, 0))
+    plot(0, xlim = c(1, xMax), ylim = c(1, nrow(subF)), type = "n", 
+         axes = FALSE, xlab = "max(OR, 1/OR)", ylab = "")
+    axis(1, pos = 1, lwd = 0, lwd.ticks = 1, tck = -0.01)
+    
+    types <- unique(out$typePred)
+    for(tp in types){
+      # Subset of the data for this type
+      subb <- subF[subF$typePred == tp, ]
+      rg <- range(subb$i)
+      op <- 0.2
+      dx <- 0.5 # 0.5 for no space
+      rect(xleft = 1, xright = xMax, 
+           ybottom = rg[1] - dx, ytop = rg[2] + dx, 
+           border = gray(0, 0), col = adjustcolor(pal[tp], op))
+      par(xpd = TRUE)
[…]

### 2022-04-11 clean/code/2_plot-map.R

@@ -1,0 +1,227 @@
+#### PLOT MAP PREDICTOR ####
+plotMapVar <- function(varPred, byp = 0.1){
+  # varPred: name of the predictor
+  # byp: interval for discretization
+  # Global variables: datasets, map shapes
+  
+  # Build minimum dataframe with information on the variable
+  tmp <- data.frame(codgeo = dat.all$codgeo, pred = dat.all[, varPred])
+  # Discretize the predictor
+  tmp$pred.std <- discretizeQ(tmp$pred, prbs = seq(0, 1, by = byp))
+  # Add to geographic data
+  mergedFrance <- merge(france, tmp, by.x = "SIREN", by.y = "codgeo", all.x = TRUE)
+  
+  # Main map
+  mf_theme("default", mar = c(0, 0, 0, 0), bg = NA)
+  
+  # Map Parameters
+  eBB <- c(.5, .2, 0, 0)
+  h2 <- c(0.01, 0.275) # (ymin, ymax) of the metropoles
+  
+  # Color palette
+  nn <- 1/byp # number of types
+  palCat <- rev(met.brewer("Hiroshige", nn, type = "continuous"))
+  names(palCat) <- 1:nn
+  
+  brks <- quantile(tmp$pred, probs = seq(0, 1, by = byp), na.rm = TRUE)
+  
+  # Initialize map
+  mf_init(france, expandBB = eBB)
+  
+  # Rename variable
+  tit <- varPred
+  if(substr(tit, 1, 1) == "X") tit <- substr(tit, 2, nchar(tit))
+  
+  # Plot map
+  mf_map(mergedFrance, type = "choro", var = "pred", 
+         pal = palCat, breaks = brks,
+         border = gray(0, 0), add = TRUE, 
+         leg_pos = "topleft", leg_title = paste0(tit, ", discretized"), leg_no_data = "no data", leg_val_cex = 0.5, leg_val_rnd = 3)
+  
+  # Fill in PLM
+  plm <- france[is.element(france$SIREN, epci.PLM), ]
+  mf_map(plm, add = TRUE, border = gray(0, 0), col = gray(0.7))
+  
+  
+  # Add departements
+  mf_map(mdeps, type = "base", add = TRUE, col = gray(0, 0), lwd = 0.5, border = "black")
+  # Add regions
[…]

### 2022-04-11 clean/code/2_plot-overTime.R

@@ -1,0 +1,80 @@
+
+
+plotPropTime <- function(out, plotDates = FALSE, plotGraduations = FALSE){
+  # out table of results, with parameter values
+  
+  # Define color palette
+  nn <- 1/unique(out$by.prbs) # Number of categories to plot
+  palCat <- rev(met.brewer("Hiroshige", nn, type = "continuous"))
+  names(palCat) <- 1:nn
+
+  mnths <- seq(as.Date(min(out$thedate)), as.Date(max(out$thedate)), by = "month")
+  
+  # For each variable
+  for(varPred in unique(out$varPred)){
+    # Initialize plot
+    par(mar = c(3, 4, 2, 2), mgp = c(1.75, 0.25, 0), las = 1, tck = - 0.01)
+    plot(0, xlim = range(as.Date(dates)), ylim = c(0, 1), axes = FALSE, 
+         xlab = "date", ylab = "Adjusted vaccination rate", yaxs = "i", xaxs = "i", 
+         main = varPred)
+    axis(1, at = mnths, labels = format(mnths, "%b"))
+    axis(2, lwd = 0, lwd.ticks = 1)
+    axis(4, lwd = 0, lwd.ticks = 1)
+    
+    if(plotGraduations){
+      for(i in seq(0, 1, by = 0.1)){
+        par(xpd = FALSE)
+        abline(h = i, col = gray(0.8))
+      }
+    }
+    
+    # Subset of the data for this predictor
+    sub <- out[out$varPred == varPred, ]
+    
+    # Plot the predicted values
+    for(i in 1:nn){
+      lines(as.Date(sub$thedate), sub[, paste0("V", i)], col = palCat[i], lwd = 2)
+    }
+    
+    # Show dates
+    if(plotDates){
+      par(xpd = FALSE)
+      colLineDate <- gray(0.5)
+      abline(v = as.Date(date.SP.announcement), lty = 2, col = colLineDate)
+      abline(v = as.Date(date.SP.implementation), col = colLineDate)
+      
+      abline(v = as.Date(date.VP.announcement), lty = 2, col = colLineDate)
+      abline(v = as.Date(date.VP.implementation), col = colLineDate)
+      
+      par(xpd = TRUE)
+      yt <- 0.015
+      cext <- 0.5
+      dtt <- 2
[…]
